### 2021-05-18 latex/ms.tex
add text

\documentclass[AMA,STIX1COL]{WileyNJD-v2}
\usepackage{moreverb}
\usepackage{lineno}
\linenumbers

\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsmath}

\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\articletype{Manuscript intended for \emph{Evolutionary Applications}, \today}%

\received{<day> <Month>, <year>}
\revised{<day> <Month>, <year>}
\accepted{<day> <Month>, <year>}

%\raggedbottom

\begin{document}

\title{Estimating the number of migrants using between-population sibling pairs}%\protect\thanks{This is an example for title footnote.}}

\author[1]{Tetsuya Akita*}

\authormark{Akita}

\address[1]{\orgdiv{Fisheries Data Sciences Division}, \orgname{Fisheries Resources Institute}, \orgaddress{\state{Kanagawa}, \country{Japan}}}

\corres{*Tetsuya Akita, Fisheries Data Sciences Division, Fisheries Resources Institute, FRA, 236-8648 Kanagawa, Japan. \email{akitatetsuya1981@affrc.go.jp}}

%\presentaddress{Present address}

\abstract[Abstract]{本ノートでは，多回繁殖(iteroparity)する種を対象として，半兄弟ペア数から親魚による２つのサブ集団間の移動率を推定する理論($\hat{M}=N_1N_2H_{\rm obs}/(4n_1n_2)$)を紹介する。この推定式は、親をサンプルする通常の標識放流と同じである。もし、繁殖ポテンシャルの分布が集団間で異なっていても上記の式で問題ないことを示した。一方，サンプル数としては$\sqrt {N}$以上のオーダーが求められる。}

\keywords{Close-kin mark recapture; Half-sibling; Population structure}

\maketitle

%\footnotetext{\textbf{Abbreviations:} ANA, anti-nuclear antibodies; APC, antigen-presenting cells; IRF, interferon regulatory factor}

\section{Introduction}\label{sec1}

Estimating the number of migrants among the populations is essential for understanding population structure and dynamics, which is a fundamental process for implementing conservation and wildlife management. Especially in fisheries management, migration rate is a critical component for delineating a synchrony among the population, providing appropriate management units. There are essentially two approaches for estimating the migrant number. The first is to use the mark-recapture method estimate it directly from the population dynamics modeling with survey data. The second is to ...

移動率の推定は，対象生物の理解に重要なだけでなく，外来種管理・希少種保全・資源の持続的利用にとっても重要である。　特に、水産資源管理にとっては、管理単位を決めるための指標として、移動率はクリティカルな指標の一つである。既存の方法論としては，大きく２種類に大別される。１つ目は標識再捕法であり，２つ目は集団遺伝学的な方法である。前者については，サンプル対象を再捕獲が見込める親個体に限定せざるを得ない，非侵襲的な方法でのラベリングが困難であること，推定精度に見合うサンプルサイズが現実的でないこと，報告率が大きくばらつく等が問題となっている。後者については，近年(すなわち$N_{\rm e}$よりも短い世代数)の集団構造については解像度がないこと，移動個体数が大きいと遺伝的には同一の集団とみなされること等が問題となっている。

本ノートでは，近親標識法(Close-kin mark-recapture, CKMR)という近年発達した方法論を用いて，移動率の推定を試みる。CKMRとは，親集団が小さいほど近親ペアが見つかりやすいことに着目した方法である。今回は，多回繁殖する生物を対象として，２つのサブ集団間で見つかる０歳の半兄弟(Half-sibling, HS)ペアを用いて，そのペアの親候補となる個体の数（もしくは移動率）を推定する。ただし，移動前の集団および移動後の集団における親魚尾数が，移動個体数の推定には必要となる。

応用例として，３年間にわたって２つのサブ集団からサンプルされた当歳魚から見出される半兄弟ペアをもとに，個体数・移動率・生存率を推定する枠組みを提示する。そこでは，同じサブ集団から年を跨いで見つかる半兄弟ペアに基づく関係式と，今回新たに開発した関係式を組み合わせて用いる。

\section{Theory}\label{sec2}

この章では，全てに共通するモデリングの仮定を述べた後，シンプルなモデルから徐々に複雑なモデルへと移行する。具体的には，最初にシンプルなモデルについて記述して，
\begin{itemize}
  \item 移動が双方向
  \item 性比1:1およびランダム交配を仮定して両性を考慮
  \item 繁殖ポテンシャルが一定でない
  \item 移動しやすさが繁殖ポテンシャルに依存
\end{itemize}
といった要素を追加していく。また，どのモデルでも共通して仮定しているのは以下の５点である。
\begin{enumerate}
  \item 年をまたぐ多回繁殖
  \item 親魚によるサブ集団間の移動は，繁殖シーズンの間に起きる
  \item サンプルされる当歳魚（０歳）は，必ずサンプルされたサブ集団で産まれる
  \item 当歳魚かどうかの判断は１００％可能
  \item サンプル間の近親判別では，１００％の成功率で半兄弟ペアか否かがなされる
\end{enumerate}
また，性成熟した個体を親と呼ぶことにする。

\subsection{Basic model}

まず最初に，最もシンプルなモデルを考える。$t$年にサブ集団１にいる$N_{1,t}$個体の母親を考えよう。$t$年に子供を産んだ後，$N_{1,t}$個体のうち$M_{1\to2}$個体がサブ集団２に移動し，$t+1$年にサブ集団２にいる母個体$N_{2,t+1}$の一部として子供を産むとする。この時，サブ集団１から$t$年に産まれた子供とサブ集団２から$t+1$年に産まれた子供が，母を共有する兄弟(Maternal half Sibling, MHS)である確率$\pi_{\rm b,1\to2}$を考える。どの母親も同じような繁殖ポテンシャルを持つと仮定すると，移動する母親の子供をサブ集団１でサンプルする確率は$M_{1\to2}/N_{1,t}$となる。同様に，移動する母親の子供をサブ集団２においてサンプルする確率は$M_{1\to2}/N_{2,t+1}$である。それぞれでサンプルした子供の母親が同一である確率は$1/M_{1\to2}$であることより，サンプルした２個体がMHSペアとなる確率が以下のように得られる。
\begin{align}
\pi_{\rm b,1\to2} &= \frac{M_{1\to2}}{N_{1,t}} \frac{M_{1\to2}}{N_{2,t+1}} \frac{1}{M_{1\to2}} \nonumber\\
&= \frac{M_{1\to2}}{N_{1,t}N_{2,t+1}}
\label{1-1}
\end{align}
サブ集団１からサブ集団２に移動する割合$m_{1\to2}$を導入することで，上式は
\begin{align}
\pi_{\rm b,1\to2} &= \frac{m_{1\to2}}{N_{2,t+1}}
\label{1-2}
\end{align}
と書ける。$M_{1\to2} = m_{1\to2}N_{1,t}$とした。$m_{1\to2}$には移動だけでなく$t+1$年の産卵までの生存確率が含まれている点に注意。

MHSペアとなる確率が得られれば，サンプル数に応じて見つかるMHSペア$H_{1\to2}$の期待値が得られる。
\begin{align}
\mathbb{E}[H_{1\to2}] &= \pi_{\rm b,1\to2} n_{1,t} n_{2,t+1} \nonumber\\
&= \frac{m_{1\to2}n_{1,t} n_{2,t+1}} {N_{2,t+1}}
\label{1-3}
\end{align}
$n_{1,t}, n_{2,t+1}$は，それぞれサブ集団１（$t$年）でのサンプル数，サブ集団２（$t+1$年）でのサンプル数である。この結果から，平均的にみて少なくとも１ペア以上を見出すには，(親魚尾数)の平方根のオーダー以上のサンプル数が要求されることがわかる。以上より，見出されたMHSペア数から母親の移動率に関する線形推定量が得られる。
\begin{align}
\widehat{m_{1\to2}} &= \frac{N_{2,t+1} H_{1\to2,{\rm obs}} } {n_{1,t}n_{2,t+1}}
\label{1-4}
\end{align}
ハットは推定量を表し，obsの添字は観測値であることを表す。

\subsection{Two-way movement}

次に，反対方向の移動について考える。すなわち，$t$年にサブ集団２にいる$N_{2,t}$個体の母親から，$M_{1\to2}$個体が$t+1$年にサブ集団１へ移動すること考えよう。これまで同様に考えて，MHSペアとなる確率は，
\begin{align}
\pi_{\rm b,2\to1} &= \frac{m_{2\to1}}{N_{1,t+1}}
\label{2-1}
\end{align}
のようになり，移動率に関する推定量
\begin{align}
\widehat{m_{2\to1}} &= \frac{N_{1,t+1} H_{2\to1,{\rm obs}} } {n_{2,t}n_{1,t+1}}
\label{2-2}
\end{align}
が得られる。すなわち，移動が一方向であろうが双方向であろうが，各方向の移動率に関する推定量は式\ref{1-4}と式\ref{2-2}から独立に得られる。したがって，以降の導出ではサブ集団１からサブ集団２に移動する個体についてだけ考え，添字を省略する。例えば，$N_1$という記載は，$t$年に親魚として存在した個体数を表す。

\subsection{Two-sex}

ここまでは、母親を介した兄弟ペアと、母親の個体数およびその移動について考えてきた。しかしながら、母親を介した兄弟か父親を介した兄弟かを見分けるには、ミトコンドリアの情報を用いた類推が必須である点、当歳魚のサンプル数が同程度でも区別しない半兄弟ペアの半数程度しか発見されない点などから、実際の応用では区別しない半兄弟ペアを用いるほうが望ましい。そこで、まずは性比=1:1（すなわち，$N_{\rm male}=N_{\rm female}=N_1/2$かつ$M_{\rm male}=M_{\rm female}=M/2$）でランダム交配を仮定した集団を考えよう。この時、サブ集団１でサンプルした当歳魚の親が移動する親個体である確率は$M_{\rm male}/N_{\rm male} + M_{\rm female}/N_{\rm female}=2M/N_1$となる。同様に，移動した親の子供をサブ集団２においてサンプルする確率は$2M/N_2$であることから，
\begin{align}
\pi &= \frac{2M}{N_{1}} \frac{2M}{N_{2}} \frac{1}{M} \nonumber\\
&= \frac{4M}{N_{1}N_{2}}
\label{3-1}
\end{align}
が得られる。その結果，移動率の推定値は新たに係数4が分母に加わって
\begin{align}
\widehat{m} &= \frac{N_{2} H_{\rm obs} } {4n_{1}n_{2}}
\end{align}
となる。

\subsection{Reproductive variation}

これまでは，母親による産卵数の偏りや，父親による放精成功の偏りは考慮していなかった。しかしながら，多回繁殖する魚類の場合，体サイズによって繁殖成功度は大きく変化すること，および体サイズの分布には偏りが存在することから，上記のシステマチックな偏りを考慮する必要があるだろう。例えば，集団に１個体の巨大魚（メス）がいて，その産卵数が他の個体よりも圧倒的に大きい場合，サンプルされる子供の母親はかなりの確率でその巨大魚になるだろう。

サブ集団１（２）にいる親$i(j)$が残す子供の数を$k_{1,i}(k_{2,j})$としよう。$k_{1,i}(k_{2,j})$は期待値$\lambda_{1,i}(\lambda_{2,j})$の分布（例えば負の二項分布など）に従うとしよう。体サイズによる重み付けを考慮したランダム交配を仮定すれば，ペアがMHSである確率は
\begin{align}
\pi | _{\boldsymbol{k_1, k_2}} &= \frac{ 2\sum_{i=1}^M k_{1,i} } { \sum_{i=1}^{N_1} k_{1,i} } \frac{ 2\sum_{j=1}^M k_{2,j} } { \sum_{j=1}^{N_2} k_{2,j} } \frac{1}{M} 
\end{align}
と書くことができる。簡単のため，$\boldsymbol{k_1}=(k_{1,1}, \ldots, k_{1,M}, \ldots, k_{1,N_1})$および$\boldsymbol{k_2}=(k_{1,2}, \ldots, k_{1,M}, \ldots, k_{1,N_2})$と記載し，また親のidが$1$から$M$の個体が移動するとして，idを配置した。$k_{1,i}$は期待値$\lambda_{1,i}$に従う確率変数であることから，このMHSペア確率の平均をとると
\begin{align}
\pi | _{\boldsymbol{\lambda_1, \lambda_2}} &= \mathbb{E}[\pi | _{\boldsymbol{k_1, k_2}}] \nonumber\\
&= \frac{4}{M} \mathbb{E}\left[\frac{ \sum_{i=1}^M k_{1,i} } { \sum_{i=1}^{N_1} k_{1,i} } \frac{ \sum_{j=1}^M k_{2,j} } { \sum_{j=1}^{N_2} k_{2,j} } \right]   \nonumber\\
&\approx \frac{4}{M} \frac{ \mathbb{E}\left[ \sum_{i=1}^M k_{1,i} \sum_{j=1}^M k_{2,j} \right] } {\mathbb{E}\left[ \sum_{i=1}^{N_1} k_{1,i} \sum_{j=1}^{N_2} k_{2,j}\right]} \nonumber\\
&= \frac{4}{M} \frac{ \sum_{i=1}^M \lambda_{1,i} \sum_{j=1}^M \lambda_{2,j} } {\sum_{i=1}^{N_1} \lambda_{1,i} \sum_{j=1}^{N_2} \lambda_{2,j}} 
\end{align}
と近似することができる。留意すべき点として，移動前の産卵数と移動後の産卵数は独立と仮定しているため，式中に$k_i^2$の項が出現せず，結果は期待値$\lambda_i$(産卵ポテンシャルと呼ぶことにしよう)だけに依存する。最初に述べたように，この個体ごとの産卵ポテンシャルはある分布に従うとしよう。例えば，高齢個体ほど体サイズが大きい場合などが想定される。また，この分布はサブ集団１とサブ集団２で異なっていて良い。すなわち，$\lambda_{1,i}$および$\lambda_{2,j}$がそれぞれ独立な確率変数であると考えて，MHSペア確率についてさらに平均をとると
\begin{align}
\pi &= \mathbb{E}[\pi | _{\boldsymbol{\lambda_1, \lambda_2}}] \nonumber\\ 
&\approx \frac{4}{M} \frac{M^2 \mathbb{E}[\lambda_1 \lambda_2]}{N_1 N_2 \mathbb{E}[\lambda_1 \lambda_2]}\nonumber\\
&= \frac{4M}{N_{1}N_{2}}
\label{4-1}
\end{align}
と近似される。結局，繁殖ポテンシャルの不均一性を考慮しない結果（式\ref{3-1}）と同様になる。なお，$\boldsymbol{\lambda_1}=(\lambda_{1,1}, \ldots, \lambda_{1,N_1})$および$\boldsymbol{\lambda_2}=(\lambda_{1,2}, \ldots, \lambda_{1,N_2})$。この近似は、独立に決まる確率変数$\lambda_1$と$\lambda_2$について、$\mathbb{E}[\lambda_1/\lambda_2]=\mathbb{E}[\lambda_1] \times \mathbb{E}[1/\lambda_2] \approx 1$となる場合に成立するので、集団中に$\lambda$が極端に低い個体が存在する場合は成立しない（サブ集団１とサブ集団２でセットにして相対的な繁殖ポテンシャルを考えれば良いので、問題ないだろう）。

\subsection{Covariation between migration and reproductive potential}

上のモデルでは，サブ集団１とサブ集団２を構成する親魚の繁殖ポテンシャルの分布をそれぞれ考慮していたが，移動個体の繁殖ポテンシャルの不均一性については考慮していなかった。最後に，移動した親魚の繁殖ポテンシャルについてもある分布に従うと仮定しよう。すなわち，$\lambda_{1,i}, \lambda_{2,j}, \lambda_{M,l}$をそれぞれ独立な確率変数とみなして，MHSペア確率を計算すると，
\begin{align}
\pi | _{\boldsymbol{\lambda_1, \lambda_2, \lambda_M}} &\approx \frac{4}{M} \frac{ \sum_{i=1}^M \lambda_{M,i} \sum_{j=1}^M \lambda_{M,j} } {\left(\sum_{i=1}^{M} \lambda_{M,i} + \sum_{i=M+1}^{N_1} \lambda_{1,i}\right) \left(\sum_{j=1}^{M} \lambda_{M,j} + \sum_{j=M+1}^{N_2} \lambda_{2,j}\right) } 
\end{align}
のようになり，$N_1$, $N_2$が$M$より十分に大きいと仮定すると、この期待値は以下のようになる，
\begin{align}
\pi &\approx \frac{4M}{N_{1}N_{2}} \mathbb{E}\left[ \frac{ \lambda_M^2 }{\lambda_1\lambda_2} \right]
\label{5-1}
\end{align}
すなわち，繁殖ポテンシャルの効果がMHSペア確率に影響するようになる。

\section{Application}\label{sec3}

ここでは応用例として，３年間にわたって２つのサブ集団からサンプルされた当歳魚から見出される半兄弟ペアをもとに，個体数($N$)・移動率($m$)・生存率($s$)を推定する理論的な枠組みを提示する。サブ集団１に生息する親魚数を、$N_1(t), N_1(t+1), N_1(t+2)$のように表記し、他のパラメータについても同様とする。個体数については６つのパラメータ、移動率および生存率は４つのパラメータとなり、合計１４のパラメータが考えられる（$t+2$年の移動率および生存率は含まれない点に注意）。まずは、これら１４個のパラメータは独立に決まるとしよう（すなわち、$N_1(t)$と$N_1(t+1)$は無関係で、$s_1(t)$と$s_1(t+1)$は独立に決める、など）。なお、この応用例では、移動する親魚は繁殖ポテンシャルによらずに決まると仮定して、式\ref{4-1}を用いることにしよう。また、全ての親魚は、年をまたぐごとに、1)サブ集団を移動して産卵するか（確率：$m$）、2)同じサブ集団に留まって産卵するか（確率：$s$）、3)死亡するか（確率：$1-m-s$）、のいずれかのイベントを経験するとする。

今回新たに開発した移動に関する関係式について、以下の６種類の親魚に関するその子供（当歳魚）ペアがありえる：
\begin{enumerate}
  \item $N_1(t)\to N_2(t+1)$
  \item $N_1(t)\to N_2(t+2)$
  \item $N_1(t+1)\to N_2(t+2)$
  \item $N_2(t)\to N_1(t+1)$
  \item $N_2(t)\to N_1(t+2)$
  \item $N_2(t+1)\to N_1(t+2)$
\end{enumerate}
右向きの矢印$\to$は、興味ある親魚が年を跨いだ後どのサブ集団に属しているかを表している。１番目を例にとると、$t$年にサブ集団１から、$t+1$年にサブ集団２からそれぞれ当歳魚をサンプルすることを意味する。加えて、同じサブ集団から年を跨いで見つかる半兄弟ペアに基づく関係式についても、以下の６種類が考えられる：
\begin{enumerate}
\setcounter{enumi}{6}
  \item $N_1(t)\to N_1(t+1)$
  \item $N_1(t)\to N_1(t+2)$
  \item $N_1(t+1)\to N_1(t+2)$
  \item $N_2(t)\to N_2(t+1)$
  \item $N_2(t)\to N_2(t+2)$
  \item $N_2(t+1)\to N_2(t+2)$
\end{enumerate}
以上の、合計１２種類の式を連立できることを示した。最大１４個のパラメータが必要となるのであったが、パラメータ数を応用先に応じて適宜減少させることができる場合、興味あるパラメータを推定することができる。

ちなみに、同一年内に同じサブ集団内で見つかるMHSペアについては、有効集団サイズの情報（正確には有効繁殖サイズ、Effective breeding size）は持っているが、センサスサイズに関するダイレクトな情報は持っていない点に注意。

\section{Discussion}\label{sec4}

\section{ACKNOWLEDGEMENTS}

The author thanks MV Bravington for motivating me to pursue this research topic. This work was supported by JSPS KAKENHI Grant Number 19K06862 and 20H03012.

\begin{comment}
Many authors submitting \( \sin \cos \tan \inf_{x} \) to NJD journals use \LaTeXe\ to
prepare their papers. This paper describes the
\textsf{WileyNJD-v2.cls} class file which can be used to convert
articles produced with other \LaTeXe\ class files into the correct
form for publication in \emph{Wiley NJD Journals}.

The \textsf{WileyNJD-v2.cls} class file preserves much of the standard
\LaTeXe\ interface so that any document which was produced using
the standard \LaTeXe\ \textsf{article} style can easily be
converted to work with the \textsf{WileyNJD-v2} style. However, the
width of text and typesize will vary from that of
\textsf{article.cls}; therefore, \emph{line breaks will change}
and it is likely that displayed mathematics and tabular material
will need re-setting.

In the following sections we describe how to lay out your code to
use \textsf{WileyNJD-v2.cls} to reproduce the typographical look of
\emph{Wiley NJD Journals}.

\subsection{Procedure to install fonts}

\begin{enumerate}
\item All font files are available under the Stix-fonts folder 
\item Font installer is available under the same folder Windows-Stix-fontinstaller.exe
\item Execute (double click the EXE file) the EXE file that will install all fonts/map files to your local drive.
\end{enumerate}

\subsection{The Three Golden Rules}

Before we proceed, we would like to
stress \emph{three golden rules} that need to be followed to
enable the most efficient use of your code at the typesetting
stage:
\begin{enumerate}
\item[(i)] keep your own macros to an absolute minimum;

\item[(ii)] as \TeX\ is designed to make sensible spacing
decisions by itself, do \emph{not} use explicit horizontal or
vertical spacing commands, except in a few accepted (mostly
mathematical) situations, such as \verb"\," before a
differential~d, or \verb"\quad" to separate an equation from its
qualifier;

\item[(iii)] follow the \emph{NJD} reference style.
\begin{enumerate}[a.]
\item Chemistry --- Use the ``AMA'' option as \verb"\documentclass[AMA]{WileyNJD-v2.cls}"

\end{enumerate}
\end{enumerate}

\section{Getting Started} The \textsf{WileyNJD-v2.cls} class file should run
on any standard \LaTeXe\ installation. If any of the fonts, class
files or packages it requires are missing from your installation,
they can be found on the \emph{\TeX\ Live} CD-ROMs or from CTAN.

LaTeX document class options

\begin{flushleft}
\begin{enumerate}[a.]
\item STIX1COL--- For STIX font large one column layout use the ``STIX1COL'' option as \verb"\documentclass[AMA,STIX1COL]{WileyNJD-v2}"
\item STIX2COL--- For STIX font large two column layout use the ``STIX2COL'' option as \verb"\documentclass[AMA,STIX2COL]{WileyNJD-v2}"
\item STIXSMALL--- For STIX font small layout use the ``STIXSMALL'' option as \verb"\documentclass[AMA,STIXSMALL]{WileyNJD-v2}"
\end{enumerate}
\end{flushleft}

\section{The Article Header Information}
The heading for any file using \textsf{WileyNJD-v2.cls} is shown in
Figure~\ref{F1}.

\subsection{Remarks}

\begin{enumerate}[(I).]

\item Use \verb"\title{<title> \protect\thanks{<title footnotes}}" for article title and title footnote.
\item Use \verb"\authormark{}" for running heads.

\item Note the use of \verb"\author[<link>]{<name>}" and \verb"\address[<link>]{<name>}" to
link names and addresses. The author for correspondence is marked
by ``*'' and \verb"\corres{}" is used to give that
author's address, which will be printed besides abstract, prefaced by
`Correspondence to:'.

\item For submitting a double-spaced manuscript, add
\verb"doublespace" as an option to the documentclass line. \verb"\documentclass[doublespace]{WileyNJD-v2}"

\item Use \verb"\presentaddress{}" for present address.

\item In abstract \verb"\abstract[<title>]{abstract paragraph}" use optional parameter for title followed by abstract paragraph.

\item For Key words use \verb"\keywords{}".

\item For how to site use \verb"\jnlcitation{\cname{\author{<author name>},"

\verb"\ctitle{<title>}, \cjournal{<Journal name>}, \cvol{<vol>}.}}".

\item For title page abbreviations use \verb"\footnotetext{<\textbf{Abbreviation title:} Abreviations>}"

\item Use \verb"\articletype{<article category}" for article header information

\item Use \verb"\received{<received date>} \revised{<revised date>} \accepted{<accepted date>}" for history dates.

\end{enumerate}

\begin{figure}[p]
\setlength{\fboxsep}{0pt}%
\setlength{\fboxrule}{0pt}%
\begin{center}
\begin{boxedverbatim}

\documentclass[AMA,STIX1COL]{WileyNJD-v2}

\articletype{Article Type}%

\received{26 April 2016}
\revised{6 June 2016}
\accepted{6 June 2016}

\begin{document}

\title{<Initial cap, lower case>\protect\thanks{<title footnote.>}}

\author[<address link>]{<Author name><corresponding author*>}

\author[<address link>,<address link>]{Author Name}

\authormark{AUTHOR ONE \textsc{et al}}

\address[<address link>]{\orgdiv{<Org Division>}, \orgname{<Org name>}, 
\orgaddress{\state{<State name>}, \country{<Country name>}}}
\address[<address link>]{\orgdiv{<Org Division>}, \orgname{<Org name>},
 \orgaddress{\state{<State name>}, \country{<Country name>}}}

\corres{<corresponding author link*> <author name, address.
 \email{<authorone@email.com>}}

\presentaddress{<Present address>}

\abstract[<Abstract heading>]{<Abstract paragraph>}

\keywords{<keyword1>, <keyword2>,...}

\jnlcitation{\cname{%
\author{<aurhor name>}, 
\author{<aurhor name>}, 
\author{<aurhor name>}, 
\author{<aurhor name>},  and 
\author{<aurhor name>}} (\cyear{<year>}), 
\ctitle{<journal title>}, \cjournal{<journal name>} <year> <vol> Page <xxx>-<xxx>}

\footnotetext{\textbf{<abbreviation head:>} <abbreviations> ..}

\maketitle

\section{Introduction}
.
.
.
\end{boxedverbatim}
\end{center}
\caption{Example for title page.\label{F1}}
\end{figure}

\section{The Body of the Article}

\subsection{Section headings}

\begin{enumerate}[(H1)]
\item Section --- use \verb"\section{}"
\item SubSection--- use \verb"\subsection{}"
\item SubSubSectioin--- use \verb"\subsubsection{}"
\item Paragraph--- use \verb"\paragraph{}"
\item Subparagraph--- use \verb"\subparagraph{}"
\end{enumerate}

\subsection{Mathematics} \textsf{WileyNJD-v2.cls} makes the full
functionality of \AmS\/\TeX\ available. We encourage the use of
the \verb"align", \verb"gather" and \verb"multline" environments
for displayed mathematics.

\subsection{Figures and Tables}

\textsf{WileyNJD-v2.cls} uses the
\textsf{graphicx} package for handling figures.

Figures are called in as follows:
\begin{verbatim}
\begin{figure}
\centering
\includegraphics{<figure name>}
\caption{<Figure caption>}
\end{figure}
\end{verbatim}

The standard coding for a table is shown in Figure~\ref{F2}.

\begin{figure}[h]
\setlength{\fboxsep}{0pt}%
\setlength{\fboxrule}{0pt}%
\begin{center}
\begin{boxedverbatim}
\begin{table}
\caption{<Table caption>}
\centering
\begin{tabular}{<table alignment>}
\toprule
<column headings>\\
\midrule
<table entries
(separated by & as usual)>\\
<table entries>\\
.
.
.\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item Source: xxx.
\item[1] xxx.
\item[2] xxx.
\end{tablenotes}
\end{table}
\end{boxedverbatim}
\end{center}
\caption{Example for table layout.\label{F2}}
\end{figure}

\subsection{Cross-referencing}
The use of the \LaTeX\ cross-reference system
for figures, tables, equations, etc., is encouraged
(using \verb"\ref{<name>}" and \verb"\label{<name>}").

\subsection{Box text}

\begin{verbatim}
\begin{boxtext}
\section*{<title>}%
Paragraph
\end{boxtext}
\end{verbatim}

\subsection{List items}

\subsubsection{Enumerate list styles}
\begin{verbatim}
\begin{enumerate}[1]
\item 
\end{enumerate}

\begin{enumerate}[1.]
\item 
\end{enumerate}

\begin{enumerate}[(1)]
\item 
\end{enumerate}

\begin{enumerate}[I]
\item 
\end{enumerate}

\begin{enumerate}[i]
\item 
\end{enumerate}

\begin{enumerate}[a]
\item 
\end{enumerate}

\end{verbatim}

\subsubsection{Bullet list styles}

\begin{verbatim}
\begin{itemize}
\item 
\end{itemize}
\end{verbatim}

\subsubsection{Description list}

\begin{verbatim}
\begin{description}
\item[<entry>] description text.
\end{description}
\end{verbatim}

\subsection{Enunciations}

\begin{verbatim}
\begin{theorem}[<Theorem subhead>]\label{thm1}
<theorem text>. 
\end{theorem}

\begin{proposition}[<proposition subhead>]\label{pro1}
<proposition text>. 
\end{proposition}

\begin{definition}[<definition subhead>]\label{dfn1}
<definition text>. 
\end{definition}

\begin{proof}
<proof text>. 
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm1}]
<proof text>.
\end{proof}

\end{verbatim}

\subsection{Program codes}

Use \verb+\begin{verbatim}...\end{verbatim}+ for program codes without math. Use \verb+\begin{alltt}...\end{alltt}+ for program codes with math. Based on the text provided inside the optional argument of \verb+\begin{code}[Psecode|Listing|Box|Code|+\hfill\break \verb+Specification|Procedure|Sourcecode|Program]...+ \verb+\end{code}+ tag corresponding boxed like floats are generated. Also note that \verb+\begin{code}[Code|Listing]...+ \verb+\end{code}+ tag with either Code or Listing text as optional argument text are set with computer modern typewriter font.  All other code environments are set with normal text font. Refer below example:

\begin{verbatim}
\begin{lstlisting}[caption={Descriptive Caption Text},label=DescriptiveLabel]
for i:=maxint to 0 do
begin
{ do nothing }
end;
Write('Case insensitive ');
WritE('Pascal keywords.');
\end{lstlisting}
\end{verbatim}

\subsection{Acknowledgements}

This work was supported by JSPS KAKENHI Grant Number 19K06862 and 20H03012.
An Acknowledgements section is started with \verb"\ack" or
\verb"\acks" for \textit{Acknowledgement} or
\textit{Acknowledgements}, respectively. It must be placed just
before the References.

\subsection{Bibliography}

\begin{enumerate}[1]
\item Use \verb"\bibliography{wileyNJD-AMA}" BST file for AMA reference style
\item Use \verb"\bibliography{wileyNJD-APA}" BST file for APA reference style
\item Use \verb"\bibliography{wileyNJD-AMS}" BST file for AMS reference style
\item Use \verb"\bibliography{wileyNJD-VANCOUVER}" BST file for Vancouver reference style
\item Use \verb"\bibliography{wileyNJD-ACS}" BST file for Chemistry reference style
\end{enumerate}

The normal commands for producing the reference list are:

\begin{verbatim}
\begin{thebibliography}{99}
\bibitem{<x-ref label>}
         <Reference details>
.
.
.
\end{thebibliography}
\end{verbatim}

\subsection{Appendix Section}

\begin{verbatim}
\appendix

\section{Section title of first appendix\label{app1}}
.
.
.

\end{verbatim}
\end{comment}

\end{document}

### 2021-05-19 latex/ms.tex
add table

@@
 
-\articletype{Manuscript intended for \emph{Evolutionary Applications}, \today}%
+\articletype{Manuscript intended for \emph{Methods in Ecology and Evolution}, \today}%
 
@@
 \section{Theory}\label{sec2}
+
+\renewcommand{\arraystretch}{0.6}
+\begin{table}[tb]
+\begin{center}
+   \caption[]{Table 1: The list of mathematical symbols employed in the main text}
+    \textbf {}\\[-4mm]
+    \begin{tabular}{llc} \hline
+       & & \\
+	$n_{\rm M,1}, n_{\rm M, 2}$			& Sample number of parents in the subpopulation 1 and 2\\ 
+		                						& \\
+	$n_{\rm O, 1}, n_{\rm O, 2}$			& Sample number of offspring in the subpopulation 1 and 2\\ 
+		                						& \\
+	$N_{1}, N_{2}$						& Number of parents in the subpopulation 1 and 2 when sampled\\
+									& offspring are born\\
+		                						& \\
+	$M$								& Number of migrants of parents from the subpopulation 1 to the subpopulation 2\\
+		                						& \\
+	$\pi_{\rm PO,1}, \pi_{\rm PO,2}$		& Probability that a randomly selected pair (mother and offspring) \\
+	                							& shares a mother-offspring relationship within the subpopulation 1 and 2\\
+									& \\
+	$\pi_{\rm PO,1}, \pi_{\rm PO,2}$		& Probability that a randomly selected pair (mother and offspring) \\
+	                							& shares a mother-offspring relationship within the subpopulation 1 and 2\\
+									& \\
+	$\pi_{\rm MS}$			& Probability that a randomly selected pair (two offspring) \\
+	                				& shares a maternal-sibling relationship\\
+	$N_{\rm b,m}$			& Effective breeding number of mothers in the population\\
+		                			& \\
+	$\phi$		 		& Overdispersion parameter under negative binomial \\
+						&reproduction\\
+		                			& \\
+	$\lambda_i$			& Expected number of surviving offspring of mother $i$\\
+						& at sampling\\
+		                			& \\	
+	$f(\lambda)$			& Frequency of $\lambda$ for all mothers.\\
+		                			& \\	
+	$c$					& Combined effect of deviation from the Poisson \\
+						&($=(1+\phi^{-1})\mathbb{E}[\lambda^2] / \mathbb{E}[\lambda]^2$)\\
+						& \\	
+	$k_i$				& Number of surviving offspring born to mother $i$\\ 
+	                				& \\
+	$H_{\rm MO}$			& Number of mother--offspring pairs observed in samples\\ 
+	                				& \\
+	$H_{\rm MS}$			& Number of maternal-sibling pairs observed in samples\\ 
+	                				& \\
+	$\pi_{\rm MO}$			& Probability that a randomly selected pair (mother and offspring) \\
+	                				& shares a mother-offspring relationship\\
+						& \\
+	$\pi_{\rm MS}$			& Probability that a randomly selected pair (two offspring) \\
+	                				& shares a maternal-sibling relationship\\
+						& \\
+	$b$					& Bias of $\widehat{N_{\rm e,m}/N_{\rm m} }$\\
+					        & & \\	                		
+	\hline
+    \end{tabular}
+    \label{symbols} 
+\end{center} 
+\end{table}
+\renewcommand{\arraystretch}{1}
 

### 2021-05-19 latex/ms.tex
modify table

--- 2021-05-18 latex/ms.tex
@@
 \section{Theory}\label{sec2}
+
+\renewcommand{\arraystretch}{0.6}
+\begin{table}[tb]
+\begin{center}
+   \caption[]{Table 1: The list of mathematical symbols employed in the main text}
+    \textbf {}\\[-4mm]
+    \begin{tabular}{llc} \hline
+       & & \\
+	$n_{\rm P,1}, n_{\rm P, 2}$			& Sample number of parents in the subpopulation 1 and 2\\ 
+		                						& \\
+	$n_{\rm O, 1}, n_{\rm O, 2}$			& Sample number of offspring in the subpopulation 1 and 2\\ 
+		                						& \\
+	$N_{1}, N_{2}$						& Number of parents in the subpopulation 1 and 2 when sampled offspring are born\\
+		                						& \\
+	$M$								& Number of migrants of parents from the subpopulation 1 to the subpopulation 2\\
+		                						& \\
+	$\pi_{\rm PO,1}, \pi_{\rm PO,2}$		& Probability that a randomly selected pair (mother and offspring) \\
+	                							& shares a parent-offspring relationship within the subpopulation 1 and 2\\
+									& \\
+	$\pi_{\rm PO, bet}$					& Probability that a randomly selected pair (parent and offspring in the population 1 and 2, respectively) \\
+	                							& shares a parent-offspring relationship between the subpopulation 1 and 2\\
+									& \\
+	$\pi_{\rm HS, bet}$					& Probability that a randomly selected pair (two offspring in the population 1 and 2) \\
+	                							& shares a half-sibling relationship between the subpopulation 1 and 2\\
+					                			& \\
+	$\lambda_{i,1}, \lambda_{i,2}$			& Expected number of surviving offspring of parent $i$ at sampling in the subpopulation 1 and 2\\
+		                						& \\
+	$\lambda_{i, M}$					& Expected number of surviving offspring of migrant $i$ at sampling\\
+		                						& \\
+	$k_{i,1}, k_{i,2}$					& Number of surviving offspring born to parent $i$ in the subpopulation 1 and 2\\ 
+	                							& \\
+	$H_{\rm PO, 1}, H_{\rm PO, 2}$		& Number of parent-offspring pairs observed in samples within the subpopulation 1 and 2\\ 
+	                							& \\
+	$H_{\rm PO, bet}$					& Number of parent-offspring pairs observed in samples between the subpopulation 1 and 2\\ 
+	                							& \\
+	$H_{\rm HS, bet}$					& Number of half-sibling pairs observed in samples between the subpopulation 1 and 2\\ 
+	                							& \\              		
+	\hline
+    \end{tabular}
+    \label{symbols} 
+\end{center} 
+\end{table}
+\renewcommand{\arraystretch}{1}
 

### 2021-05-21 latex/ms.tex
start #4
add simple POP-model
define additional estimators including those for migration rate

@@
 
+\subsection{Assumptions}
+
 この章では，全てに共通するモデリングの仮定を述べた後，シンプルなモデルから徐々に複雑なモデルへと移行する。具体的には，最初にシンプルなモデルについて記述して，
@@
 
-\subsection{Basic model}
+\subsection{HSP-based model}
 
+\begin{align}
+\pi_{\rm HS,bet} &= \frac{2M}{N_{1}} \frac{2M}{N_{2}} \frac{1}{M} \nonumber\\
+&= \frac{4M}{N_{1}N_{2}}
+\label{HS-1}
+\end{align}
+
+\begin{align}
+\mathbb{E}[H_{\rm HS, bet}] &= \pi_{\rm HS,bet} n_{\rm O, 1} n_{\rm O, 2} \nonumber\\
+&= \frac{ 4 n_{\rm O, 1} n_{\rm O, 2} M } { N_{1} N_{2} } \\
+&= \frac{ 4 n_{\rm O, 1} n_{\rm O, 2} m } { N_{2} }
+\label{HS-2}
+\end{align}
+
+\begin{align}
+\widehat{M_1} &= \frac{N_{1} N_{2} \widetilde{H}_{\rm HS, bet} } {4 n_{\rm O, 1} n_{\rm O, 2} }
+\label{HS-3}
+\end{align}
+
+\begin{align}
+\widehat{m_1} &= \frac{N_{2} \widetilde{H}_{\rm HS, bet} } {4 n_{\rm O, 1} n_{\rm O, 2} }
+\label{HS-3}
+\end{align}
+
+より一般的な説明は付録に載せた。
+
+\subsection{POP-based model}
+
+\begin{align}
+\pi_{\rm PO,bet} &= \frac{2M}{N_{1}} \frac{M}{N_{2}} \frac{1}{M} \nonumber\\
+&= \frac{2M}{N_{1}N_{2}}
+\label{PO-1}
+\end{align}
+
+\begin{align}
+\mathbb{E}[H_{\rm PO, bet}] &= \pi_{\rm PO,bet} n_{\rm O, 1} n_{\rm P, 2} \nonumber\\
+&= \frac{ 2 n_{\rm O, 1} n_{\rm P, 2} M } { N_{1} N_{2} }
+\label{PO-2}
+\end{align}
+
+\begin{align}
+\widehat{M_2} &= \frac{N_{1} N_{2} \widetilde{H}_{\rm PO,bet} } {2 n_{\rm O, 1} n_{\rm P, 2} }
+\label{PO-3}
+\end{align}
+
+\section{Applications}\label{sec3}
+
+\subsection{Parent number can be estimated by PO pairs found within a subpopulation}
+
+\begin{align}
+\widehat{M_3} &= \frac{ N_{1} N_{2} \left(\widetilde{H}_{\rm HS,bet} + \widetilde{H}_{\rm PO,bet}\right) } {2n_{\rm O, 1} \left(2 n_{\rm O, 2} + n_{\rm P, 2}\right) }
+\label{AP-1}
+\end{align}
+
+\begin{align}
+\widehat{m_3} &= \frac{ N_{2} \left(\widetilde{H}_{\rm HS,bet} + \widetilde{H}_{\rm PO,bet}\right) } {2n_{\rm O, 1} \left(2 n_{\rm O, 2} + n_{\rm P, 2}\right) }
+\label{AP-2}
+\end{align}
+
+サンプル数の少なさを補えるかも。
+
+\begin{align}
+\widehat{N_2} &= \frac{ 2 n_{\rm O, 2} n_{\rm P, 2} + 1 }{\widetilde{H}_{\rm PO, 2} + 1} 
+\label{AP-3}
+\end{align}
+subpop2の親子もわかるはず。migration rateを推定すると考えると、$N_2$を推定値で置き換えて
+
+\begin{align}
+\widehat{m_3} &=  \frac{ \left(\widetilde{H}_{\rm HS,bet} + \widetilde{H}_{\rm PO,bet}\right) \left(2 n_{\rm O, 2} n_{\rm P, 2} + 1\right)} {2n_{\rm O, 1} \left(2 n_{\rm O, 2} + n_{\rm P, 2}\right) \left(\widetilde{H}_{\rm PO, 2} + 1\right)}
+\label{AP-4}
+\end{align}
+
+\begin{align}
+\widehat{N_1} &= \frac{ 2 n_{\rm O, 1} n_{\rm P, 1} + 1 }{\widetilde{H}_{\rm PO, 1} + 1} 
+\label{AP-5}
+\end{align}
+
+\begin{align}
+\widehat{M_5} &=  \frac{ \left(\widetilde{H}_{\rm HS,bet} + \widetilde{H}_{\rm PO,bet}\right) \left(2 n_{\rm O, 1} n_{\rm P, 1} + 1\right) \left(2 n_{\rm O, 2} n_{\rm P, 2} + 1\right)} {2n_{\rm O, 1} \left(2 n_{\rm O, 2} + n_{\rm P, 2}\right) \left(\widetilde{H}_{\rm PO, 1} + 1\right) \left(\widetilde{H}_{\rm PO, 2} + 1\right)}
+\label{AP-6}
+\end{align}
+
+\begin{comment}%%%%%%%%%%%%%%%
 まず最初に，最もシンプルなモデルを考える。$t$年にサブ集団１にいる$N_{1,t}$個体の母親を考えよう。$t$年に子供を産んだ後，$N_{1,t}$個体のうち$M_{1\to2}$個体がサブ集団２に移動し，$t+1$年にサブ集団２にいる母個体$N_{2,t+1}$の一部として子供を産むとする。この時，サブ集団１から$t$年に産まれた子供とサブ集団２から$t+1$年に産まれた子供が，母を共有する兄弟(Maternal half Sibling, MHS)である確率$\pi_{\rm b,1\to2}$を考える。どの母親も同じような繁殖ポテンシャルを持つと仮定すると，移動する母親の子供をサブ集団１でサンプルする確率は$M_{1\to2}/N_{1,t}$となる。同様に，移動する母親の子供をサブ集団２においてサンプルする確率は$M_{1\to2}/N_{2,t+1}$である。それぞれでサンプルした子供の母親が同一である確率は$1/M_{1\to2}$であることより，サンプルした２個体がMHSペアとなる確率が以下のように得られる。
@@
 
+ここでは応用例として，３年間にわたって２つのサブ集団からサンプルされた当歳魚から見出される半兄弟ペアをもとに，個体数($N$)・移動率($m$)・生存率($s$)を推定する理論的な枠組みを提示する。サブ集団１に生息する親魚数を、$N_1(t), N_1(t+1), N_1(t+2)$のように表記し、他のパラメータについても同様とする。個体数については６つのパラメータ、移動率および生存率は４つのパラメータとなり、合計１４のパラメータが考えられる（$t+2$年の移動率および生存率は含まれない点に注意）。まずは、これら１４個のパラメータは独立に決まるとしよう（すなわち、$N_1(t)$と$N_1(t+1)$は無関係で、$s_1(t)$と$s_1(t+1)$は独立に決める、など）。なお、この応用例では、移動する親魚は繁殖ポテンシャルによらずに決まると仮定して、式\ref{4-1}を用いることにしよう。また、全ての親魚は、年をまたぐごとに、1)サブ集団を移動して産卵するか（確率：$m$）、2)同じサブ集団に留まって産卵するか（確率：$s$）、3)死亡するか（確率：$1-m-s$）、のいずれかのイベントを経験するとする。
+
+今回新たに開発した移動に関する関係式について、以下の６種類の親魚に関するその子供（当歳魚）ペアがありえる：
+\begin{enumerate}
+  \item $N_1(t)\to N_2(t+1)$
+  \item $N_1(t)\to N_2(t+2)$
+  \item $N_1(t+1)\to N_2(t+2)$
+  \item $N_2(t)\to N_1(t+1)$
+  \item $N_2(t)\to N_1(t+2)$
+  \item $N_2(t+1)\to N_1(t+2)$
+\end{enumerate}
+右向きの矢印$\to$は、興味ある親魚が年を跨いだ後どのサブ集団に属しているかを表している。１番目を例にとると、$t$年にサブ集団１から、$t+1$年にサブ集団２からそれぞれ当歳魚をサンプルすることを意味する。加えて、同じサブ集団から年を跨いで見つかる半兄弟ペアに基づく関係式についても、以下の６種類が考えられる：
+\begin{enumerate}
+\setcounter{enumi}{6}
+  \item $N_1(t)\to N_1(t+1)$
+  \item $N_1(t)\to N_1(t+2)$
+  \item $N_1(t+1)\to N_1(t+2)$
+  \item $N_2(t)\to N_2(t+1)$
+  \item $N_2(t)\to N_2(t+2)$
+  \item $N_2(t+1)\to N_2(t+2)$
+\end{enumerate}
+以上の、合計１２種類の式を連立できることを示した。最大１４個のパラメータが必要となるのであったが、パラメータ数を応用先に応じて適宜減少させることができる場合、興味あるパラメータを推定することができる。
+
+ちなみに、同一年内に同じサブ集団内で見つかるMHSペアについては、有効集団サイズの情報（正確には有効繁殖サイズ、Effective breeding size）は持っているが、センサスサイズに関するダイレクトな情報は持っていない点に注意。
+\end{comment}%%%%%%%%%%%%%%%
+
+\section{Results and Discussion}\label{sec4}
+
+\begin{enumerate}
+  \item $M$ではなく$m$の推定であれば、N2だけ分かれば良い
+  \item 
+  \item サンプルされる当歳魚（０歳）は，必ずサンプルされたサブ集団で産まれる
+  \item 当歳魚かどうかの判断は１００％可能
+  \item サンプル間の近親判別では，１００％の成功率で半兄弟ペアか否かがなされる
+\end{enumerate}
+
+\section{ACKNOWLEDGEMENTS}
+
+The author thanks MV Bravington for motivating me to pursue this research topic. This work was supported by JSPS KAKENHI Grant Number 19K06862 and 20H03012.
+
+\clearpage
+
+\section*{APPENDIX A}
+\setcounter{equation}{0}
+
+\section*{Distribution of the number of surviving offspring per mother and its variance}
+
+\renewcommand{\theequation}{A\arabic{equation}}
+
 \subsection{Reproductive variation}
@@
 
-\section{Application}\label{sec3}
+Let $k_i$ denote the total number of surviving offspring from a mother  $i$ ($i= 1, 2, \dots, N_{\rm m}$) at time of sampling.
+Following \cite{Akita_2019} and giving the expected number of the surviving offspring per mother at time of sampling, $\lambda_i$ ($>0$), $k_i$ is assumed to follow a negative binomial distribution through a conventional parametrization:
+\begin{equation}
+{\rm Pr}[ k_i | \lambda_i ] = \frac{\Gamma[k_i+\phi]}{k_i! \Gamma[\phi]} \left( \frac{\lambda_i}{\phi+\lambda_i} \right)^{k_i} \left( \frac{\phi}{\phi+\lambda_i} \right)^{\phi}, 
+\label{NB}
+\end{equation}
+where $\phi$ ($>0$) denotes the overdispersion parameter describing the degree of nonparental variation.
+In the current work, $\phi$ is assumed to be constant across mothers, whereas the expected number of surviving offspring ($\lambda_i$) varies across mothers.
+The mean and variance of this distribution are denoted by $\lambda_i$ and $\lambda_i + \lambda_i^2/\phi$, respectively.
+In the limit of infinite $\phi$, this distribution becomes a Poisson distribution, which is given by ${\rm Pr}[ k_i | \lambda_i ]=\lambda_i^{k_i} \mathrm{e}^{-\lambda_i}/(k_i!)$.
+We assume $\lambda_i$ to be independent and identically distributed with the density function $f(\lambda)$, producing a parental variation.
+The shape of the density function is often complex, but may be described by information from the population, for example, the mother's weight composition in the population.
+The specific form of $f(\lambda)$ is given in {\bf Appendix B} and is used for running an individual-based model.
 
-ここでは応用例として，３年間にわたって２つのサブ集団からサンプルされた当歳魚から見出される半兄弟ペアをもとに，個体数($N$)・移動率($m$)・生存率($s$)を推定する理論的な枠組みを提示する。サブ集団１に生息する親魚数を、$N_1(t), N_1(t+1), N_1(t+2)$のように表記し、他のパラメータについても同様とする。個体数については６つのパラメータ、移動率および生存率は４つのパラメータとなり、合計１４のパラメータが考えられる（$t+2$年の移動率および生存率は含まれない点に注意）。まずは、これら１４個のパラメータは独立に決まるとしよう（すなわち、$N_1(t)$と$N_1(t+1)$は無関係で、$s_1(t)$と$s_1(t+1)$は独立に決める、など）。なお、この応用例では、移動する親魚は繁殖ポテンシャルによらずに決まると仮定して、式\ref{4-1}を用いることにしよう。また、全ての親魚は、年をまたぐごとに、1)サブ集団を移動して産卵するか（確率：$m$）、2)同じサブ集団に留まって産卵するか（確率：$s$）、3)死亡するか（確率：$1-m-s$）、のいずれかのイベントを経験するとする。
-
-今回新たに開発した移動に関する関係式について、以下の６種類の親魚に関するその子供（当歳魚）ペアがありえる：
-\begin{enumerate}
-  \item $N_1(t)\to N_2(t+1)$
-  \item $N_1(t)\to N_2(t+2)$
-  \item $N_1(t+1)\to N_2(t+2)$
-  \item $N_2(t)\to N_1(t+1)$
-  \item $N_2(t)\to N_1(t+2)$
-  \item $N_2(t+1)\to N_1(t+2)$
-\end{enumerate}
-右向きの矢印$\to$は、興味ある親魚が年を跨いだ後どのサブ集団に属しているかを表している。１番目を例にとると、$t$年にサブ集団１から、$t+1$年にサブ集団２からそれぞれ当歳魚をサンプルすることを意味する。加えて、同じサブ集団から年を跨いで見つかる半兄弟ペアに基づく関係式についても、以下の６種類が考えられる：
-\begin{enumerate}
-\setcounter{enumi}{6}
-  \item $N_1(t)\to N_1(t+1)$
-  \item $N_1(t)\to N_1(t+2)$
-  \item $N_1(t+1)\to N_1(t+2)$
-  \item $N_2(t)\to N_2(t+1)$
-  \item $N_2(t)\to N_2(t+2)$
-  \item $N_2(t+1)\to N_2(t+2)$
-\end{enumerate}
-以上の、合計１２種類の式を連立できることを示した。最大１４個のパラメータが必要となるのであったが、パラメータ数を応用先に応じて適宜減少させることができる場合、興味あるパラメータを推定することができる。
-
-ちなみに、同一年内に同じサブ集団内で見つかるMHSペアについては、有効集団サイズの情報（正確には有効繁殖サイズ、Effective breeding size）は持っているが、センサスサイズに関するダイレクトな情報は持っていない点に注意。
-
-\section{Discussion}\label{sec4}
-
-\section{ACKNOWLEDGEMENTS}
-
-The author thanks MV Bravington for motivating me to pursue this research topic. This work was supported by JSPS KAKENHI Grant Number 19K06862 and 20H03012.
+The variance of the offspring number can be given by 
+\begin{eqnarray}
+\mathbb{V}[k] &=& \mathbb{E}[ \mathbb{V}[k|\lambda] ] + \mathbb{V}[ \mathbb{E}[k|\lambda] ] \nonumber\\
+&=& \mathbb{E}[ \lambda + \lambda^2 / \phi ] + \mathbb{V}[ \lambda ].
+\label{V_k}
+\end{eqnarray}
 

### 2021-05-21 latex/ms.tex
set all equations; close #4

@@
 
-\title{Estimating the number of migrants using between-population sibling pairs}%\protect\thanks{This is an example for title footnote.}}
+\title{Estimating the number of migrants based on kinship relationships}%\protect\thanks{This is an example for title footnote.}}
 
@@
 
+\begin{align}
+\widehat{m_2} &= \frac{N_{2} \widetilde{H}_{\rm PO,bet} } {2 n_{\rm O, 1} n_{\rm P, 2} }
+\label{PO-4}
+\end{align}
+
 \section{Applications}\label{sec3}
@@
 \begin{align}
-\widehat{m_3} &=  \frac{ \left(\widetilde{H}_{\rm HS,bet} + \widetilde{H}_{\rm PO,bet}\right) \left(2 n_{\rm O, 2} n_{\rm P, 2} + 1\right)} {2n_{\rm O, 1} \left(2 n_{\rm O, 2} + n_{\rm P, 2}\right) \left(\widetilde{H}_{\rm PO, 2} + 1\right)}
+\widehat{m_4} &=  \frac{ \left(\widetilde{H}_{\rm HS,bet} + \widetilde{H}_{\rm PO,bet}\right) \left(2 n_{\rm O, 2} n_{\rm P, 2} + 1\right)} {2n_{\rm O, 1} \left(2 n_{\rm O, 2} + n_{\rm P, 2}\right) \left(\widetilde{H}_{\rm PO, 2} + 1\right)}
 \label{AP-4}
@@
 \begin{align}
-\widehat{M_5} &=  \frac{ \left(\widetilde{H}_{\rm HS,bet} + \widetilde{H}_{\rm PO,bet}\right) \left(2 n_{\rm O, 1} n_{\rm P, 1} + 1\right) \left(2 n_{\rm O, 2} n_{\rm P, 2} + 1\right)} {2n_{\rm O, 1} \left(2 n_{\rm O, 2} + n_{\rm P, 2}\right) \left(\widetilde{H}_{\rm PO, 1} + 1\right) \left(\widetilde{H}_{\rm PO, 2} + 1\right)}
+\widehat{M_4} &=  \frac{ \left(\widetilde{H}_{\rm HS,bet} + \widetilde{H}_{\rm PO,bet}\right) \left(2 n_{\rm O, 1} n_{\rm P, 1} + 1\right) \left(2 n_{\rm O, 2} n_{\rm P, 2} + 1\right)} {2n_{\rm O, 1} \left(2 n_{\rm O, 2} + n_{\rm P, 2}\right) \left(\widetilde{H}_{\rm PO, 1} + 1\right) \left(\widetilde{H}_{\rm PO, 2} + 1\right)}
 \label{AP-6}

### 2021-05-21 latex/ms.tex
make table for summrizing estimators; close #5

@@
 \end{align}
-subpop2の親子もわかるはず。migration rateを推定すると考えると、$N_2$を推定値で置き換えて
+subpop2の親子もわかるはず。$N_2$を推定値で置き換えて
+
+\begin{align}
+\widehat{M_4} &=  \frac{ N_{1} \left(\widetilde{H}_{\rm HS,bet} + \widetilde{H}_{\rm PO,bet}\right) \left(2 n_{\rm O, 2} n_{\rm P, 2} + 1\right)} {2n_{\rm O, 1} \left(2 n_{\rm O, 2} + n_{\rm P, 2}\right) \left(\widetilde{H}_{\rm PO, 2} + 1\right)}
+\label{AP-4}
+\end{align}
+
+migration rateを推定すると考えると、
 
@@
 \widehat{m_4} &=  \frac{ \left(\widetilde{H}_{\rm HS,bet} + \widetilde{H}_{\rm PO,bet}\right) \left(2 n_{\rm O, 2} n_{\rm P, 2} + 1\right)} {2n_{\rm O, 1} \left(2 n_{\rm O, 2} + n_{\rm P, 2}\right) \left(\widetilde{H}_{\rm PO, 2} + 1\right)}
-\label{AP-4}
+\label{AP-5}
+\end{align}
+
+同様に、$N_1$も推定値で置き換えて
+\begin{align}
+\widehat{N_1} &= \frac{ 2 n_{\rm O, 1} n_{\rm P, 1} + 1 }{\widetilde{H}_{\rm PO, 1} + 1} 
+\label{AP-6}
 \end{align}
@@
 \begin{align}
-\widehat{N_1} &= \frac{ 2 n_{\rm O, 1} n_{\rm P, 1} + 1 }{\widetilde{H}_{\rm PO, 1} + 1} 
-\label{AP-5}
+\widehat{M_5} &=  \frac{ \left(\widetilde{H}_{\rm HS,bet} + \widetilde{H}_{\rm PO,bet}\right) \left(2 n_{\rm O, 1} n_{\rm P, 1} + 1\right) \left(2 n_{\rm O, 2} n_{\rm P, 2} + 1\right)} {2n_{\rm O, 1} \left(2 n_{\rm O, 2} + n_{\rm P, 2}\right) \left(\widetilde{H}_{\rm PO, 1} + 1\right) \left(\widetilde{H}_{\rm PO, 2} + 1\right)}
+\label{AP-7}
 \end{align}
 
-\begin{align}
-\widehat{M_4} &=  \frac{ \left(\widetilde{H}_{\rm HS,bet} + \widetilde{H}_{\rm PO,bet}\right) \left(2 n_{\rm O, 1} n_{\rm P, 1} + 1\right) \left(2 n_{\rm O, 2} n_{\rm P, 2} + 1\right)} {2n_{\rm O, 1} \left(2 n_{\rm O, 2} + n_{\rm P, 2}\right) \left(\widetilde{H}_{\rm PO, 1} + 1\right) \left(\widetilde{H}_{\rm PO, 2} + 1\right)}
-\label{AP-6}
-\end{align}
+\renewcommand{\arraystretch}{0.6}
+\begin{table}[tb]
+\begin{center}
+   \caption[]{Table 1: Summary of proposed estimators for input parameters}
+    \textbf {}\\[-0mm]
+    \begin{tabular}{cccccccc} \hline
+       	\\
+	Estimator			& $N_1$ 		& $N_2$ 		& $n_{\rm O, 1}$	& $n_{\rm O, 2}$	& $n_{\rm P, 1}$	& $n_{\rm P, 2}$\\
+	\\
+	\hline
+	\\
+	$\widehat{M_1}$	& given 		& given 		& \checkmark		& \checkmark \\ 
+		                						& \\
+	$\widehat{M_2}$	& given		& given		& \checkmark		& 				&				& \checkmark \\
+		                						& \\
+	$\widehat{M_3}$	& given		& given		& \checkmark		&  \checkmark		&				& \checkmark \\
+		                						& \\
+	$\widehat{M_4}$	& given		& estimated	& \checkmark		&  \checkmark		&				& \checkmark \\
+		                						& \\
+	$\widehat{M_5}$	& estimated	& estimated	& \checkmark		&  \checkmark		& \checkmark		& \checkmark \\
+									& \\
+	$\widehat{m_1}$	& ---			& given		& \checkmark		& \checkmark \\ 
+									& \\
+	$\widehat{m_2}$	& ---			& given		& \checkmark		& 				&				& \checkmark \\
+					                			& \\
+	$\widehat{m_3}$	& ---			& given 		& \checkmark		&  \checkmark		&				& \checkmark \\
+		                						& \\
+	$\widehat{m_4}$	& ---			& estimated	& \checkmark		&  \checkmark		& 				& \checkmark \\
+		                						& \\
+	\hline
+    \end{tabular}
+    \label{symbols} 
+\end{center} 
+\end{table}
+\renewcommand{\arraystretch}{1}
 
@@
 \section{Results and Discussion}\label{sec4}
-
-\begin{enumerate}
-  \item $M$ではなく$m$の推定であれば、N2だけ分かれば良い
-  \item 
-  \item サンプルされる当歳魚（０歳）は，必ずサンプルされたサブ集団で産まれる
-  \item 当歳魚かどうかの判断は１００％可能
-  \item サンプル間の近親判別では，１００％の成功率で半兄弟ペアか否かがなされる
-\end{enumerate}
 

### 2021-05-21 latex/ms.tex
modify main text
modify table 2

@@
 
-\subsection{Parent number can be estimated by PO pairs found within a subpopulation}
+\subsection{Efficient use of kinship pairs between subploulations}
 
@@
 サンプル数の少なさを補えるかも。
+
+\subsection{Parent number can be estimated by PO pairs found within a subpopulation}
 
@@
 
+\subsection{Individual-based model}
+
 \renewcommand{\arraystretch}{0.6}
@@
 \begin{center}
-   \caption[]{Table 1: Summary of proposed estimators for input parameters}
+   \caption[]{Table 1: Summary of proposed estimators for required parameters and kinship types}
     \textbf {}\\[-0mm]
-    \begin{tabular}{cccccccc} \hline
+    \begin{tabular}{ccccccccc} \hline
        	\\
-	Estimator			& $N_1$ 		& $N_2$ 		& $n_{\rm O, 1}$	& $n_{\rm O, 2}$	& $n_{\rm P, 1}$	& $n_{\rm P, 2}$\\
+	Estimator			& $N_1$ 		& $N_2$ 		& $n_{\rm O, 1}$	& $n_{\rm O, 2}$	& $n_{\rm P, 1}$	& $n_{\rm P, 2}$	& Required kinship type\\
 	\\
@@
 	\\
-	$\widehat{M_1}$	& given 		& given 		& \checkmark		& \checkmark \\ 
+	$\widehat{M_1}$	& given 		& given 		& \checkmark		& \checkmark 		&				&				& HSP\\ 
 		                						& \\
-	$\widehat{M_2}$	& given		& given		& \checkmark		& 				&				& \checkmark \\
+	$\widehat{M_2}$	& given		& given		& \checkmark		& 				&				& \checkmark 		& POP\\
 		                						& \\
-	$\widehat{M_3}$	& given		& given		& \checkmark		&  \checkmark		&				& \checkmark \\
+	$\widehat{M_3}$	& given		& given		& \checkmark		&  \checkmark		&				& \checkmark 		& HSP \& POP\\
 		                						& \\
-	$\widehat{M_4}$	& given		& estimated	& \checkmark		&  \checkmark		&				& \checkmark \\
+	$\widehat{M_4}$	& given		& estimated	& \checkmark		&  \checkmark		&				& \checkmark 		& HSP \& POP\\
 		                						& \\
-	$\widehat{M_5}$	& estimated	& estimated	& \checkmark		&  \checkmark		& \checkmark		& \checkmark \\
+	$\widehat{M_5}$	& estimated	& estimated	& \checkmark		&  \checkmark		& \checkmark		& \checkmark 		& HSP \& POP\\
 									& \\
-	$\widehat{m_1}$	& ---			& given		& \checkmark		& \checkmark \\ 
+	$\widehat{m_1}$	& ---			& given		& \checkmark		& \checkmark 		&				&				& HSP\\ 
 									& \\
-	$\widehat{m_2}$	& ---			& given		& \checkmark		& 				&				& \checkmark \\
+	$\widehat{m_2}$	& ---			& given		& \checkmark		& 				&				& \checkmark 		& POP\\					                			& \\
+	$\widehat{m_3}$	& ---			& given 		& \checkmark		&  \checkmark		&				& \checkmark 		& HSP \& POP\\
 		                						& \\
-	$\widehat{m_3}$	& ---			& given 		& \checkmark		&  \checkmark		&				& \checkmark \\
-		                						& \\
-	$\widehat{m_4}$	& ---			& estimated	& \checkmark		&  \checkmark		& 				& \checkmark \\
+	$\widehat{m_4}$	& ---			& estimated	& \checkmark		&  \checkmark		& 				& \checkmark 		& HSP \& POP\\
 		                						& \\

### 2021-05-25 latex/ms.tex
update main text
double-spaced in the main text

@@
 \linenumbers
+\usepackage[doublespacing]{setspace}
 
@@
 
-\title{Estimating the number of migrants based on kinship relationships}%\protect\thanks{This is an example for title footnote.}}
+\title{Estimating the migrant number and rate based on kinship relationships}%\protect\thanks{This is an example for title footnote.}}
 
@@
 \section{Theory}\label{sec2}
+The main symbols used in the current paper are summarized in Table \ref{symbols}.
 
@@
 \begin{center}
-   \caption[]{Table 1: The list of mathematical symbols employed in the main text}
+   \caption[]{The list of mathematical symbols employed in the main text}
     \textbf {}\\[-4mm]
@@
 
+\subsection{Required sample size}
+
+\begin{align}
+n_{\rm O, 1} n_{\rm O, 2} &> \frac{ N_{2} } { 4m }
+\label{RS-1}
+\end{align}
+
+\begin{align}
+n_{\rm O, 1} n_{\rm P, 2} &> \frac{ N_{2} } { 2m }
+\label{RS-2}
+\end{align}
+
 \section{Applications}\label{sec3}
@@
 \begin{center}
-   \caption[]{Table 1: Summary of proposed estimators for required parameters and kinship types}
+   \caption[]{Summary of proposed estimators for required parameters and kinship types}
     \textbf {}\\[-0mm]
@@
     \end{tabular}
-    \label{symbols} 
+    \label{parameter} 
 \end{center} 
@@
 
+オーダーは$m\approx0.1$程度を想定。これよりもずっと小さければ、遺伝的に異なる系群と考えられFstも大きく出るので、ベイズアスなどから推定できるだろう。一方、その場合はサンプル数が大量になり、今回提案した方法は向かない。
+
 \section{ACKNOWLEDGEMENTS}
@@
 
-\section*{Distribution of the number of surviving offspring per mother and its variance}
+\section*{Equation X holds under flexible assumptions for the distribution of surviving offspring number per parent}
 
 \renewcommand{\theequation}{A\arabic{equation}}
-
-\subsection{Reproductive variation}
 

### 2021-05-25 latex/ms.tex
modify table 1

@@
 					                			& \\
-	$\lambda_{i,1}, \lambda_{i,2}$			& Expected number of surviving offspring of parent $i$ at sampling in the subpopulation 1 and 2\\
+	$\lambda_{i,1}, \lambda_{j,2}$			& Expected number of surviving offspring of parent $i$ and $j$ at sampling in the subpopulation 1 and 2\\
 		                						& \\
@@
 		                						& \\
-	$k_{i,1}, k_{i,2}$					& Number of surviving offspring born to parent $i$ in the subpopulation 1 and 2\\ 
+	$k_{i,1}, k_{j,2}$					& Number of surviving offspring born to parent $i$ and $j$ in the subpopulation 1 and 2\\ 
 	                							& \\
@@
 
-\subsection{Efficient use of kinship pairs between subploulations}
+\subsection{Efficient use of kinship pairs found between subpopulations}
 

### 2021-05-25 latex/ms.tex
add fig1

@@
 
-\articletype{Manuscript intended for \emph{Methods in Ecology and Evolution}, \today}%
+\articletype{Research article, \today}%
 
@@
 
-\title{Estimating the migrant number and rate based on kinship relationships}%\protect\thanks{This is an example for title footnote.}}
+\title{Estimating migrant rates using kinship pairs \protect\thanks{Running head line: Estimating migrant rates using kinship pairs}}
 
-\author[1]{Tetsuya Akita*}
-
+\author[1]{Tetsuya Akita}
 \authormark{Akita}
@@
 
-\abstract[Abstract]{本ノートでは，多回繁殖(iteroparity)する種を対象として，半兄弟ペア数から親魚による２つのサブ集団間の移動率を推定する理論($\hat{M}=N_1N_2H_{\rm obs}/(4n_1n_2)$)を紹介する。この推定式は、親をサンプルする通常の標識放流と同じである。もし、繁殖ポテンシャルの分布が集団間で異なっていても上記の式で問題ないことを示した。一方，サンプル数としては$\sqrt {N}$以上のオーダーが求められる。}
+\abstract[Abstract]{The Abstract must not exceed 350 words and should list the main results and conclusions, using simple, factual, numbered statements:
+
+Point 1: set the context for and purpose of the work;
+
+Point 2: indicate the approach and methods;
+
+Point 3: outline the main results;
+
+Point 4: identify the conclusions and the wider implications.
+
+1. aaa\\
+2. bbb
+
+本ノートでは，多回繁殖(iteroparity)する種を対象として，半兄弟ペア数から親魚による２つのサブ集団間の移動率を推定する理論($\hat{M}=N_1N_2H_{\rm obs}/(4n_1n_2)$)を紹介する。この推定式は、親をサンプルする通常の標識放流と同じである。もし、繁殖ポテンシャルの分布が集団間で異なっていても上記の式で問題ないことを示した。一方，サンプル数としては$\sqrt {N}$以上のオーダーが求められる。}
 
@@
 また，性成熟した個体を親と呼ぶことにする。
+
+%%%FIGURE 1%%%
+\begin{figure}[!h]
+	\begin{center}
+		\includegraphics[width=0.3\textwidth]{/Users/akita/Dropbox/research/close_kin/Mig/Figs/cartoon.eps}
+		\caption{Example of relationships between mothers and their offspring number.
+The open, gray, and filled circles represent mothers, their eggs, and their offspring, respectively.
+The area of an open circle indicates the degree of reproductive potential of each mother (i.e., $\lambda_i$).
+The dotted and thin arrows denote mother--egg and egg--offspring relationships, respectively.
+The symbol x denotes a failure to survive at sampling.
+Sampled individuals are denoted with squares.
+In this example, $M=6$, }
+		\label{cartoon}
+	\end{center}
+\end{figure}
+%%%%%%%%%%%
 

### 2021-05-27 latex/ms.tex
add text in Theory

@@
 
-\title{Estimating migrant rates using kinship pairs \protect\thanks{Running head line: Estimating migrant rates using kinship pairs}}
+\title{Estimating migrantation rates using kinship pairs \protect\thanks{Running head line: Estimating migrantation rates using kinship pairs}}
 
@@
 
-\subsection{Assumptions}
+\subsection{Hypothetical population and sampling scheme}
 
-この章では，全てに共通するモデリングの仮定を述べた後，シンプルなモデルから徐々に複雑なモデルへと移行する。具体的には，最初にシンプルなモデルについて記述して，
+Suppose that we have a set of two populations labelled 1 and 2.
+
+and there are migrant individuals between the two subpopulations.
+also no population subdivision or spatial struc- ture.
+In this study, a mature female is called a mother even if she does not produce offspring.
+For mathematical tractability, we assume that only one spawning ground exists in which the mothers remain for the entire spawning season.
+Following (Akita, 2020), our modeling frame- work employs two types of overdispersed reproduction: parental and nonparental variations.
+Thus, the former indicates a variation caused by the mother's covariates, such as age, weight, and residence time on the spawning ground, while the latter indicates a variation caused by nonrandom stochastic events during a series of reproductive episodes, which are independent of the mother's covariates, such as family-correlated survivorship or the mating behavior effects (e.g., competition for males/females and correlation between mating op- portunities of the mother and the number of her offspring).
+Figure 1 illustrates a schematic diagram of the effects of parental and non- parental variations exemplified by age-dependent reproduction and family-correlated survival on kinship relationships in a population.
+Detailed definitions of parental and nonparental variations are stated in (Akita, 2020).
+Appendix 1 provides the theoretical foundation of both parental and nonparental variations in reproduction.
+
 \begin{itemize}

### 2021-05-27 latex/ms.tex
change title and add text in Theory

@@
 
-\title{Estimating migrantation rates using kinship pairs \protect\thanks{Running head line: Estimating migrantation rates using kinship pairs}}
+\title{Estimating migration rates for iteroparous species using kinship pairs found between populations\protect\thanks{Running head line: Estimating migration rates using kinship pairs}}
 
@@
 \section{Theory}\label{sec2}
-The main symbols used in the current paper are summarized in Table \ref{symbols}.
+In this section, we derivate the estimators of migrant number and migration rates using HS pairs or PO pairs found between two populations.
+While the estimators can hold under complex assumptions for reproduction theoretical foundation for estimating
+このセクションでは、migrantやmigration rateの推定量を導出する。導出された推定量は、付録にある通りフレキシブルな仮定のもとでも成立するが、ここではシンプルな状況を例に出して説明する。The main symbols used in the current paper are summarized in Table \ref{symbols}.
 
@@
 
-\subsection{Hypothetical population and sampling scheme}
+\subsection{Hypothetical population}
 
 Suppose that we have a set of two populations labelled 1 and 2.
+Mating occurs within each population and parents can move to the other population after the end of the reproductive season.
+Hereafter, without loss of generality, we consider the parents that move from population 1 to population 2.
+In this study, a mature individual is called a parent even if it does not produce offspring.
+
+ある年に集団１ではN1のおやがいるとする。親とは〜。交配はN1の集団内だけで行われ、産卵シーズン終了後に一部の親が集団２に移動する。翌年に、集団２ではN2個体の親がいて、そのうちの一部は集団１から移動してきた親であるとする。移動親のうち、集団２における産卵期まで生存した数をMとする。
+
+\subsection{Sampling}
 

### 2021-05-28 latex/ms.tex
add text in Theory

@@
        & & \\
-	$n_{\rm P,1}, n_{\rm P, 2}$			& Sample number of parents in the subpopulation 1 and 2\\ 
+	$n_{\rm P,1}, n_{\rm P, 2}$			& Sample number of parents in the population 1 and 2\\ 
 		                						& \\
-	$n_{\rm O, 1}, n_{\rm O, 2}$			& Sample number of offspring in the subpopulation 1 and 2\\ 
+	$n_{\rm O, 1}, n_{\rm O, 2}$			& Sample number of offspring in the population 1 and 2\\ 
 		                						& \\
-	$N_{1}, N_{2}$						& Number of parents in the subpopulation 1 and 2 when sampled offspring are born\\
+	$N_{1}, N_{2}$						& Number of parents in the population 1 and 2 when sampled offspring are born\\
 		                						& \\
-	$M$								& Number of migrants of parents from the subpopulation 1 to the subpopulation 2\\
+	$M$								& Number of survived migrants of parents from the population 1 to population 2\\
 		                						& \\
 	$\pi_{\rm PO,1}, \pi_{\rm PO,2}$		& Probability that a randomly selected pair (mother and offspring) \\
-	                							& shares a parent-offspring relationship within the subpopulation 1 and 2\\
+	                							& shares a parent-offspring relationship within the population 1 and 2\\
 									& \\
 	$\pi_{\rm PO, bet}$					& Probability that a randomly selected pair (parent and offspring in the population 1 and 2, respectively) \\
-	                							& shares a parent-offspring relationship between the subpopulation 1 and 2\\
+	                							& shares a parent-offspring relationship between the population 1 and 2\\
 									& \\
 	$\pi_{\rm HS, bet}$					& Probability that a randomly selected pair (two offspring in the population 1 and 2) \\
-	                							& shares a half-sibling relationship between the subpopulation 1 and 2\\
+	                							& shares a half-sibling relationship between the population 1 and 2\\
 					                			& \\
-	$\lambda_{i,1}, \lambda_{j,2}$			& Expected number of surviving offspring of parent $i$ and $j$ at sampling in the subpopulation 1 and 2\\
+	$\lambda_{i,1}, \lambda_{j,2}$			& Expected number of surviving offspring of parent $i$ and $j$ at sampling in the population 1 and 2\\
 		                						& \\
@@
 		                						& \\
-	$k_{i,1}, k_{j,2}$					& Number of surviving offspring born to parent $i$ and $j$ in the subpopulation 1 and 2\\ 
+	$k_{i,1}, k_{j,2}$					& Number of surviving offspring born to parent $i$ and $j$ in the population 1 and 2\\ 
 	                							& \\
-	$H_{\rm PO, 1}, H_{\rm PO, 2}$		& Number of parent-offspring pairs observed in samples within the subpopulation 1 and 2\\ 
+	$H_{\rm PO, 1}, H_{\rm PO, 2}$		& Number of parent-offspring pairs observed in samples within the population 1 and 2\\ 
 	                							& \\
-	$H_{\rm PO, bet}$					& Number of parent-offspring pairs observed in samples between the subpopulation 1 and 2\\ 
+	$H_{\rm PO, bet}$					& Number of parent-offspring pairs observed in samples between the population 1 and 2\\ 
 	                							& \\
-	$H_{\rm HS, bet}$					& Number of half-sibling pairs observed in samples between the subpopulation 1 and 2\\ 
+	$H_{\rm HS, bet}$					& Number of half-sibling pairs observed in samples between the population 1 and 2\\ 
 	                							& \\              		
@@
 
-Suppose that we have a set of two populations labelled 1 and 2.
-Mating occurs within each population and parents can move to the other population after the end of the reproductive season.
-Hereafter, without loss of generality, we consider the parents that move from population 1 to population 2.
+Suppose that we have a set of two populations labelled 1 and 2 where random mating occurs within each population and that parents can move to the other population after the end of the reproductive season.
+Hereafter, without loss of generality, we consider the movement of parents in the direction from population 1 to population 2 once a year.
 In this study, a mature individual is called a parent even if it does not produce offspring.
 
-ある年に集団１ではN1のおやがいるとする。親とは〜。交配はN1の集団内だけで行われ、産卵シーズン終了後に一部の親が集団２に移動する。翌年に、集団２ではN2個体の親がいて、そのうちの一部は集団１から移動してきた親であるとする。移動親のうち、集団２における産卵期まで生存した数をMとする。
+Suppose there are $N_1$ parents in the population 1 at the beginning of year and there are $N_2$ parents in the population 2 at the beginning of the next year.
+There are $M$ survived parents at the beginning of the next year that are moved from population 1 to population 2.
+各親は繁殖ポテンシャルに従って、子供を残すとしよう。For the explanation purpose, lambdaは全ての親で一定とするが、この仮定をゆるくしても多くの場合我々の議論は成立する。
+
+どのように子供を産むのか。我々のモデルは、フレキシブルな仮定に対応できるが詳細は付録に
+
+Figure \ref{cartoon} illustrates an example of kinship relationships and movements of parents between populations.
 
@@
 
-and there are migrant individuals between the two subpopulations.
+and there are migrant individuals between the two populations.
 also no population subdivision or spatial struc- ture.
@@
 
-\subsection{Efficient use of kinship pairs found between subpopulations}
+\subsection{Efficient use of kinship pairs found between populations}
 
@@
 
-\subsection{Parent number can be estimated by PO pairs found within a subpopulation}
+\subsection{Parent number can be estimated by PO pairs found within a population}
 

### 2021-06-22 latex/ms.tex
modify Fig and count parameters
write theory section, #6

@@
 \section{Theory}\label{sec2}
-In this section, we derivate the estimators of migrant number and migration rates using HS pairs or PO pairs found between two populations.
-While the estimators can hold under complex assumptions for reproduction theoretical foundation for estimating
-このセクションでは、migrantやmigration rateの推定量を導出する。導出された推定量は、付録にある通りフレキシブルな仮定のもとでも成立するが、ここではシンプルな状況を例に出して説明する。The main symbols used in the current paper are summarized in Table \ref{symbols}.
+In this section, we present the theoretical foundation for estimating a migrant number and a migration rate using HS or PO pairs, which are found between two populations with a different sample timing.
+While the estimators can hold under flexible assumptions for reproduction (see {\bf Appendix}), here we assume a relatively simple situation for explanation purposes.
+It should be noted that the formulation of the estimators, presented in Equations 4-5 and 7-8, is a function with parent numbers in the two populations; in the next section, we provide the treatment for estimating the unknown parent numbers from genetic dataset which is used for obtaining HS or PO pairs.
+The main symbols used in the current paper are summarized in Table \ref{symbols}.
 
@@
 Sampled individuals are denoted with squares.
-In this example, $M=6$, }
+Input parameters in this example: $n_{\rm P, 1}=4$, $n_{\rm P, 2}=4$, $n_{\rm O, 1}=4$, $n_{\rm O, 2}=4$, $N_{1}=16$, $N_{2}=14$, and $M=6$.
+The numbers of kinship pairs: $H_{\rm PO, 1}=1$, $H_{\rm PO, 2}=1$, $H_{\rm PO, bet}=1$, and $H_{\rm HS, bet}=2$.	}
 		\label{cartoon}

### 2021-06-24 latex/ms.tex
write theory section something, #6
remove Wiley-formed tex

@@
-\documentclass[AMA,STIX1COL]{WileyNJD-v2}
-\usepackage{moreverb}
-\usepackage{lineno}
-\linenumbers
-\usepackage[doublespacing]{setspace}
-
+\documentclass[12pt, English]{article}
+\usepackage{geometry}
+\geometry{verbose,letterpaper,tmargin=2.54cm,bmargin=2.54cm,lmargin=2.54cm,rmargin=2.54cm}
+%\usepackage{apacite}
+\usepackage[natbibapa]{apacite}
+%\renewcommand{\APACrefYearMonthDay}[3]{\APACrefYear{#1} 
+%  \cite<pre>[post]{key}
 \usepackage{amsfonts}
@@
 \usepackage{amsmath}
-
-\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08em
-T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-
-\articletype{Research article, \today}%
-
-\received{<day> <Month>, <year>}
-\revised{<day> <Month>, <year>}
-\accepted{<day> <Month>, <year>}
-
-%\raggedbottom
-
+\usepackage{comment}
+\usepackage{enumerate}
+\usepackage{graphicx}
+\usepackage{boxedminipage}
+\usepackage{oldgerm}
+\usepackage{setspace}
+\usepackage{booktabs}
+\usepackage{wrapfig}
+\usepackage{indentfirst}
+\usepackage{mathptmx}
+\usepackage{setspace}
+\usepackage{lscape} 
+\usepackage[mathlines]{lineno}
+\renewcommand{\ttdefault}{mathptmx}
+\usepackage[latin9]{inputenc}
+\usepackage{bm}
+\usepackage{relsize}
+\usepackage[normalem]{ulem} %%
+%\linenumbers
+\usepackage{bm}
+\setlength{\parindent}{20pt}
+\usepackage[labelformat=empty,labelsep=none]{caption}
+\usepackage[singlelinecheck=false]{caption}
+\usepackage{color}
+\def\RED#1{\textcolor{black}{#1}} %% 
+\def\BLUE#1{\textcolor{blue}{#1}} %% 
 \begin{document}
 
-\title{Estimating migration rates for iteroparous species using kinship pairs found between populations\protect\thanks{Running head line: Estimating migration rates using kinship pairs}}
-
-\author[1]{Tetsuya Akita}
-\authormark{Akita}
-
-\address[1]{\orgdiv{Fisheries Data Sciences Division}, \orgname{Fisheries Resources Institute}, \orgaddress{\state{Kanagawa}, \country{Japan}}}
-
-\corres{*Tetsuya Akita, Fisheries Data Sciences Division, Fisheries Resources Institute, FRA, 236-8648 Kanagawa, Japan. \email{akitatetsuya1981@affrc.go.jp}}
-
-%\presentaddress{Present address}
-
-\abstract[Abstract]{The Abstract must not exceed 350 words and should list the main results and conclusions, using simple, factual, numbered statements:
-
-Point 1: set the context for and purpose of the work;
-
-Point 2: indicate the approach and methods;
-
-Point 3: outline the main results;
-
-Point 4: identify the conclusions and the wider implications.
-
-1. aaa\\
-2. bbb
-
-本ノートでは，多回繁殖(iteroparity)する種を対象として，半兄弟ペア数から親魚による２つのサブ集団間の移動率を推定する理論($\hat{M}=N_1N_2H_{\rm obs}/(4n_1n_2)$)を紹介する。この推定式は、親をサンプルする通常の標識放流と同じである。もし、繁殖ポテンシャルの分布が集団間で異なっていても上記の式で問題ないことを示した。一方，サンプル数としては$\sqrt {N}$以上のオーダーが求められる。}
-
-\keywords{Close-kin mark recapture; Half-sibling; Population structure}
-
+\title{Estimating migration rates for iteroparous species using kinship pairs found between populations}
+\author{
+Tetsuya Akita$^{a}$\thanks{
+\emph{Corresponding author}:
+    Fisheries Resources Institute, Fisheries Research and Education Agency, Kanagawa 236-8648, Japan.
+    E-mail: akitatetsuya1981@affrc.go.jp} \\ 
+   \small $^{a}$Fisheries Resources Institute, Fisheries Research and Education Agency, \\
+   \small Kanagawa, 236-8648, Japan.
+   }
+\date{Manuscript Intended for \emph{Methods in Ecology and Evolution}, \today}
 \maketitle
 
-%\footnotetext{\textbf{Abbreviations:} ANA, anti-nuclear antibodies; APC, antigen-presenting cells; IRF, interferon regulatory factor}
+\begin{abstract}
+本ノートでは，多回繁殖(iteroparity)する種を対象として，半兄弟ペア数から親魚による２つのサブ集団間の移動率を推定する理論($\hat{M}=N_1N_2H_{\rm obs}/(4n_1n_2)$)を紹介する。この推定式は、親をサンプルする通常の標識放流と同じである。もし、繁殖ポテンシャルの分布が集団間で異なっていても上記の式で問題ないことを示した。一方，サンプル数としては$\sqrt {N}$以上のオーダーが求められる。
+\\
+\end{abstract}
+\textbf{Key words:} effective population size; sibship assignment; overdispersed reproduction; close-kin mark-recapture\\
+\textbf{Running head:} Estimating migration rates using kinship pairs\\
 
-\section{Introduction}\label{sec1}
+\pagebreak
+\begin{spacing}{1.9}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%FIGURE S1%%%
+\newcommand{\NeNbias}{S1}
+%%%%%%%%%%%
+
+%%%FIGURE S2%%%
+\newcommand{\Nebias}{S2}
+%%%%%%%%%%%
+
+%%%FIGURE S3%%%
+\newcommand{\Ninvbias}{S3}
+%%%%%%%%%%%
+
+%%%FIGURE S4%%%
+\newcommand{\NeNcv}{S4}
+%%%%%%%%%%%
+
+%%%FIGURE S5%%%
+\newcommand{\Necv}{S5}
+%%%%%%%%%%%
+
+%%%FIGURE S6%%%
+\newcommand{\Ninvcv}{S6}
+%%%%%%%%%%%
+
+\section{INTRODUCTION}
 
@@
 
-\renewcommand{\arraystretch}{0.6}
-\begin{table}[tb]
-\begin{center}
-   \caption[]{The list of mathematical symbols employed in the main text}
-    \textbf {}\\[-4mm]
-    \begin{tabular}{llc} \hline
-       & & \\
-	$n_{\rm P,1}, n_{\rm P, 2}$			& Sample number of parents in the population 1 and 2\\ 
-		                						& \\
-	$n_{\rm O, 1}, n_{\rm O, 2}$			& Sample number of offspring in the population 1 and 2\\ 
-		                						& \\
-	$N_{1}, N_{2}$						& Number of parents in the population 1 and 2 when sampled offspring are born\\
-		                						& \\
-	$M$								& Number of survived migrants of parents from the population 1 to population 2\\
-		                						& \\
-	$\pi_{\rm PO,1}, \pi_{\rm PO,2}$		& Probability that a randomly selected pair (mother and offspring) \\
-	                							& shares a parent-offspring relationship within the population 1 and 2\\
-									& \\
-	$\pi_{\rm PO, bet}$					& Probability that a randomly selected pair (parent and offspring in the population 1 and 2, respectively) \\
-	                							& shares a parent-offspring relationship between the population 1 and 2\\
-									& \\
-	$\pi_{\rm HS, bet}$					& Probability that a randomly selected pair (two offspring in the population 1 and 2) \\
-	                							& shares a half-sibling relationship between the population 1 and 2\\
-					                			& \\
-	$\lambda_{i,1}, \lambda_{j,2}$			& Expected number of surviving offspring of parent $i$ and $j$ at sampling in the population 1 and 2\\
-		                						& \\
-	$\lambda_{i, M}$					& Expected number of surviving offspring of migrant $i$ at sampling\\
-		                						& \\
-	$k_{i,1}, k_{j,2}$					& Number of surviving offspring born to parent $i$ and $j$ in the population 1 and 2\\ 
-	                							& \\
-	$H_{\rm PO, 1}, H_{\rm PO, 2}$		& Number of parent-offspring pairs observed in samples within the population 1 and 2\\ 
-	                							& \\
-	$H_{\rm PO, bet}$					& Number of parent-offspring pairs observed in samples between the population 1 and 2\\ 
-	                							& \\
-	$H_{\rm HS, bet}$					& Number of half-sibling pairs observed in samples between the population 1 and 2\\ 
-	                							& \\              		
-	\hline
-    \end{tabular}
-    \label{symbols} 
-\end{center} 
-\end{table}
-\renewcommand{\arraystretch}{1}
-
 \subsection{Hypothetical population}
@@
 Suppose that we have a set of two populations labelled 1 and 2 where random mating occurs within each population and that parents can move to the other population after the end of the reproductive season.
-Hereafter, without loss of generality, we consider the movement of parents in the direction from population 1 to population 2 once a year.
-In this study, a mature individual is called a parent even if it does not produce offspring.
+Hereafter, without loss of generality, we consider the movement of parents in the direction from population 1 to population 2 and focus on the migration number or rate, and that is what we attempt to estimate.
+In this framework, two reproductive seasons (hereafter, we call them "the first year" and "the second year") are enough to estimate it.
 
-Suppose there are $N_1$ parents in the population 1 at the beginning of year and there are $N_2$ parents in the population 2 at the beginning of the next year.
-There are $M$ survived parents at the beginning of the next year that are moved from population 1 to population 2.
-各親は繁殖ポテンシャルに従って、子供を残すとしよう。For the explanation purpose, lambdaは全ての親で一定とするが、この仮定をゆるくしても多くの場合我々の議論は成立する。
+Suppose there are $N_1$ parents in the population 1 at the beginning of the first year.
+Each parent produces offspring in which the number is determined by the parent's reproductive potential, denoted by $\lambda_{i,1}$ ($i=1,2,\ldots,N_1$).
+After the reproductive season, part of the parents would start to moving towards the population 2; $M$ survived migrants arrive in the population 2 so that there are $N_2$ parents in the population 2 at the beginning of the second year ($M<N_2$).
+Similar to the population, $N_2$ parents produce offspring in which the number is determined by $\lambda_{j,2}$ ($j=1,2,\ldots,N_2$).
 
 どのように子供を産むのか。我々のモデルは、フレキシブルな仮定に対応できるが詳細は付録に
+In this study, a mature individual is called a parent even if it does not produce offspring.
 
@@
 
-%%%FIGURE 1%%%
-\begin{figure}[!h]
-	\begin{center}
-		\includegraphics[width=0.3\textwidth]{/Users/akita/Dropbox/research/close_kin/Mig/Figs/cartoon.eps}
-		\caption{Example of relationships between mothers and their offspring number.
-The open, gray, and filled circles represent mothers, their eggs, and their offspring, respectively.
-The area of an open circle indicates the degree of reproductive potential of each mother (i.e., $\lambda_i$).
-The dotted and thin arrows denote mother--egg and egg--offspring relationships, respectively.
-The symbol x denotes a failure to survive at sampling.
-Sampled individuals are denoted with squares.
-Input parameters in this example: $n_{\rm P, 1}=4$, $n_{\rm P, 2}=4$, $n_{\rm O, 1}=4$, $n_{\rm O, 2}=4$, $N_{1}=16$, $N_{2}=14$, and $M=6$.
-The numbers of kinship pairs: $H_{\rm PO, 1}=1$, $H_{\rm PO, 2}=1$, $H_{\rm PO, bet}=1$, and $H_{\rm HS, bet}=2$.	}
-		\label{cartoon}
-	\end{center}
-\end{figure}
-%%%%%%%%%%%
+\subsection{HSP-based model}
 
-\subsection{HSP-based model}
+Here we consider the probability that two offspring sampled in the population 1 and 2 share an HS relationship with an arbitrary mother or father, denoted by $\pi_{\rm HS, bet}$.
+
+For the explanation purpose,
+
+lambdaは全ての親で一定とするが、この仮定をゆるくしても多くの場合我々の議論は成立する。
+
+Assuming that every fathers in the population 1 has a same reproductive potential, どの母親も同じような繁殖ポテンシャルを持つと仮定 すると，移動する母親の子供をサブ集団1でサンプルする確率は$rM/rN$...となる。
 
@@
 
-\section{Applications}\label{sec3}
-
 \subsection{Efficient use of kinship pairs found between populations}
@@
 サンプル数の少なさを補えるかも。
+
+\section{Applications}\label{sec3}
 
@@
 
-\begin{comment}%%%%%%%%%%%%%%%
-まず最初に，最もシンプルなモデルを考える。$t$年にサブ集団１にいる$N_{1,t}$個体の母親を考えよう。$t$年に子供を産んだ後，$N_{1,t}$個体のうち$M_{1\to2}$個体がサブ集団２に移動し，$t+1$年にサブ集団２にいる母個体$N_{2,t+1}$の一部として子供を産むとする。この時，サブ集団１から$t$年に産まれた子供とサブ集団２から$t+1$年に産まれた子供が，母を共有する兄弟(Maternal half Sibling, MHS)である確率$\pi_{\rm b,1\to2}$を考える。どの母親も同じような繁殖ポテンシャルを持つと仮定すると，移動する母親の子供をサブ集団１でサンプルする確率は$M_{1\to2}/N_{1,t}$となる。同様に，移動する母親の子供をサブ集団２においてサンプルする確率は$M_{1\to2}/N_{2,t+1}$である。それぞれでサンプルした子供の母親が同一である確率は$1/M_{1\to2}$であることより，サンプルした２個体がMHSペアとなる確率が以下のように得られる。
-\begin{align}
-\pi_{\rm b,1\to2} &= \frac{M_{1\to2}}{N_{1,t}} \frac{M_{1\to2}}{N_{2,t+1}} \frac{1}{M_{1\to2}} \nonumber\\
-&= \frac{M_{1\to2}}{N_{1,t}N_{2,t+1}}
-\label{1-1}
-\end{align}
-サブ集団１からサブ集団２に移動する割合$m_{1\to2}$を導入することで，上式は
-\begin{align}
-\pi_{\rm b,1\to2} &= \frac{m_{1\to2}}{N_{2,t+1}}
-\label{1-2}
-\end{align}
-と書ける。$M_{1\to2} = m_{1\to2}N_{1,t}$とした。$m_{1\to2}$には移動だけでなく$t+1$年の産卵までの生存確率が含まれている点に注意。
+The estimation of the ratio of the contemporary effective population size to the census size ($N_{\rm e}/N$) has attracted much research attention for providing information about a current population, especially in the context of conservation biology and wildlife management \cite[]{Palstra_2012,FRANKHAM201456}.
+Small $N_{\rm e}/N$ demonstrates large variance in reproductive success \cite[]{Wang:2016aa, JFB:JFB13143, Akita_2019}, resulting from the variance of reproductive potential \cite[e.g., the big old fat fecund female fish hypothesis;][]{Hixon_2014} or from the situation in which only some families successfully reproduce \cite[referred to as the ``Sweepstakes reproductive success'' hypothesis,][]{hedgecock2011sweepstakes}.
+Moreover, if $N_{\rm e}/N$ is invariant across years, then $N_{\rm e}$ may behave like an index of $N$, and vice versa \cite[]{luikart2010estimation}.
+However, if $N_{\rm e}/N$ fluctuates across years, the trends can clarify the interpretation of environmental and/or anthropological factors, causing the variance of reproductive potential, family-correlated survivorship, or fluctuating population dynamics.
+Besides, low precision and/or large bias for estimating $N_{\rm e}/N$ may lead to a wrong interpretation of the population \cite[]{Tallmon:2012aa}.
 
-MHSペアとなる確率が得られれば，サンプル数に応じて見つかるMHSペア$H_{1\to2}$の期待値が得られる。
-\begin{align}
-\mathbb{E}[H_{1\to2}] &= \pi_{\rm b,1\to2} n_{1,t} n_{2,t+1} \nonumber\\
-&= \frac{m_{1\to2}n_{1,t} n_{2,t+1}} {N_{2,t+1}}
-\label{1-3}
-\end{align}
-$n_{1,t}, n_{2,t+1}$は，それぞれサブ集団１（$t$年）でのサンプル数，サブ集団２（$t+1$年）でのサンプル数である。この結果から，平均的にみて少なくとも１ペア以上を見出すには，(親魚尾数)の平方根のオーダー以上のサンプル数が要求されることがわかる。以上より，見出されたMHSペア数から母親の移動率に関する線形推定量が得られる。
-\begin{align}
-\widehat{m_{1\to2}} &= \frac{N_{2,t+1} H_{1\to2,{\rm obs}} } {n_{1,t}n_{2,t+1}}
-\label{1-4}
-\end{align}
-ハットは推定量を表し，obsの添字は観測値であることを表す。
+The estimation of $N_{\rm e}/N$ has been performed by utilizing the estimated values of contemporary effective population size ($N_{\rm e}$) and census size ($N$), unless complete pedigree data and/or full census data are available.
+Additionally, there are numerous methods for estimating $N_{\rm e}$ from genetic markers \cite[][and the references contained therein]{Wang:2016aa}.
+There are also numerous methods for estimating $N$, such as a mark-recapture method or population dynamics modeling with survey data \cite[e.g.,][]{seber1982estimation,quinn1999quantitative,kery2011bayesian,methot2013stock}.
+It is known that there are large variations in both estimators; thus, their combination (i.e., the estimator of $N_{\rm e}/N$) also shows large variation \cite[]{Palstra_2012,Marandel_2018}.
+There is currently a little theoretical foundation for the estimator of $N_{\rm e}/N$, indicating no guidance for a sample size to ensure the required accuracy and precision.
 
-\subsection{Two-way movement}
+Close-kin mark-recapture (CKMR) is a recently developed method for estimating $N$ that utilizes the information about kinship in a sample.
+This was possible owing to the recent advances in genetic methods for kinship determination \cite[]{Bravington_2016,bravington2016close,skaug2017parent,Hillary_2018} although similar methods have been proposed in the beginning of the 21st century \cite[]{nielsen2001statistical, pearse2001genetic, julius2001allele}.
+Besides, the rationale is that the presence of a kinship pair in the sample is analogous to the recapture of a marked individual in mark-recapture.
+Kinship pairs in the sample are less likely to be observed in larger populations; thus, the number of kinship pairs may reflect $N$.
+While the original CKMR is designed to estimate adult abundance (i.e., $N$), the monitoring data for CKMR also produce the estimator of $N_{\rm e}$ by detecting half-sibling (HS) pairs within the same cohort \cite[]{Akita_2019}.
+This kinship-oriented estimation of $N_{\rm e}$ was presented in the context of the sibship assignment method \cite[]{wang2009new} and is expected to provide a much more accurate estimator as kinship determination becomes more accurate.
 
-次に，反対方向の移動について考える。すなわち，$t$年にサブ集団２にいる$N_{2,t}$個体の母親から，$M_{1\to2}$個体が$t+1$年にサブ集団１へ移動すること考えよう。これまで同様に考えて，MHSペアとなる確率は，
-\begin{align}
-\pi_{\rm b,2\to1} &= \frac{m_{2\to1}}{N_{1,t+1}}
-\label{2-1}
-\end{align}
-のようになり，移動率に関する推定量
-\begin{align}
-\widehat{m_{2\to1}} &= \frac{N_{1,t+1} H_{2\to1,{\rm obs}} } {n_{2,t}n_{1,t+1}}
-\label{2-2}
-\end{align}
-が得られる。すなわち，移動が一方向であろうが双方向であろうが，各方向の移動率に関する推定量は式\ref{1-4}と式\ref{2-2}から独立に得られる。したがって，以降の導出ではサブ集団１からサブ集団２に移動する個体についてだけ考え，添字を省略する。例えば，$N_1$という記載は，$t$年に親魚として存在した個体数を表す。
+In this study, we propose a new method for estimating the ratio of contemporary effective mother size to the census size ($N_{\rm e,m}/N_{\rm m}$) in a population, as a proxy of $N_{\rm e}/N$.
+Assuming that kinships are genetically detected without any error, this method is based on the numbers of maternal-sibling (MS) and mother--offspring (MO) pairs in a sample.
+Sampling is completed at a single breeding time; sampling offspring within the same cohort and mothers probably shares MO relationship with sampled offspring.
+Our model provides a nearly unbiased estimator of $N_{\rm e,m}/N_{\rm m}$ that explicitly incorporates two types of overdispersed reproduction \cite[i.e., parental and nonparental variations;][]{Akita_2019}, making it possible to target a species that shows iteroparity (i.e., multiple reproductive cycles during the lifetime) and/or sweepstakes reproductive success.
+This estimator applying an iteroparous species corresponds to the estimator of the ratio of contemporary effective breeding mother size to the census size, $N_{\rm b,m}/N_{\rm m}$.
+First, we explain the modeling assumption and sampling scheme.
+Then, we analytically determine (nearly) the unbiased estimators of $N_{\rm e,m}$, $ 1/N_{\rm m}$, and $N_{\rm e,m}/N_{\rm m}$, which are based on the numbers of MS and/or MO pairs.
+Finally, by running an individual-based model, we investigate the performance of the estimator and provide a guide for a sample size.
+It is noteworthy that our modeling framework can be applied to diverse animal species.
+However, the description of the model focuses on fish species, which are presently the best candidate target of our proposed method.
 
-\subsection{Two-sex}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{THEORY}\label{theory}
 
-ここまでは、母親を介した兄弟ペアと、母親の個体数およびその移動について考えてきた。しかしながら、母親を介した兄弟か父親を介した兄弟かを見分けるには、ミトコンドリアの情報を用いた類推が必須である点、当歳魚のサンプル数が同程度でも区別しない半兄弟ペアの半数程度しか発見されない点などから、実際の応用では区別しない半兄弟ペアを用いるほうが望ましい。そこで、まずは性比=1:1（すなわち，$N_{\rm male}=N_{\rm female}=N_1/2$かつ$M_{\rm male}=M_{\rm female}=M/2$）でランダム交配を仮定した集団を考えよう。この時、サブ集団１でサンプルした当歳魚の親が移動する親個体である確率は$M_{\rm male}/N_{\rm male} + M_{\rm female}/N_{\rm female}=2M/N_1$となる。同様に，移動した親の子供をサブ集団２においてサンプルする確率は$2M/N_2$であることから，
-\begin{align}
-\pi &= \frac{2M}{N_{1}} \frac{2M}{N_{2}} \frac{1}{M} \nonumber\\
-&= \frac{4M}{N_{1}N_{2}}
-\label{3-1}
-\end{align}
-が得られる。その結果，移動率の推定値は新たに係数4が分母に加わって
-\begin{align}
-\widehat{m} &= \frac{N_{2} H_{\rm obs} } {4n_{1}n_{2}}
-\end{align}
-となる。
+In this section, we present the theoretical foundation for estimating $N_{\rm e,m}/N_{\rm m}$.
+The estimator is based on previous studies that provides the estimator of $N_{\rm e,m}$ \cite[]{Akita_2019} and $1/N_{\rm m}$ \cite[]{Akita2018}.
+The main contribution of this paper is formulation of the estimator of $N_{\rm e,m}/N_{\rm m}$, presented in Eq.~\ref{NeN_hat2}.
+The main symbols used in the current paper are summarized in {\bf Table \ref{symbols}}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Hypothetical population}
 
-ここでは応用例として，３年間にわたって２つのサブ集団からサンプルされた当歳魚から見出される半兄弟ペアをもとに，個体数($N$)・移動率($m$)・生存率($s$)を推定する理論的な枠組みを提示する。サブ集団１に生息する親魚数を、$N_1(t), N_1(t+1), N_1(t+2)$のように表記し、他のパラメータについても同様とする。個体数については６つのパラメータ、移動率および生存率は４つのパラメータとなり、合計１４のパラメータが考えられる（$t+2$年の移動率および生存率は含まれない点に注意）。まずは、これら１４個のパラメータは独立に決まるとしよう（すなわち、$N_1(t)$と$N_1(t+1)$は無関係で、$s_1(t)$と$s_1(t+1)$は独立に決める、など）。なお、この応用例では、移動する親魚は繁殖ポテンシャルによらずに決まると仮定して、式\ref{4-1}を用いることにしよう。また、全ての親魚は、年をまたぐごとに、1)サブ集団を移動して産卵するか（確率：$m$）、2)同じサブ集団に留まって産卵するか（確率：$s$）、3)死亡するか（確率：$1-m-s$）、のいずれかのイベントを経験するとする。
+We suppose that there is a hypothetical population comprising $N_{\rm m}$ mothers and there is also no population subdivision or spatial structure.
+In this study, a mature female is called a mother even if she does not produce offspring.
+For mathematical tractability, we assume that only one spawning ground exists in which the mothers remain for the entire spawning season.
+Following \cite{Akita_2019}, our modeling framework employs two types of overdispersed reproduction: parental and nonparental variations.
+Thus, the former indicates a variation caused by the mother's covariates, such as age, weight, and residence time on the spawning ground, while the latter indicates a variation caused by nonrandom stochastic events during a series of reproductive episodes, which are independent of the mother's covariates, such as family-correlated survivorship or the mating behavior effects (e.g., competition for males/females and correlation between mating opportunities of the mother and the number of her offspring).
+{\bf Figure~1} illustrates a schematic diagram of the effects of parental and nonparental variations exemplified by age-dependent reproduction and family-correlated survival on kinship relationships in a population.
+Detailed definitions of parental and nonparental variations are stated in \cite{Akita_2019}.
+{\bf Appendix A} provides the theoretical foundation of both parental and nonparental variations in reproduction.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Sampling}
 
-今回新たに開発した移動に関する関係式について、以下の６種類の親魚に関するその子供（当歳魚）ペアがありえる：
-\begin{enumerate}
-  \item $N_1(t)\to N_2(t+1)$
-  \item $N_1(t)\to N_2(t+2)$
-  \item $N_1(t+1)\to N_2(t+2)$
-  \item $N_2(t)\to N_1(t+1)$
-  \item $N_2(t)\to N_1(t+2)$
-  \item $N_2(t+1)\to N_1(t+2)$
-\end{enumerate}
-右向きの矢印$\to$は、興味ある親魚が年を跨いだ後どのサブ集団に属しているかを表している。１番目を例にとると、$t$年にサブ集団１から、$t+1$年にサブ集団２からそれぞれ当歳魚をサンプルすることを意味する。加えて、同じサブ集団から年を跨いで見つかる半兄弟ペアに基づく関係式についても、以下の６種類が考えられる：
-\begin{enumerate}
-\setcounter{enumi}{6}
-  \item $N_1(t)\to N_1(t+1)$
-  \item $N_1(t)\to N_1(t+2)$
-  \item $N_1(t+1)\to N_1(t+2)$
-  \item $N_2(t)\to N_2(t+1)$
-  \item $N_2(t)\to N_2(t+2)$
-  \item $N_2(t+1)\to N_2(t+2)$
-\end{enumerate}
-以上の、合計１２種類の式を連立できることを示した。最大１４個のパラメータが必要となるのであったが、パラメータ数を応用先に応じて適宜減少させることができる場合、興味あるパラメータを推定することができる。
+To obtain the estimator of $N_{\rm e,m}/N_{\rm m}$, we utilize the number of MS and MO pairs observed in a sample.
+For the mathematical tractability, only one reproductive season is targeted for sampling.
+Thus, the sampling method does not affect our modeling framework whether it is invasive or noninvasive.
+In the population, $n_{\rm M}$ mothers are randomly sampled immediately after the end of the reproductive season.
+Additionally, in the population, $n_{\rm O}$ offspring are also randomly sampled.
+The numbers of MS and MO pairs are determined by pairwise comparison of all the sample individuals (${}_{n_{\rm O}}\mathrm{C}_2$ and $n_{\rm M}n_{\rm O}$ comparisons, respectively).
+As depicted in {\bf Fig~\ref{example}}, six offspring and three mothers are sampled and two MS and three MO pairs are observed.
+In our modeling framework, if an MS pair also shares a paternal-sibling (PS) relationship, we count it as an MS pair and ignore the existing full-sibling (FS) relationship.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Linking $N_{\rm e,m}/N_{\rm m}$ to kinship relationships}
 
-ちなみに、同一年内に同じサブ集団内で見つかるMHSペアについては、有効集団サイズの情報（正確には有効繁殖サイズ、Effective breeding size）は持っているが、センサスサイズに関するダイレクトな情報は持っていない点に注意。
-\end{comment}%%%%%%%%%%%%%%%
+In this subsection, we provide the theoretical foundation for understanding how $N_{\rm e,m}/N_{\rm m}$ is associated with kinship relationships in a population, based on work presented in previous studies.
+The rationale is that the observed number of MS and MO pairs have information about $N_{\rm e,m}$ and $N_{\rm m}$, respectively, as noted below.
 
-\section{Results and Discussion}\label{sec4}
+First, we consider the relationship between the number of MS pairs and $N_{\rm e,m}$. \cite{Akita_2019} defined the contemporary effective mother size as follows: 
+\begin{equation}
+N_{\rm e,m} = \frac{1}{\pi_{\rm MS}},
+\label{Ne}
+\end{equation}
+where $\pi_{\rm MS}$ denotes the probability that two offspring share an MS relationship with an arbitrary mother.
+This definition is related to the inbreeding effective population size \cite[]{nordborg2002separation,wang2009new}.
+When sampling from a single cohort in a population with overlapping generations, the effective mother size in our definition corresponds to the effective breeding mother size per breeding-time unit (e.g., year), which produces the single cohort and is denoted by $N_{\rm b,m}$ \cite[]{waples1991genetic}.
+Hereafter, the description of the model focuses on species with discrete generations; thus, we use $N_{\rm e,m}$ to denote the contemporary effective mother size, although $N_{\rm b,m}$ is the appropriate notation in the left-hand side of Eq.~\ref{Ne} when the target species is iteroparous with overlapping generations, as exemplified in {\bf Appendix B}.
 
-オーダーは$m\approx0.1$程度を想定。これよりもずっと小さければ、遺伝的に異なる系群と考えられFstも大きく出るので、ベイズアスなどから推定できるだろう。一方、その場合はサンプル数が大量になり、今回提案した方法は向かない。
+Given the total mother number and the degree of overdisepered reproduction in the population, \cite{Akita_2019} derived $\pi_{\rm MS}$, which is approximately given by
+\begin{equation}
+\pi_{\rm MS} \approx \frac{c}{N_{\rm m}+c-1},
+\label{pi_MS}
+\end{equation}
+where $c$ indicates combined effect of both parental and nonparental variations and satisfies $\ge1$.
+Without either parental or nonparental variation (i.e., $c\to1$, see details in {\bf Appendix C}), $\pi_{\rm MS}$ converges to $1/N_{\rm m}$, corresponding to the Poisson variance in reproduction for all mothers.
+The mathematical description of $c$ is briefly summarized in {\bf Appendix C}.
 
-\section{ACKNOWLEDGEMENTS}
+Next, we consider the relationship between the number of MO pairs and $N_{\rm m}$.
+It is natural to consider that the probability of a randomly sampled mother and her offspring sharing an MO relationship (denoted by $\pi_{\rm MO}$) can be associated with the total mother number, given by
+\begin{equation}
+\pi_{\rm MO} = \frac{1}{N_{\rm m}}.
+\label{pi_MO}
+\end{equation} 
+It is noteworthy that $\pi_{\rm MO}$ is independent of the distribution of the offspring number \cite[]{Akita2018}.
 
-The author thanks MV Bravington for motivating me to pursue this research topic. This work was supported by JSPS KAKENHI Grant Number 19K06862 and 20H03012.
+Together with Eqs.~\ref{Ne} and \ref{pi_MO}, we finally obtain the ratio of the effective mother size to census size as follows: 
+\begin{equation}
+\frac{N_{\rm e,m}}{N_{\rm m}} = \frac{\pi_{\rm MO}}{\pi_{\rm MS}},
+\label{NeN}
+\end{equation}
+indicating that $N_{\rm e,m}/N_{\rm m}$ is associated with kinship relationships (i.e., MS and MO) in a population.
+In other words, when $1/\pi_{\rm MS}$ and $\pi_{\rm MO}$ is estimated from observed MS and MO pairs, respectively, the ratio can also be estimated.
+Meanwhile, \cite{Akita_2019} obtained an alternative formulation of the ratio using Eqs.~\ref{Ne} and \ref{pi_MS}:
+\begin{eqnarray}
+\frac{N_{\rm e,m}}{N_{\rm m}} &=& \frac{1}{\pi_{\rm MS}} \frac{1}{N_{\rm m}} \nonumber\\
+&\approx& \frac{1}{c},  
+\label{NeN}
+\end{eqnarray}
+where $N_{\rm m} \gg 1$ is assumed for approximation. This theoretical connection indicates that estimating $N_{\rm e,m}/N_{\rm m}$ corresponds to estimating $1/c$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Estimator of $N_{\rm e,m}/N_{\rm m}$}
+
+This subsection proposes the estimator of $N_{\rm e,m}/N_{\rm m}$  as follows:
+\begin{equation}
+\widehat{\left(\frac{N_{\rm e,m}}{N_{\rm m}}\right) } = \widehat{N_{\rm e,m}}\widehat{\left(\frac{1}{N_{\rm m}}\right)}.
+\label{NeN_hat1}
+\end{equation}
+A ``hat'' denotes the estimator of a variable in this study.
+The requisite condition that satisfies Eq.~\ref{NeN_hat1} is independent of $\widehat{N_{\rm e,m}}$ and $\widehat{1/N_{\rm m}}$.
+This property will be shown later in this subsection.
+\cite{Akita_2019} derived the nearly unbiased estimator of $N_{\rm e,m}$, which is given by
+\begin{eqnarray}
+\widehat{N_{\rm e,m}} &=& \widehat{\left(\frac{1}{\pi_{\rm MS}}\right)}\nonumber\\
+ &=& \frac{\binom{n_{\rm O}}{2}+1}{H_{\rm MS}^{\rm obs}+1},
+\label{Ne_hat}
+\end{eqnarray}
+where $H_{\rm MS}^{\rm obs}$ denotes the observed number of MS pairs in a sample.
+This estimator works well unless $n_{\rm O}$ is very small, which is based on the idea that the observation of $1/(H_{\rm MS} + 1)$ approximately provides a linear estimator of $N_{\rm e,m}$.
+
+Next, we consider to estimate $1/N_{\rm m}$ by estimating $\pi_{\rm MO}$.
+By definition of $\pi_{\rm MO}$, we can set its estimator by $H_{\rm MO}^{\rm obs}/(n_{\rm M}n_{\rm O})$, where $H_{\rm MO}^{\rm obs}$ denotes the observed number of MO pairs in a sample.
+Thus, using Eq.~\ref{pi_MO}, the estimator can be determined as follows:
+\begin{eqnarray}
+\widehat{\left(\frac{1}{N_{\rm m}}\right)} &=& \widehat{\pi_{\rm MS}}\nonumber\\
+ &=& \frac{H_{\rm MO}^{\rm obs} } {n_{\rm M}n_{\rm O}}.
+\label{N_inv_hat}
+\end{eqnarray}
+Equation~\ref{N_inv_hat} provides a linear estimator of $1/N_{\rm m}$, thus this estimator also works well.
+Meanwhile, the inverse of the right-hand side in Eq.~\ref{N_inv_hat} is a standard (moment) estimator of $N_{\rm m}$ in the context of CKMR \cite[]{bravington2016close}.
+
+Finally, substituting $\widehat{N_{\rm e,m}}$ (Eq.~\ref{Ne_hat}) and $\widehat{1/N_{\rm m}}$ (Eq.~\ref{N_inv_hat}) into Eq.~\ref{NeN_hat1}, we obtain the estimator of $N_{\rm e,m}/N_{\rm m}$ as follows:
+\begin{equation}
+\widehat{\left(\frac{N_{\rm e,m}}{N_{\rm m}}\right) } = \frac{\binom{n_{\rm O}}{2}+1}{H_{\rm MS}^{\rm obs}+1} \frac{H_{\rm MO}^{\rm obs} } {n_{\rm M}n_{\rm O}}.
+\label{NeN_hat2}
+\end{equation}
+Let both $n_{\rm M}$ and $n_{\rm O}$ be given.
+We numerically confirmed that there is no correlation between $H_{\rm MO}^{\rm obs}$ and $H_{\rm MS}^{\rm obs}$ (results are not shown).
+To intuitively explain this independency, we consider three mothers ($i=1, 2, 3$) and their offspring, and assume that $(k_1, k_2, k_3)=(3, 1, 1)$ and $(n_{\rm M}, n_{\rm O})=(1,3)$.
+When the three offspring born to the first mother are sampled (i.e., $H_{\rm MS}^{\rm obs}=3$), the expected number of MO relationship is one ($=1/3\times3 + 1/3\times0 + 1/3\times0$).
+Meanwhile, when an offspring is sampled from each mother's offspring (i.e., $H_{\rm MS}^{\rm obs}=0$), the expected number of MO relationship is also one ($=1/3\times1 + 1/3\times1 + 1/3\times1$).
+Therefore, we conclude that both $\widehat{N_{\rm e,m}}$ and $\widehat{1/N_{\rm m}}$ are independent, and $\widehat{N_{\rm e,m}/N_{\rm m}}$ is expected to work well (see details in the {\bf RESULTS} section).
+
+The bias of $\widehat{N_{\rm e,m}/N_{\rm m} }$ is defined by $b$, which is approximately given by (see {\bf Appendix D} for the derivation)
+\begin{eqnarray}
+b &=& \mathbb{E}\left[ \widehat{\left(\frac{N_{\rm e,m}}{N_{\rm m}}\right) } \right] - \left(\frac{N_{\rm e,m}}{N_{\rm m}}\right)\nonumber\\
+&\approx& -\left(\frac{N_{\rm e,m}}{N_{\rm m}}\right) \left(1-\frac{1}{N_{\rm e,m}}\right)^{\binom{n_{\rm O}}{2}+1}.
+\label{bias}
+\end{eqnarray}
+It is noteworthy that $\widehat{N_{\rm e,m}/N_{\rm m}}$ is downwardly biased, especially when $n_{\rm O}$ is very small.
+However, this bias may be ignored for a wide range of parameters (see details in the {\bf RESULTS} section).
+Theoretically, $b$ asymptotically converges to zero as $n_{\rm O}$ increases, making $\widehat{N_{\rm e,m}/N_{\rm m}}$ a nearly unbiased estimator.
+Moreover, as demonstrated in the {\bf RESULTS} section, it is observed that an extremely skewed reproduction breaks down the unbiasedness (e.g., in the case that $c=$ 20 and 100 in the results).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Individual-based model}
+
+We developed an individual-based model that tracks kinship relationships to evaluate the estimator's performance (e.g., $\widehat{N_{\rm e,m}/N_{\rm m}}$).
+The population structure was assumed to be identical to that in the development of the estimators.
+In addition, the population comprised mothers and their offspring, and it was assumed to follow a Poisson or negative binomial reproduction (the degree of skewness due to the nonparental variation is controlled by a parameter $\phi$; see {\bf Appendix B} for detalis).
+The expected number of the surviving offspring of a mother (denoted by $\lambda$) followed the density distribution $f(\lambda)$ (which is involved to the parental variation; see {\bf Appendix B} for details).
+We calculated overdispersion parameter ($c$) from $\phi$ and $f(\lambda)$, as well as confirmed numerically that the value of $c$ gives the same statistics of the estimators even if the combination of $\phi$ and $f(\lambda)$ differs (results are not shown).
+Therefore, each offspring retained the mother's ID, making it possible to trace an MS and MO relationship.
+
+Let a parameter set ($n_{\rm O}$, $n_{\rm M}$, $N_{\rm m}$, $\phi$, and parameters that determine $f(\lambda)$) be given.
+We simulated a population history in which $N_{\rm m}$ mothers generated offspring; this process was repeated 100 times.
+The sampling process for each history was repeated 10{,}000 times, acquiring 1{,}000{,}000 data points that were utilized to construct the distribution of the estimators for each parameter set.
+Furthermore, true value of $N_{\rm e,m}$ was calculated from $N_{\rm m}$ and $c$ (Eqs.~\ref{Ne} and \ref{pi_MS}).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{RESULTS}
+
+We numerically evaluated the performance of $\widehat{N_{\rm e,m}/N_{\rm m}}$ for the case in which the number of mothers, $N_{\rm m}$, and the combined effect of deviation from the Poisson, $c$, were unknown.
+We changed the parameter values for $N_{\rm m}$ ($10^3$ and $10^4$) and $c$ (1, 10, 20, and 100).
+In addition, based on a given parameter set ($N_{\rm m}$ and $c$), we mainly addressed the number of samples ($n_{\rm M}$ and $n_{\rm O}$) required to obtain adequate accuracy and precision.
+In this study, we evaluated the performance of $\widehat{N_{\rm e,m}/N_{\rm m}}$ for specific ranges of the sample sizes (50-200 when $N_{\rm m}=10^3$, and 200-1000 when $N_{\rm m}=10^4$).
+Meanwhile, other estimators (i.e., $\widehat{N_{\rm e,m}}$ and $\widehat{1/N_{\rm m}}$) are also evaluated and provided in {\bf Supporting Information}.
+
+First, we evaluated the accuracy of estimators based on their relative bias calculated by applying the individual-based model, which is defined as follows: ``averaged estimator $-$ true value/true value.'' For a given combination of $N_{\rm m}$ and $c$, the value of the relative bias of $\widehat{N_{\rm e,m}/N_{\rm m}}$ is represented on a violin plot for limiting cases where the sample number of mothers and offspring is same (i.e., $n_{\rm M} = n_{\rm O}$), as depicted in {\bf Fig.~\ref{violin}}.
+Meanwhile, detailed results of the relative bias are represented on a heatmap as a function of $n_{\rm M}$ and $n_{\rm O}$ (see {\bf Fig.~\NeNbias{}} in {\bf Supporting Information}).
+For most of the investigated parameter sets, we observed that their relative bias is less than 10\%.
+As expected, the relative bias is not affected by $n_{\rm M}$ since $\widehat{1/N_{\rm m}}$ is exactly an unbiased estimator of $1/N_{\rm m}$ (see Eq.~\ref{Ninv_bias_app} in {\bf Appendix D} and also {\bf Fig.~\Ninvbias{}} in {\bf Supporting Information}).
+Meanwhile, $\widehat{N_{\rm e,m}}$ is downwardly biased when $n_{\rm O}$ is relatively small to true $N_{\rm e,m}$ (e.g., see {\bf Fig.~\Nebias{}} for $c=1$ in {\bf Supporting Information}), as presented in \cite{Akita_2019}; thus, $\widehat{N_{\rm e,m}/N_{\rm m}}$ is downwardly biased.
+Contrary to the theoretical prediction for the direction of the bias (Eq.~\ref{bias}), relatively strong overdispersion results in an upwardly bias for $\widehat{N_{\rm e,m}/N_{\rm m}}$ when $N_m$ is relatively small and $c$ is relatively large (e.g., $c=20$ and $100$ in {\bf Fig.~\ref{violin}a}).
+This inconsistency may be caused by the breakdown of the approximation for deriving $\widehat{N_{\rm e,m}}$ \cite[Eq.~S14 in][]{Akita_2019}.
+Thus, as described in Eq.~\ref{V_k2}, extremely large $c$ results in a large variance of offspring number, generating a situation in which the behavior of random variable $H_{\rm MS}$ far deviates from the binomial distribution.
+
+Next, we evaluated the precision of estimators based on their coefficient of variation.
+As demonstrated in {\bf Fig.~\NeNcv{}} in {\bf Supporting Information}, the value of the coefficient of variation of $\widehat{N_{\rm e,m}/N_{\rm m}}$ is also represented on a heatmap as a function of $n_{\rm M}$ and $n_{\rm O}$; meanwhile, the violin plot ({\bf Fig.~\ref{violin}}) visually provides the degree of precision.
+For the investigated parameter sets, the degree of the coefficient of variation strongly depends on the sample sizes.
+As shown in {\bf Figs.~\Necv{} and \Ninvcv{}} in {\bf Supporting Information}, the dependency results from the combined effects of variation of both $\widehat{1/N_{\rm m}}$ and $\widehat{N_{\rm e,m}}$.
+As $c$ increases, it is noteworthy that the parameter space of sample sizes demonstrating large variation of $\widehat{1/N_{\rm m}}$ (e.g., $CV>30\%$) expands; however, when $c$ is small (e.g., $c=1$), relatively small $n_{\rm O}$ results in large variation of $\widehat{N_{\rm e,m}}$ because of a relatively large $N_{\rm e,m}$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{DISCUSSION}
+
+We theoretically developed a nearly unbiased estimator of the ratio of contemporary effective mother size to the census size ($N_{\rm e,m}/N_{\rm m}$) in a population (Eq.~\ref{NeN_hat2}).
+The proposed estimator is based on known MO relationship and MS relationships observed within the same cohort, in which sampled individuals in the cohort probably share MO relationships with sampled mothers ({\bf Fig~\ref{example}}).
+The performance of the estimator (accuracy and precision) was quantitatively evaluated by running an individual-based model ({\bf Fig.~\ref{violin}}; see also {\bf Figs.~\NeNbias{}--~\Ninvcv{}}).
+Meanwhile, the bias is analytically provided (Eq.~\ref{bias}).
+Our modeling framework utilizes two types of reproductive variations \cite[]{Akita_2019}: variance of the average offspring number per mother (parental variation, denoted by $f(\lambda)$), and variance of the offspring number across mothers with the same reproductive potential (nonparental variation, denoted by $\phi$).
+Additionally, these two effects result in a skewed distribution of offspring number and are summarized into one parameter ($c$) in the framework.
+Thus, our estimator can be calculated from sample sizes of mother and offspring ($n_{\rm M}$ and $n_{\rm O}$, respectively) and the observed numbers of MS and MO pairs ($H_{\rm MS}^{\rm obs}$ and $H_{\rm MO}^{\rm obs}$, respectively), and it does not require other parameters.
+The rationale for this is the following: i) the frequency of MS and MO pairs contains information about $N_{\rm e,m}$ and $N_{\rm m}$, respectively; ii) the estimators of $N_{\rm e,m}$ and $1/N_{\rm m}$ are independently determined based on a pedigree structure in the population and sample sizes, generating the estimator of $N_{\rm e,m}/N_{\rm m}$ by multiplying both estimators ($\widehat{N_{\rm e,m}}$ and $\widehat{1/N_{\rm m}}$).
+In this study, although $\widehat{N_{\rm e,m}/N_{\rm m}}$ is considered as a proxy of $\widehat{N_{\rm e}/N}$, our theoretical results can easily be extended to the estimator of the ratio of contemporary effective father size to the census size if fathers are also sampled.
+The comparison of both ratios could clarify the underlying processes that differentiate between the sexes in the context of reproductive ecology.
+
+The novelty of this study is that $\widehat{N_{\rm e,m}/N_{\rm m}}$ can be obtained only from the genetic data, and there are numerous advantages in using the proposed estimator instead of separately estimating $N_{\rm e}$ (via genetical method) and $N$ (via non-genetical method).
+First, sampling and analyzing designs have become substantially simplified.
+Requirements for the proposed estimator are sampling of mothers and (potentially) their offspring in an appropriate time, and the extraction of their DNA that satisfies an adequate number of markers for kinship detection.
+In addition, both MO and MS pairs can be detected by a applying unified framework of genetic analyzes (there are many algorithms to detect kinship pairs from single nucleotide polymorphisms (SNPs) or short tandem repeats (STRs)), although an MS pair involves many more DNA markers (e.g., several thousands of SNPs are required for detection) than an MO pair (e.g., several hundreds of SNPs are required for detection).
+Second, our theoretical results guide sample sizes ($n_{\rm M}$ and $n_{\rm O}$) to ensure the required accuracy and precision, especially if the order of the number of effective mothers is approximately known.
+This is due to the simple formulation of the estimator determined only by the observed values (Eq.~\ref{NeN_hat2}).
+Third, the proposed estimator directly reflects the amounts of $N_{\rm e,m}$ and $N_{\rm m}$ at the same timing (i.e., immediately after the end of the reproductive season), leading to a clear interpretation of the results, especially for genetic monitoring.
+For example, when the strong cohort is added to the spawning population in the beginning of the year, the estimator of $N_{\rm e}$ without reflecting this addition may results in an inappropriate estimation of $N_{\rm e}/N$ \cite[details of the temporal scale relevant to estimated $N_{\rm e}$ for each method were discussed in][]{Wang:2016aa}.
+
+Our modeling framework is presented by combining the context of the sibship assignment method (for estimating $N_{\rm e,m}$) and the CKMR method (for estimating $1/N_{\rm m}$), which defines a kinship-oriented estimation of effective/census population size.
+Improvements to these methods directly contribute to the estimation of $N_{\rm e,m}/N_{\rm m}$.
+Furthermore, the original theory of the sibship assignment method requires HS and FS pairs but does not require a distinction between the MS and PS pairs \cite[]{wang2009new}.
+This is a significant advantage due to the difficulty of the distinction from genetic data.
+However, the limitation of using MS or PS pair enables us to employ a nearly unbiased estimator of $N_{\rm e}$ for particular sex \cite[]{Akita_2019}, which greatly improves the accuracy of the estimation of the $N_{\rm e,m}$ in this study and thus that of $N_{\rm e,m}/N_{\rm m}$ (see {\bf Fig.~E\ref{violin_wang}} in {\bf Appendix E}).
+It is noteworthy that the estimator of $1/N$ is given by
+\begin{equation}
+\widehat{\left(\frac{1}{N}\right)} = \frac{H_{\rm PO}^{\rm obs} } {2n_{\rm P}n_{\rm O}},
+\label{N_inv_hat2}
+\end{equation}
+where $n_{\rm P}$ and $H_{\rm PO}^{\rm obs}$ denotes the sample size of the parent and the observed number of parent--offspring (PO) pairs in a sample, respectively \cite[]{bravington2016close}.
+The development of the unbiased estimator of $N_{\rm e}$ without a distinction between MS and PS pairs that could provide an unbiased estimator of $N_{\rm e}/N$ coupled with Eq.~\ref{N_inv_hat2}, is a study for the future.
+Furthermore, using cross-cohort HS pairs, the CKMR method also provides the estimator of $N$ \cite[]{bravington2016close} that does not require the sampling of the parent, which probably provides the estimator of $N_{\rm e}/N$ only from unmatured samples.
+This perspective of the study will also be conducted in the future.
+
+Finally, we note the advantage of partitioning variance in reproductive success into two components.
+As denoted in Eq.~\ref{c} in {\bf Appendix C}, the combined effect of parental and nonparental variations is given by
+\begin{equation}
+c = ({\rm effect\ of\ nonparental\ variation}) \times ({\rm effect\ of\ parental\ variation}).
+\label{partition}
+\end{equation}
+Meanwhile, as denoted in Eq.~\ref{NeN}, the estimator of $N_{\rm e,m}/N_{\rm m}$ provides the information for the lefthand-side of Eq.~\ref{partition}.
+Thus, when we obtain parental variation information from the life-history table or from other species, the estimator of $N_{\rm e,m}/N_{\rm m}$ can also estimate the degree of nonparental variation.
+This procedure provides an insight into sweepstake reproduction or family-correlated sampling of offspring (i.e., nonrandom sampling), although the theoretical formulation and its evaluation remain a task for future research.
+Alternatively, Waples et al.
+(2018) developed a genetical method for estimating $N_{\rm e}/N$ and $N_{\rm b}/N$ via estimating the degree of nonparental variation from fecundity data in southern bluefin tuna.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{ACKNOWLEDGMENTS}
+The author thanks R.
+Nakamichi for fruitful discussions.
+The author also thanks Robin Waples and an anonymous reviewer for constructive feedback that substantially improved the quality of this manuscript.
+This work was supported by JSPS KAKENHI Grant Number 19K06862.
+
+\section*{CONFLICT OF INTEREST}
+The author declares no conflict of interest.
+
+\section*{AUTHOR CONTRIBUTIONS}
+{\bf Tetsuya Akita:} Conceptualization (lead); formal analysis (lead); funding acquisition (lead); methodology (lead); writing--original draft (lead); writing--review and editing (lead).
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section*{DATA ACCESSIBILITY}
+No datasets were generated or analyzed in this study.
+
+\bibliographystyle{apacite}
+\bibliography{akita}
 
@@
 
-\section*{APPENDIX A}
+\renewcommand{\arraystretch}{0.6}
+\begin{table}[tb]
+\begin{center}
+   \caption[]{The list of mathematical symbols employed in the main text}
+    \textbf {}\\[-4mm]
+    \begin{tabular}{llc} \hline
+       & & \\
+	$n_{\rm P,1}, n_{\rm P, 2}$			& Sample number of parents in the population 1 and 2\\ 
+		                						& \\
+	$n_{\rm O, 1}, n_{\rm O, 2}$			& Sample number of offspring in the population 1 and 2\\ 
+		                						& \\
+	$N_{1}, N_{2}$						& Number of parents in the population 1 and 2 when sampled offspring are born\\
+		                						& \\
+	$M$								& Number of survived migrants of parents from the population 1 to population 2\\
+		                						& \\
+	$r$								& Sex ratio\\
+		                						& \\
+	$\pi_{\rm PO,1}, \pi_{\rm PO,2}$		& Probability that a randomly selected pair (mother and offspring) \\
+	                							& shares a parent-offspring relationship within the population 1 and 2\\
+									& \\
+	$\pi_{\rm PO, bet}$					& Probability that a randomly selected pair (parent and offspring in the population 1 and 2, respectively) \\
+	                							& shares a parent-offspring relationship between the population 1 and 2\\
+									& \\
+	$\pi_{\rm HS, bet}$					& Probability that a randomly selected pair (two offspring in the population 1 and 2) \\
+	                							& shares a half-sibling relationship between the population 1 and 2\\
+					                			& \\
+	$\lambda_{i,1}, \lambda_{j,2}$			& Expected number of surviving offspring of parent $i$ and $j$ at sampling in the population 1 and 2\\
+		                						& \\
+	$\lambda_{i, M}$					& Expected number of surviving offspring of migrant $i$ at sampling\\
+		                						& \\
+	$k_{i,1}, k_{j,2}$					& Number of surviving offspring born to parent $i$ and $j$ in the population 1 and 2\\ 
+	                							& \\
+	$H_{\rm PO, 1}, H_{\rm PO, 2}$		& Number of parent-offspring pairs observed in samples within the population 1 and 2\\ 
+	                							& \\
+	$H_{\rm PO, bet}$					& Number of parent-offspring pairs observed in samples between the population 1 and 2\\ 
+	                							& \\
+	$H_{\rm HS, bet}$					& Number of half-sibling pairs observed in samples between the population 1 and 2\\ 
+	                							& \\              		
+	\hline
+    \end{tabular}
+    \label{symbols} 
+\end{center} 
+\end{table}
+\renewcommand{\arraystretch}{1}
+
+\clearpage
+
+\newcommand{\figcapa}{Example of relationships between mothers and their offspring number.
+The open, gray, and filled circles represent mothers, their eggs, and their offspring, respectively.
+The area of an open circle indicates the degree of reproductive potential of each mother (i.e., $\lambda_i$).
+The dotted and thin arrows denote mother--egg and egg--offspring relationships, respectively.
+The symbol x denotes a failure to survive at sampling.
+Sampled individuals are denoted with squares.
+Input parameters in this example: $n_{\rm P, 1}=4$, $n_{\rm P, 2}=4$, $n_{\rm O, 1}=4$, $n_{\rm O, 2}=4$, $N_{1}=16$, $N_{2}=14$, and $M=6$.
+The numbers of kinship pairs: $H_{\rm PO, 1}=1$, $H_{\rm PO, 2}=1$, $H_{\rm PO, bet}=1$, and $H_{\rm HS, bet}=2$.}
+
+\newcommand{\figcapb}{Violin plots showing the distribution of relative bias in our estimator (Eq.~\ref{NeN_hat2}) for various values of $c$ and sample size.
+Filled circles represent the mean values.
+Sample sizes for mothers and offspring are identical (i.e., $n=n_{\rm M} = n_{\rm O}$) and indicated in the legend.
+For the demonstration purposes, the distribution is truncated, although the mean values are calculated including the truncated values.
+(a) $N_{\rm m}=1{,}000$, (b) $N_{\rm m}=10{,}000$.}
+
+\newcommand{\figcapsg}{Violin plots showing the distribution of relative bias of $N_{\rm e}/N$ (denoted in Eq.~\ref{NeN_wang}) for various sample sizes.
+Filled circles represent the mean values.
+The sample numbers of parents and offspring are identical (i.e., $n=n_{\rm P} = n_{\rm O}$) and indicated in the legend.
+For demonstration purposes, the distribution is truncated, although the mean values are calculated including the truncated values.
+(a) $N=2{,}000$, (b) $N=20{,}000$.}
+
+%%%FIGURE 1%%%
+\begin{figure}[!h]
+	\begin{center}
+		\includegraphics[width=0.3\textwidth]{/Users/akita/Dropbox/research/close_kin/Mig/Figs/cartoon.eps}
+		\caption{{\bf FIGURE 1} \figcapa{}}
+		\label{example}
+	\end{center}
+\end{figure}
+%%%%%%%%%%%
+
+\clearpage
+
+\section*{APPENDIX X}
 \setcounter{equation}{0}
@@
 
-\subsection{Covariation between migration and reproductive potential}
+\section*{APPENDIX A}
+\setcounter{equation}{0}
 
-上のモデルでは，サブ集団１とサブ集団２を構成する親魚の繁殖ポテンシャルの分布をそれぞれ考慮していたが，移動個体の繁殖ポテンシャルの不均一性については考慮していなかった。最後に，移動した親魚の繁殖ポテンシャルについてもある分布に従うと仮定しよう。すなわち，$\lambda_{1,i}, \lambda_{2,j}, \lambda_{M,l}$をそれぞれ独立な確率変数とみなして，MHSペア確率を計算すると，
-\begin{align}
-\pi | _{\boldsymbol{\lambda_1, \lambda_2, \lambda_M}} &\approx \frac{4}{M} \frac{ \sum_{i=1}^M \lambda_{M,i} \sum_{j=1}^M \lambda_{M,j} } {\left(\sum_{i=1}^{M} \lambda_{M,i} + \sum_{i=M+1}^{N_1} \lambda_{1,i}\right) \left(\sum_{j=1}^{M} \lambda_{M,j} + \sum_{j=M+1}^{N_2} \lambda_{2,j}\right) }
-\end{align}
-のようになり，$N_1$, $N_2$が$M$より十分に大きいと仮定すると、この期待値は以下のようになる，
-\begin{align}
-\pi &\approx \frac{4M}{N_{1}N_{2}} \mathbb{E}\left[ \frac{ \lambda_M^2 }{\lambda_1\lambda_2} \right]
-\label{5-1}
-\end{align}
-すなわち，繁殖ポテンシャルの効果がMHSペア確率に影響するようになる。
+\section*{Distribution of the number of surviving offspring per mother and its variance}
+
+\renewcommand{\theequation}{A\arabic{equation}}
 
@@
 
-\begin{comment}
-Many authors submitting \( \sin \cos \tan \inf_{x} \) to NJD journals use \LaTeXe\ to
-prepare their papers. This paper describes the
-\textsf{WileyNJD-v2.cls} class file which can be used to convert
-articles produced with other \LaTeXe\ class files into the correct
-form for publication in \emph{Wiley NJD Journals}.
+\section*{Appendix B}
+\setcounter{equation}{0}
+\section*{Probability density function and its moment of offspring number per mother}
+\renewcommand{\theequation}{B\arabic{equation}}
 
-The \textsf{WileyNJD-v2.cls} class file preserves much of the standard
-\LaTeXe\ interface so that any document which was produced using
-the standard \LaTeXe\ \textsf{article} style can easily be
-converted to work with the \textsf{WileyNJD-v2} style. However, the
-width of text and typesize will vary from that of
-\textsf{article.cls}; therefore, \emph{line breaks will change}
-and it is likely that displayed mathematics and tabular material
-will need re-setting.
+As stated in the main text, our modeling framework does not require the specific form of the density function of offspring number per mother (denoted by $f(\lambda)$); it only requires the ratio of the second moment to the squared first moment ($\mathbb{E}[\lambda^2] / \mathbb{E}[\lambda]^2$) instead.
+However, the specific form is required for evaluating the theoretical results (i.e., calculating the moment or running the individual-based model).
+Herein, we model an age-structured fish population that serves as a representative example, demonstrating both parental and nonparental variations.
+The following contents are almost the same as those of \cite{Akita_2019} except for the parameter values that produce the setting $c=$ 20 and 100.
 
-In the following sections we describe how to lay out your code to
-use \textsf{WileyNJD-v2.cls} to reproduce the typographical look of
-\emph{Wiley NJD Journals}.
+Suppose that the mean fecundity of a mother depends on her age.
+Let $\lambda_a$ denote the mean fecundity, which is a function of age (denoted by $a$).
+The moment can be defined as $\mathbb{E}[\lambda^m] = \sum_{a=0}^{a_{\rm max}} \lambda_a^m h_{\rm mat}(a)$, where $h_{\rm mat}(a)$ is the frequency of mature mothers at a given age, and $a_{\rm max}$ denotes the maximum age.
+Thus, we can numerically obtain the moment by applying $\lambda_a$ and $h_{\rm mat}(a)$.
 
-\subsection{Procedure to install fonts}
+For marine species with a type-III survivorship curve, it is generally assumed that individual fecundity is proportional to weight.
+By utilizing the von Bertalanffy growth equation for body weight, $\lambda_a$ is explicitly defined as a function of age as follows:
+\begin{equation}
+\lambda_a \propto ( 1-{\rm exp}[-\kappa(a-a_0)])^{\beta}, 
+\label{VB}
+\end{equation}
+where $\kappa$, $a_0$, and $\beta$ are conventionally used parameters in the von Bertalanffy equation, and they denote the growth rate, the adjuster of the equation for the initial size of the animal, and the allometric growth parameter, respectively.
+To obtain a specific value of $\lambda$, a coefficient value of 10 multiplied by the right-hand side of Eq.~\ref{VB} was used when running the individual-based model.
 
-\begin{enumerate}
-\item All font files are available under the Stix-fonts folder 
-\item Font installer is available under the same folder Windows-Stix-fontinstaller.exe
-\item Execute (double click the EXE file) the EXE file that will install all fonts/map files to your local drive.
-\end{enumerate}
+The frequency of mature mothers at a given age can be given as the following: 
+\begin{equation}
+h_{\rm mat}(a) \propto h(a)Q(a),
+\label{freq}
+\end{equation}
+satisfying $\sum_{a=0}^{a_{\rm max}}h_{\rm mat}(a)=1$, where $h(a)$ and $Q(a)$ denote the frequency and maturity at a given age, respectively.
+Although $f(a)$ is affected by historical population dynamics and age-dependent survival, for simplicity, the mortality rate is assumed to be constant (i.e., age independent):
+\begin{equation}
+	h(a)\propto
+	\left \{
+	\begin{array}{l}
+		S^{a}\\
+		0
+	\end{array}
+	\begin{array}{l}
+		{\rm if}\ a < a_{\rm max}\\
+		{\rm if}\ a = a_{\rm max}
+	\end{array}
+	\right.
+	,
+	\label{survival}
+\end{equation}
+where $S$ denotes a survival probability. The maturity at age ($Q(a)$) is assumed to be a knife-edge function, which is given by
+\begin{equation}
+	Q(a)=
+	\left \{
+	\begin{array}{l}
+		1\\
+		0
+	\end{array}
+	\begin{array}{l}
+		{\rm if}\ a\geq a_{\rm mat}\\
+		{\rm otherwise }
+	\end{array}
+	\right.
+	,
+	\label{Q}
+\end{equation}
+where $a_{\rm mat}$ denotes the mature age.
 
-\subsection{The Three Golden Rules}
+To calculate $\mathbb{E}[\lambda^2] / \mathbb{E}[\lambda]^2$, the required parameter set is $(a_{\rm max}, \kappa, a_0, \beta, S, a_{\rm mat})$.
+In this study, for the purpose of representation, we fixed the values of several parameters as follows: $a_{\rm max}=20$, $\kappa=0.3$, $a_0=0$, $S=0.5$ and $a_{\rm mat}=0$.
+In addition, we selected parameter value $c$ (defined in Eq.~\ref{c} in the main text) to be 1, 10, 20, and 100 for comparison with the results in the main text that are derived from the parameter set $(\phi, \beta)=(1000,0.0009)$, $(0.1302,0.9)$, $(0.06111,0.9)$, and $(0.01165,0.9)$, respectively.
 
-Before we proceed, we would like to
-stress \emph{three golden rules} that need to be followed to
-enable the most efficient use of your code at the typesetting
-stage:
-\begin{enumerate}
-\item[(i)] keep your own macros to an absolute minimum;
+Finally, we provide specific forms of $f(\lambda)$; thus, when $\lambda_a$ and $h_{\rm mat}(a)$ are obtained, $f(\lambda)$ is given by
+\begin{equation}
+	f(\lambda) =
+	\left \{
+	\begin{array}{l}
+		h_{\rm mat}(a)\\
+		0
+	\end{array}
+	\begin{array}{l}
+		{\rm if}\ \lambda = \lambda_a\\
+		{\rm otherwise }
+	\end{array}
+	\right.
+	.
+	\label{f_lambda}
+\end{equation}
 
-\item[(ii)] as \TeX\ is designed to make sensible spacing
-decisions by itself, do \emph{not} use explicit horizontal or
-vertical spacing commands, except in a few accepted (mostly
-mathematical) situations, such as \verb"\," before a
-differential~d, or \verb"\quad" to separate an equation from its
-qualifier;
+\section*{Appendix C}
+\setcounter{equation}{0}
+\section*{Combined effect of parental and nonparental variations}
 
-\item[(iii)] follow the \emph{NJD} reference style.
-\begin{enumerate}[a.]
-\item Chemistry --- Use the ``AMA'' option as \verb"\documentclass[AMA]{WileyNJD-v2.cls}"
+\renewcommand{\theequation}{C\arabic{equation}}
 
-\end{enumerate}
-\end{enumerate}
+Following \cite{Akita_2019}, combined effect of parental and nonparental variations can be partitioned into the two components, such as: 
+\begin{equation}
+c = (1+\phi^{-1}) \times \left(\frac{\mathbb{E}[\lambda^2]}{\mathbb{E}[\lambda]^2}\right). 
+\label{c}
+\end{equation}
+The first and second parentheses give the effect of nonparental variation and parental variation, respectively.
+When $\lambda$ is constant across mothers, $\mathbb{E}[\lambda^2]$ equals $\mathbb{E}[\lambda]^2$ and $c$ converges to $(1+\phi^{-1})$; meanwhile, $\phi \to \infty$, $c$ converges to $\mathbb{E}[\lambda^2]/\mathbb{E}[\lambda]^2$.
+Without either parental or nonparental variation, $c$ converges to 1 and $\pi_{\rm MS}$ converges to $1/N_{\rm m}$.
+In the main text, we refer to ``overdispersion'' as the skewed distribution of the offspring number resulting from this combined effect.
 
-\section{Getting Started} The \textsf{WileyNJD-v2.cls} class file should run
-on any standard \LaTeXe\ installation. If any of the fonts, class
-files or packages it requires are missing from your installation,
-they can be found on the \emph{\TeX\ Live} CD-ROMs or from CTAN.
+Using Eqs.~\ref{V_k} and \ref{c}, the variance of the offspring number can be expressed as  
+\begin{equation}
+\mathbb{V}[k] = \mathbb{E}[\lambda] + \mathbb{E}[\lambda]^2 (c-1),  
+\label{V_k2}
+\end{equation}
+suggesting that the variance substantially increases with $c$.
 
-LaTeX document class options
+\section*{Appendix D}
+\setcounter{equation}{0}
+\section*{Derivation of the bias of $\widehat{N_{\rm e,m}/N_{\rm m}}$}
+\renewcommand{\theequation}{D\arabic{equation}}
 
-\begin{flushleft}
-\begin{enumerate}[a.]
-\item STIX1COL--- For STIX font large one column layout use the ``STIX1COL'' option as \verb"\documentclass[AMA,STIX1COL]{WileyNJD-v2}"
-\item STIX2COL--- For STIX font large two column layout use the ``STIX2COL'' option as \verb"\documentclass[AMA,STIX2COL]{WileyNJD-v2}"
-\item STIXSMALL--- For STIX font small layout use the ``STIXSMALL'' option as \verb"\documentclass[AMA,STIXSMALL]{WileyNJD-v2}"
-\end{enumerate}
-\end{flushleft}
+For calculation of the bias of $\widehat{N_{\rm e,m}/N_{\rm m}}$, we require an expectation of the estimator given by
 
-\section{The Article Header Information}
-The heading for any file using \textsf{WileyNJD-v2.cls} is shown in
-Figure~\ref{F1}.
+\begin{equation}
+\mathbb{E}\left[\widehat{\left(\frac{N_{\rm e,m}}{N_{\rm m}}\right) }\right] = \mathbb{COV}\left[\widehat{\left(\frac{1}{N_{\rm m}}\right)}, \widehat{N_{\rm e,m}} \right] + \mathbb{E}\left[\widehat{\left(\frac{1}{N_{\rm m}}\right)}\right] \mathbb{E}\left[ \widehat{N_{\rm e,m}} \right].
+\label{E_NeN}
+\end{equation}
+As stated in the main text, both $\widehat{N_{\rm e,m}}$ and $\widehat{1/N_{\rm m}}$ are independent.
+Thus, the first term in the right-hand side of Eq.~\ref{E_NeN} can be ignored.
+The expectation of $\widehat{1/N_{\rm m}}$ is given by
+\begin{eqnarray}
+ \mathbb{E}\left[\widehat{\left(\frac{1}{N_{\rm m}}\right)}\right] &=& \frac{\mathbb{E}\left[ H_{\rm MO}\right]}{n_{\rm M}n_{\rm O}}\nonumber\\
+ &=& \frac{1}{N_{\rm m}}.
+ \label{Ninv_bias_app}
+\end{eqnarray}
+From the first to the second line of Eq.~\ref{Ninv_bias_app} , we applied the relationship $\pi_{\rm MO} = \mathbb{E}[\pi_{\rm MO}] = \mathbb{E}[H_{\rm MO}]/(n_{\rm M}n_{\rm O})$ and Eq.~\ref{pi_MO}.
+Equation~\ref{Ninv_bias_app} indicates that $\widehat{1/N_{\rm m}}$ is the unbiased estimator.
+The expectation of $\widehat{N_{\rm e,m}}$ is given by
+\begin{equation}
+\mathbb{E}[\widehat{N_{\rm e,m}}] = N_{\rm e,m} - N_{\rm e,m}\left(1-\frac{1}{N_{\rm e,m}}\right)^{\binom{n_{\rm O}}{2}+1},
+\label{bias_Ne}
+\end{equation}
+which is illustrated in Appendix D of \cite{Akita_2019}. Together with these relationships, we can obtain the bias of $\widehat{N_{\rm e,m}/N_{\rm m}}$ described in Eq.~\ref{bias}.
 
-\subsection{Remarks}
+\section*{Appendix E}
+\setcounter{equation}{0}
+\section*{Individual-based model with application of Wang's estimator}
+\renewcommand{\theequation}{E\arabic{equation}}
 
-\begin{enumerate}[(I).]
+Our modeling framework estimates the ratio of contemporary effective mother size to census size (denoted by $N_{\rm e,m}/N_{\rm m}$), as a proxy for the ratio of contemporary effective size to census size (denoted by $N_{\rm e}/N$).
+To compare the performance of our method with that of other methods for directly estimating $N_{\rm e}/N$, we propose the estimator of $N_{\rm e}/N$, given by
+\begin{eqnarray}
+\widehat{\left(\frac{N_{\rm e}}{N}\right) } &=& \widehat{N_{\rm e}}\widehat{\left(\frac{1}{N}\right)}\nonumber\\
+&=& \frac{4\binom{n_{\rm O}}{2}}{H_{\rm HS}^{\rm obs}+H_{\rm FS}^{\rm obs}} \frac{H_{\rm PO}^{\rm obs} } {2n_{\rm P}n_{\rm O}}.
+\label{NeN_wang}
+\end{eqnarray}
+$n_{\rm P}$ and $n_{\rm O}$ indicate the sample numbers of parents and offspring, respectively, and $H_{\rm HS}^{\rm obs}$, $H_{\rm FS}^{\rm obs}$, and $H_{\rm PO}^{\rm obs}$ indicate the observed number of half-sibling, full-sibling, and parent-offspring pairs, respectively.
+$\widehat{N_{\rm e}}$ is based on \cite{wang2009new} assuming random mating and $\widehat{1/N}$ is defined in Eq.~\ref{N_inv_hat2} in the main text.
 
-\item Use \verb"\title{<title> \protect\thanks{<title footnotes}}" for article title and title footnote.
-\item Use \verb"\authormark{}" for running heads.
+We evaluated the estimator's performance on data simulated by running an individual-based model under the Wright-Fisher process for a diploid population.
+In the current comparison, we did not consider the case of overdispersion (i.e., $N_{\rm e} = N$).
+Sex ratio was fixed to 0.5 in both whole and sampled populations.
+Each parent retained the ID of its offspring, making it possible to trace HS, FS, and PO relationships.
+Given a parameter set ($N$, $n_{\rm O}$, and $n_{\rm P}$), we backwardly simulated a population history in which  mother-offspring and father-offspring relationships were randomly specified from $n_{\rm O}$ offspring; this process was repeated 10{,}000 times, acquiring 10{,}000 data points that were used to construct the distribution of $\widehat{N_{\rm e}/N}$ for each parameter set.
+If neither HS nor FS pairs were found in a sample, we did not include that trial when constructing the distribution.
+For ease of comparison, we used the same sample size and population structure for both methods.
 
-\item Note the use of \verb"\author[<link>]{<name>}" and \verb"\address[<link>]{<name>}" to
-link names and addresses. The author for correspondence is marked
-by ``*'' and \verb"\corres{}" is used to give that
-author's address, which will be printed besides abstract, prefaced by
-`Correspondence to:'.
+{\bf Figure.~E\ref{violin_wang}} illustrates the distribution of the relative bias of $\widehat{N_{\rm e}/N}$ for limiting cases where parent and offspring sample numbers are identical (i.e., $n_{\rm P} = n_{\rm O}$).
+Our results indicate that the estimator is upwardly biased, particularly when sample size is small.
+Alternatively, our estimator shows a broader region such that unbiasedness is approximately achieved.
+For example, when $n = 100$ and $150$ in $N = 2000$ (i.e., $N_{\rm m}=1000$), the bias of $\widehat{N_{\rm e}/N}$ is clearly observed ({\bf Fig.~E\ref{violin_wang}a}); meanwhile, $N_{\rm e,m}/N_{\rm m}$ does not produce a bias in these conditions ({\bf Fig.~\ref{violin}a}).
 
-\item For submitting a double-spaced manuscript, add
-\verb"doublespace" as an option to the documentclass line. \verb"\documentclass[doublespace]{WileyNJD-v2}"
+\clearpage
 
-\item Use \verb"\presentaddress{}" for present address.
+%\begin{comment}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\section*{Supporting Information}
 
-\item In abstract \verb"\abstract[<title>]{abstract paragraph}" use optional parameter for title followed by abstract paragraph.
+%\setcounter{figure}{0}
+%\newcommand{\figcapsa}{Heatmap showing the relative bias of $\widehat{N_{\rm e,m}/N_{\rm m}}$ as a function of both $n_{\rm M}$ and $n_{\rm O}$.
+The value of the relative bias is indicated in the legend.
+The value of the combined effect of parental and nonparental variations increases from left to right ($c=1, 10, 20$, and $100$).
+(a) $N_{\rm m}=1{,}000$, (b) $N_{\rm m}=10{,}000$.
+}
 
-\item For Key words use \verb"\keywords{}".
+%\newcommand{\figcapsb}{Heatmap showing the relative bias of $\widehat{N_{\rm e,m}}$ as a function of both $n_{\rm M}$ and $n_{\rm O}$.
+The value of the relative bias is indicated in the legend.
+The value of the combined effect of parental and nonparental variations increases from left to right ($c=1, 10, 20$, and $100$).
+(a) $N_{\rm m}=1{,}000$, (b) $N_{\rm m}=10{,}000$.
+}
 
-\item For how to site use \verb"\jnlcitation{\cname{\author{<author name>},"
+%\newcommand{\figcapsc}{Heatmap showing the relative bias of $\widehat{1/N_{\rm m}}$ as a function of both $n_{\rm M}$ and $n_{\rm O}$.
+The value of the relative bias is indicated in the legend.
+The value of the combined effect of parental and nonparental variations increases from left to right ($c=1, 10, 20$, and $100$).
+(a) $N_{\rm m}=1{,}000$, (b) $N_{\rm m}=10{,}000$.
+}
 
-\verb"\ctitle{<title>}, \cjournal{<Journal name>}, \cvol{<vol>}.}}".
+%\newcommand{\figcapsd}{Heatmap showing the coefficient of variation of $\widehat{N_{\rm e,m}/N_{\rm m}}$ as a function of both $n_{\rm M}$ and $n_{\rm O}$.
+The value of the coefficient of variation is indicated in the legend.
+The value of the combined effect of parental and nonparental variations increases from left to right ($c=1, 10, 20$, and $100$).
+(a) $N_{\rm m}=1{,}000$, (b) $N_{\rm m}=10{,}000$.}
 
-\item For title page abbreviations use \verb"\footnotetext{<\textbf{Abbreviation title:} Abreviations>}"
+%\newcommand{\figcapse}{Heatmap showing the coefficient of variation of $\widehat{N_{\rm e,m}}$ as a function of both $n_{\rm M}$ and $n_{\rm O}$.
+The value of the coefficient of variation is indicated in the legend.
+The value of the combined effect of parental and nonparental variations increases from left to right ($c=1, 10, 20$, and $100$).
+(a) $N_{\rm m}=1{,}000$, (b) $N_{\rm m}=10{,}000$.}
 
-\item Use \verb"\articletype{<article category}" for article header information
+%\newcommand{\figcapsf}{Heatmap showing the coefficient of variation of $\widehat{1/N_{\rm m}}$ as a function of both $n_{\rm M}$ and $n_{\rm O}$.
+The value of the coefficient of variation is indicated in the legend.
+The value of the combined effect of parental and nonparental variations increases from left to right ($c=1, 10, 20$, and $100$).
+(a) $N_{\rm m}=1{,}000$, (b) $N_{\rm m}=10{,}000$.}
 
-\item Use \verb"\received{<received date>} \revised{<revised date>} \accepted{<accepted date>}" for history dates.
+%%%FIGURE S1%%%
+%\begin{figure}[!h]
+%	\begin{center}
+%		\includegraphics[width=1\textwidth]{figs/NeN_bias.pdf}
+%		\caption{{\bf FIGURE S1} \figcapsa{}}
+%		\label{NeN_bias}
+%	\end{center}
+%\end{figure}
+%%%%%%%%%%%
 
-\end{enumerate}
+%%%FIGURE S2%%%
+%\begin{figure}[!h]
+%	\begin{center}
+%		\includegraphics[width=1\textwidth]{figs/Ne_bias.pdf}
+%		\caption{{\bf FIGURE S2} \figcapsb{}}
+%		\label{Ne_bias}
+%	\end{center}
+%\end{figure}
+%%%%%%%%%%%
 
-\begin{figure}[p]
-\setlength{\fboxsep}{0pt}%
-\setlength{\fboxrule}{0pt}%
-\begin{center}
-\begin{boxedverbatim}
+%%%FIGURE S3%%%
+%\begin{figure}[!h]
+%	\begin{center}
+%		\includegraphics[width=1\textwidth]{figs/Ninv_bias.pdf}
+%		\caption{{\bf FIGURE S3} \figcapsc{}}
+%		\label{Ninv_bias}
+%	\end{center}
+%\end{figure}
+%%%%%%%%%%%
 
-\documentclass[AMA,STIX1COL]{WileyNJD-v2}
+%%%FIGURE S4%%%
+%\begin{figure}[!h]
+%	\begin{center}
+%		\includegraphics[width=1\textwidth]{figs/NeN_cv.pdf}
+%		\caption{{\bf FIGURE S4} \figcapsd{}}
+%		\label{NeN_cv}
+%	\end{center}
+%\end{figure}
+%%%%%%%%%%%
 
-\articletype{Article Type}%
+%%%FIGURE S5%%%
+%\begin{figure}[!h]
+%	\begin{center}
+%		\includegraphics[width=1\textwidth]{figs/Ne_cv.pdf}
+%		\caption{{\bf FIGURE S5} \figcapse{}}
+%		\label{Ne_cv}
+%	\end{center}
+%\end{figure}
+%%%%%%%%%%%
 
-\received{26 April 2016}
-\revised{6 June 2016}
-\accepted{6 June 2016}
+%%%FIGURE S6%%%
+%\begin{figure}[!h]
+%	\begin{center}
+%		\includegraphics[width=1\textwidth]{figs/Ninv_cv.pdf}
+%		\caption{{\bf FIGURE S6} \figcapsf{}}
+%		\label{Ninv_cv}
+%	\end{center}
+%\end{figure}
+%%%%%%%%%%%
+%\clearpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\end{comment}
 
-\begin{document}
-
-\title{<Initial cap, lower case>\protect\thanks{<title footnote.>}}
-
-\author[<address link>]{<Author name><corresponding author*>}
-
-\author[<address link>,<address link>]{Author Name}
-
-\authormark{AUTHOR ONE \textsc{et al}}
-
-\address[<address link>]{\orgdiv{<Org Division>}, \orgname{<Org name>}, 
-\orgaddress{\state{<State name>}, \country{<Country name>}}}
-\address[<address link>]{\orgdiv{<Org Division>}, \orgname{<Org name>},
- \orgaddress{\state{<State name>}, \country{<Country name>}}}
-
-\corres{<corresponding author link*> <author name, address.
- \email{<authorone@email.com>}}
-
-\presentaddress{<Present address>}
-
-\abstract[<Abstract heading>]{<Abstract paragraph>}
-
-\keywords{<keyword1>, <keyword2>,...}
-
-\jnlcitation{\cname{%
-\author{<aurhor name>}, 
-\author{<aurhor name>}, 
-\author{<aurhor name>}, 
-\author{<aurhor name>},  and 
-\author{<aurhor name>}} (\cyear{<year>}), 
-\ctitle{<journal title>}, \cjournal{<journal name>} <year> <vol> Page <xxx>-<xxx>}
-
-\footnotetext{\textbf{<abbreviation head:>} <abbreviations> ..}
-
-\maketitle
-
-\section{Introduction}
-.
-.
-.
-\end{boxedverbatim}
-\end{center}
-\caption{Example for title page.\label{F1}}
-\end{figure}
-
-\section{The Body of the Article}
-
-\subsection{Section headings}
-
-\begin{enumerate}[(H1)]
-\item Section --- use \verb"\section{}"
-\item SubSection--- use \verb"\subsection{}"
-\item SubSubSectioin--- use \verb"\subsubsection{}"
-\item Paragraph--- use \verb"\paragraph{}"
-\item Subparagraph--- use \verb"\subparagraph{}"
-\end{enumerate}
-
-\subsection{Mathematics} \textsf{WileyNJD-v2.cls} makes the full
-functionality of \AmS\/\TeX\ available. We encourage the use of
-the \verb"align", \verb"gather" and \verb"multline" environments
-for displayed mathematics.
-
-\subsection{Figures and Tables}
-
-\textsf{WileyNJD-v2.cls} uses the
-\textsf{graphicx} package for handling figures.
-
-Figures are called in as follows:
-\begin{verbatim}
-\begin{figure}
-\centering
-\includegraphics{<figure name>}
-\caption{<Figure caption>}
-\end{figure}
-\end{verbatim}
-
-The standard coding for a table is shown in Figure~\ref{F2}.
-
-\begin{figure}[h]
-\setlength{\fboxsep}{0pt}%
-\setlength{\fboxrule}{0pt}%
-\begin{center}
-\begin{boxedverbatim}
-\begin{table}
-\caption{<Table caption>}
-\centering
-\begin{tabular}{<table alignment>}
-\toprule
-<column headings>\\
-\midrule
-<table entries
-(separated by & as usual)>\\
-<table entries>\\
-.
-.
-.\\
-\bottomrule
-\end{tabular}
-\begin{tablenotes}
-\item Source: xxx.
-\item[1] xxx.
-\item[2] xxx.
-\end{tablenotes}
-\end{table}
-\end{boxedverbatim}
-\end{center}
-\caption{Example for table layout.\label{F2}}
-\end{figure}
-
-\subsection{Cross-referencing}
-The use of the \LaTeX\ cross-reference system
-for figures, tables, equations, etc., is encouraged
-(using \verb"\ref{<name>}" and \verb"\label{<name>}").
-
-\subsection{Box text}
-
-\begin{verbatim}
-\begin{boxtext}
-\section*{<title>}%
-Paragraph
-\end{boxtext}
-\end{verbatim}
-
-\subsection{List items}
-
-\subsubsection{Enumerate list styles}
-\begin{verbatim}
-\begin{enumerate}[1]
-\item 
-\end{enumerate}
-
-\begin{enumerate}[1.]
-\item 
-\end{enumerate}
-
-\begin{enumerate}[(1)]
-\item 
-\end{enumerate}
-
-\begin{enumerate}[I]
-\item 
-\end{enumerate}
-
-\begin{enumerate}[i]
-\item 
-\end{enumerate}
-
-\begin{enumerate}[a]
-\item 
-\end{enumerate}
-
-\end{verbatim}
-
-\subsubsection{Bullet list styles}
-
-\begin{verbatim}
-\begin{itemize}
-\item 
-\end{itemize}
-\end{verbatim}
-
-\subsubsection{Description list}
-
-\begin{verbatim}
-\begin{description}
-\item[<entry>] description text.
-\end{description}
-\end{verbatim}
-
-\subsection{Enunciations}
-
-\begin{verbatim}
-\begin{theorem}[<Theorem subhead>]\label{thm1}
-<theorem text>. 
-\end{theorem}
-
-\begin{proposition}[<proposition subhead>]\label{pro1}
-<proposition text>. 
-\end{proposition}
-
-\begin{definition}[<definition subhead>]\label{dfn1}
-<definition text>. 
-\end{definition}
-
-\begin{proof}
-<proof text>. 
-\end{proof}
-
-\begin{proof}[Proof of Theorem~\ref{thm1}]
-<proof text>.
-\end{proof}
-
-\end{verbatim}
-
-\subsection{Program codes}
-
-Use \verb+\begin{verbatim}...\end{verbatim}+ for program codes without math.
-Use \verb+\begin{alltt}...\end{alltt}+ for program codes with math.
-Based on the text provided inside the optional argument of \verb+\begin{code}[Psecode|Listing|Box|Code|+\hfill\break \verb+Specification|Procedure|Sourcecode|Program]...+ \verb+\end{code}+ tag corresponding boxed like floats are generated.
-Also note that \verb+\begin{code}[Code|Listing]...+ \verb+\end{code}+ tag with either Code or Listing text as optional argument text are set with computer modern typewriter font.
-All other code environments are set with normal text font.
-Refer below example:
-
-\begin{verbatim}
-\begin{lstlisting}[caption={Descriptive Caption Text},label=DescriptiveLabel]
-for i:=maxint to 0 do
-begin
-{ do nothing }
-end;
-Write('Case insensitive ');
-WritE('Pascal keywords.');
-\end{lstlisting}
-\end{verbatim}
-
-\subsection{Acknowledgements}
-
-This work was supported by JSPS KAKENHI Grant Number 19K06862 and 20H03012.
-An Acknowledgements section is started with \verb"\ack" or
-\verb"\acks" for \textit{Acknowledgement} or
-\textit{Acknowledgements}, respectively. It must be placed just
-before the References.
-
-\subsection{Bibliography}
-
-\begin{enumerate}[1]
-\item Use \verb"\bibliography{wileyNJD-AMA}" BST file for AMA reference style
-\item Use \verb"\bibliography{wileyNJD-APA}" BST file for APA reference style
-\item Use \verb"\bibliography{wileyNJD-AMS}" BST file for AMS reference style
-\item Use \verb"\bibliography{wileyNJD-VANCOUVER}" BST file for Vancouver reference style
-\item Use \verb"\bibliography{wileyNJD-ACS}" BST file for Chemistry reference style
-\end{enumerate}
-
-The normal commands for producing the reference list are:
-
-\begin{verbatim}
-\begin{thebibliography}{99}
-\bibitem{<x-ref label>}
-         <Reference details>
-.
-.
-.
-\end{thebibliography}
-\end{verbatim}
-
-\subsection{Appendix Section}
-
-\begin{verbatim}
-\appendix
-
-\section{Section title of first appendix\label{app1}}
-.
-.
-.
-
-\end{verbatim}
-\end{comment}
-
+\end{spacing}
 \end{document}

### 2021-06-24 latex/ms.tex
write 2.1 and start 2.2, #6

@@
 While the estimators can hold under flexible assumptions for reproduction (see {\bf Appendix}), here we assume a relatively simple situation for explanation purposes.
-It should be noted that the formulation of the estimators, presented in Equations 4-5 and 7-8, is a function with parent numbers in the two populations; in the next section, we provide the treatment for estimating the unknown parent numbers from genetic dataset which is used for obtaining HS or PO pairs.
+It should be noted that the formulation of the estimators, presented in Equations 4-5 and 7-8, is a function with parent numbers for each population; in the next section, we provide the treatment for estimating the unknown parent numbers from genetic dataset which is used for obtaining HS and/or PO pairs.
 The main symbols used in the current paper are summarized in Table \ref{symbols}.
+
+%%%%%%%%%%%%%%
+\begin{center}
+Table \ref{symbols} is here. 
+\end{center}
+%%%%%%%%%%%%%%
 
@@
 Hereafter, without loss of generality, we consider the movement of parents in the direction from population 1 to population 2 and focus on the migration number or rate, and that is what we attempt to estimate.
-In this framework, two reproductive seasons (hereafter, we call them "the first year" and "the second year") are enough to estimate it.
+In this framework, considering two reproductive seasons (hereafter, we call them "the first year" and "the second year") is enough to estimate it.
 
@@
 After the reproductive season, part of the parents would start to moving towards the population 2; $M$ survived migrants arrive in the population 2 so that there are $N_2$ parents in the population 2 at the beginning of the second year ($M<N_2$).
-Similar to the population, $N_2$ parents produce offspring in which the number is determined by $\lambda_{j,2}$ ($j=1,2,\ldots,N_2$).
+Similar to the population 1, $N_2$ parents produce offspring in which the number is determined by $\lambda_{j,2}$ ($j=1,2,\ldots,N_2$).
+
+\subsection{Sampling}
+
+To estimate the migration number or rate, we utilize the number of HS and/or PO pairs observed in a sample.
+In the both populations, $n_{\rm P, 1}$ and $n_{\rm P, 2}$ parents are randomly sampled immediately after the end of the reproductive season in the first and second year, respectively.
+Additionally, $n_{\rm O, 1}$ and $n_{\rm O, 2}$ offspring are also randomly sampled.
+It should be noted that the four kinds of a sample are not always required for estimating migration number or rate; what kinds of samples are needed depends on the situation, as explained later.
+
+ The numbers of MS and MO pairs are determined by pairwise comparison of all the sample individuals (${}_{n_{\rm O}}\mathrm{C}_2$ and $n_{\rm M}n_{\rm O}$ comparisons, respectively).
+As depicted in {\bf Fig~\ref{example}}, six offspring and three mothers are sampled and two MS and three MO pairs are observed.
+In our modeling framework, if an MS pair also shares a paternal-sibling (PS) relationship, we count it as an MS pair and ignore the existing full-sibling (FS) relationship.
+
+\textcolor{red}{kokomade!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!}
+
+Figure \ref{cartoon} illustrates an example of kinship relationships and movements of parents between populations.
+
+Although the theoretical framework allows a flexible setting of the reproductive potential,
 
@@
 
-Figure \ref{cartoon} illustrates an example of kinship relationships and movements of parents between populations.
-
-\subsection{Sampling}
+%%%%%%%%%%%%%%
+\begin{center}
+Figure \ref{cartoon} is here. 
+\end{center}
+%%%%%%%%%%%%%%
 
@@
 		\caption{{\bf FIGURE 1} \figcapa{}}
-		\label{example}
+		\label{cartoon}
 	\end{center}

### 2021-06-25 latex/ms.tex
write 1st para in 2.2, #6

@@
 While the estimators can hold under flexible assumptions for reproduction (see {\bf Appendix}), here we assume a relatively simple situation for explanation purposes.
-It should be noted that the formulation of the estimators, presented in Equations 4-5 and 7-8, is a function with parent numbers for each population; in the next section, we provide the treatment for estimating the unknown parent numbers from genetic dataset which is used for obtaining HS and/or PO pairs.
-The main symbols used in the current paper are summarized in Table \ref{symbols}.
+It should be noted that the formulation of the estimators, presented in Equations 4-5 and 7-8, is a function with parent numbers for each population; in the next section, we provide the treatment for estimating the unknown parent numbers by additional usage of HS and/or PO pairs.
+The main symbols used in the current paper are summarized in {\bf Table \ref{symbols}}.
 
@@
 In this framework, considering two reproductive seasons (hereafter, we call them "the first year" and "the second year") is enough to estimate it.
+{\bf Figure \ref{cartoon}} presents a schematic representation of the kinship relationships and movements of parents.
 
 Suppose there are $N_1$ parents in the population 1 at the beginning of the first year.
-Each parent produces offspring in which the number is determined by the parent's reproductive potential, denoted by $\lambda_{i,1}$ ($i=1,2,\ldots,N_1$).
-After the reproductive season, part of the parents would start to moving towards the population 2; $M$ survived migrants arrive in the population 2 so that there are $N_2$ parents in the population 2 at the beginning of the second year ($M<N_2$).
+Each parent produces offspring in which the number is governed by the parent's reproductive potential, denoted by $\lambda_{i,1}$ ($i=1,2,\ldots,N_1$).
+After the reproductive season, part of the parents would start to moving towards the population 2; $M$ survived migrants arrive in the population 2 so that there are $N_2$ parents in the population 2 at the beginning of the second year ($M < N_2$).
 Similar to the population 1, $N_2$ parents produce offspring in which the number is determined by $\lambda_{j,2}$ ($j=1,2,\ldots,N_2$).
+Theoretically speaking, the number of offspring for each parent is a random variable with mean $\lambda_{i,1}$ or $\lambda_{j,2}$.
 
@@
 To estimate the migration number or rate, we utilize the number of HS and/or PO pairs observed in a sample.
-In the both populations, $n_{\rm P, 1}$ and $n_{\rm P, 2}$ parents are randomly sampled immediately after the end of the reproductive season in the first and second year, respectively.
-Additionally, $n_{\rm O, 1}$ and $n_{\rm O, 2}$ offspring are also randomly sampled.
-It should be noted that the four kinds of a sample are not always required for estimating migration number or rate; what kinds of samples are needed depends on the situation, as explained later.
+In the both populations, $n_{\rm O, 1}$ and $n_{\rm O, 2}$ offspring are randomly sampled.
+Additionally, $n_{\rm P, 1}$ and $n_{\rm P, 2}$ parents are randomly sampled immediately after the end of the reproductive season in the first and second year, respectively.
+For mathematical tractability, parents have to survive during the reproductive season; therefore, both mother and father of a certain offspring have a potential to be sampled.
+Assuming invasive sampling, sampled parents in the population 1 are never sampled in the population 2.
+It should be noted that al the four kinds of a sample (i.e., $n_{\rm P, 1}$, $n_{\rm P, 2}$, $n_{\rm O, 1}$ and $n_{\rm O, 2}$) are not always required for estimating migration number or rate; what kinds of a sample are needed depends on the situation, as explained later.
 
@@
 \textcolor{red}{kokomade!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!}
-
-Figure \ref{cartoon} illustrates an example of kinship relationships and movements of parents between populations.
 
@@
 
-\renewcommand{\arraystretch}{0.6}
-\begin{table}[tb]
-\begin{center}
-   \caption[]{Summary of proposed estimators for required parameters and kinship types}
-    \textbf {}\\[-0mm]
-    \begin{tabular}{ccccccccc} \hline
-       	\\
-	Estimator			& $N_1$ 		& $N_2$ 		& $n_{\rm O, 1}$	& $n_{\rm O, 2}$	& $n_{\rm P, 1}$	& $n_{\rm P, 2}$	& Required kinship type\\
-	\\
-	\hline
-	\\
-	$\widehat{M_1}$	& given 		& given 		& \checkmark		& \checkmark 		&				&				& HSP\\ 
-		                						& \\
-	$\widehat{M_2}$	& given		& given		& \checkmark		& 				&				& \checkmark 		& POP\\
-		                						& \\
-	$\widehat{M_3}$	& given		& given		& \checkmark		&  \checkmark		&				& \checkmark 		& HSP \& POP\\
-		                						& \\
-	$\widehat{M_4}$	& given		& estimated	& \checkmark		&  \checkmark		&				& \checkmark 		& HSP \& POP\\
-		                						& \\
-	$\widehat{M_5}$	& estimated	& estimated	& \checkmark		&  \checkmark		& \checkmark		& \checkmark 		& HSP \& POP\\
-									& \\
-	$\widehat{m_1}$	& ---			& given		& \checkmark		& \checkmark 		&				&				& HSP\\ 
-									& \\
-	$\widehat{m_2}$	& ---			& given		& \checkmark		& 				&				& \checkmark 		& POP\\					                			& \\
-	$\widehat{m_3}$	& ---			& given 		& \checkmark		&  \checkmark		&				& \checkmark 		& HSP \& POP\\
-		                						& \\
-	$\widehat{m_4}$	& ---			& estimated	& \checkmark		&  \checkmark		& 				& \checkmark 		& HSP \& POP\\
-		                						& \\
-	\hline
-    \end{tabular}
-    \label{parameter} 
-\end{center} 
-\end{table}
-\renewcommand{\arraystretch}{1}
-
 The estimation of the ratio of the contemporary effective population size to the census size ($N_{\rm e}/N$) has attracted much research attention for providing information about a current population, especially in the context of conservation biology and wildlife management \cite[]{Palstra_2012,FRANKHAM201456}.
@@
 \begin{center}
-   \caption[]{The list of mathematical symbols employed in the main text}
+   \caption[]{Table 1: The list of mathematical symbols employed in the main text}
     \textbf {}\\[-4mm]
@@
 									& \\
-	$\pi_{\rm PO, bet}$					& Probability that a randomly selected pair (parent and offspring in the population 1 and 2, respectively) \\
-	                							& shares a parent-offspring relationship between the population 1 and 2\\
+	$\pi_{\rm PO, bet}$					& Probability that a randomly selected pair (parent and offspring in the population 1 and 2, \\
+	                							& respectively) shares a parent-offspring relationship between the population 1 and 2\\
 									& \\
@@
     \label{symbols} 
+\end{center} 
+\end{table}
+\renewcommand{\arraystretch}{1}
+
+\clearpage
+
+\renewcommand{\arraystretch}{0.6}
+\begin{table}[tb]
+\begin{center}
+   \caption[]{Table 2: Summary of proposed estimators for required parameters and kinship types}
+    \textbf {}\\[-0mm]
+    \begin{tabular}{ccccccccc} \hline
+       	\\
+	Estimator			& $N_1$ 		& $N_2$ 		& $n_{\rm O, 1}$	& $n_{\rm O, 2}$	& $n_{\rm P, 1}$	& $n_{\rm P, 2}$	& Required kinship type\\
+	\\
+	\hline
+	\\
+	$\widehat{M_1}$	& given 		& given 		& \checkmark		& \checkmark 		&				&				& HSP\\ 
+		                						& \\
+	$\widehat{M_2}$	& given		& given		& \checkmark		& 				&				& \checkmark 		& POP\\
+		                						& \\
+	$\widehat{M_3}$	& given		& given		& \checkmark		&  \checkmark		&				& \checkmark 		& HSP \& POP\\
+		                						& \\
+	$\widehat{M_4}$	& given		& estimated	& \checkmark		&  \checkmark		&				& \checkmark 		& HSP \& POP\\
+		                						& \\
+	$\widehat{M_5}$	& estimated	& estimated	& \checkmark		&  \checkmark		& \checkmark		& \checkmark 		& HSP \& POP\\
+									& \\
+	$\widehat{m_1}$	& ---			& given		& \checkmark		& \checkmark 		&				&				& HSP\\ 
+									& \\
+	$\widehat{m_2}$	& ---			& given		& \checkmark		& 				&				& \checkmark 		& POP\\					                			& \\
+	$\widehat{m_3}$	& ---			& given 		& \checkmark		&  \checkmark		&				& \checkmark 		& HSP \& POP\\
+		                						& \\
+	$\widehat{m_4}$	& ---			& estimated	& \checkmark		&  \checkmark		& 				& \checkmark 		& HSP \& POP\\
+		                						& \\
+	\hline
+    \end{tabular}
+    \label{parameter} 
 \end{center} 
@@
 
+\section*{Reproductive potential}
+
+\renewcommand{\theequation}{A\arabic{equation}}
+Here, we introduce the concept of the reproductive potential of parent $i$ or $j$, which is defined as the expected number of surviving offspring at sampling time, denoted by $\lambda_{i,1}$ or $\lambda_{j,2}$.
+The reproductive potential is determined by several factors, including the parent’s age, weight, residence time on the spawning ground.
+It should be noted that the magnitude of this parameter ($\lambda_{i,1}$ or $\lambda_{i,2}$) includes information about the survival rate of the offspring, the number of days after egg hatching, and the egg number; this implies that the parameter reflects the sample timing.
+It should also be noted that the modeling framework does not depend on whether the reproductive potential is heritable or not.
+
 \section*{Equation X holds under flexible assumptions for the distribution of surviving offspring number per parent}
 
-\renewcommand{\theequation}{A\arabic{equation}}
+\renewcommand{\theequation}{B\arabic{equation}}
 

### 2021-06-25 latex/ms.tex
write 2nd para in 2.2, #6

@@
 For mathematical tractability, parents have to survive during the reproductive season; therefore, both mother and father of a certain offspring have a potential to be sampled.
-Assuming invasive sampling, sampled parents in the population 1 are never sampled in the population 2.
-It should be noted that al the four kinds of a sample (i.e., $n_{\rm P, 1}$, $n_{\rm P, 2}$, $n_{\rm O, 1}$ and $n_{\rm O, 2}$) are not always required for estimating migration number or rate; what kinds of a sample are needed depends on the situation, as explained later.
-
- The numbers of MS and MO pairs are determined by pairwise comparison of all the sample individuals (${}_{n_{\rm O}}\mathrm{C}_2$ and $n_{\rm M}n_{\rm O}$ comparisons, respectively).
-As depicted in {\bf Fig~\ref{example}}, six offspring and three mothers are sampled and two MS and three MO pairs are observed.
-In our modeling framework, if an MS pair also shares a paternal-sibling (PS) relationship, we count it as an MS pair and ignore the existing full-sibling (FS) relationship.
+It should be noted that al the four kinds of a sample (i.e., $n_{\rm P, 1}$, $n_{\rm P, 2}$, $n_{\rm O, 1}$ and $n_{\rm O, 2}$) are not always required for estimating migration number or rate; what kinds of a sample are needed depends on the situation.
+In this section, we only focus HS pairs and PO pairs found between the two populations.
+For the applicability of fishery management, we assume invasive sampling procedure, preventing the finding of a parent-offspring pair such that a parent and offspring is sampled in the population 1 and 2, respectively.
+
+The numbers of HS and PO pairs found between the two populations are determined by pairwise comparison of all the sample individuals ($n_{\rm O,1}n_{\rm O,2}$ and $n_{\rm O,1}n_{\rm P,2}$ comparisons, respectively).
+As depicted in {\bf Fig~\ref{cartoon}}, X offspring and Y parents are sampled in the population 1 and X offspring and Y parents are sampled in the population 1, and X HS and Y PO pairs found between the two populations are observed.
+In addition, X and Y PO pairs found within the same population are observed, which are available to estimate parent numbers, as explain the next section.
+In our modeling framework, if full-sibling (FS) relationship is found, we count it as two HS pairs.
 

### 2021-06-28 latex/ms.tex
modify Fig.1, #3

@@
 
+%%%%%%%%%%%%%%
+\begin{center}
+Figure \ref{cartoon} is here. 
+\end{center}
+%%%%%%%%%%%%%%
+
 \subsection{Sampling}
@@
 
-The numbers of HS and PO pairs found between the two populations are determined by pairwise comparison of all the sample individuals ($n_{\rm O,1}n_{\rm O,2}$ and $n_{\rm O,1}n_{\rm P,2}$ comparisons, respectively).
-As depicted in {\bf Fig~\ref{cartoon}}, X offspring and Y parents are sampled in the population 1 and X offspring and Y parents are sampled in the population 1, and X HS and Y PO pairs found between the two populations are observed.
-In addition, X and Y PO pairs found within the same population are observed, which are available to estimate parent numbers, as explain the next section.
+The numbers of HS and PO pairs found between the two populations are determined by pairwise comparison of all the sample individuals ($n_{\rm O,1}\times n_{\rm O,2}$ and $n_{\rm O,1}\times n_{\rm P,2}$ comparisons, respectively).
+In the example depicted in {\bf Fig~\ref{cartoon}}, five offspring and four parents are sampled in the population 1 and four offspring and six parents are sampled in the population 2, and two HS and one PO pairs found between the two populations are observed.
+In addition, there are several PO pairs observed within the same population, which are available to estimate parent numbers, as explain the next section.
 In our modeling framework, if full-sibling (FS) relationship is found, we count it as two HS pairs.
@@
 In this study, a mature individual is called a parent even if it does not produce offspring.
-
-%%%%%%%%%%%%%%
-\begin{center}
-Figure \ref{cartoon} is here. 
-\end{center}
-%%%%%%%%%%%%%%
 
@@
 Sampled individuals are denoted with squares.
-Input parameters in this example: $n_{\rm P, 1}=4$, $n_{\rm P, 2}=4$, $n_{\rm O, 1}=4$, $n_{\rm O, 2}=4$, $N_{1}=16$, $N_{2}=14$, and $M=6$.
-The numbers of kinship pairs: $H_{\rm PO, 1}=1$, $H_{\rm PO, 2}=1$, $H_{\rm PO, bet}=1$, and $H_{\rm HS, bet}=2$.}
+Input parameters in this example: $n_{\rm P, 1}=4$, $n_{\rm O, 1}=5$, $n_{\rm P, 2}=6$, $n_{\rm O, 2}=4$, $N_{1}=16$, $N_{2}=14$, and $M=6$.
+The numbers of kinship pairs: $H_{\rm PO, bet}=1$, $H_{\rm HS, bet}=2$, $H_{\rm PO, 1}=3$, and $H_{\rm PO, 2}=2$.}
 

### 2021-06-28 latex/ms.tex
done in 2.2, #6

@@
 \section{Theory}\label{sec2}
-In this section, we present the theoretical foundation for estimating a migrant number and a migration rate using HS or PO pairs, which are found between two populations with a different sample timing.
+In this section, we present the theoretical foundation for estimating a migrant number and a migration rate of iteroparous species using HS or PO pairs, which are found between two populations with a different sample timing.
 While the estimators can hold under flexible assumptions for reproduction (see {\bf Appendix}), here we assume a relatively simple situation for explanation purposes.
@@
 \begin{center}
-Table \ref{symbols} is here. 
+\fbox{Table \ref{symbols} is here. }
 \end{center}
@@
 Similar to the population 1, $N_2$ parents produce offspring in which the number is determined by $\lambda_{j,2}$ ($j=1,2,\ldots,N_2$).
-Theoretically speaking, the number of offspring for each parent is a random variable with mean $\lambda_{i,1}$ or $\lambda_{j,2}$.
+The reproductive potential is determined by several factors and its details are summarized in {\bf Appendix}; theoretically speaking, the number of offspring for each parent is set as a random variable with mean $\lambda_{i,1}$ or $\lambda_{j,2}$.
 
@@
 \begin{center}
-Figure \ref{cartoon} is here. 
+\fbox{Figure \ref{cartoon} is here. }
 \end{center}
@@
 To estimate the migration number or rate, we utilize the number of HS and/or PO pairs observed in a sample.
-In the both populations, $n_{\rm O, 1}$ and $n_{\rm O, 2}$ offspring are randomly sampled.
+In the both populations, $n_{\rm O, 1}$ and $n_{\rm O, 2}$ offspring are randomly sampled, which are identified as young-of-year individuals without errors.
 Additionally, $n_{\rm P, 1}$ and $n_{\rm P, 2}$ parents are randomly sampled immediately after the end of the reproductive season in the first and second year, respectively.
-For mathematical tractability, parents have to survive during the reproductive season; therefore, both mother and father of a certain offspring have a potential to be sampled.
+For mathematical tractability, parents have to survive during the reproductive season; therefore, both mother and father of a certain offspring have a potential to be sampled even in the same year.
 It should be noted that al the four kinds of a sample (i.e., $n_{\rm P, 1}$, $n_{\rm P, 2}$, $n_{\rm O, 1}$ and $n_{\rm O, 2}$) are not always required for estimating migration number or rate; what kinds of a sample are needed depends on the situation.
 In this section, we only focus HS pairs and PO pairs found between the two populations.
-For the applicability of fishery management, we assume invasive sampling procedure, preventing the finding of a parent-offspring pair such that a parent and offspring is sampled in the population 1 and 2, respectively.
-
-The numbers of HS and PO pairs found between the two populations are determined by pairwise comparison of all the sample individuals ($n_{\rm O,1}\times n_{\rm O,2}$ and $n_{\rm O,1}\times n_{\rm P,2}$ comparisons, respectively).
+For the applicability of fishery management, we assume invatsive sampling procedure, preventing the finding of a parent-offspring pair such that a parent and offspring is sampled in the population 1 and 2, respectively.
+
 In the example depicted in {\bf Fig~\ref{cartoon}}, five offspring and four parents are sampled in the population 1 and four offspring and six parents are sampled in the population 2, and two HS and one PO pairs found between the two populations are observed.
@@
 In our modeling framework, if full-sibling (FS) relationship is found, we count it as two HS pairs.
+The numbers of HS and PO pairs found between the two populations are determined by pairwise comparison of all the sample individuals ($n_{\rm O,1}\times n_{\rm O,2}$ and $n_{\rm O,1}\times n_{\rm P,2}$ comparisons, respectively).
 
 \textcolor{red}{kokomade!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!}
-
-Although the theoretical framework allows a flexible setting of the reproductive potential,
-
-どのように子供を産むのか。我々のモデルは、フレキシブルな仮定に対応できるが詳細は付録に
-In this study, a mature individual is called a parent even if it does not produce offspring.
-
-and there are migrant individuals between the two populations.
-also no population subdivision or spatial struc- ture.
-In this study, a mature female is called a mother even if she does not produce offspring.
-For mathematical tractability, we assume that only one spawning ground exists in which the mothers remain for the entire spawning season.
-Following (Akita, 2020), our modeling frame- work employs two types of overdispersed reproduction: parental and nonparental variations.
-Thus, the former indicates a variation caused by the mother's covariates, such as age, weight, and residence time on the spawning ground, while the latter indicates a variation caused by nonrandom stochastic events during a series of reproductive episodes, which are independent of the mother's covariates, such as family-correlated survivorship or the mating behavior effects (e.g., competition for males/females and correlation between mating op- portunities of the mother and the number of her offspring).
-Figure 1 illustrates a schematic diagram of the effects of parental and non- parental variations exemplified by age-dependent reproduction and family-correlated survival on kinship relationships in a population.
-Detailed definitions of parental and nonparental variations are stated in (Akita, 2020).
-Appendix 1 provides the theoretical foundation of both parental and nonparental variations in reproduction.
-
-\begin{itemize}
-  \item 移動が双方向
-  \item 性比1:1およびランダム交配を仮定して両性を考慮
-  \item 繁殖ポテンシャルが一定でない
-  \item 移動しやすさが繁殖ポテンシャルに依存
-\end{itemize}
-といった要素を追加していく。また，どのモデルでも共通して仮定しているのは以下の５点である。
-\begin{enumerate}
-  \item 年をまたぐ多回繁殖
-  \item 親魚によるサブ集団間の移動は，繁殖シーズンの間に起きる
-  \item サンプルされる当歳魚（０歳）は，必ずサンプルされたサブ集団で産まれる
-  \item 当歳魚かどうかの判断は１００％可能
-  \item サンプル間の近親判別では，１００％の成功率で半兄弟ペアか否かがなされる
-\end{enumerate}
-また，性成熟した個体を親と呼ぶことにする。
 

### 2021-06-28 latex/ms.tex
done in 2.3, #6

@@
 For mathematical tractability, parents have to survive during the reproductive season; therefore, both mother and father of a certain offspring have a potential to be sampled even in the same year.
-It should be noted that al the four kinds of a sample (i.e., $n_{\rm P, 1}$, $n_{\rm P, 2}$, $n_{\rm O, 1}$ and $n_{\rm O, 2}$) are not always required for estimating migration number or rate; what kinds of a sample are needed depends on the situation.
+It should be noted that al the four kinds of a sample (i.e., $n_{\rm P, 1}$, $n_{\rm P, 2}$, $n_{\rm O, 1}$, and $n_{\rm O, 2}$) are not always required for estimating migration number or rate; what kinds of a sample are needed depends on the situation.
 In this section, we only focus HS pairs and PO pairs found between the two populations.
-For the applicability of fishery management, we assume invatsive sampling procedure, preventing the finding of a parent-offspring pair such that a parent and offspring is sampled in the population 1 and 2, respectively.
+For the applicability of fishery management, we assume invasive sampling procedure, preventing the finding of a parent-offspring pair such that a parent and offspring is sampled in the population 1 and 2, respectively.
 
@@
 
-\textcolor{red}{kokomade!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!}
-
-\subsection{HSP-based model}
+\subsection{HS pair-based model}
 
 Here we consider the probability that two offspring sampled in the population 1 and 2 share an HS relationship with an arbitrary mother or father, denoted by $\pi_{\rm HS, bet}$.
+For the explanation purpose, we assume equal reproductive potential among parents, although this assumption can be relaxed for most of the case (see details in {\bf Appendix}).
+$\pi_{\rm HS, bet}$ can be partitioned into the three probabilities: (i) the probability that sampled offspring in the population 1 born to a parent that safely arrives in the population 2 (hereafter, called "migrant"); (ii) the probability that sampled offspring in the population 2 born to a migrant; and (iii) the probability that randomly selected two migrants are identical.
 
-For the explanation purpose,
-
-lambdaは全ての親で一定とするが、この仮定をゆるくしても多くの場合我々の議論は成立する。
-
-Assuming that every fathers in the population 1 has a same reproductive potential, どの母親も同じような繁殖ポテンシャルを持つと仮定 すると，移動する母親の子供をサブ集団1でサンプルする確率は$rM/rN$...となる。
-
+To assess these probabilities, recall there must be two parents of arbitral offspring; the first probability is the sum of father-offspring and mother-offspring relationship, which can be written by $r_{\rm M}M/(r_{\rm S,1}N_{1}) + (1 - r_{\rm M})M/((1-r_{\rm S,1})N_{1})$, where $r_{\rm M}$ and $r_{\rm S,1}$ indicates sex ratio of parents in the migrants and in the whole of the population 1, respectively.
+Assuming $r_{\rm M} = r_{\rm S,1}$, the probability is simplified as $2M/N_{1}$.
+Similarly, the second probability is simplified as $2M/N_{2}$, implying the assumption of equal sex ratio in the migrants and the others.
+Taken together, we obtain
 \begin{align}
 \pi_{\rm HS,bet} &= \frac{2M}{N_{1}} \frac{2M}{N_{2}} \frac{1}{M} \nonumber\\
-&= \frac{4M}{N_{1}N_{2}}
+&= \frac{4M}{N_{1}N_{2}}.
 \label{HS-1}
 \end{align}
+This form also holds under a flexible setting for the reproductive potential, such as a situation with random variable of $\lambda_{i,1}$ and $\lambda_{j,2}$, as noted in {\bf Appendix}.
+
+Let $H_{\rm HS,bet}$ be the number of HS pairs found in offspring samples of size $n_{\rm O, 1}$ and $n_{\rm O, 2}$.
+Assuming that the total number of HS pairs in the population is much higher than $H_{\rm HS,bet}$, the distribution is approximated by a binomial form (i.e., $H_{\rm HS,bet} \sim {\rm Binom}[\pi_{\rm HS,bet}, n_{\rm O, 1} n_{\rm O, 2}]$); thus, the theoretical expectation of $H_{\rm HS,bet}$ is
 
@@
 \mathbb{E}[H_{\rm HS, bet}] &= \pi_{\rm HS,bet} n_{\rm O, 1} n_{\rm O, 2} \nonumber\\
-&= \frac{ 4 n_{\rm O, 1} n_{\rm O, 2} M } { N_{1} N_{2} } \\
-&= \frac{ 4 n_{\rm O, 1} n_{\rm O, 2} m } { N_{2} }
-\label{HS-2}
+&= \frac{ 4 n_{\rm O, 1} n_{\rm O, 2} M } { N_{1} N_{2} } \label{HS-2-1}\\
+&= \frac{ 4 n_{\rm O, 1} n_{\rm O, 2} m } { N_{2} },
+\label{HS-2-2}
 \end{align}
+where $m$ indicates the migration rate satisfying $M = mN_{1}$.
+The observed number of HS pairs in a sample is defined by $\widetilde{H}_{\rm HS, bet}$, and $\mathbb{E}[H_{\rm HS, bet}]$ in Equation \ref{HS-2-1} is replaced by $\widetilde{H}_{\rm HS, bet}$, generating the linear estimator of $M$:
 
 \begin{align}
-\widehat{M_1} &= \frac{N_{1} N_{2} \widetilde{H}_{\rm HS, bet} } {4 n_{\rm O, 1} n_{\rm O, 2} }
+\widehat{M_1} &= \frac{N_{1} N_{2} \widetilde{H}_{\rm HS, bet} } {4 n_{\rm O, 1} n_{\rm O, 2} }.
 \label{HS-3}
 \end{align}
+In this paper, a ``tilde'' and ``hat'' indicates the observation and estimator of a variable, respectively.
+Similarly, $\mathbb{E}[H_{\rm HS, bet}]$ in Equation \ref{HS-2-2} is replaced by $\widetilde{H}_{\rm HS, bet}$, generating the linear estimator of $m$:
 
@@
 \end{align}
+Subscription of these estimators indicates the numbering of proposed estimators appeared in this paper, which is summarized in Table \ref{parameter}.
 
-より一般的な説明は付録に載せた。
+%%%%%%%%%%%%%%
+\begin{center}
+\fbox{Table \ref{parameter} is here. }
+\end{center}
+%%%%%%%%%%%%%%
 
-\subsection{POP-based model}
+\textcolor{red}{kokomade!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!}
+
+\subsection{PO pair-based model}
 

### 2021-06-29 latex/ms.tex
write 1st para in 2.4, #6

@@
 
-Here we consider the probability that two offspring sampled in the population 1 and 2 share an HS relationship with an arbitrary mother or father, denoted by $\pi_{\rm HS, bet}$.
-For the explanation purpose, we assume equal reproductive potential among parents, although this assumption can be relaxed for most of the case (see details in {\bf Appendix}).
-$\pi_{\rm HS, bet}$ can be partitioned into the three probabilities: (i) the probability that sampled offspring in the population 1 born to a parent that safely arrives in the population 2 (hereafter, called "migrant"); (ii) the probability that sampled offspring in the population 2 born to a migrant; and (iii) the probability that randomly selected two migrants are identical.
+Here, we consider the probability that two offspring sampled in the population 1 and 2 share an HS relationship with an arbitrary mother or father, denoted by $\pi_{\rm HS, bet}$.
+For the explanation purpose, we assume equal reproductive potential among parents in this section, although this assumption can be relaxed for most of the case (see details in {\bf Appendix}).
+$\pi_{\rm HS, bet}$ can be partitioned into the three probabilities: (i) the probability that sampled offspring in the population 1 born to a parent that safely arrives in the population 2 (hereafter, called "migrant"); (ii) the probability that sampled offspring in the population 2 born to a migrant; and (iii) the probability that the migrant of a sampled offspring in the population 1 and the migrant of a sampled offspring in the population 2 are identical.
 
@@
 Similarly, the second probability is simplified as $2M/N_{2}$, implying the assumption of equal sex ratio in the migrants and the others.
+The third probability corresponds to the probability that randomly selected two migrants are identical, that is $1/M$.
 Taken together, we obtain
@@
 
+\subsection{PO pair-based model}
+
+Next, we consider the probability that offspring sampled in the population 1 and a parent sampled in the population 2 share an PO relationship, denoted by $\pi_{\rm PO, bet}$.
+$\pi_{\rm PO, bet}$ can be partitioned into the three probabilities: (i) the probability that sampled offspring in the population 1 born to a migrant; (ii) the probability that a migrant is sampled; and (iii) the probability that the migrant of a sampled offspring in the population 1 and the migrant sampled in the population 2 are identical.
+
 \textcolor{red}{kokomade!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!}
 
-\subsection{PO pair-based model}
-
+To assess these probabilities, recall there must be two parents of arbitral offspring; the first probability is the sum of father-offspring and mother-offspring relationship, which can be written by $r_{\rm M}M/(r_{\rm S,1}N_{1}) + (1 - r_{\rm M})M/((1-r_{\rm S,1})N_{1})$, where $r_{\rm M}$ and $r_{\rm S,1}$ indicates sex ratio of parents in the migrants and in the whole of the population 1, respectively.
+Assuming $r_{\rm M} = r_{\rm S,1}$, the probability is simplified as $2M/N_{1}$.
+Similarly, the second probability is simplified as $2M/N_{2}$, implying the assumption of equal sex ratio in the migrants and the others.
+Taken together, we obtain
 \begin{align}

### 2021-06-30 latex/ms.tex
done 2.4,#6

@@
 where $m$ indicates the migration rate satisfying $M = mN_{1}$.
-The observed number of HS pairs in a sample is defined by $\widetilde{H}_{\rm HS, bet}$, and $\mathbb{E}[H_{\rm HS, bet}]$ in Equation \ref{HS-2-1} is replaced by $\widetilde{H}_{\rm HS, bet}$, generating the linear estimator of $M$:
+The observed number of HS pairs in a sample found between the two populations is defined by $\widetilde{H}_{\rm HS, bet}$, and $\mathbb{E}[H_{\rm HS, bet}]$ in Equation \ref{HS-2-1} is replaced by $\widetilde{H}_{\rm HS, bet}$, generating the linear estimator of $M$:
 
@@
 
-\textcolor{red}{kokomade!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!}
-
-To assess these probabilities, recall there must be two parents of arbitral offspring; the first probability is the sum of father-offspring and mother-offspring relationship, which can be written by $r_{\rm M}M/(r_{\rm S,1}N_{1}) + (1 - r_{\rm M})M/((1-r_{\rm S,1})N_{1})$, where $r_{\rm M}$ and $r_{\rm S,1}$ indicates sex ratio of parents in the migrants and in the whole of the population 1, respectively.
-Assuming $r_{\rm M} = r_{\rm S,1}$, the probability is simplified as $2M/N_{1}$.
-Similarly, the second probability is simplified as $2M/N_{2}$, implying the assumption of equal sex ratio in the migrants and the others.
+The first and second probabilities are the same as the one introduced in the previous subsection, that is, $2M/N_{1}$ and $1/M$.
+The second probability is $M/N_{2}$ by definition.
 Taken together, we obtain
@@
 
+Let $H_{\rm PO,bet}$ be the number of PO pairs found in offspring samples of size $n_{\rm O, 1}$ and parent samples of size $n_{\rm P, 2}$.
+Assuming that the total number of PO pairs in the two populations is much higher than $H_{\rm PO,bet}$, the distribution is approximated by a binomial form (i.e., $H_{\rm PO,bet} \sim {\rm Binom}[\pi_{\rm PO,bet}, n_{\rm O, 1} n_{\rm P, 2}]$); thus, the theoretical expectation of $H_{\rm PO,bet}$ is
 \begin{align}
 \mathbb{E}[H_{\rm PO, bet}] &= \pi_{\rm PO,bet} n_{\rm O, 1} n_{\rm P, 2} \nonumber\\
-&= \frac{ 2 n_{\rm O, 1} n_{\rm P, 2} M } { N_{1} N_{2} }
-\label{PO-2}
-\end{align}
-
-\begin{align}
-\widehat{M_2} &= \frac{N_{1} N_{2} \widetilde{H}_{\rm PO,bet} } {2 n_{\rm O, 1} n_{\rm P, 2} }
+&= \frac{ 2 n_{\rm O, 1} n_{\rm P, 2} M } { N_{1} N_{2} } \label{PO-2-1} \\
+&= \frac{ 2 n_{\rm O, 1} n_{\rm P, 2} m } { N_{2} }
+\label{PO-2-2}
+\end{align}
+
+The observed number of PO pairs in a sample is defined by $\widetilde{H}_{\rm PO, bet}$, and $\mathbb{E}[H_{\rm PO, bet}]$ in Equation \ref{HS-2-1} is replaced by $\widetilde{H}_{\rm HS, bet}$, generating the linear estimator of $M$ and $m$:
+\begin{align}
+\widehat{M_2} &= \frac{N_{1} N_{2} \widetilde{H}_{\rm PO,bet} } {2 n_{\rm O, 1} n_{\rm P, 2} },
 \label{PO-3}
 \end{align}
-
-\begin{align}
-\widehat{m_2} &= \frac{N_{2} \widetilde{H}_{\rm PO,bet} } {2 n_{\rm O, 1} n_{\rm P, 2} }
+and
+\begin{align}
+\widehat{m_2} &= \frac{N_{2} \widetilde{H}_{\rm PO,bet} } {2 n_{\rm O, 1} n_{\rm P, 2} }.
 \label{PO-4}
@@
 \end{align}
+
+\textcolor{red}{kokomade!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!}
 

### 2021-06-30 latex/ms.tex
done 2.5,#6

@@
 
-\begin{align}
-n_{\rm O, 1} n_{\rm O, 2} &> \frac{ N_{2} } { 4m }
+Proposed estimators are based on the observed number of kinship pairs.
+Their expected number is linearly determined by the number of pairwise comparison (Eqs.~\ref{HS-2-1}-\ref{HS-2-2} and \ref{PO-2-1}-\ref{PO-2-2}), providing guidance for a sample size to ensure the condition that at least one or more kinship pairs can be found.
+The conditions are given by
+\begin{align}
+n_{\rm O, 1} n_{\rm O, 2} &> \frac{ N_{2} } { 4m },
 \label{RS-1}
 \end{align}
-
-\begin{align}
-n_{\rm O, 1} n_{\rm P, 2} &> \frac{ N_{2} } { 2m }
+and
+\begin{align}
+n_{\rm O, 1} n_{\rm P, 2} &> \frac{ N_{2} } { 2m }.
 \label{RS-2}
 \end{align}
+Roughly speaking, required sample size to ensure above conditions is that $n>\sqrt{N_2}$, where $n = n_{\rm O, 1}=n_{\rm O, 2}=n_{\rm P, 2}$.
+It should be noted that very tiny $m$, which dramatically increases the required sample size, produces genetic differences between two populations.
+In such a case, there are several methods to estimate migration rate by population genetics technique; alternatively, we focus the situation of moderate/large migration rate, which leads little genetic differences between two populations.
 

### 2021-07-19 latex/ms.tex
roughly done section 2, #6

@@
 \usepackage{color}
-\def\RED#1{\textcolor{black}{#1}} %% 
+\def\RED#1{\textcolor{red}{#1}} %% 
 \def\BLUE#1{\textcolor{blue}{#1}} %% 
@@
 After the reproductive season, part of the parents would start to moving towards the population 2; $M$ survived migrants arrive in the population 2 so that there are $N_2$ parents in the population 2 at the beginning of the second year ($M < N_2$).
-Similar to the population 1, $N_2$ parents produce offspring in which the number is determined by $\lambda_{j,2}$ ($j=1,2,\ldots,N_2$).
+Similar to the population 1, $N_2$ parents produce offspring in which the number is governed by $\lambda_{j,2}$ ($j=1,2,\ldots,N_2$).
 The reproductive potential is determined by several factors and its details are summarized in {\bf Appendix}; theoretically speaking, the number of offspring for each parent is set as a random variable with mean $\lambda_{i,1}$ or $\lambda_{j,2}$.
@@
 For mathematical tractability, parents have to survive during the reproductive season; therefore, both mother and father of a certain offspring have a potential to be sampled even in the same year.
-It should be noted that al the four kinds of a sample (i.e., $n_{\rm P, 1}$, $n_{\rm P, 2}$, $n_{\rm O, 1}$, and $n_{\rm O, 2}$) are not always required for estimating migration number or rate; what kinds of a sample are needed depends on the situation.
+It should be noted that all the four kinds of a sample (i.e., $n_{\rm P, 1}$, $n_{\rm P, 2}$, $n_{\rm O, 1}$, and $n_{\rm O, 2}$) are not always required for estimating migration number or rate; what kinds of a sample are needed depends on the situation \RED{(rewrite clearly)}.
 In this section, we only focus HS pairs and PO pairs found between the two populations.
@@
 
+\subsection{Efficient use of kinship pairs found between populations}
+
+So far, we only focus the usage of HS pairs or PO pairs found between populations.
+When the both kinship pairs are available, we can obtain efficient estimators by combined $\widehat{M_1}$ and $\widehat{M_2}$ for migration number:
+\begin{align}
+\widehat{M_3} &= \frac{ N_{1} N_{2} \left(\widetilde{H}_{\rm HS,bet} + \widetilde{H}_{\rm PO,bet}\right) } {2n_{\rm O, 1} \left(2 n_{\rm O, 2} + n_{\rm P, 2}\right), }
+\label{AP-1}
+\end{align}
+and by combining $\widehat{m_1}$ and $\widehat{m_2}$ for migration rate: 
+\begin{align}
+\widehat{m_3} &= \frac{ N_{2} \left(\widetilde{H}_{\rm HS,bet} + \widetilde{H}_{\rm PO,bet}\right) } {2n_{\rm O, 1} \left(2 n_{\rm O, 2} + n_{\rm P, 2}\right). }
+\label{AP-2}
+\end{align}
+For those estimators, $\widetilde{H}_{\rm HS,bet}$ and $\widetilde{H}_{\rm PO,bet}$ is weighted by a sample size $n_{\rm O, 2}$ and $n_{\rm P, 2}$, respectively.
+
 \textcolor{red}{kokomade!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!}
-
-\subsection{Efficient use of kinship pairs found between populations}
-
-\begin{align}
-\widehat{M_3} &= \frac{ N_{1} N_{2} \left(\widetilde{H}_{\rm HS,bet} + \widetilde{H}_{\rm PO,bet}\right) } {2n_{\rm O, 1} \left(2 n_{\rm O, 2} + n_{\rm P, 2}\right) }
-\label{AP-1}
-\end{align}
-
-\begin{align}
-\widehat{m_3} &= \frac{ N_{2} \left(\widetilde{H}_{\rm HS,bet} + \widetilde{H}_{\rm PO,bet}\right) } {2n_{\rm O, 1} \left(2 n_{\rm O, 2} + n_{\rm P, 2}\right) }
-\label{AP-2}
-\end{align}
-
-サンプル数の少なさを補えるかも。
-
 \section{Applications}\label{sec3}

### 2021-08-18 latex/ms.tex
memo 3.1,#7
Application is merged into Theory,#7

@@
 While the estimators can hold under flexible assumptions for reproduction (see {\bf Appendix}), here we assume a relatively simple situation for explanation purposes.
-It should be noted that the formulation of the estimators, presented in Equations 4-5 and 7-8, is a function with parent numbers for each population; in the next section, we provide the treatment for estimating the unknown parent numbers by additional usage of HS and/or PO pairs.
 The main symbols used in the current paper are summarized in {\bf Table \ref{symbols}}.
@@
 $\pi_{\rm PO, bet}$ can be partitioned into the three probabilities: (i) the probability that sampled offspring in the population 1 born to a migrant; (ii) the probability that a migrant is sampled; and (iii) the probability that the migrant of a sampled offspring in the population 1 and the migrant sampled in the population 2 are identical.
-
 The first and second probabilities are the same as the one introduced in the previous subsection, that is, $2M/N_{1}$ and $1/M$.
@@
 \pi_{\rm PO,bet} &= \frac{2M}{N_{1}} \frac{M}{N_{2}} \frac{1}{M} \nonumber\\
-&= \frac{2M}{N_{1}N_{2}}
+&= \frac{2M}{N_{1}N_{2}}.
 \label{PO-1}
@@
 &= \frac{ 2 n_{\rm O, 1} n_{\rm P, 2} M } { N_{1} N_{2} } \label{PO-2-1} \\
-&= \frac{ 2 n_{\rm O, 1} n_{\rm P, 2} m } { N_{2} }
+&= \frac{ 2 n_{\rm O, 1} n_{\rm P, 2} m } { N_{2} }.
 \label{PO-2-2}
 \end{align}
-
 The observed number of PO pairs in a sample is defined by $\widetilde{H}_{\rm PO, bet}$, and $\mathbb{E}[H_{\rm PO, bet}]$ in Equation \ref{HS-2-1} is replaced by $\widetilde{H}_{\rm HS, bet}$, generating the linear estimator of $M$ and $m$:
@@
 
-So far, we only focus the usage of HS pairs or PO pairs found between populations.
-When the both kinship pairs are available, we can obtain efficient estimators by combined $\widehat{M_1}$ and $\widehat{M_2}$ for migration number:
+When the both HS pairs and PO pairs, which are found between populations, are simultaneously available, we can obtain efficient estimators by combined $\widehat{M_1}$ and $\widehat{M_2}$ for migration number:
 \begin{align}
@@
 
+\subsection{Parent number can be estimated by PO pairs found within a population}
+
+So far, we provide the formulation of the estimators, presented in Equations 4-5 and 7-8, is a function with parent numbers for each population.
+
+; in this subsection, we provide the treatment for estimating the unknown parent numbers by additional usage of HS and/or PO pairs.
+
 \textcolor{red}{kokomade!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!}
-\section{Applications}\label{sec3}
-
-\subsection{Parent number can be estimated by PO pairs found within a population}
+
+これまでは、N1とN2は既知として推定量を導出してきた。もしこれらが未知であるのあらば、N1やN2は何かしらの方法で推定する必要がある。このセクションでは、CKMRの知見に基づきこれらについても近親関係から推定することで、移動率に関する推定を、近親関係からのみで完結させる。
+
+前のセクションでは、２年目に集団２から親と子を両方サンプルしていて、移動を推定していた。これらのサンプルを用いて、N2を推定することが可能である。
 
@@
 \subsection{Individual-based model}
+
+\section{Results and Discussion}\label{sec3}
 

### 2021-08-20 latex/ms.tex
Done 2.7,#7

@@
 It should be noted that all the four kinds of a sample (i.e., $n_{\rm P, 1}$, $n_{\rm P, 2}$, $n_{\rm O, 1}$, and $n_{\rm O, 2}$) are not always required for estimating migration number or rate; what kinds of a sample are needed depends on the situation \RED{(rewrite clearly)}.
-In this section, we only focus HS pairs and PO pairs found between the two populations.
+Up to the subsection 2.6, we only focus HS pairs and PO pairs found between the two populations.
 For the applicability of fishery management, we assume invasive sampling procedure, preventing the finding of a parent-offspring pair such that a parent and offspring is sampled in the population 1 and 2, respectively.
@@
 \widehat{m_1} &= \frac{N_{2} \widetilde{H}_{\rm HS, bet} } {4 n_{\rm O, 1} n_{\rm O, 2} }
-\label{HS-3}
+\label{HS-4}
 \end{align}
@@
 \end{align}
-The observed number of PO pairs in a sample is defined by $\widetilde{H}_{\rm PO, bet}$, and $\mathbb{E}[H_{\rm PO, bet}]$ in Equation \ref{HS-2-1} is replaced by $\widetilde{H}_{\rm HS, bet}$, generating the linear estimator of $M$ and $m$:
+The observed number of PO pairs in a sample is defined by $\widetilde{H}_{\rm PO, bet}$, and $\mathbb{E}[H_{\rm PO, bet}]$ in Equations \ref{PO-2-1} and \ref{PO-2-2} are replaced by $\widetilde{H}_{\rm PO, bet}$, generating the linear estimator of $M$ and $m$:
 \begin{align}
@@
 
-So far, we provide the formulation of the estimators, presented in Equations 4-5 and 7-8, is a function with parent numbers for each population.
-
-; in this subsection, we provide the treatment for estimating the unknown parent numbers by additional usage of HS and/or PO pairs.
-
-\textcolor{red}{kokomade!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!}
-
-これまでは、N1とN2は既知として推定量を導出してきた。もしこれらが未知であるのあらば、N1やN2は何かしらの方法で推定する必要がある。このセクションでは、CKMRの知見に基づきこれらについても近親関係から推定することで、移動率に関する推定を、近親関係からのみで完結させる。
-
-前のセクションでは、２年目に集団２から親と子を両方サンプルしていて、移動を推定していた。これらのサンプルを用いて、N2を推定することが可能である。
-
-\begin{align}
-\widehat{N_2} &= \frac{ 2 n_{\rm O, 2} n_{\rm P, 2} + 1 }{\widetilde{H}_{\rm PO, 2} + 1} 
+So far, we provide the formulation of the estimators, presented in Equations \ref{HS-3}-\ref{HS-4} and \ref{PO-3}-\ref{PO-4}, is a function with parent numbers for each population ($N_1$ and/or $N_2$); in other words, such estimators are available only when those parent number(s) are known.
+In this subsection, we provide the treatment for estimating the unknown parent numbers by additional usage of PO pairs, producing estimators for migrant number and migration rate that can be obtained only from the genetic data.
+
+When PO pairs found in offspring samples and parent samples both from the population 2 in the second year are available, standard estimator of parental number can be obtained \cite[]{bravington2016close}, given by
+
+\begin{align}
+\widehat{N_2} &= \frac{ 2 n_{\rm O, 2} n_{\rm P, 2} + 1 }{\widetilde{H}_{\rm PO, 2} + 1} ,
 \label{AP-3}
 \end{align}
-subpop2の親子もわかるはず。$N_2$を推定値で置き換えて
-
-\begin{align}
-\widehat{M_4} &=  \frac{ N_{1} \left(\widetilde{H}_{\rm HS,bet} + \widetilde{H}_{\rm PO,bet}\right) \left(2 n_{\rm O, 2} n_{\rm P, 2} + 1\right)} {2n_{\rm O, 1} \left(2 n_{\rm O, 2} + n_{\rm P, 2}\right) \left(\widetilde{H}_{\rm PO, 2} + 1\right)}
+where $\widetilde{H}_{\rm PO, 2}$ be the observed number of PO pairs found in offspring samples of size $n_{\rm O, 2}$ and parent samples of size $n_{\rm P, 2}$.
+The term ``$+1$'' reduces the bias especially when $\widetilde{H}_{\rm PO, 2}$ is small \cite[e.g.,][]{ecolevol2021p}, where a similar derivation of this bias correction is provided in \cite{Akita_2019}.
+By replacing $N_2$ by $\widehat{N_2}$ in Eqs.~\ref{AP-1} and \ref{AP-2}, we can obtain the following estimators:
+
+\begin{align}
+\widehat{M_4} &=  \frac{ N_{1} \left(\widetilde{H}_{\rm HS,bet} + \widetilde{H}_{\rm PO,bet}\right) \left(2 n_{\rm O, 2} n_{\rm P, 2} + 1\right)} {2n_{\rm O, 1} \left(2 n_{\rm O, 2} + n_{\rm P, 2}\right) \left(\widetilde{H}_{\rm PO, 2} + 1\right)},
 \label{AP-4}
 \end{align}
-
-migration rateを推定すると考えると、
-
-\begin{align}
-\widehat{m_4} &=  \frac{ \left(\widetilde{H}_{\rm HS,bet} + \widetilde{H}_{\rm PO,bet}\right) \left(2 n_{\rm O, 2} n_{\rm P, 2} + 1\right)} {2n_{\rm O, 1} \left(2 n_{\rm O, 2} + n_{\rm P, 2}\right) \left(\widetilde{H}_{\rm PO, 2} + 1\right)}
+and
+\begin{align}
+\widehat{m_4} &=  \frac{ \left(\widetilde{H}_{\rm HS,bet} + \widetilde{H}_{\rm PO,bet}\right) \left(2 n_{\rm O, 2} n_{\rm P, 2} + 1\right)} {2n_{\rm O, 1} \left(2 n_{\rm O, 2} + n_{\rm P, 2}\right) \left(\widetilde{H}_{\rm PO, 2} + 1\right)}.
 \label{AP-5}
 \end{align}
-
-同様に、$N_1$も推定値で置き換えて
-\begin{align}
-\widehat{N_1} &= \frac{ 2 n_{\rm O, 1} n_{\rm P, 1} + 1 }{\widetilde{H}_{\rm PO, 1} + 1} 
+While estimator of the migrate number (Eq.~\ref{AP-4}) requires the (unknown) parent number in the population 1 ($N_{1}$), estimator of the migration rate (Eq.~\ref{AP-5}) can be obtained only the observed kinship pairs.
+
+Similar to estimating $N_2$, when PO pairs found in offspring samples and parent samples both from the population 1 in the first year are also available, we can obtain the estimator of $N_1$, written by
+\begin{align}
+\widehat{N_1} &= \frac{ 2 n_{\rm O, 1} n_{\rm P, 1} + 1 }{\widetilde{H}_{\rm PO, 1} + 1},
 \label{AP-6}
 \end{align}
-
-\begin{align}
-\widehat{M_5} &=  \frac{ \left(\widetilde{H}_{\rm HS,bet} + \widetilde{H}_{\rm PO,bet}\right) \left(2 n_{\rm O, 1} n_{\rm P, 1} + 1\right) \left(2 n_{\rm O, 2} n_{\rm P, 2} + 1\right)} {2n_{\rm O, 1} \left(2 n_{\rm O, 2} + n_{\rm P, 2}\right) \left(\widetilde{H}_{\rm PO, 1} + 1\right) \left(\widetilde{H}_{\rm PO, 2} + 1\right)}
+where $\widetilde{H}_{\rm PO, 1}$ be the observed number of PO pairs found in offspring samples of size $n_{\rm O, 1}$ and parent samples of size $n_{\rm P, 1}$.
+By replacing $N_1$ by $\widehat{N_1}$ in Eq.~\ref{AP-4}, we can obtain the estimator of migration number that can be calculated only from genetic data, given by
+\begin{align}
+\widehat{M_5} &=  \frac{ \left(\widetilde{H}_{\rm HS,bet} + \widetilde{H}_{\rm PO,bet}\right) \left(2 n_{\rm O, 1} n_{\rm P, 1} + 1\right) \left(2 n_{\rm O, 2} n_{\rm P, 2} + 1\right)} {2n_{\rm O, 1} \left(2 n_{\rm O, 2} + n_{\rm P, 2}\right) \left(\widetilde{H}_{\rm PO, 1} + 1\right) \left(\widetilde{H}_{\rm PO, 2} + 1\right)}.
 \label{AP-7}
@@
 \section{Results and Discussion}\label{sec3}
+
+\begin{comment}
 
@@
 (2018) developed a genetical method for estimating $N_{\rm e}/N$ and $N_{\rm b}/N$ via estimating the degree of nonparental variation from fecundity data in southern bluefin tuna.
+
+\end{comment}
 

### 2021-08-20 latex/ms.tex
add new subsection for explation of extension of the model, 2.8,#7

@@
 
-\subsection{Parent number can be estimated by PO pairs found within a population}
+\subsection{Estimation of parent number by PO pairs found within a population}
 
@@
 
+Table \ref{parameter} summarizes the conditions for estimators appeared in this paper as to whether $N_1$ and/or $N_2$ are known and which type of samples are needed for estimation, and provides required kinship type for calculating the estimator.
+
+\subsection{Variation in reproductive potential among individuals and populations}
+
+\RED{kokomade!!!!!!!!!!!!!!!!!!!!}
+
 \subsection{Individual-based model}
+
+We developed an individual-based model that tracks kinship relationships to evaluate the estimator's performance (e.g., $\widehat{N_{\rm e,m}/N_{\rm m}}$).
+The population structure was assumed to be identical to that in the development of the estimators.
+In addition, the population comprised mothers and their offspring, and it was assumed to follow a Poisson or negative binomial reproduction (the degree of skewness due to the nonparental variation is controlled by a parameter $\phi$; see {\bf Appendix B} for detalis).
+The expected number of the surviving offspring of a mother (denoted by $\lambda$) followed the density distribution $f(\lambda)$ (which is involved to the parental variation; see {\bf Appendix B} for details).
+We calculated overdispersion parameter ($c$) from $\phi$ and $f(\lambda)$, as well as confirmed numerically that the value of $c$ gives the same statistics of the estimators even if the combination of $\phi$ and $f(\lambda)$ differs (results are not shown).
+Therefore, each offspring retained the mother's ID, making it possible to trace an MS and MO relationship.
+
+Let a parameter set ($n_{\rm O}$, $n_{\rm M}$, $N_{\rm m}$, $\phi$, and parameters that determine $f(\lambda)$) be given.
+We simulated a population history in which $N_{\rm m}$ mothers generated offspring; this process was repeated 100 times.
+The sampling process for each history was repeated 10{,}000 times, acquiring 1{,}000{,}000 data points that were utilized to construct the distribution of the estimators for each parameter set.
+Furthermore, true value of $N_{\rm e,m}$ was calculated from $N_{\rm m}$ and $c$ (Eqs.~\ref{Ne} and \ref{pi_MS}).
 

### 2021-08-20 latex/ms.tex
done 2.8,#7

@@
 Here, we consider the probability that two offspring sampled in the population 1 and 2 share an HS relationship with an arbitrary mother or father, denoted by $\pi_{\rm HS, bet}$.
-For the explanation purpose, we assume equal reproductive potential among parents in this section, although this assumption can be relaxed for most of the case (see details in {\bf Appendix}).
+For the explanation purpose, we assume equal reproductive potential among parents up to the subsection 2.7, although this assumption can be relaxed for most of the case (see details in {\bf Appendix}).
 $\pi_{\rm HS, bet}$ can be partitioned into the three probabilities: (i) the probability that sampled offspring in the population 1 born to a parent that safely arrives in the population 2 (hereafter, called "migrant"); (ii) the probability that sampled offspring in the population 2 born to a migrant; and (iii) the probability that the migrant of a sampled offspring in the population 1 and the migrant of a sampled offspring in the population 2 are identical.
@@
 \subsection{Variation in reproductive potential among individuals and populations}
+
+The proposed estimators are derived under the assumption that reproductive potential is the same among individuals.
+As noted in {\bf Appendix}, this assumption can be relaxed and the estimators still hold, which is exemplified in iteroparous species that may show significant variation in reproductive potential among individuals.
+Furthermore, the estimators even hold for most of the case where mean reproductive potential are different between population 1 and 2, which is exemplified in the situation that the environmental condition for reproductive success varies between populations.
+The necessary condition is that the migration event does not depends on the degree of reproductive potential (see details in  {\bf Appendix}).
 

### 2021-09-27 latex/ms.tex
add memo ,#8
catch up manuscript

@@
 Hereafter, without loss of generality, we consider the movement of parents in the direction from population 1 to population 2 and focus on the migration number or rate, and that is what we attempt to estimate.
-In this framework, considering two reproductive seasons (hereafter, we call them "the first year" and "the second year") is enough to estimate it.
+In this framework, we show that considering two reproductive seasons (hereafter, we call them "the first year" and "the second year") is enough to estimate it.
 {\bf Figure \ref{cartoon}} presents a schematic representation of the kinship relationships and movements of parents.
@@
 For mathematical tractability, parents have to survive during the reproductive season; therefore, both mother and father of a certain offspring have a potential to be sampled even in the same year.
-It should be noted that all the four kinds of a sample (i.e., $n_{\rm P, 1}$, $n_{\rm P, 2}$, $n_{\rm O, 1}$, and $n_{\rm O, 2}$) are not always required for estimating migration number or rate; what kinds of a sample are needed depends on the situation \RED{(rewrite clearly)}.
+It should be noted that all the four kinds of a sample (i.e., $n_{\rm P, 1}$, $n_{\rm P, 2}$, $n_{\rm O, 1}$, and $n_{\rm O, 2}$) are not always required for estimating migration number or rate; what kinds of a sample are needed depends on the situation, as explained later.
 Up to the subsection 2.6, we only focus HS pairs and PO pairs found between the two populations.
@@
 Roughly speaking, required sample size to ensure above conditions is that $n>\sqrt{N_2}$, where $n = n_{\rm O, 1}=n_{\rm O, 2}=n_{\rm P, 2}$.
-It should be noted that very tiny $m$, which dramatically increases the required sample size, produces genetic differences between two populations.
-In such a case, there are several methods to estimate migration rate by population genetics technique; alternatively, we focus the situation of moderate/large migration rate, which leads little genetic differences between two populations.
+It should be noted that very tiny $m$, which dramatically increases the required sample size, produces significant genetic differences between two populations.
+In such a case, there are several methods to estimate migration rate by population genetics technique; alternatively, we focus the situation of moderate/large migration rate, which leads little genetic differences between two populations (see details in {\bf Results and Discussion} section).
 
@@
 \end{align}
-where $\widetilde{H}_{\rm PO, 2}$ be the observed number of PO pairs found in offspring samples of size $n_{\rm O, 2}$ and parent samples of size $n_{\rm P, 2}$.
+where $\widetilde{H}_{\rm PO, 2}$ is the observed number of PO pairs found in offspring samples of size $n_{\rm O, 2}$ and parent samples of size $n_{\rm P, 2}$.
 The term ``$+1$'' reduces the bias especially when $\widetilde{H}_{\rm PO, 2}$ is small \cite[e.g.,][]{ecolevol2021p}, where a similar derivation of this bias correction is provided in \cite{Akita_2019}.
@@
 \end{align}
-where $\widetilde{H}_{\rm PO, 1}$ be the observed number of PO pairs found in offspring samples of size $n_{\rm O, 1}$ and parent samples of size $n_{\rm P, 1}$.
+where $\widetilde{H}_{\rm PO, 1}$ is the observed number of PO pairs found in offspring samples of size $n_{\rm O, 1}$ and parent samples of size $n_{\rm P, 1}$.
 By replacing $N_1$ by $\widehat{N_1}$ in Eq.~\ref{AP-4}, we can obtain the estimator of migration number that can be calculated only from genetic data, given by
@@
 と近似される。結局，繁殖ポテンシャルの不均一性を考慮しない結果（式\ref{3-1}）と同様になる。なお，$\boldsymbol{\lambda_1}=(\lambda_{1,1}, \ldots, \lambda_{1,N_1})$および$\boldsymbol{\lambda_2}=(\lambda_{1,2}, \ldots, \lambda_{1,N_2})$。この近似は、独立に決まる確率変数$\lambda_1$と$\lambda_2$について、$\mathbb{E}[\lambda_1/\lambda_2]=\mathbb{E}[\lambda_1] \times \mathbb{E}[1/\lambda_2] \approx 1$となる場合に成立するので、集団中に$\lambda$が極端に低い個体が存在する場合は成立しない（サブ集団１とサブ集団２でセットにして相対的な繁殖ポテンシャルを考えれば良いので、問題ないだろう）。
+
+親子ペアから親の数を推定する場合も、繁殖ポテンシャルの不均一性は問題にならない。すなわち、ビッグマザーが存在していても、それをサンプルできるかどうかは運であり、期待値は推定値に漸近するからである。
 

### 2021-09-28 latex/ms.tex
complete #7, and change variable name in .R

@@
 To estimate the migration number or rate, we utilize the number of HS and/or PO pairs observed in a sample.
-In the both populations, $n_{\rm O, 1}$ and $n_{\rm O, 2}$ offspring are randomly sampled, which are identified as young-of-year individuals without errors.
+In the both populations, $n_{\rm O, 1}$ and $n_{\rm O, 2}$ offspring are randomly sampled in the first and second year, respectively, which are identified as young-of-year individuals without errors.
 Additionally, $n_{\rm P, 1}$ and $n_{\rm P, 2}$ parents are randomly sampled immediately after the end of the reproductive season in the first and second year, respectively.
@@
 
+\subsection{Individual-based model}
+
+We developed an individual-based model that tracks kinship relationships to evaluate the estimator's performance.
+The population structure was assumed to be identical to that in the development of the estimators.
+The population 1 and 2 comprised $N_1$ and $N_2$ parents with an equal sex ratio, and their offspring number was assumed to follow the geometric distribution with mean $\lambda_1$ and $\lambda_2$ (i.e., Poisson reproduction with mean $\lambda_{i,1}$ and $\lambda_{j,2}$ which follows the exponential distribution with mean $\lambda_1$ and $\lambda_2$), respectively.
+Migrant parents were randomly chosen from the population 1 at the end of the first year.
+Each offspring retained the parent's ID, making it possible to trace an HS and PO relationship.
+
+Let a parameter set ($N_1$, $N_2$, $M$, $\lambda_1$, $\lambda_2$, $n_{\rm O,1}$, $n_{\rm O,2}$, $n_{\rm P,1}$, $n_{\rm P,2}$) be given.
+We simulated a population history and a sampling process, which generates proposed estimators; this process was repeated 1000 times, making it possible to construct the distribution of the estimators for each parameter set.
+
 \RED{kokomade!!!!!!!!!!!!!!!!!!!!}
-
-\subsection{Individual-based model}
-
-We developed an individual-based model that tracks kinship relationships to evaluate the estimator's performance (e.g., $\widehat{N_{\rm e,m}/N_{\rm m}}$).
-The population structure was assumed to be identical to that in the development of the estimators.
-In addition, the population comprised mothers and their offspring, and it was assumed to follow a Poisson or negative binomial reproduction (the degree of skewness due to the nonparental variation is controlled by a parameter $\phi$; see {\bf Appendix B} for detalis).
-The expected number of the surviving offspring of a mother (denoted by $\lambda$) followed the density distribution $f(\lambda)$ (which is involved to the parental variation; see {\bf Appendix B} for details).
-We calculated overdispersion parameter ($c$) from $\phi$ and $f(\lambda)$, as well as confirmed numerically that the value of $c$ gives the same statistics of the estimators even if the combination of $\phi$ and $f(\lambda)$ differs (results are not shown).
-Therefore, each offspring retained the mother's ID, making it possible to trace an MS and MO relationship.
-
-Let a parameter set ($n_{\rm O}$, $n_{\rm M}$, $N_{\rm m}$, $\phi$, and parameters that determine $f(\lambda)$) be given.
-We simulated a population history in which $N_{\rm m}$ mothers generated offspring; this process was repeated 100 times.
-The sampling process for each history was repeated 10{,}000 times, acquiring 1{,}000{,}000 data points that were utilized to construct the distribution of the estimators for each parameter set.
-Furthermore, true value of $N_{\rm e,m}$ was calculated from $N_{\rm m}$ and $c$ (Eqs.~\ref{Ne} and \ref{pi_MS}).
 
@@
 \begin{table}[tb]
-\begin{center}
+%\centering
    \caption[]{Table 1: The list of mathematical symbols employed in the main text}
@@
        & & \\
-	$n_{\rm P,1}, n_{\rm P, 2}$			& Sample number of parents in the population 1 and 2\\ 
-		                						& \\
-	$n_{\rm O, 1}, n_{\rm O, 2}$			& Sample number of offspring in the population 1 and 2\\ 
+	$n_{\rm P,1}, n_{\rm P, 2}$			& Sampled number of parents from the population 1 and 2\\ 
+		                						& \\
+	$n_{\rm O, 1}, n_{\rm O, 2}$			& Sampled number of offspring from the population 1 and 2\\ 
 		                						& \\
@@
 		                						& \\
-	$\pi_{\rm PO,1}, \pi_{\rm PO,2}$		& Probability that a randomly selected pair (mother and offspring) \\
+	$\pi_{\rm PO,1}, \pi_{\rm PO,2}$		& Probability that a randomly selected pair (parent and offspring) \\
 	                							& shares a parent-offspring relationship within the population 1 and 2\\
 									& \\
-	$\pi_{\rm PO, bet}$					& Probability that a randomly selected pair (parent and offspring in the population 1 and 2, \\
-	                							& respectively) shares a parent-offspring relationship between the population 1 and 2\\
-									& \\
-	$\pi_{\rm HS, bet}$					& Probability that a randomly selected pair (two offspring in the population 1 and 2) \\
+	$\pi_{\rm PO, bet}$					& Probability that a randomly selected pair (parent and offspring) \\
+	                							& shares a parent-offspring relationship between the population 1 and 2\\
+									& \\
+	$\pi_{\rm HS, bet}$					& Probability that a randomly selected pair (two offspring) \\
 	                							& shares a half-sibling relationship between the population 1 and 2\\
@@
     \label{symbols} 
-\end{center} 
+\\Subscription ``1'' and ``2'' indicates the quantity in the population 1 during the first year and in the population 2 during the second year, respectively. 
 \end{table}

### 2021-09-28 handle_main_2.R

@@ -11,16 +11,17 @@ rm(list=ls())
 #library(tidyverse)
 start.time = proc.time()
 options(readr.show_progress = FALSE)
-init_parent_pair_number_0 = init_parent_pair_number_1 = 500
-sampled_child_number_0 = sampled_child_number_1 = 100
-sampled_father_number_0 = sampled_father_number_1 = 100
-sampled_mother_number_0 = sampled_mother_number_1 = 100
+options(scipen=1)
+init_parent_pair_number_0 = init_parent_pair_number_1 = 100000
+sampled_child_number_0 = sampled_child_number_1 = 2000
+sampled_father_number_0 = sampled_father_number_1 = 1000
+sampled_mother_number_0 = sampled_mother_number_1 = 1000
 migration_number = 100 # true migrant number is multiplied twice
 lambda_0 = 3
-lambda_1 = 10
-flag_constant = 0
-REP = 1000
-HS_01 = PO_0 = PO_1 = PO_01 = pi_est_PO = pi_est_HS = M_est0_PO = M_est0_HS = M_est0_both = M_est_PO = M_est_HS = M_est_both = N_0_est = N_1_est = rep(NA, REP)
+lambda_1 = 3
+flag_constant = 1
+REP = 100
+HS_01 = PO_0 = PO_1 = PO_01 = pi_est_PO = pi_est_HS = M_est0_PO = M_est0_HS = M_est0_both = M_est1_both= M_est2_both = N_0_est = N_1_est = rep(NA, REP)
 INLINE = paste("./model_2",
                init_parent_pair_number_0, 
                init_parent_pair_number_1,
@@ -84,19 +85,19 @@ for (rep in 1:REP) {
   M_est0_HS[rep] = pi_est_HS[rep] * (2*init_parent_pair_number_0) * (2*init_parent_pair_number_1) / 4
   M_est0_PO[rep] = pi_est_PO[rep] * (2*init_parent_pair_number_0) * (2*init_parent_pair_number_1) / 2
   M_est0_both[rep] = ( (2*init_parent_pair_number_0) * (2*init_parent_pair_number_1) / 2 / sampled_child_number_0 ) * ( (HS_01[rep]+PO_01[rep]) / (2*sampled_child_number_0 + (sampled_father_number_1+sampled_mother_number_1)) )
-  M_est_HS[rep] = pi_est_HS[rep] * N_0_est[rep] * N_1_est[rep] / 4
[…]

### 2021-09-29 handle_main_2.R
confirm that M_i and m_i have same statistical property, #9

@@ -12,16 +12,17 @@ rm(list=ls())
 start.time = proc.time()
 options(readr.show_progress = FALSE)
 options(scipen=1)
-init_parent_pair_number_0 = init_parent_pair_number_1 = 100000
-sampled_child_number_0 = sampled_child_number_1 = 2000
-sampled_father_number_0 = sampled_father_number_1 = 1000
-sampled_mother_number_0 = sampled_mother_number_1 = 1000
+init_parent_pair_number_0 = init_parent_pair_number_1 = 1000
+sampled_child_number_0 = sampled_child_number_1 = 100
+sampled_father_number_0 = sampled_father_number_1 = 50
+sampled_mother_number_0 = sampled_mother_number_1 = 50
 migration_number = 100 # true migrant number is multiplied twice
+migration_rate = migration_number/init_parent_pair_number_0
 lambda_0 = 3
 lambda_1 = 3
 flag_constant = 1
 REP = 100
-HS_01 = PO_0 = PO_1 = PO_01 = pi_est_PO = pi_est_HS = M_est0_PO = M_est0_HS = M_est0_both = M_est1_both= M_est2_both = N_0_est = N_1_est = rep(NA, REP)
+HS_01 = PO_0 = PO_1 = PO_01 = pi_est_PO = pi_est_HS = M_est0_PO = M_est0_HS = M_est0_both = M_est1_both= M_est2_both = N_0_est = N_1_est = m_est1 = m_est2 = m_est3 = m_est4 = rep(NA, REP)
 INLINE = paste("./model_2",
                init_parent_pair_number_0, 
                init_parent_pair_number_1,
@@ -89,15 +90,27 @@ for (rep in 1:REP) {
   #M_est_PO[rep] = pi_est_PO[rep] * N_0_est[rep] * N_1_est[rep] / 2
   M_est1_both[rep] = ( N_0_est[rep] * (2*init_parent_pair_number_1) / 2 / sampled_child_number_0 ) * ( (HS_01[rep]+PO_01[rep]) / (2*sampled_child_number_0 + (sampled_father_number_1+sampled_mother_number_1)) )
   M_est2_both[rep] = ( N_0_est[rep] * N_1_est[rep] / 2 / sampled_child_number_0 ) * ( (HS_01[rep]+PO_01[rep]) / (2*sampled_child_number_0 + (sampled_father_number_1+sampled_mother_number_1)) )
+  
+  m_est1[rep] = pi_est_HS[rep] * (2*init_parent_pair_number_1) / 4
[…]

### 2021-09-29 handle_main_many.R
make handle_main_many.R,#9

@@ -1,0 +1,72 @@
+# ---
+# many-run and drawing result
+# 1: simulation 6 estimators with various sets of fixed parameters
+# 2: draw
+# ---
+
+# 1: simulation 6 estimators with various sets of fixed parameters
+
+library(tidyverse)
+setwd("~/git/CKMRmig/")
+rm(list=ls())
+#start.time = proc.time()
+options(readr.show_progress = FALSE)
+options(scipen=5)
+
+result_grid = tidyr::crossing(
+  N_0 = c(1000, 10000, 100000), 
+  N_1 = c(1000, 10000, 100000), 
+  m = c(0.05, 0.1, 0.2),
+  lambda_0 = 2,
+  lambda_1 = 5,
+  flag_constant = c(0, 1),
+  nP_0 = c(50,100,200,400,800,1600),
+  nP_1 = c(50,100,200,400,800,1600),
+  nO_0 = c(50,100,200,400,800,1600),
+  nO_1 = c(50,100,200,400,800,1600)
+) %>% 
+  dplyr::filter((N_0==1000 & nP_0<=200 & nO_0<=200)
+                | (N_0==10000 & nP_0>=100 & nP_0<=400 & nO_0>=100 & nO_0<=400)
+                | (N_0==100000 & nP_0>=400 & nO_0>=400)
+                ) %>%
+  dplyr::filter((N_1==1000 & nP_1<=200 & nO_1<=200)
+                | (N_1==10000 & nP_1>=100 & nP_1<=400 & nO_1>=100 & nO_1<=400)
+                | (N_1==100000 & nP_1>=400 & nO_1>=400)
+                ) %>%
+  dplyr::filter((N_0==N_1 & nP_0==nP_1 & nO_0==nO_1)
+                | (N_0==10000 & N_1==1000 & nP_0==(2*nP_1) & nO_0==(2*nO_1))
+                | (N_0==100000 & N_1==1000 & nP_0==(8*nP_1) & nO_0==(8*nO_1))
+                | (N_0==100000 & N_1==10000 & nP_0==(4*nP_1) & nO_0==(4*nO_1))
+  ) %>%
+  dplyr::filter((nP_0==nO_0) & (nP_1==nO_1)) %>%
+  dplyr::filter(N_0>=N_1)
+para_len <- nrow(result_grid)
+REP = 100
+system("g++ model_2.cpp -Wall -Wextra -o3 -std=c++17 -o model_2")
[…]

### 2021-10-18 draw_violin.R
fix draw.R for many outputs

@@ -1,0 +1,30 @@
+rm(list=ls())
+
+load(file="~/Dropbox/research/_output/CKMRmig/res.Rdata")
+library(tidyverse)
+theme_set(theme_classic(base_size = 12, base_family = "Helvetica"))
+setwd("~/git/CKMRmig/")
+
+p = 1 # set ID for parameter set
+result_grid[p,]
+migration_number = result_grid$N_0[p]/2 * result_grid$m[p]
+df_tmp = tibble("M1" = M_est1[p,], 
+            "M2" = M_est2[p,], 
+            "M3" = M_est3[p,], 
+            "M4" = M_est4[p,],
+            "M5" = M_est5[p,]) %>%
+  gather(M1, M2, M3, M4, M5, key = "M", value = "value") %>%
+  dplyr::mutate(relative_bias = (value - 2*migration_number) / (2*migration_number))
+
+gp <- ggplot(df_tmp, aes(x = M, y = relative_bias)) +
+  geom_violin(adjust=1,trim=T) +
+  geom_hline(yintercept=0,size=0.5,alpha=.5,linetype=1) +
+  stat_summary(fun = "mean", size=2, geom="point",colour ="black",
+               position=position_dodge(width = 0.9))+
+  ylab("Relative bias") +
+  coord_cartesian(ylim=c(-1,3)) +
+  theme(axis.title = element_text(size=16), 
+        axis.text = element_text(size=12),
+        legend.title = element_text(size=12),
+        legend.text = element_text(size=10))
+plot(gp)

### 2021-10-19 draw_violin.R
output for multiple violin plots, #9

@@ -5,7 +5,9 @@ library(tidyverse)
 theme_set(theme_classic(base_size = 12, base_family = "Helvetica"))
 setwd("~/git/CKMRmig/")
 
-p = 1 # set ID for parameter set
+#1.  only one parameter set is shown
+
+p = 5 # set ID for parameter set
 result_grid[p,]
 migration_number = result_grid$N_0[p]/2 * result_grid$m[p]
 df_tmp = tibble("M1" = M_est1[p,], 
@@ -28,3 +30,183 @@ gp <- ggplot(df_tmp, aes(x = M, y = relative_bias)) +
         legend.title = element_text(size=12),
         legend.text = element_text(size=10))
 plot(gp)
+
+
+#2. several n are shown
+out_grid = result_grid %>% 
+  tibble::rownames_to_column(var = "rowname")
+use_grid = out_grid %>%
+  dplyr::filter( (N_0==10^3)&(N_1==10^3) ) %>%
+  dplyr::filter(m==0.1) %>%
+  dplyr::filter(flag_constant==0)
+use_id = use_grid %>%
+  dplyr::select(rowname) %>%
+  dplyr::pull() %>% as.numeric()  
+n_index = use_grid %>%
+  dplyr::select(nP_0) %>%
+  dplyr::pull() %>% as.numeric() 
+migration_number = use_grid$N_0[1]/2 * use_grid$m[1]
+
+for ( i in 1:5){
+  tmp_use_M_est = get(paste0("M_est",i))[use_id,]
+  rownames(tmp_use_M_est) = paste0("n = ",n_index)
+  df = tmp_use_M_est %>% t() %>% as_tibble() 
+  tb_tmp = tidyr::gather(df) %>% 
+    dplyr::mutate(M = paste0("M",i)) %>%
+    dplyr::mutate(relative_bias = (value - 2*migration_number) / (2*migration_number))
+  assign(paste0("tb", i), tb_tmp)
+}
+tb = dplyr::full_join(tb1,tb2) %>%
+  dplyr::full_join(tb3) %>%
+  dplyr::full_join(tb4) %>%
+  dplyr::full_join(tb5)
+
+gp <- ggplot(tb, aes(x = as_factor(M), y = relative_bias, fill = as_factor(key))) +
+  scale_fill_grey(start = 0.6, end = 0.9) + theme_classic() +
+  geom_violin(adjust=1,trim=T) +
+  geom_hline(yintercept=0,size=0.5,alpha=.5,linetype=1) +
[…]

### 2021-10-19 handle_main_many.R

@@ -45,7 +45,7 @@ result_grid = tidyr::crossing(
   dplyr::filter((nP_0==nO_0) & (nP_1==nO_1)) %>%
   dplyr::filter(N_0>=N_1)
 para_len <- nrow(result_grid)
-REP = 1
+REP = 1000
 system("g++ model_2.cpp -Wall -Wextra -o3 -std=c++17 -o model_2")
 HS_01 = PO_0 = PO_1 = PO_01 = pi_est_PO = pi_est_HS = M_est1 = M_est2 = M_est3 = M_est4 = M_est5 = N_0_est = N_1_est = m_est1 = m_est2 = m_est3 = m_est4 = matrix(NA,nrow = para_len, ncol = REP)
 
@@ -137,3 +137,4 @@ for (p in 1:para_len) {
 }
 end.time = proc.time()
 (end.time-start.time)
+save(list=ls(), file="out/res.Rdata")

### 2021-10-19 make_summary_table.R
make big summary table, #9

@@ -1,0 +1,52 @@
+rm(list=ls())
+
+load(file="~/Dropbox/research/_output/CKMRmig/res.Rdata")
+library(tidyverse)
+theme_set(theme_classic(base_size = 12, base_family = "Helvetica"))
+setwd("~/git/CKMRmig/")
+
+# migration_number = result_grid$N_0[p]/2 * result_grid$m[p]
+# dplyr::mutate(relative_bias = (value - 2*migration_number) / (2*migration_number))
+
+summary_table = result_grid %>%
+  dplyr::mutate(migration_number = N_0 * m) %>% # this is not input migration_number (not divided by 2)
+  dplyr::mutate(M_mean1 = apply(M_est1, 1, mean)) %>%
+  dplyr::mutate(M_mean2 = apply(M_est2, 1, mean)) %>%
+  dplyr::mutate(M_mean3 = apply(M_est3, 1, mean)) %>%
+  dplyr::mutate(M_mean4 = apply(M_est4, 1, mean)) %>%
+  dplyr::mutate(M_mean5 = apply(M_est5, 1, mean)) %>%
+  dplyr::mutate(m_mean1 = apply(m_est1, 1, mean)) %>%
+  dplyr::mutate(m_mean2 = apply(m_est2, 1, mean)) %>%
+  dplyr::mutate(m_mean3 = apply(m_est3, 1, mean)) %>%
+  dplyr::mutate(m_mean4 = apply(m_est4, 1, mean)) %>%
+  dplyr::mutate(M_var1 = apply(M_est1, 1, var)) %>%
+  dplyr::mutate(M_var2 = apply(M_est2, 1, var)) %>%
+  dplyr::mutate(M_var3 = apply(M_est3, 1, var)) %>%
+  dplyr::mutate(M_var4 = apply(M_est4, 1, var)) %>%
+  dplyr::mutate(M_var5 = apply(M_est5, 1, var)) %>%
+  dplyr::mutate(m_var1 = apply(m_est1, 1, var)) %>%
+  dplyr::mutate(m_var2 = apply(m_est2, 1, var)) %>%
+  dplyr::mutate(m_var3 = apply(m_est3, 1, var)) %>%
+  dplyr::mutate(m_var4 = apply(m_est4, 1, var)) %>%
+  dplyr::mutate(M_bias1 = (M_mean1 - migration_number) / migration_number) %>%
[…]

### 2021-10-20 latex/ms.tex
add Fig2

@@
 We simulated a population history and a sampling process, which generates proposed estimators; this process was repeated 1000 times, making it possible to construct the distribution of the estimators for each parameter set.
+All scripts and documentation for these analyses are available at \\https://github.com/teTUNAakita/CKMRmig.
 
@@
 \section{Results and Discussion}\label{sec3}
+
+%%%%%%%%%%%%%%
+\begin{center}
+\fbox{Figure \ref{violins} is here. }
+\end{center}
+%%%%%%%%%%%%%%
 
@@
 \section*{ACKNOWLEDGMENTS}
-The author thanks R.
-Nakamichi for fruitful discussions.
-The author also thanks Robin Waples and an anonymous reviewer for constructive feedback that substantially improved the quality of this manuscript.
-This work was supported by JSPS KAKENHI Grant Number 19K06862.
+The author thanks Y. Tsukahara and N. Suzuki for fruitful discussions. This work was supported by JSPS KAKENHI Grant Number 19K06862 and 20H03012.
 
@@
 	$M$								& Number of survived migrants of parents from the population 1 to population 2\\
+		                						& \\
+	$m$								& Migration rate of parents from the population 1 to population 2, defined by $M/N_1$.\\
 		                						& \\
@@
 		\label{cartoon}
+	\end{center}
+\end{figure}
+%%%%%%%%%%%
+
+%%%FIGURE 2%%%
+\begin{figure}[!h]
+	\begin{center}
+		\includegraphics[width=1\textwidth]{/Users/akita/Dropbox/research/close_kin/Mig/Figs/violins.eps}
+		\caption{{\bf FIGURE 2} \figcapb{}}
+		\label{violins}
 	\end{center}

### 2021-10-20 draw_violin.R

@@ -204,7 +204,8 @@ for (j in 1:9) {
           axis.text = element_text(size=10),
           legend.title = element_text(size=10),
           legend.text = element_text(size=8),
-          legend.position="top")
+          legend.position="top"
+          )
   assign(paste0("gp", j), gp)
 }
 

### 2021-12-13 handle_main_2.R
fix fatal bug in estimator M3-M5 #12

@@ -12,15 +12,19 @@ rm(list=ls())
 start.time = proc.time()
 options(readr.show_progress = FALSE)
 options(scipen=1)
-init_parent_pair_number_0 = init_parent_pair_number_1 = 1000
-sampled_child_number_0 = sampled_child_number_1 = 200
-sampled_father_number_0 = sampled_father_number_1 = 500
-sampled_mother_number_0 = sampled_mother_number_1 = 500
-migration_number = 50 # true migrant number is multiplied twice
+init_parent_pair_number_0 = 5000
+init_parent_pair_number_1 = 500
+sampled_child_number_0 = 100
+sampled_child_number_1 = 50
+sampled_father_number_0 = 50
+sampled_father_number_1 = 25
+sampled_mother_number_0 = 50
+sampled_mother_number_1 = 25
+migration_number = 250 # true migrant number is multiplied twice
 migration_rate = migration_number/init_parent_pair_number_0
 lambda_0 = 3
 lambda_1 = 7
-flag_constant = 1
+flag_constant = 0
 flag_invasive = 1
 REP = 1000
 HS_01 = PO_0 = PO_1 = PO_01 = pi_est_PO = pi_est_HS = M_est0_PO = M_est0_HS = M_est0_both = M_est1_both= M_est2_both = N_0_est = N_1_est = m_est1 = m_est2 = m_est3 = m_est4 = rep(NA, REP)
@@ -87,11 +91,11 @@ for (rep in 1:REP) {
   N_1_est[rep] = (2*sampled_child_number_1 * (sampled_father_number_1+sampled_mother_number_1) + 1) / (PO_1[rep] + 1)
   M_est0_HS[rep] = pi_est_HS[rep] * (2*init_parent_pair_number_0) * (2*init_parent_pair_number_1) / 4
   M_est0_PO[rep] = pi_est_PO[rep] * (2*init_parent_pair_number_0) * (2*init_parent_pair_number_1) / 2
-  M_est0_both[rep] = ( (2*init_parent_pair_number_0) * (2*init_parent_pair_number_1) / 2 / sampled_child_number_0 ) * ( (HS_01[rep]+PO_01[rep]) / (2*sampled_child_number_0 + (sampled_father_number_1+sampled_mother_number_1)) )
[…]

### 2021-12-13 handle_main_many.R

@@ -117,16 +117,16 @@ for (p in 1:para_len) {
     
     M_est1[p,rep] = pi_est_HS[p,rep] * (2*init_parent_pair_number_0) * (2*init_parent_pair_number_1) / 4
     M_est2[p,rep] = pi_est_PO[p,rep] * (2*init_parent_pair_number_0) * (2*init_parent_pair_number_1) / 2
-    M_est3[p,rep] = ( (2*init_parent_pair_number_0) * (2*init_parent_pair_number_1) / 2 / sampled_child_number_0 ) * ( (HS_01[p,rep]+PO_01[p,rep]) / (2*sampled_child_number_0 + (sampled_father_number_1+sampled_mother_number_1)) )
+    M_est3[p,rep] = ( (2*init_parent_pair_number_0) * (2*init_parent_pair_number_1) / 2 / sampled_child_number_0 ) * ( (HS_01[p,rep]+PO_01[p,rep]) / (2*sampled_child_number_1 + (sampled_father_number_1+sampled_mother_number_1)) )
     #M_est_HS[rep] = pi_est_HS[rep] * N_0_est[rep] * N_1_est[rep] / 4
     #M_est_PO[rep] = pi_est_PO[rep] * N_0_est[rep] * N_1_est[rep] / 2
-    M_est4[p,rep] = ( N_0_est[p,rep] * (2*init_parent_pair_number_1) / 2 / sampled_child_number_0 ) * ( (HS_01[p,rep]+PO_01[p,rep]) / (2*sampled_child_number_0 + (sampled_father_number_1+sampled_mother_number_1)) )
-    M_est5[p,rep] = ( N_0_est[p,rep] * N_1_est[p,rep] / 2 / sampled_child_number_0 ) * ( (HS_01[p,rep]+PO_01[p,rep]) / (2*sampled_child_number_0 + (sampled_father_number_1+sampled_mother_number_1)) )
+    M_est4[p,rep] = ( N_0_est[p,rep] * (2*init_parent_pair_number_1) / 2 / sampled_child_number_0 ) * ( (HS_01[p,rep]+PO_01[p,rep]) / (2*sampled_child_number_1 + (sampled_father_number_1+sampled_mother_number_1)) )
[…]

### 2021-12-13 handle_main_many.R
add constrains for selecting parameter set

@@ -37,7 +37,8 @@ result_grid = tidyr::crossing(
                 | (N_0==100000 & N_1==10000 & nP_0==(4*nP_1) & nO_0==(4*nO_1))
   ) %>%
   dplyr::filter((nP_0==nO_0) & (nP_1==nO_1)) %>%
-  dplyr::filter(N_0>=N_1)
+  dplyr::filter(N_0 >= N_1) %>%
+  dplyr::filter(N_1>(m*N_0))
 para_len <- nrow(result_grid)
 REP = 1000
 system("g++ model_3.cpp -Wall -Wextra -o3 -std=c++17 -o model_3")

### 2021-12-14 latex/ms.tex
fix Eqs.13-14
add range of M in main text

@@
 Each parent produces offspring in which the number is governed by the parent's reproductive potential, denoted by $\lambda_{i,1}$ ($i=1,2,\ldots,N_1$).
-After the reproductive season, part of the parents would start to moving towards the population 2; $M$ survived migrants arrive in the population 2 so that there are $N_2$ parents in the population 2 at the beginning of the second year ($M < N_2$).
+After the reproductive season, part of the parents would start to moving towards the population 2; $M$ survived migrants arrive in the population 2 so that there are $N_2$ parents in the population 2 at the beginning of the second year ($M \le N_1$ and $M \le N_2$).
 Similar to the population 1, $N_2$ parents produce offspring in which the number is governed by $\lambda_{j,2}$ ($j=1,2,\ldots,N_2$).
@@
 \end{align}
-This form also holds under a flexible setting for the reproductive potential, such as a situation with random variable of $\lambda_{i,1}$ and $\lambda_{j,2}$, as noted in {\bf Appendix}.
+This form holds under a flexible setting for the reproductive potential, such as a situation with random variable of $\lambda_{i,1}$ and $\lambda_{j,2}$, as noted in {\bf Appendix}.
+If all $N_1$ parents safely move to the population 2 (i.e., $M = N_1$), $\pi_{\rm HS,bet}$ equals $4/N_2$; meanwhile, if the population 2 consists only of migrants (i.e., $M = N_2$), $\pi_{\rm HS,bet}$ equals $4/N_1$.
+These probabilities in the extreme cases are similar forms to HS probability that is randomly sampled from two different cohorts within a population \cite[]{bravington2016close}.
 
@@
 \end{align}
+This form also holds under a flexible setting for the reproductive potential, as noted in {\bf Appendix}.
+If all $N_1$ parents safely move to the population 2 (i.e., $M = N_1$), $\pi_{\rm PO,bet}$ equals $2/N_2$; meanwhile, if the population 2 consists only of migrants (i.e., $M = N_2$), $\pi_{\rm PO,bet}$ equals $2/N_1$.
+These probabilities in the extreme cases are similar forms to PO probability that is randomly sampled within a population \cite[]{bravington2016close}.
 
@@
 \begin{align}
-\widehat{M_3} &= \frac{ N_{1} N_{2} \left(\widetilde{H}_{\rm HS,bet} + \widetilde{H}_{\rm PO,bet}\right) } {2n_{\rm O, 1} \left(2 n_{\rm O, 2} + n_{\rm P, 2}\right), }
+\widehat{M_3} &= \frac{ N_{1} N_{2} \left(\widetilde{H}_{\rm HS,bet} + \widetilde{H}_{\rm PO,bet}\right) } {2n_{\rm O, 1} \left(2 n_{\rm O, 2} + n_{\rm P, 2}\right) },
 \label{AP-1}
@@
 \begin{align}
-\widehat{m_3} &= \frac{ N_{2} \left(\widetilde{H}_{\rm HS,bet} + \widetilde{H}_{\rm PO,bet}\right) } {2n_{\rm O, 1} \left(2 n_{\rm O, 2} + n_{\rm P, 2}\right). }
+\widehat{m_3} &= \frac{ N_{2} \left(\widetilde{H}_{\rm HS,bet} + \widetilde{H}_{\rm PO,bet}\right) } {2n_{\rm O, 1} \left(2 n_{\rm O, 2} + n_{\rm P, 2}\right)}.
 \label{AP-2}

### 2021-12-14 latex/ms.tex
add timeline chart as figure 1a in main text

@@
 For the applicability of fishery management, we assume invasive sampling procedure, preventing the finding of a parent-offspring pair such that a parent and offspring is sampled in the population 1 and 2, respectively.
-
-In the example depicted in {\bf Fig~\ref{cartoon}}, five offspring and four parents are sampled in the population 1 and four offspring and six parents are sampled in the population 2, and two HS and one PO pairs found between the two populations are observed.
+{\bf Figure~\ref{cartoon}a} illustrates a timeline of sampling scheme for hypothetical populations.
+
+In the example depicted in {\bf Fig~\ref{cartoon}b}, five offspring and four parents are sampled in the population 1 and four offspring and six parents are sampled in the population 2, and two HS and one PO pairs found between the two populations are observed.
 In addition, there are several PO pairs observed within the same population, which are available to estimate parent numbers, as explain the next section.
@@
 	\begin{center}
-		\includegraphics[width=0.3\textwidth]{/Users/akita/Dropbox/research/close_kin/Mig/Figs/cartoon.eps}
+		\includegraphics[width=0.7\textwidth]{/Users/akita/Dropbox/research/close_kin/Mig/Figs/cartoon.eps}
 		\caption{{\bf FIGURE 1} \figcapa{}}

### 2021-12-14 latex/ms.tex
add caption of Fig1 in main text

@@
 
-\newcommand{\figcapa}{Example of relationships between mothers and their offspring number.
-The open, gray, and filled circles represent mothers, their eggs, and their offspring, respectively.
-The area of an open circle indicates the degree of reproductive potential of each mother (i.e., $\lambda_i$).
-The dotted and thin arrows denote mother--egg and egg--offspring relationships, respectively.
-The symbol x denotes a failure to survive at sampling.
-Sampled individuals are denoted with squares.
-Input parameters in this example: $n_{\rm P, 1}=4$, $n_{\rm O, 1}=5$, $n_{\rm P, 2}=6$, $n_{\rm O, 2}=4$, $N_{1}=16$, $N_{2}=14$, and $M=6$.
-The numbers of kinship pairs: $H_{\rm PO, bet}=1$, $H_{\rm HS, bet}=2$, $H_{\rm PO, 1}=3$, and $H_{\rm PO, 2}=2$.}
+\newcommand{\figcapa}{(a) The phases of the events relevant to this study along the time line.
+(b) Example of relationships between parents and their offspring number between/within populations.
+Upper and lower square indicates individuals belonging to the population 1 before migrations (at sample timing in the first year) and individuals belonging to the population 2 after reproduction (at sample timing in the second year), respectively.
+The open circles on the left side, right side, and the center represent mothers, fathers, and their offspring, respectively.
+The thin line denotes parent-offspring relationship.
+The bold arrow denotes the migration and the symbol x denotes a failure to survive at sampling in the second year.
+The number of sampled individuals in this example: $n_{\rm P, 1}=4$, $n_{\rm O, 1}=5$, $n_{\rm P, 2}=6$, $n_{\rm O, 2}=4$, $N_{1}=16$, $N_{2}=14$, and $M=6$; the numbers of kinship pairs: $H_{\rm PO, bet}=1$, $H_{\rm HS, bet}=2$, $H_{\rm PO, 1}=3$, and $H_{\rm PO, 2}=2$.}
 

### 2021-12-14 latex/ms.tex
modify caption of Fig1 in main text

@@
 In the example depicted in {\bf Fig~\ref{cartoon}b}, five offspring and four parents are sampled in the population 1 and four offspring and six parents are sampled in the population 2, and two HS and one PO pairs found between the two populations are observed.
-In addition, there are several PO pairs observed within the same population, which are available to estimate parent numbers, as explain the next section.
+In addition, there are several PO pairs observed within the same population, which are available to estimate parent numbers, as explained in the following section.
 In our modeling framework, if full-sibling (FS) relationship is found, we count it as two HS pairs.
@@
 \newcommand{\figcapa}{(a) The phases of the events relevant to this study along the time line.
-(b) Example of relationships between parents and their offspring number between/within populations.
-Upper and lower square indicates individuals belonging to the population 1 before migrations (at sample timing in the first year) and individuals belonging to the population 2 after reproduction (at sample timing in the second year), respectively.
+(b) Hypothetical populations with $N_{1}=16$, $N_{2}=14$, and $M=6$.
+Upper and lower square indicates individuals belonging to the population 1 before migration (at sample timing in the first year) and individuals belonging to the population 2 after reproduction (at sample timing in the second year), respectively.
 The open circles on the left side, right side, and the center represent mothers, fathers, and their offspring, respectively.
@@
 The bold arrow denotes the migration and the symbol x denotes a failure to survive at sampling in the second year.
-The number of sampled individuals in this example: $n_{\rm P, 1}=4$, $n_{\rm O, 1}=5$, $n_{\rm P, 2}=6$, $n_{\rm O, 2}=4$, $N_{1}=16$, $N_{2}=14$, and $M=6$; the numbers of kinship pairs: $H_{\rm PO, bet}=1$, $H_{\rm HS, bet}=2$, $H_{\rm PO, 1}=3$, and $H_{\rm PO, 2}=2$.}
+Sampled individuals are labeled with an index number.
+The number of sampled individuals in this example: $n_{\rm P, 1}=4$, $n_{\rm O, 1}=5$, $n_{\rm P, 2}=6$, $n_{\rm O, 2}=4$; the numbers of kinship pairs: $H_{\rm PO, bet}=1$ (i.e., ``7-10'' pair), $H_{\rm HS, bet}=2$ (i.e., ``8-16'' and ``9-16'' pairs), $H_{\rm PO, 1}=3$ (i.e., ``1-6'', ``3-5'' and ``4-7'' pairs), and $H_{\rm PO, 2}=2$ (i.e., ``11-17'' and ``15-16'' pairs).}
 

### 2021-12-14 latex/ms.tex
something

@@
 \renewcommand{\theequation}{A\arabic{equation}}
-Here, we introduce the concept of the reproductive potential of parent $i$ or $j$, which is defined as the expected number of surviving offspring at sampling time, denoted by $\lambda_{i,1}$ or $\lambda_{j,2}$.
-The reproductive potential is determined by several factors, including the parent’s age, weight, residence time on the spawning ground.
-It should be noted that the magnitude of this parameter ($\lambda_{i,1}$ or $\lambda_{i,2}$) includes information about the survival rate of the offspring, the number of days after egg hatching, and the egg number; this implies that the parameter reflects the sample timing.
+Here, we introduce the concept of the reproductive potential of parent $i$ in the population $m$, which is defined as the expected number of surviving offspring at sampling time, denoted by $\lambda_{i,m}$.
+The reproductive potential is determined by several factors, including the parent's age, weight, residence time on the spawning ground.
+It should be noted that the magnitude of this parameter ($\lambda_{i,m}$) includes information about the survival rate of the offspring, the number of days after egg hatching, and the egg number; this implies that the parameter reflects the sample timing.
 It should also be noted that the modeling framework does not depend on whether the reproductive potential is heritable or not.

### 2021-12-15 latex/ms.tex
add derivation of pi_HS in appendix, #8

@@
 
-\section*{APPENDIX X}
+\section*{APPENDIX 1}
 \setcounter{equation}{0}
+\renewcommand{\theequation}{A\arabic{equation}}
 
@@
 \renewcommand{\theequation}{A\arabic{equation}}
-Here, we introduce the concept of the reproductive potential of parent $i$ in the population $m$, which is defined as the expected number of surviving offspring at sampling time, denoted by $\lambda_{i,m}$.
+Here, we introduce the concept of the reproductive potential of parent $i$ and $j$ in the population 1 and 2, respectively, which are defined as the expected number of surviving offspring at sampling time, denoted by $\lambda_{i,1}$ and $\lambda_{j,2}$ ($i=(1, \ldots, N_1)$ and $j=(1, \ldots, N_2)$).
 The reproductive potential is determined by several factors, including the parent's age, weight, residence time on the spawning ground.
-It should be noted that the magnitude of this parameter ($\lambda_{i,m}$) includes information about the survival rate of the offspring, the number of days after egg hatching, and the egg number; this implies that the parameter reflects the sample timing.
+It should be noted that the magnitude of this parameter includes information about the survival rate of the offspring, the number of days after egg hatching, and the egg number; this implies that the parameter reflects the sample timing.
 It should also be noted that the modeling framework does not depend on whether the reproductive potential is heritable or not.
 
-\section*{Equation X holds under flexible assumptions for the distribution of surviving offspring number per parent}
-
-\renewcommand{\theequation}{B\arabic{equation}}
-
-これまでは，母親による産卵数の偏りや，父親による放精成功の偏りは考慮していなかった。しかしながら，多回繁殖する魚類の場合，体サイズによって繁殖成功度は大きく変化すること，および体サイズの分布には偏りが存在することから，上記のシステマチックな偏りを考慮する必要があるだろう。例えば，集団に１個体の巨大魚（メス）がいて，その産卵数が他の個体よりも圧倒的に大きい場合，サンプルされる子供の母親はかなりの確率でその巨大魚になるだろう。
-
-サブ集団１（２）にいる親$i(j)$が残す子供の数を$k_{1,i}(k_{2,j})$としよう。$k_{1,i}(k_{2,j})$は期待値$\lambda_{1,i}(\lambda_{2,j})$の分布（例えば負の二項分布など）に従うとしよう。体サイズによる重み付けを考慮したランダム交配を仮定すれば，ペアがMHSである確率は
-\begin{align}
-\pi | _{\boldsymbol{k_1, k_2}} &= \frac{ 2\sum_{i=1}^M k_{1,i} } { \sum_{i=1}^{N_1} k_{1,i} } \frac{ 2\sum_{j=1}^M k_{2,j} } { \sum_{j=1}^{N_2} k_{2,j} } \frac{1}{M} 
-\end{align}
-と書くことができる。簡単のため，$\boldsymbol{k_1}=(k_{1,1}, \ldots, k_{1,M}, \ldots, k_{1,N_1})$および$\boldsymbol{k_2}=(k_{1,2}, \ldots, k_{1,M}, \ldots, k_{1,N_2})$と記載し，また親のidが$1$から$M$の個体が移動するとして，idを配置した。$k_{1,i}$は期待値$\lambda_{1,i}$に従う確率変数であることから，このMHSペア確率の平均をとると
-\begin{align}
-\pi | _{\boldsymbol{\lambda_1, \lambda_2}} &= \mathbb{E}[\pi | _{\boldsymbol{k_1, k_2}}] \nonumber\\
-&= \frac{4}{M} \mathbb{E}\left[\frac{ \sum_{i=1}^M k_{1,i} } { \sum_{i=1}^{N_1} k_{1,i} } \frac{ \sum_{j=1}^M k_{2,j} } { \sum_{j=1}^{N_2} k_{2,j} } \right]   \nonumber\\
-&\approx \frac{4}{M} \frac{ \mathbb{E}\left[ \sum_{i=1}^M k_{1,i} \sum_{j=1}^M k_{2,j} \right] } {\mathbb{E}\left[ \sum_{i=1}^{N_1} k_{1,i} \sum_{j=1}^{N_2} k_{2,j}\right]} \nonumber\\
-&= \frac{4}{M} \frac{ \sum_{i=1}^M \lambda_{1,i} \sum_{j=1}^M \lambda_{2,j} } {\sum_{i=1}^{N_1} \lambda_{1,i} \sum_{j=1}^{N_2} \lambda_{2,j}} 
-\end{align}
-と近似することができる。留意すべき点として，移動前の産卵数と移動後の産卵数は独立と仮定しているため，式中に$k_i^2$の項が出現せず，結果は期待値$\lambda_i$(産卵ポテンシャルと呼ぶことにしよう)だけに依存する。最初に述べたように，この個体ごとの産卵ポテンシャルはある分布に従うとしよう。例えば，高齢個体ほど体サイズが大きい場合などが想定される。また，この分布はサブ集団１とサブ集団２で異なっていて良い。すなわち，$\lambda_{1,i}$および$\lambda_{2,j}$がそれぞれ独立な確率変数であると考えて，MHSペア確率についてさらに平均をとると
-\begin{align}
-\pi &= \mathbb{E}[\pi | _{\boldsymbol{\lambda_1, \lambda_2}}] \nonumber\\ 
-&\approx \frac{4}{M} \frac{M^2 \mathbb{E}[\lambda_1 \lambda_2]}{N_1 N_2 \mathbb{E}[\lambda_1 \lambda_2]}\nonumber\\
-&= \frac{4M}{N_{1}N_{2}}
-\label{4-1}
-\end{align}
-と近似される。結局，繁殖ポテンシャルの不均一性を考慮しない結果（式\ref{3-1}）と同様になる。なお，$\boldsymbol{\lambda_1}=(\lambda_{1,1}, \ldots, \lambda_{1,N_1})$および$\boldsymbol{\lambda_2}=(\lambda_{1,2}, \ldots, \lambda_{1,N_2})$。この近似は、独立に決まる確率変数$\lambda_1$と$\lambda_2$について、$\mathbb{E}[\lambda_1/\lambda_2]=\mathbb{E}[\lambda_1] \times \mathbb{E}[1/\lambda_2] \approx 1$となる場合に成立するので、集団中に$\lambda$が極端に低い個体が存在する場合は成立しない（サブ集団１とサブ集団２でセットにして相対的な繁殖ポテンシャルを考えれば良いので、問題ないだろう）。
-
-親子ペアから親の数を推定する場合も、繁殖ポテンシャルの不均一性は問題にならない。すなわち、ビッグマザーが存在していても、それをサンプルできるかどうかは運であり、期待値は推定値に漸近するからである。
+\section*{APPENDIX 2}
+\section*{Derivation of Equations~\ref{HS-1} and \ref{PO-1} when reproductive potential is variable among parents}
+
+In the main text, we ignore the variation of reproductive potential among parents (i.e., both $\lambda_{i,1}$ and $\lambda_{j,2}$ are constant) to derive $\pi_{\rm HS,bet}$ and $\pi_{\rm PO,bet}$, which corresponds to the probability that two offspring sampled in the population 1 and 2 share an HS relationship and that offspring sampled in the population 1 and a parent sampled in the population 2 share an PO relationship, respectively.
+Let $k_{i,1}$ and $k_{j,2}$ be the number of surviving offspring of parent $i$ and $j$ at sampling in the population 1 and 2, respectively, and $k_{i,1}$ and $k_{j,2}$ is assumed to follow a kind of discrete distribution (e.g., negative binomial distribution) with mean $\lambda_{i,1}$ and $\lambda_{j,2}$.
+Without loss of generality, we set the index such that parents with $i=1$ to $M$ in the population 1 and $j=1$ to $M$ in the population 2 are identical migrants; for example, the parent with $i=1$ reproduce $k_{1,1}$ offspring (in the population 1) and then reproduce $k_{1,2}$ offspring (in the population 2) after migration.
+Giving $k_{i,1}$ and $k_{j,2}$, the conditional probability that two offspring sampled in the population 1 and 2 share an HS relationship is
+\begin{align}
+\pi_{\rm HS,bet} | _{\boldsymbol{k_1, k_2}} &= \frac{ 2\sum_{i=1}^M k_{i,1} } { \sum_{i=1}^{N_1} k_{i,1} } \frac{ 2\sum_{j=1}^M k_{j,2} } { \sum_{j=1}^{N_2} k_{j,2} } \frac{1}{M}, 
+\end{align}
+where $\boldsymbol{k_1}=(k_{1,1}, \ldots, k_{M,1}, \ldots, k_{N_1,1})$ and $\boldsymbol{k_2}=(k_{1,2}, \ldots, k_{M,2}, \ldots, k_{N_2,2})$.
+It should be noted that $k_{i,1}$ and $k_{j,1}$ is a random variable with mean $\lambda_{i,1}$ and $\lambda_{j,2}$, respectively.
+By taking the expectation over the distribution of offspring number, the conditional probability is given by
+\begin{align}
+\pi_{\rm HS,bet} | _{\boldsymbol{\lambda_1, \lambda_2}} &= \mathbb{E}[\pi | _{\boldsymbol{k_1, k_2}}] \nonumber\\
+&= \frac{4}{M} \mathbb{E}\left[\frac{ \sum_{i=1}^M k_{i,1} } { \sum_{i=1}^{N_1} k_{i,1} } \frac{ \sum_{j=1}^M k_{j,2} } { \sum_{j=1}^{N_2} k_{j,2} } \right]   \nonumber\\
+&\approx \frac{4}{M} \frac{ \mathbb{E}\left[ \sum_{i=1}^M k_{i,1} \sum_{j=1}^M k_{j,2} \right] } {\mathbb{E}\left[ \sum_{i=1}^{N_1} k_{i,1} \sum_{j=1}^{N_2} k_{j,2}\right]} \nonumber\\
+&= \frac{4}{M} \frac{ \sum_{i=1}^M \lambda_{i,1} \sum_{j=1}^M \lambda_{j,2} } {\sum_{i=1}^{N_1} \lambda_{i,1} \sum_{j=1}^{N_2} \lambda_{j,2}},
+\end{align}
+where $\boldsymbol{\lambda_1}=(\lambda_{1,1}, \ldots, \lambda_{M,1}, \ldots, \lambda_{N_1,1})$ and $\boldsymbol{\lambda_2}=(\lambda_{1,2}, \ldots, \lambda_{M,2}, \ldots, \lambda_{N_2,2})$.
+From the second to the third line, we use the approximation that $\mathbb{E}[g1(k)/g2(k)] \approx \mathbb{E}[g_1(k)] / \mathbb{E}[g_2(k)]$.
+From the third to the forth line, we use the relationship that $\mathbb{E}[k_{i,1}k_{j,2} | _{\lambda_{i,1}, \lambda_{j,2}}] = \mathbb{E}[k_{i,1}|_{\lambda_{i,1}}]\mathbb{E}[k_{j,2}|_{\lambda_{j,2}}]$, implying statistical independence of offspring number before and after parental movement.
+In other words, the conditional probability does not affected by $\mathbb{V}[k|_\lambda]$.
+As noted above, we assume that $\lambda_{i,1}$ and $\lambda_{j,2}$ is also a random variable followed by an arbitral function with mean ${\bar \lambda_{1}}$ and ${\bar \lambda_{2}}$, respectively.
+By taking the expectation over $\lambda$ and applying a similar approximation, the unconditional probability is given by
+\begin{align}
+\pi_{\rm HS,bet} &= \mathbb{E}[\pi | _{\boldsymbol{\lambda_1, \lambda_2}}] \nonumber\\ 
+&= \frac{4}{M} \mathbb{E}\left[\frac{ \sum_{i=1}^M \lambda_{i,1} } { \sum_{i=1}^{N_1} \lambda_{i,1} } \frac{ \sum_{j=1}^M \lambda_{j,2} } { \sum_{j=1}^{N_2} \lambda_{j,2} } \right]   \nonumber\\
+&\approx \frac{4}{M} \frac{ \mathbb{E}\left[ \sum_{i=1}^M \lambda_{i,1} \sum_{j=1}^M \lambda_{j,2} \right] } {\mathbb{E}\left[ \sum_{i=1}^{N_1} \lambda_{i,1} \sum_{j=1}^{N_2} \lambda_{j,2}\right]} \nonumber\\
+&= \frac{4}{M} \frac{M^2 {\bar \lambda_1} {\bar \lambda_2}}{N_1 N_2 {\bar \lambda_1} {\bar \lambda_2}}\nonumber\\
+&= \frac{4M}{N_{1}N_{2}},
+\end{align}
+which provides the same formulation described in Eq.\ref{HS-1}.
+It should be noted that, from the third to the forth line, we assume statistical independence of reproductive potential before and after parental movement.
+In {\bf Appendix 3}, we consider the situation in which the statistical independence does not hold.
 

### 2021-12-16 latex/ms.tex
add derivation of pi_PO in appendix, #8

@@
 
-In the main text, we ignore the variation of reproductive potential among parents (i.e., both $\lambda_{i,1}$ and $\lambda_{j,2}$ are constant) to derive $\pi_{\rm HS,bet}$ and $\pi_{\rm PO,bet}$, which corresponds to the probability that two offspring sampled in the population 1 and 2 share an HS relationship and that offspring sampled in the population 1 and a parent sampled in the population 2 share an PO relationship, respectively.
+In the main text, we ignore the variation of reproductive potential among parents (i.e., both $\lambda_{i,1}$ and $\lambda_{j,2}$ are constant) to derive $\pi_{\rm HS,bet}$ and $\pi_{\rm PO,bet}$.
 Let $k_{i,1}$ and $k_{j,2}$ be the number of surviving offspring of parent $i$ and $j$ at sampling in the population 1 and 2, respectively, and $k_{i,1}$ and $k_{j,2}$ is assumed to follow a kind of discrete distribution (e.g., negative binomial distribution) with mean $\lambda_{i,1}$ and $\lambda_{j,2}$.
@@
 In {\bf Appendix 3}, we consider the situation in which the statistical independence does not hold.
+
+Similar to the derivation of $\pi_{\rm HS,bet}$, the conditional probability that offspring sampled in the population 1 and a parent sampled in the population 2 share an PO relationship is
+\begin{align}
+\pi_{\rm PO,bet} | _{\boldsymbol{k_1, k_2}} &= \frac{ 2\sum_{i=1}^M k_{i,1} } { \sum_{i=1}^{N_1} k_{i,1} } \frac{ \sum_{j=1}^M k_{j,2} } { \sum_{j=1}^{N_2} k_{j,2} } \frac{1}{M}.
+\end{align}
+By taking the expectation over $k$ and $\lambda$, in the same manner as noted above, the unconditional probability is given by
+\begin{align}
+\pi_{\rm PO,bet} &= \mathbb{E}[\mathbb{E}[\pi | _{\boldsymbol{k_1, k_2}}]] \nonumber\\ 
+&\approx  \frac{2M}{N_{1}N_{2}},
+\end{align}
+which provides the same formulation described in Eq.\ref{PO-1}.
+
+\section*{APPENDIX 3}
 

### 2021-12-16 latex/ms.tex
start writing App3, #8

@@
 It should be noted that $k_{i,1}$ and $k_{j,1}$ is a random variable with mean $\lambda_{i,1}$ and $\lambda_{j,2}$, respectively.
-By taking the expectation over the distribution of offspring number, the conditional probability is given by
+By taking the expectation over the distribution of offspring number, the conditional probability is approximately given by
 \begin{align}
@@
 \end{align}
-By taking the expectation over $k$ and $\lambda$, in the same manner as noted above, the unconditional probability is given by
+By taking the expectation over $k$ and $\lambda$, in the same manner as noted above, the unconditional probability is approximately given by
 \begin{align}
@@
 \section*{APPENDIX 3}
+
+\section*{Covariation between migration and reproductive potential}
+
+Here, we consider the situation in which migrants have a distinguishable distribution of reproductive potential from non-migrant parents.
+
+上のモデルでは，サブ集団１とサブ集団２を構成する親魚の繁殖ポテンシャルの分布をそれぞれ考慮していたが，移動個体の繁殖ポテンシャルの不均一性については考慮していなかった。最後に，移動した親魚の繁殖ポテンシャルについてもある分布に従うと仮定しよう。すなわち，$\lambda_{1,i}, \lambda_{2,j}, \lambda_{M,l}$をそれぞれ独立な確率変数とみなして，MHSペア確率を計算すると，
+\begin{align}
+\pi | _{\boldsymbol{\lambda_1, \lambda_2, \lambda_M}} &\approx \frac{4}{M} \frac{ \sum_{i=1}^M \lambda_{M,i} \sum_{j=1}^M \lambda_{M,j} } {\left(\sum_{i=1}^{M} \lambda_{M,i} + \sum_{i=M+1}^{N_1} \lambda_{1,i}\right) \left(\sum_{j=1}^{M} \lambda_{M,j} + \sum_{j=M+1}^{N_2} \lambda_{2,j}\right) }
+\end{align}
+のようになり，$N_1$, $N_2$が$M$より十分に大きいと仮定すると、この期待値は以下のようになる，
+\begin{align}
+\pi &\approx \frac{4M}{N_{1}N_{2}} \mathbb{E}\left[ \frac{ \lambda_M^2 }{\lambda_1\lambda_2} \right]
+\label{5-1}
+\end{align}
+すなわち，繁殖ポテンシャルの効果がMHSペア確率に影響するようになる。
 

### 2021-12-17 latex/ms.tex
done App3, #8

--- 2021-12-16 latex/ms.tex
@@
 In other words, the conditional probability does not affected by $\mathbb{V}[k|_\lambda]$.
-As noted above, we assume that $\lambda_{i,1}$ and $\lambda_{j,2}$ is also a random variable followed by an arbitral function with mean ${\bar \lambda_{1}}$ and ${\bar \lambda_{2}}$, respectively.
+We assume that $\lambda_{i,1}$ and $\lambda_{j,2}$ is also a random variable followed by an arbitral function with mean ${\bar \lambda_{1}}$ and ${\bar \lambda_{2}}$, respectively.
 By taking the expectation over $\lambda$ and applying a similar approximation, the unconditional probability is given by
@@
 &= \frac{4M}{N_{1}N_{2}},
+\label{App2}
 \end{align}
 which provides the same formulation described in Eq.\ref{HS-1}.
-It should be noted that, from the third to the forth line, we assume statistical independence of reproductive potential before and after parental movement.
-In {\bf Appendix 3}, we consider the situation in which the statistical independence does not hold.
-
-Similar to the derivation of $\pi_{\rm HS,bet}$, the conditional probability that offspring sampled in the population 1 and a parent sampled in the population 2 share an PO relationship is
+It should be noted that, from the third to the forth line, we assume that $\lambda_{l,1}$ and $\lambda_{l,2}$ ($l = 1, \ldots, M$) are independent variables (i.e., $\mathbb{E}[\lambda_{l,1}\lambda_{l,2}] = {\bar \lambda_{1}}{\bar \lambda_{2}}$), implying variable reproductive potential of an identical parent before and after migration.
+
+Next, we derive the probability that offspring sampled in the population 1 and a parent sampled in the population 2 share an PO relationship ($\pi_{\rm PO,bet}$) under the flexible settings of $\lambda$, which is similar to the derivation of $\pi_{\rm HS,bet}$.
+The conditional probability is given by
 \begin{align}
@@
 \section*{APPENDIX 3}
+
+\section*{Difference in reproductive potential between migrants and non-migrants}
+
+In the process of the derivation of $\pi_{\rm HS,bet}$ and $\pi_{\rm PO,bet}$ in {\bf APPENDIX 2}, we ignore covariation between migration and reproductive potential.
+Here, we consider the situation in which migrants have a distinguishable distribution of reproductive potential from non-migrant parents.
+Let $\lambda_{i,1}$, $\lambda_{j,2}$, $\lambda_{M,l,1}$ and $\lambda_{M,l,2}$ be a reproductive potential of non-migrant in the population 1 and 2 and migrants in the population 1 and 2 with mean ${\bar \lambda_{1}}$, ${\bar \lambda_{2}}$, ${\bar \lambda_{M,1}}$ and ${\bar \lambda_{M,2}}$, respectively.
+Under this setting, $\pi_{\rm HS,bet}$ can be written by
+\begin{align}
+\pi_{\rm HS,bet} &\approx \frac{4}{M}  \frac{ \mathbb{E}\left[ \sum_{l=1}^M \lambda_{M,l,1} \sum_{l=1}^M \lambda_{M,l,2} \right]} {\mathbb{E}\left[ \left(\sum_{l=1}^{M} \lambda_{M,l,1} + \sum_{i=M+1}^{N_1} \lambda_{i,1}\right) \left(\sum_{l=1}^{M} \lambda_{M,l,2} + \sum_{j=M+1}^{N_2} \lambda_{j,2}\right) \right] }\nonumber\\
+&= \frac{4}{M} \frac{ M^2 {\bar \lambda_{M,1}} {\bar \lambda_{M,2}} } { M {\bar \lambda_{M,1}} + (N_1 - M) {\bar \lambda_1} + M {\bar \lambda_{M,2}} + (N_2 - M) {\bar \lambda_2} }.
+\label{App3}
+\end{align}
+If ${\bar \lambda_{M,1}} = {\bar \lambda_{1}}$ and ${\bar \lambda_{M,2}} = {\bar \lambda_{2}}$, Eq.~\ref{App3} reduces to Eq.\ref{App2}.
+This formulation include reproductive potential terms, so that distinct reproductive potential between migrants and non-migrants vanishes the usefulness from proposed HS-based estimators (this is also applied to PO-based estimators proposed in this paper).
 

### 2021-12-17 latex/ms.tex
done figure caption in Fig2, #9

@@
 In this section, we present the theoretical foundation for estimating a migrant number and a migration rate of iteroparous species using HS or PO pairs, which are found between two populations with a different sample timing.
-While the estimators can hold under flexible assumptions for reproduction (see {\bf Appendix}), here we assume a relatively simple situation for explanation purposes.
+While the estimators can hold under flexible assumptions for reproduction (see {\bf Appendix 2}), here we assume a relatively simple situation for explanation purposes.
 The main symbols used in the current paper are summarized in {\bf Table \ref{symbols}}.
@@
 In this framework, we show that considering two reproductive seasons (hereafter, we call them "the first year" and "the second year") is enough to estimate it.
-{\bf Figure \ref{cartoon}} presents a schematic representation of the kinship relationships and movements of parents.
+{\bf Figure \ref{cartoon}a} presents a schematic representation of the kinship relationships and movements of parents.
 
@@
 Similar to the population 1, $N_2$ parents produce offspring in which the number is governed by $\lambda_{j,2}$ ($j=1,2,\ldots,N_2$).
-The reproductive potential is determined by several factors and its details are summarized in {\bf Appendix}; theoretically speaking, the number of offspring for each parent is set as a random variable with mean $\lambda_{i,1}$ or $\lambda_{j,2}$.
+The reproductive potential is determined by several factors and its details are summarized in {\bf Appendix 1}; theoretically speaking, the number of offspring for each parent is set as a random variable with mean $\lambda_{i,1}$ or $\lambda_{j,2}$.
 
@@
 For the applicability of fishery management, we assume invasive sampling procedure, preventing the finding of a parent-offspring pair such that a parent and offspring is sampled in the population 1 and 2, respectively.
-{\bf Figure~\ref{cartoon}a} illustrates a timeline of sampling scheme for hypothetical populations.
-
-In the example depicted in {\bf Fig~\ref{cartoon}b}, five offspring and four parents are sampled in the population 1 and four offspring and six parents are sampled in the population 2, and two HS and one PO pairs found between the two populations are observed.
+{\bf Figure~\ref{cartoon}b} illustrates a timeline of sampling scheme for hypothetical populations.
+
+In the example depicted in {\bf Fig~\ref{cartoon}a}, five offspring and four parents are sampled in the population 1 and four offspring and six parents are sampled in the population 2, and two HS and one PO pairs found between the two populations are observed.
 In addition, there are several PO pairs observed within the same population, which are available to estimate parent numbers, as explained in the following section.
@@
 Here, we consider the probability that two offspring sampled in the population 1 and 2 share an HS relationship with an arbitrary mother or father, denoted by $\pi_{\rm HS, bet}$.
-For the explanation purpose, we assume equal reproductive potential among parents up to the subsection 2.7, although this assumption can be relaxed for most of the case (see details in {\bf Appendix}).
+For the explanation purpose, we assume equal reproductive potential among parents up to the subsection 2.7, although this assumption can be relaxed for most of the case (see details in {\bf Appendix 2}).
 $\pi_{\rm HS, bet}$ can be partitioned into the three probabilities: (i) the probability that sampled offspring in the population 1 born to a parent that safely arrives in the population 2 (hereafter, called "migrant"); (ii) the probability that sampled offspring in the population 2 born to a migrant; and (iii) the probability that the migrant of a sampled offspring in the population 1 and the migrant of a sampled offspring in the population 2 are identical.
@@
 \end{align}
-This form holds under a flexible setting for the reproductive potential, such as a situation with random variable of $\lambda_{i,1}$ and $\lambda_{j,2}$, as noted in {\bf Appendix}.
+This form holds under a flexible setting for the reproductive potential, such as a situation with random variable of $\lambda_{i,1}$ and $\lambda_{j,2}$, as noted in {\bf Appendix 2}.
 If all $N_1$ parents safely move to the population 2 (i.e., $M = N_1$), $\pi_{\rm HS,bet}$ equals $4/N_2$; meanwhile, if the population 2 consists only of migrants (i.e., $M = N_2$), $\pi_{\rm HS,bet}$ equals $4/N_1$.
@@
 \end{align}
-While estimator of the migrate number (Eq.~\ref{AP-4}) requires the (unknown) parent number in the population 1 ($N_{1}$), estimator of the migration rate (Eq.~\ref{AP-5}) can be obtained only the observed kinship pairs.
+While estimator of the migrate number (Equation~\ref{AP-4}) requires the (unknown) parent number in the population 1 ($N_{1}$), estimator of the migration rate (Equation~\ref{AP-5}) can be obtained only the observed kinship pairs.
 
@@
 The proposed estimators are derived under the assumption that reproductive potential is the same among individuals.
-As noted in {\bf Appendix}, this assumption can be relaxed and the estimators still hold, which is exemplified in iteroparous species that may show significant variation in reproductive potential among individuals.
+As noted in {\bf Appendix 2}, this assumption can be relaxed and the estimators still hold, which is exemplified in iteroparous species that may show significant variation in reproductive potential among individuals.
 Furthermore, the estimators even hold for most of the case where mean reproductive potential are different between population 1 and 2, which is exemplified in the situation that the environmental condition for reproductive success varies between populations.
-The necessary condition is that the migration event does not depends on the degree of reproductive potential (see details in  {\bf Appendix}).
+The necessary condition is that the migration event does not depends on the degree of reproductive potential (see details in  {\bf Appendix 3}).
 
@@
 The population structure was assumed to be identical to that in the development of the estimators.
-The population 1 and 2 comprised $N_1$ and $N_2$ parents with an equal sex ratio, and their offspring number was assumed to follow the geometric distribution with mean $\lambda_1$ and $\lambda_2$ (i.e., Poisson reproduction with mean $\lambda_{i,1}$ and $\lambda_{j,2}$ which follows the exponential distribution with mean $\lambda_1$ and $\lambda_2$), respectively.
+The population 1 and 2 comprised $N_1$ and $N_2$ parents with an equal sex ratio, and their offspring number was assumed to follow the geometric distribution with mean ${\bar \lambda_1}$ and ${\bar \lambda_2}$ (i.e., Poisson reproduction with mean $\lambda_{i,1}$ and $\lambda_{j,2}$ which follows the exponential distribution with mean ${\bar \lambda_1}$ and ${\bar \lambda_2}$), respectively.
 Migrant parents were randomly chosen from the population 1 at the end of the first year.
@@
 
-Let a parameter set ($N_1$, $N_2$, $M$, $\lambda_1$, $\lambda_2$, $n_{\rm O,1}$, $n_{\rm O,2}$, $n_{\rm P,1}$, $n_{\rm P,2}$) be given.
+Let a parameter set ($N_1$, $N_2$, $M$, ${\bar \lambda_1}$, ${\bar \lambda_2}$, $n_{\rm O,1}$, $n_{\rm O,2}$, $n_{\rm P,1}$, $n_{\rm P,2}$) be given.
 We simulated a population history and a sampling process, which generates proposed estimators; this process was repeated 1000 times, making it possible to construct the distribution of the estimators for each parameter set.
@@
 		                						& \\
-	$\lambda_{i, M}$					& Expected number of surviving offspring of migrant $i$ at sampling\\
+	$\lambda_{M,l,1}, \lambda_{M,l,2}$		& Expected number of surviving offspring of migrant $l$ at sampling in the population 1 and 2\\
 		                						& \\
@@
 
-\newcommand{\figcapa}{(a) The phases of the events relevant to this study along the time line.
-(b) Hypothetical populations with $N_{1}=16$, $N_{2}=14$, and $M=6$.
+\newcommand{\figcapa}{(a) Hypothetical populations with $N_{1}=16$, $N_{2}=14$, and $M=6$.
 Upper and lower square indicates individuals belonging to the population 1 before migration (at sample timing in the first year) and individuals belonging to the population 2 after reproduction (at sample timing in the second year), respectively.
@@
 Sampled individuals are labeled with an index number.
-The number of sampled individuals in this example: $n_{\rm P, 1}=4$, $n_{\rm O, 1}=5$, $n_{\rm P, 2}=6$, $n_{\rm O, 2}=4$; the numbers of kinship pairs: $H_{\rm PO, bet}=1$ (i.e., ``7-10'' pair), $H_{\rm HS, bet}=2$ (i.e., ``8-16'' and ``9-16'' pairs), $H_{\rm PO, 1}=3$ (i.e., ``1-6'', ``3-5'' and ``4-7'' pairs), and $H_{\rm PO, 2}=2$ (i.e., ``11-17'' and ``15-16'' pairs).}
-
-\newcommand{\figcapb}{Violin plots showing the distribution of relative bias in our estimator (Eq.~\ref{NeN_hat2}) for various values of $c$ and sample size.
+The number of sampled individuals in this example: $n_{\rm P, 1}=4$, $n_{\rm O, 1}=5$, $n_{\rm P, 2}=6$, $n_{\rm O, 2}=4$; the numbers of kinship pairs: $H_{\rm PO, bet}=1$ (i.e., ``7-10'' pair), $H_{\rm HS, bet}=2$ (i.e., ``8-16'' and ``9-16'' pairs), $H_{\rm PO, 1}=3$ (i.e., ``1-6'', ``3-5'' and ``4-7'' pairs), and $H_{\rm PO, 2}=2$ (i.e., ``11-17'' and ``15-16'' pairs).
+(b) The phases of the events relevant to this study along the time line.}
+
+\newcommand{\figcapb}{Violin plots showing the distribution of relative bias in our estimator of $M$ for various values sample sizes, parent numbers and migration rate.
 Filled circles represent the mean values.
-Sample sizes for mothers and offspring are identical (i.e., $n=n_{\rm M} = n_{\rm O}$) and indicated in the legend.
+Sample sizes for parents and offspring are identical (i.e., $n=n_{\rm P,1}=n_{\rm P,2}=n_{\rm O,1}= n_{\rm O,2}$) and parent sizes in the two populations are also identical (i.e., $N=N_1=N_2$), which are indicated in the legend.
+Migration rate $m$ is specified by $N_1/M$.
 For the demonstration purposes, the distribution is truncated, although the mean values are calculated including the truncated values.
-(a) $N_{\rm m}=1{,}000$, (b) $N_{\rm m}=10{,}000$.}
+}
 
@@
 
-\section*{APPENDIX A}
-\setcounter{equation}{0}
-
-\section*{Distribution of the number of surviving offspring per mother and its variance}
-
-\renewcommand{\theequation}{A\arabic{equation}}
-
-Let $k_i$ denote the total number of surviving offspring from a mother  $i$ ($i= 1, 2, \dots, N_{\rm m}$) at time of sampling.
-Following \cite{Akita_2019} and giving the expected number of the surviving offspring per mother at time of sampling, $\lambda_i$ ($>0$), $k_i$ is assumed to follow a negative binomial distribution through a conventional parametrization:
-\begin{equation}
-{\rm Pr}[ k_i | \lambda_i ] = \frac{\Gamma[k_i+\phi]}{k_i! \Gamma[\phi]} \left( \frac{\lambda_i}{\phi+\lambda_i} \right)^{k_i} \left( \frac{\phi}{\phi+\lambda_i} \right)^{\phi}, 
-\label{NB}
-\end{equation}
-where $\phi$ ($>0$) denotes the overdispersion parameter describing the degree of nonparental variation.
-In the current work, $\phi$ is assumed to be constant across mothers, whereas the expected number of surviving offspring ($\lambda_i$) varies across mothers.
-The mean and variance of this distribution are denoted by $\lambda_i$ and $\lambda_i + \lambda_i^2/\phi$, respectively.
-In the limit of infinite $\phi$, this distribution becomes a Poisson distribution, which is given by ${\rm Pr}[ k_i | \lambda_i ]=\lambda_i^{k_i} \mathrm{e}^{-\lambda_i}/(k_i!)$.
-We assume $\lambda_i$ to be independent and identically distributed with the density function $f(\lambda)$, producing a parental variation.
-The shape of the density function is often complex, but may be described by information from the population, for example, the mother's weight composition in the population.
-The specific form of $f(\lambda)$ is given in {\bf Appendix B} and is used for running an individual-based model.
-
-The variance of the offspring number can be given by 
-\begin{eqnarray}
-\mathbb{V}[k] &=& \mathbb{E}[ \mathbb{V}[k|\lambda] ] + \mathbb{V}[ \mathbb{E}[k|\lambda] ] \nonumber\\
-&=& \mathbb{E}[ \lambda + \lambda^2 / \phi ] + \mathbb{V}[ \lambda ].
-\label{V_k}
-\end{eqnarray}
-
-\section*{Appendix B}
-\setcounter{equation}{0}
-\section*{Probability density function and its moment of offspring number per mother}
-\renewcommand{\theequation}{B\arabic{equation}}
-
-As stated in the main text, our modeling framework does not require the specific form of the density function of offspring number per mother (denoted by $f(\lambda)$); it only requires the ratio of the second moment to the squared first moment ($\mathbb{E}[\lambda^2] / \mathbb{E}[\lambda]^2$) instead.
-However, the specific form is required for evaluating the theoretical results (i.e., calculating the moment or running the individual-based model).
-Herein, we model an age-structured fish population that serves as a representative example, demonstrating both parental and nonparental variations.
-The following contents are almost the same as those of \cite{Akita_2019} except for the parameter values that produce the setting $c=$ 20 and 100.
-
-Suppose that the mean fecundity of a mother depends on her age.
-Let $\lambda_a$ denote the mean fecundity, which is a function of age (denoted by $a$).
-The moment can be defined as $\mathbb{E}[\lambda^m] = \sum_{a=0}^{a_{\rm max}} \lambda_a^m h_{\rm mat}(a)$, where $h_{\rm mat}(a)$ is the frequency of mature mothers at a given age, and $a_{\rm max}$ denotes the maximum age.
-Thus, we can numerically obtain the moment by applying $\lambda_a$ and $h_{\rm mat}(a)$.
-
-For marine species with a type-III survivorship curve, it is generally assumed that individual fecundity is proportional to weight.
-By utilizing the von Bertalanffy growth equation for body weight, $\lambda_a$ is explicitly defined as a function of age as follows:
-\begin{equation}
-\lambda_a \propto ( 1-{\rm exp}[-\kappa(a-a_0)])^{\beta}, 
-\label{VB}
-\end{equation}
-where $\kappa$, $a_0$, and $\beta$ are conventionally used parameters in the von Bertalanffy equation, and they denote the growth rate, the adjuster of the equation for the initial size of the animal, and the allometric growth parameter, respectively.
-To obtain a specific value of $\lambda$, a coefficient value of 10 multiplied by the right-hand side of Eq.~\ref{VB} was used when running the individual-based model.
-
-The frequency of mature mothers at a given age can be given as the following: 
-\begin{equation}
-h_{\rm mat}(a) \propto h(a)Q(a),
-\label{freq}
-\end{equation}
-satisfying $\sum_{a=0}^{a_{\rm max}}h_{\rm mat}(a)=1$, where $h(a)$ and $Q(a)$ denote the frequency and maturity at a given age, respectively.
-Although $f(a)$ is affected by historical population dynamics and age-dependent survival, for simplicity, the mortality rate is assumed to be constant (i.e., age independent):
-\begin{equation}
-	h(a)\propto
-	\left \{
-	\begin{array}{l}
-		S^{a}\\
-		0
-	\end{array}
-	\begin{array}{l}
-		{\rm if}\ a < a_{\rm max}\\
-		{\rm if}\ a = a_{\rm max}
-	\end{array}
-	\right.
-	,
-	\label{survival}
-\end{equation}
-where $S$ denotes a survival probability. The maturity at age ($Q(a)$) is assumed to be a knife-edge function, which is given by
-\begin{equation}
-	Q(a)=
-	\left \{
-	\begin{array}{l}
-		1\\
-		0
-	\end{array}
-	\begin{array}{l}
-		{\rm if}\ a\geq a_{\rm mat}\\
-		{\rm otherwise }
-	\end{array}
-	\right.
-	,
-	\label{Q}
-\end{equation}
-where $a_{\rm mat}$ denotes the mature age.
-
-To calculate $\mathbb{E}[\lambda^2] / \mathbb{E}[\lambda]^2$, the required parameter set is $(a_{\rm max}, \kappa, a_0, \beta, S, a_{\rm mat})$.
-In this study, for the purpose of representation, we fixed the values of several parameters as follows: $a_{\rm max}=20$, $\kappa=0.3$, $a_0=0$, $S=0.5$ and $a_{\rm mat}=0$.
-In addition, we selected parameter value $c$ (defined in Eq.~\ref{c} in the main text) to be 1, 10, 20, and 100 for comparison with the results in the main text that are derived from the parameter set $(\phi, \beta)=(1000,0.0009)$, $(0.1302,0.9)$, $(0.06111,0.9)$, and $(0.01165,0.9)$, respectively.
-
-Finally, we provide specific forms of $f(\lambda)$; thus, when $\lambda_a$ and $h_{\rm mat}(a)$ are obtained, $f(\lambda)$ is given by
-\begin{equation}
-	f(\lambda) =
-	\left \{
-	\begin{array}{l}
-		h_{\rm mat}(a)\\
-		0
-	\end{array}
-	\begin{array}{l}
-		{\rm if}\ \lambda = \lambda_a\\
-		{\rm otherwise }
-	\end{array}
-	\right.
-	.
-	\label{f_lambda}
-\end{equation}
-
-\section*{Appendix C}
-\setcounter{equation}{0}
-\section*{Combined effect of parental and nonparental variations}
-
-\renewcommand{\theequation}{C\arabic{equation}}
-
-Following \cite{Akita_2019}, combined effect of parental and nonparental variations can be partitioned into the two components, such as: 
-\begin{equation}
-c = (1+\phi^{-1}) \times \left(\frac{\mathbb{E}[\lambda^2]}{\mathbb{E}[\lambda]^2}\right). 
-\label{c}
-\end{equation}
-The first and second parentheses give the effect of nonparental variation and parental variation, respectively.
-When $\lambda$ is constant across mothers, $\mathbb{E}[\lambda^2]$ equals $\mathbb{E}[\lambda]^2$ and $c$ converges to $(1+\phi^{-1})$; meanwhile, $\phi \to \infty$, $c$ converges to $\mathbb{E}[\lambda^2]/\mathbb{E}[\lambda]^2$.
-Without either parental or nonparental variation, $c$ converges to 1 and $\pi_{\rm MS}$ converges to $1/N_{\rm m}$.
-In the main text, we refer to ``overdispersion'' as the skewed distribution of the offspring number resulting from this combined effect.
-
-Using Eqs.~\ref{V_k} and \ref{c}, the variance of the offspring number can be expressed as  
-\begin{equation}
-\mathbb{V}[k] = \mathbb{E}[\lambda] + \mathbb{E}[\lambda]^2 (c-1),  
-\label{V_k2}
-\end{equation}
-suggesting that the variance substantially increases with $c$.
-
-\section*{Appendix D}
-\setcounter{equation}{0}
-\section*{Derivation of the bias of $\widehat{N_{\rm e,m}/N_{\rm m}}$}
-\renewcommand{\theequation}{D\arabic{equation}}
-
-For calculation of the bias of $\widehat{N_{\rm e,m}/N_{\rm m}}$, we require an expectation of the estimator given by
-
-\begin{equation}
-\mathbb{E}\left[\widehat{\left(\frac{N_{\rm e,m}}{N_{\rm m}}\right) }\right] = \mathbb{COV}\left[\widehat{\left(\frac{1}{N_{\rm m}}\right)}, \widehat{N_{\rm e,m}} \right] + \mathbb{E}\left[\widehat{\left(\frac{1}{N_{\rm m}}\right)}\right] \mathbb{E}\left[ \widehat{N_{\rm e,m}} \right].
-\label{E_NeN}
-\end{equation}
-As stated in the main text, both $\widehat{N_{\rm e,m}}$ and $\widehat{1/N_{\rm m}}$ are independent.
-Thus, the first term in the right-hand side of Eq.~\ref{E_NeN} can be ignored.
-The expectation of $\widehat{1/N_{\rm m}}$ is given by
-\begin{eqnarray}
- \mathbb{E}\left[\widehat{\left(\frac{1}{N_{\rm m}}\right)}\right] &=& \frac{\mathbb{E}\left[ H_{\rm MO}\right]}{n_{\rm M}n_{\rm O}}\nonumber\\
- &=& \frac{1}{N_{\rm m}}.
- \label{Ninv_bias_app}
-\end{eqnarray}
-From the first to the second line of Eq.~\ref{Ninv_bias_app} , we applied the relationship $\pi_{\rm MO} = \mathbb{E}[\pi_{\rm MO}] = \mathbb{E}[H_{\rm MO}]/(n_{\rm M}n_{\rm O})$ and Eq.~\ref{pi_MO}.
-Equation~\ref{Ninv_bias_app} indicates that $\widehat{1/N_{\rm m}}$ is the unbiased estimator.
-The expectation of $\widehat{N_{\rm e,m}}$ is given by
-\begin{equation}
-\mathbb{E}[\widehat{N_{\rm e,m}}] = N_{\rm e,m} - N_{\rm e,m}\left(1-\frac{1}{N_{\rm e,m}}\right)^{\binom{n_{\rm O}}{2}+1},
-\label{bias_Ne}
-\end{equation}
-which is illustrated in Appendix D of \cite{Akita_2019}. Together with these relationships, we can obtain the bias of $\widehat{N_{\rm e,m}/N_{\rm m}}$ described in Eq.~\ref{bias}.
-
-\section*{Appendix E}
-\setcounter{equation}{0}
-\section*{Individual-based model with application of Wang's estimator}
-\renewcommand{\theequation}{E\arabic{equation}}
-
-Our modeling framework estimates the ratio of contemporary effective mother size to census size (denoted by $N_{\rm e,m}/N_{\rm m}$), as a proxy for the ratio of contemporary effective size to census size (denoted by $N_{\rm e}/N$).
-To compare the performance of our method with that of other methods for directly estimating $N_{\rm e}/N$, we propose the estimator of $N_{\rm e}/N$, given by
-\begin{eqnarray}
-\widehat{\left(\frac{N_{\rm e}}{N}\right) } &=& \widehat{N_{\rm e}}\widehat{\left(\frac{1}{N}\right)}\nonumber\\
-&=& \frac{4\binom{n_{\rm O}}{2}}{H_{\rm HS}^{\rm obs}+H_{\rm FS}^{\rm obs}} \frac{H_{\rm PO}^{\rm obs} } {2n_{\rm P}n_{\rm O}}.
-\label{NeN_wang}
-\end{eqnarray}
-$n_{\rm P}$ and $n_{\rm O}$ indicate the sample numbers of parents and offspring, respectively, and $H_{\rm HS}^{\rm obs}$, $H_{\rm FS}^{\rm obs}$, and $H_{\rm PO}^{\rm obs}$ indicate the observed number of half-sibling, full-sibling, and parent-offspring pairs, respectively.
-$\widehat{N_{\rm e}}$ is based on \cite{wang2009new} assuming random mating and $\widehat{1/N}$ is defined in Eq.~\ref{N_inv_hat2} in the main text.
-
-We evaluated the estimator's performance on data simulated by running an individual-based model under the Wright-Fisher process for a diploid population.
-In the current comparison, we did not consider the case of overdispersion (i.e., $N_{\rm e} = N$).
-Sex ratio was fixed to 0.5 in both whole and sampled populations.
-Each parent retained the ID of its offspring, making it possible to trace HS, FS, and PO relationships.
-Given a parameter set ($N$, $n_{\rm O}$, and $n_{\rm P}$), we backwardly simulated a population history in which  mother-offspring and father-offspring relationships were randomly specified from $n_{\rm O}$ offspring; this process was repeated 10{,}000 times, acquiring 10{,}000 data points that were used to construct the distribution of $\widehat{N_{\rm e}/N}$ for each parameter set.
-If neither HS nor FS pairs were found in a sample, we did not include that trial when constructing the distribution.
-For ease of comparison, we used the same sample size and population structure for both methods.
-
-{\bf Figure.~E\ref{violin_wang}} illustrates the distribution of the relative bias of $\widehat{N_{\rm e}/N}$ for limiting cases where parent and offspring sample numbers are identical (i.e., $n_{\rm P} = n_{\rm O}$).
-Our results indicate that the estimator is upwardly biased, particularly when sample size is small.
-Alternatively, our estimator shows a broader region such that unbiasedness is approximately achieved.
-For example, when $n = 100$ and $150$ in $N = 2000$ (i.e., $N_{\rm m}=1000$), the bias of $\widehat{N_{\rm e}/N}$ is clearly observed ({\bf Fig.~E\ref{violin_wang}a}); meanwhile, $N_{\rm e,m}/N_{\rm m}$ does not produce a bias in these conditions ({\bf Fig.~\ref{violin}a}).
-
 \clearpage

### 2021-12-20 latex/ms.tex
add text for CV and required sample size

@@
 It should be noted that very tiny $m$, which dramatically increases the required sample size, produces significant genetic differences between two populations.
-In such a case, there are several methods to estimate migration rate by population genetics technique; alternatively, we focus the situation of moderate/large migration rate, which leads little genetic differences between two populations (see details in {\bf Results and Discussion} section).
+In such a case, there are several methods to estimate migration rate by population genetics technique; alternatively, we focus the situation of moderate/large migration rate, which leads little genetic differences between two populations (see details in {\bf Discussion} section).
+
+Other guidance for the required sample size is obtained by an approximate lower bound on the CV (coefficient of variation) of $M_1$ or $m_1$, which is defined by $1/\sqrt{H_{\rm HS, bet}}$.
+For example, to achieve a 30\% CV, the target of $H_{\rm HS, bet}$ is more than 10, providing the required sample size when population parameters are given (e.g., $N_1$, $N_2$ and $M$).
+Similarly, the CV of $M_2$ or $m_2$, defined by $1/\sqrt{H_{\rm PO, bet}}$, provides the required sample size for estimating $M_2$ or $m_2$.
 
@@
 
-\section{Results and Discussion}\label{sec3}
+\section{Results}\label{sec3}
+
+\section{Discussion}\label{sec4}
 

### 2021-12-20 latex/ms.tex
add citation about CV

@@
 
-Other guidance for the required sample size is obtained by an approximate lower bound on the CV (coefficient of variation) of $M_1$ or $m_1$, which is defined by $1/\sqrt{H_{\rm HS, bet}}$.
+Other guidance for the required sample size is obtained by an approximate lower bound on the CV (coefficient of variation) of $M_1$ or $m_1$, defined by $1/\sqrt{H_{\rm HS, bet}}$, which is applied in the context of a classic mark-recapture \cite[]{seber1982estimation} or close-kin mark-recapture \cite[]{bravington2016close}.
 For example, to achieve a 30\% CV, the target of $H_{\rm HS, bet}$ is more than 10, providing the required sample size when population parameters are given (e.g., $N_1$, $N_2$ and $M$).

### 2021-12-20 latex/ms.tex
add intro in Results section, #13

@@
 
-\section{Discussion}\label{sec4}
+We numerically evaluated the performance of ${\hat M}$ or ${\hat m}$ for the case in which variable reproductive potential among parents.
+Scaled statistical properties of ${\hat m_1}$,  ${\hat m_2}$,  ${\hat m_3}$ and ${\hat m_4}$ are completely the same to ${\hat M_1}$, ${\hat M_2}$, ${\hat M_3}$ and ${\hat M_4}$, hereafter, we only demonstrate the results of ${\hat M_1}$-${\hat M_5}$.
+{\bf Figure~\ref{violins}} illustrates the distribution of the relative bias of ${\hat M}$ for limiting cases where parent and offspring sample numbers are identical (i.e., $n=n_{\rm P,1}=n_{\rm P,2}=n_{\rm O,1}= n_{\rm O,2}$) and parent numbers in the two populations are also identical (i.e., $N=N_1=N_2$).
+Relative bias is calculated by applying outputs of the individual-based model, which is defined as follows: ``averaged estimator - true value/true value.'' Full list of parameter sets to evaluate the performance (relative bias and CV of ${\hat M}$) is summarized in {\bf Table S1} in {\bf Supporting Information}.
 
@@
 %%%%%%%%%%%%%%
+
+\subsection{Properties of ${\hat M}$}
+
+%property of M_i (all are unbiased estimators (accuracy), M_3 shows the best performance (precision))
+
+\subsection{Required sample size}
+
+\subsection{Invasive sampling}
+
+\subsection{Case of $N_1 \neq N_2$}
+
+\section{Discussion}\label{sec4}
 

### 2021-12-21 latex/ms.tex
add 3para in Results section, #13

@@
 {\bf Figure~\ref{violins}} illustrates the distribution of the relative bias of ${\hat M}$ for limiting cases where parent and offspring sample numbers are identical (i.e., $n=n_{\rm P,1}=n_{\rm P,2}=n_{\rm O,1}= n_{\rm O,2}$) and parent numbers in the two populations are also identical (i.e., $N=N_1=N_2$).
-Relative bias is calculated by applying outputs of the individual-based model, which is defined as follows: ``averaged estimator - true value/true value.'' Full list of parameter sets to evaluate the performance (relative bias and CV of ${\hat M}$) is summarized in {\bf Table S1} in {\bf Supporting Information}.
+Relative bias is calculated by applying outputs of the individual-based model, which is defined as follows: ``averaged estimator - true value/true value.'' Full list of parameter sets to evaluate the performance (relative bias and CV of ${\hat M}$s) is summarized in {\bf Table S1} in {\bf Supporting Information}.
 
@@
 
-\subsection{Properties of ${\hat M}$}
+First, we evaluated the accuracy of ${\hat M}$s based on their relative bias.
+As expected, for most of the investigated parameter sets, we observed that their relative bias is less than 5\%, as demonstrated in {\bf Table S1} in {\bf Supporting Information}.
+Thus, when the assumption that kinships are detected without any error is satisfied, it is reasonable to call ${\hat M}$s (nearly) unbiased estimators.
 
-%property of M_i (all are unbiased estimators (accuracy), M_3 shows the best performance (precision))
+Next, we evaluated the precision of ${\hat M}$s based on their CV.
+{\bf Table S1} in {\bf Supporting Information} demonstrated the value of the CV; meanwhile, the violin plot ({\bf Figure~\ref{violins}}) visually provides the degree of precision.
+For each estimator ${\hat M}$, the precision increases with increasing of sample size.
+It should be noted that total sample size depends on the estimator.
+For example, $n=50$ in Fig.~\ref{violins}, the total sample size of ${\hat M_1}$, ${\hat M_2}$, ${\hat M_3}$, ${\hat M_4}$ and ${\hat M_5}$ is 100 ($=n_{\rm O,1}+n_{\rm O,2}$), 100 ($=n_{\rm O,1}+n_{\rm P,2}$), 150 ($=n_{\rm O,1}+n_{\rm O,2}+n_{\rm P,2}$), 150 ($=n_{\rm O,1}+n_{\rm O,2}+n_{\rm P,2}$) and 200 ($=n_{\rm O,1}+n_{\rm O,2}+n_{\rm P,1}+n_{\rm P,2}$), respectively.
 
-\subsection{Required sample size}
+As sample size or migrants increase, the precision increases and the shape of the distribution asymptotically becomes symmetric ({\bf Figure~\ref{violins}}).
+This is because increasing of a sample size or migrants increases of the probability that randomly selected two individuals share kinship between the two populations and thus decreases the CV.
+
+\subsection{Case of $N_1 \neq N_2$}
 
@@
 
-\subsection{Case of $N_1 \neq N_2$}
-
 \section{Discussion}\label{sec4}
-
-\begin{comment}
-
-The estimation of the ratio of the contemporary effective population size to the census size ($N_{\rm e}/N$) has attracted much research attention for providing information about a current population, especially in the context of conservation biology and wildlife management \cite[]{Palstra_2012,FRANKHAM201456}.
-Small $N_{\rm e}/N$ demonstrates large variance in reproductive success \cite[]{Wang:2016aa, JFB:JFB13143, Akita_2019}, resulting from the variance of reproductive potential \cite[e.g., the big old fat fecund female fish hypothesis;][]{Hixon_2014} or from the situation in which only some families successfully reproduce \cite[referred to as the ``Sweepstakes reproductive success'' hypothesis,][]{hedgecock2011sweepstakes}.
-Moreover, if $N_{\rm e}/N$ is invariant across years, then $N_{\rm e}$ may behave like an index of $N$, and vice versa \cite[]{luikart2010estimation}.
-However, if $N_{\rm e}/N$ fluctuates across years, the trends can clarify the interpretation of environmental and/or anthropological factors, causing the variance of reproductive potential, family-correlated survivorship, or fluctuating population dynamics.
-Besides, low precision and/or large bias for estimating $N_{\rm e}/N$ may lead to a wrong interpretation of the population \cite[]{Tallmon:2012aa}.
-
-The estimation of $N_{\rm e}/N$ has been performed by utilizing the estimated values of contemporary effective population size ($N_{\rm e}$) and census size ($N$), unless complete pedigree data and/or full census data are available.
-Additionally, there are numerous methods for estimating $N_{\rm e}$ from genetic markers \cite[][and the references contained therein]{Wang:2016aa}.
-There are also numerous methods for estimating $N$, such as a mark-recapture method or population dynamics modeling with survey data \cite[e.g.,][]{seber1982estimation,quinn1999quantitative,kery2011bayesian,methot2013stock}.
-It is known that there are large variations in both estimators; thus, their combination (i.e., the estimator of $N_{\rm e}/N$) also shows large variation \cite[]{Palstra_2012,Marandel_2018}.
-There is currently a little theoretical foundation for the estimator of $N_{\rm e}/N$, indicating no guidance for a sample size to ensure the required accuracy and precision.
-
-Close-kin mark-recapture (CKMR) is a recently developed method for estimating $N$ that utilizes the information about kinship in a sample.
-This was possible owing to the recent advances in genetic methods for kinship determination \cite[]{Bravington_2016,bravington2016close,skaug2017parent,Hillary_2018} although similar methods have been proposed in the beginning of the 21st century \cite[]{nielsen2001statistical, pearse2001genetic, julius2001allele}.
-Besides, the rationale is that the presence of a kinship pair in the sample is analogous to the recapture of a marked individual in mark-recapture.
-Kinship pairs in the sample are less likely to be observed in larger populations; thus, the number of kinship pairs may reflect $N$.
-While the original CKMR is designed to estimate adult abundance (i.e., $N$), the monitoring data for CKMR also produce the estimator of $N_{\rm e}$ by detecting half-sibling (HS) pairs within the same cohort \cite[]{Akita_2019}.
-This kinship-oriented estimation of $N_{\rm e}$ was presented in the context of the sibship assignment method \cite[]{wang2009new} and is expected to provide a much more accurate estimator as kinship determination becomes more accurate.
-
-In this study, we propose a new method for estimating the ratio of contemporary effective mother size to the census size ($N_{\rm e,m}/N_{\rm m}$) in a population, as a proxy of $N_{\rm e}/N$.
-Assuming that kinships are genetically detected without any error, this method is based on the numbers of maternal-sibling (MS) and mother--offspring (MO) pairs in a sample.
-Sampling is completed at a single breeding time; sampling offspring within the same cohort and mothers probably shares MO relationship with sampled offspring.
-Our model provides a nearly unbiased estimator of $N_{\rm e,m}/N_{\rm m}$ that explicitly incorporates two types of overdispersed reproduction \cite[i.e., parental and nonparental variations;][]{Akita_2019}, making it possible to target a species that shows iteroparity (i.e., multiple reproductive cycles during the lifetime) and/or sweepstakes reproductive success.
-This estimator applying an iteroparous species corresponds to the estimator of the ratio of contemporary effective breeding mother size to the census size, $N_{\rm b,m}/N_{\rm m}$.
-First, we explain the modeling assumption and sampling scheme.
-Then, we analytically determine (nearly) the unbiased estimators of $N_{\rm e,m}$, $ 1/N_{\rm m}$, and $N_{\rm e,m}/N_{\rm m}$, which are based on the numbers of MS and/or MO pairs.
-Finally, by running an individual-based model, we investigate the performance of the estimator and provide a guide for a sample size.
-It is noteworthy that our modeling framework can be applied to diverse animal species.
-However, the description of the model focuses on fish species, which are presently the best candidate target of our proposed method.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{THEORY}\label{theory}
-
-In this section, we present the theoretical foundation for estimating $N_{\rm e,m}/N_{\rm m}$.
-The estimator is based on previous studies that provides the estimator of $N_{\rm e,m}$ \cite[]{Akita_2019} and $1/N_{\rm m}$ \cite[]{Akita2018}.
-The main contribution of this paper is formulation of the estimator of $N_{\rm e,m}/N_{\rm m}$, presented in Eq.~\ref{NeN_hat2}.
-The main symbols used in the current paper are summarized in {\bf Table \ref{symbols}}.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Hypothetical population}
-
-We suppose that there is a hypothetical population comprising $N_{\rm m}$ mothers and there is also no population subdivision or spatial structure.
-In this study, a mature female is called a mother even if she does not produce offspring.
-For mathematical tractability, we assume that only one spawning ground exists in which the mothers remain for the entire spawning season.
-Following \cite{Akita_2019}, our modeling framework employs two types of overdispersed reproduction: parental and nonparental variations.
-Thus, the former indicates a variation caused by the mother's covariates, such as age, weight, and residence time on the spawning ground, while the latter indicates a variation caused by nonrandom stochastic events during a series of reproductive episodes, which are independent of the mother's covariates, such as family-correlated survivorship or the mating behavior effects (e.g., competition for males/females and correlation between mating opportunities of the mother and the number of her offspring).
-{\bf Figure~1} illustrates a schematic diagram of the effects of parental and nonparental variations exemplified by age-dependent reproduction and family-correlated survival on kinship relationships in a population.
-Detailed definitions of parental and nonparental variations are stated in \cite{Akita_2019}.
-{\bf Appendix A} provides the theoretical foundation of both parental and nonparental variations in reproduction.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Sampling}
-
-To obtain the estimator of $N_{\rm e,m}/N_{\rm m}$, we utilize the number of MS and MO pairs observed in a sample.
-For the mathematical tractability, only one reproductive season is targeted for sampling.
-Thus, the sampling method does not affect our modeling framework whether it is invasive or noninvasive.
-In the population, $n_{\rm M}$ mothers are randomly sampled immediately after the end of the reproductive season.
-Additionally, in the population, $n_{\rm O}$ offspring are also randomly sampled.
-The numbers of MS and MO pairs are determined by pairwise comparison of all the sample individuals (${}_{n_{\rm O}}\mathrm{C}_2$ and $n_{\rm M}n_{\rm O}$ comparisons, respectively).
-As depicted in {\bf Fig~\ref{example}}, six offspring and three mothers are sampled and two MS and three MO pairs are observed.
-In our modeling framework, if an MS pair also shares a paternal-sibling (PS) relationship, we count it as an MS pair and ignore the existing full-sibling (FS) relationship.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Linking $N_{\rm e,m}/N_{\rm m}$ to kinship relationships}
-
-In this subsection, we provide the theoretical foundation for understanding how $N_{\rm e,m}/N_{\rm m}$ is associated with kinship relationships in a population, based on work presented in previous studies.
-The rationale is that the observed number of MS and MO pairs have information about $N_{\rm e,m}$ and $N_{\rm m}$, respectively, as noted below.
-
-First, we consider the relationship between the number of MS pairs and $N_{\rm e,m}$. \cite{Akita_2019} defined the contemporary effective mother size as follows: 
-\begin{equation}
-N_{\rm e,m} = \frac{1}{\pi_{\rm MS}},
-\label{Ne}
-\end{equation}
-where $\pi_{\rm MS}$ denotes the probability that two offspring share an MS relationship with an arbitrary mother.
-This definition is related to the inbreeding effective population size \cite[]{nordborg2002separation,wang2009new}.
-When sampling from a single cohort in a population with overlapping generations, the effective mother size in our definition corresponds to the effective breeding mother size per breeding-time unit (e.g., year), which produces the single cohort and is denoted by $N_{\rm b,m}$ \cite[]{waples1991genetic}.
-Hereafter, the description of the model focuses on species with discrete generations; thus, we use $N_{\rm e,m}$ to denote the contemporary effective mother size, although $N_{\rm b,m}$ is the appropriate notation in the left-hand side of Eq.~\ref{Ne} when the target species is iteroparous with overlapping generations, as exemplified in {\bf Appendix B}.
-
-Given the total mother number and the degree of overdisepered reproduction in the population, \cite{Akita_2019} derived $\pi_{\rm MS}$, which is approximately given by
-\begin{equation}
-\pi_{\rm MS} \approx \frac{c}{N_{\rm m}+c-1},
-\label{pi_MS}
-\end{equation}
-where $c$ indicates combined effect of both parental and nonparental variations and satisfies $\ge1$.
-Without either parental or nonparental variation (i.e., $c\to1$, see details in {\bf Appendix C}), $\pi_{\rm MS}$ converges to $1/N_{\rm m}$, corresponding to the Poisson variance in reproduction for all mothers.
-The mathematical description of $c$ is briefly summarized in {\bf Appendix C}.
-
-Next, we consider the relationship between the number of MO pairs and $N_{\rm m}$.
-It is natural to consider that the probability of a randomly sampled mother and her offspring sharing an MO relationship (denoted by $\pi_{\rm MO}$) can be associated with the total mother number, given by
-\begin{equation}
-\pi_{\rm MO} = \frac{1}{N_{\rm m}}.
-\label{pi_MO}
-\end{equation} 
-It is noteworthy that $\pi_{\rm MO}$ is independent of the distribution of the offspring number \cite[]{Akita2018}.
-
-Together with Eqs.~\ref{Ne} and \ref{pi_MO}, we finally obtain the ratio of the effective mother size to census size as follows: 
-\begin{equation}
-\frac{N_{\rm e,m}}{N_{\rm m}} = \frac{\pi_{\rm MO}}{\pi_{\rm MS}},
-\label{NeN}
-\end{equation}
-indicating that $N_{\rm e,m}/N_{\rm m}$ is associated with kinship relationships (i.e., MS and MO) in a population.
-In other words, when $1/\pi_{\rm MS}$ and $\pi_{\rm MO}$ is estimated from observed MS and MO pairs, respectively, the ratio can also be estimated.
-Meanwhile, \cite{Akita_2019} obtained an alternative formulation of the ratio using Eqs.~\ref{Ne} and \ref{pi_MS}:
-\begin{eqnarray}
-\frac{N_{\rm e,m}}{N_{\rm m}} &=& \frac{1}{\pi_{\rm MS}} \frac{1}{N_{\rm m}} \nonumber\\
-&\approx& \frac{1}{c},  
-\label{NeN}
-\end{eqnarray}
-where $N_{\rm m} \gg 1$ is assumed for approximation. This theoretical connection indicates that estimating $N_{\rm e,m}/N_{\rm m}$ corresponds to estimating $1/c$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Estimator of $N_{\rm e,m}/N_{\rm m}$}
-
-This subsection proposes the estimator of $N_{\rm e,m}/N_{\rm m}$  as follows:
-\begin{equation}
-\widehat{\left(\frac{N_{\rm e,m}}{N_{\rm m}}\right) } = \widehat{N_{\rm e,m}}\widehat{\left(\frac{1}{N_{\rm m}}\right)}.
-\label{NeN_hat1}
-\end{equation}
-A ``hat'' denotes the estimator of a variable in this study.
-The requisite condition that satisfies Eq.~\ref{NeN_hat1} is independent of $\widehat{N_{\rm e,m}}$ and $\widehat{1/N_{\rm m}}$.
-This property will be shown later in this subsection.
-\cite{Akita_2019} derived the nearly unbiased estimator of $N_{\rm e,m}$, which is given by
-\begin{eqnarray}
-\widehat{N_{\rm e,m}} &=& \widehat{\left(\frac{1}{\pi_{\rm MS}}\right)}\nonumber\\
- &=& \frac{\binom{n_{\rm O}}{2}+1}{H_{\rm MS}^{\rm obs}+1},
-\label{Ne_hat}
-\end{eqnarray}
-where $H_{\rm MS}^{\rm obs}$ denotes the observed number of MS pairs in a sample.
-This estimator works well unless $n_{\rm O}$ is very small, which is based on the idea that the observation of $1/(H_{\rm MS} + 1)$ approximately provides a linear estimator of $N_{\rm e,m}$.
-
-Next, we consider to estimate $1/N_{\rm m}$ by estimating $\pi_{\rm MO}$.
-By definition of $\pi_{\rm MO}$, we can set its estimator by $H_{\rm MO}^{\rm obs}/(n_{\rm M}n_{\rm O})$, where $H_{\rm MO}^{\rm obs}$ denotes the observed number of MO pairs in a sample.
-Thus, using Eq.~\ref{pi_MO}, the estimator can be determined as follows:
-\begin{eqnarray}
-\widehat{\left(\frac{1}{N_{\rm m}}\right)} &=& \widehat{\pi_{\rm MS}}\nonumber\\
- &=& \frac{H_{\rm MO}^{\rm obs} } {n_{\rm M}n_{\rm O}}.
-\label{N_inv_hat}
-\end{eqnarray}
-Equation~\ref{N_inv_hat} provides a linear estimator of $1/N_{\rm m}$, thus this estimator also works well.
-Meanwhile, the inverse of the right-hand side in Eq.~\ref{N_inv_hat} is a standard (moment) estimator of $N_{\rm m}$ in the context of CKMR \cite[]{bravington2016close}.
-
-Finally, substituting $\widehat{N_{\rm e,m}}$ (Eq.~\ref{Ne_hat}) and $\widehat{1/N_{\rm m}}$ (Eq.~\ref{N_inv_hat}) into Eq.~\ref{NeN_hat1}, we obtain the estimator of $N_{\rm e,m}/N_{\rm m}$ as follows:
-\begin{equation}
-\widehat{\left(\frac{N_{\rm e,m}}{N_{\rm m}}\right) } = \frac{\binom{n_{\rm O}}{2}+1}{H_{\rm MS}^{\rm obs}+1} \frac{H_{\rm MO}^{\rm obs} } {n_{\rm M}n_{\rm O}}.
-\label{NeN_hat2}
-\end{equation}
-Let both $n_{\rm M}$ and $n_{\rm O}$ be given.
-We numerically confirmed that there is no correlation between $H_{\rm MO}^{\rm obs}$ and $H_{\rm MS}^{\rm obs}$ (results are not shown).
-To intuitively explain this independency, we consider three mothers ($i=1, 2, 3$) and their offspring, and assume that $(k_1, k_2, k_3)=(3, 1, 1)$ and $(n_{\rm M}, n_{\rm O})=(1,3)$.
-When the three offspring born to the first mother are sampled (i.e., $H_{\rm MS}^{\rm obs}=3$), the expected number of MO relationship is one ($=1/3\times3 + 1/3\times0 + 1/3\times0$).
-Meanwhile, when an offspring is sampled from each mother's offspring (i.e., $H_{\rm MS}^{\rm obs}=0$), the expected number of MO relationship is also one ($=1/3\times1 + 1/3\times1 + 1/3\times1$).
-Therefore, we conclude that both $\widehat{N_{\rm e,m}}$ and $\widehat{1/N_{\rm m}}$ are independent, and $\widehat{N_{\rm e,m}/N_{\rm m}}$ is expected to work well (see details in the {\bf RESULTS} section).
-
-The bias of $\widehat{N_{\rm e,m}/N_{\rm m} }$ is defined by $b$, which is approximately given by (see {\bf Appendix D} for the derivation)
-\begin{eqnarray}
-b &=& \mathbb{E}\left[ \widehat{\left(\frac{N_{\rm e,m}}{N_{\rm m}}\right) } \right] - \left(\frac{N_{\rm e,m}}{N_{\rm m}}\right)\nonumber\\
-&\approx& -\left(\frac{N_{\rm e,m}}{N_{\rm m}}\right) \left(1-\frac{1}{N_{\rm e,m}}\right)^{\binom{n_{\rm O}}{2}+1}.
-\label{bias}
-\end{eqnarray}
-It is noteworthy that $\widehat{N_{\rm e,m}/N_{\rm m}}$ is downwardly biased, especially when $n_{\rm O}$ is very small.
-However, this bias may be ignored for a wide range of parameters (see details in the {\bf RESULTS} section).
-Theoretically, $b$ asymptotically converges to zero as $n_{\rm O}$ increases, making $\widehat{N_{\rm e,m}/N_{\rm m}}$ a nearly unbiased estimator.
-Moreover, as demonstrated in the {\bf RESULTS} section, it is observed that an extremely skewed reproduction breaks down the unbiasedness (e.g., in the case that $c=$ 20 and 100 in the results).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Individual-based model}
-
-We developed an individual-based model that tracks kinship relationships to evaluate the estimator's performance (e.g., $\widehat{N_{\rm e,m}/N_{\rm m}}$).
-The population structure was assumed to be identical to that in the development of the estimators.
-In addition, the population comprised mothers and their offspring, and it was assumed to follow a Poisson or negative binomial reproduction (the degree of skewness due to the nonparental variation is controlled by a parameter $\phi$; see {\bf Appendix B} for detalis).
-The expected number of the surviving offspring of a mother (denoted by $\lambda$) followed the density distribution $f(\lambda)$ (which is involved to the parental variation; see {\bf Appendix B} for details).
-We calculated overdispersion parameter ($c$) from $\phi$ and $f(\lambda)$, as well as confirmed numerically that the value of $c$ gives the same statistics of the estimators even if the combination of $\phi$ and $f(\lambda)$ differs (results are not shown).
-Therefore, each offspring retained the mother's ID, making it possible to trace an MS and MO relationship.
-
-Let a parameter set ($n_{\rm O}$, $n_{\rm M}$, $N_{\rm m}$, $\phi$, and parameters that determine $f(\lambda)$) be given.
-We simulated a population history in which $N_{\rm m}$ mothers generated offspring; this process was repeated 100 times.
-The sampling process for each history was repeated 10{,}000 times, acquiring 1{,}000{,}000 data points that were utilized to construct the distribution of the estimators for each parameter set.
-Furthermore, true value of $N_{\rm e,m}$ was calculated from $N_{\rm m}$ and $c$ (Eqs.~\ref{Ne} and \ref{pi_MS}).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{RESULTS}
-
-We numerically evaluated the performance of $\widehat{N_{\rm e,m}/N_{\rm m}}$ for the case in which the number of mothers, $N_{\rm m}$, and the combined effect of deviation from the Poisson, $c$, were unknown.
-We changed the parameter values for $N_{\rm m}$ ($10^3$ and $10^4$) and $c$ (1, 10, 20, and 100).
-In addition, based on a given parameter set ($N_{\rm m}$ and $c$), we mainly addressed the number of samples ($n_{\rm M}$ and $n_{\rm O}$) required to obtain adequate accuracy and precision.
-In this study, we evaluated the performance of $\widehat{N_{\rm e,m}/N_{\rm m}}$ for specific ranges of the sample sizes (50-200 when $N_{\rm m}=10^3$, and 200-1000 when $N_{\rm m}=10^4$).
-Meanwhile, other estimators (i.e., $\widehat{N_{\rm e,m}}$ and $\widehat{1/N_{\rm m}}$) are also evaluated and provided in {\bf Supporting Information}.
-
-First, we evaluated the accuracy of estimators based on their relative bias calculated by applying the individual-based model, which is defined as follows: ``averaged estimator $-$ true value/true value.'' For a given combination of $N_{\rm m}$ and $c$, the value of the relative bias of $\widehat{N_{\rm e,m}/N_{\rm m}}$ is represented on a violin plot for limiting cases where the sample number of mothers and offspring is same (i.e., $n_{\rm M} = n_{\rm O}$), as depicted in {\bf Fig.~\ref{violin}}.
-Meanwhile, detailed results of the relative bias are represented on a heatmap as a function of $n_{\rm M}$ and $n_{\rm O}$ (see {\bf Fig.~\NeNbias{}} in {\bf Supporting Information}).
-For most of the investigated parameter sets, we observed that their relative bias is less than 10\%.
-As expected, the relative bias is not affected by $n_{\rm M}$ since $\widehat{1/N_{\rm m}}$ is exactly an unbiased estimator of $1/N_{\rm m}$ (see Eq.~\ref{Ninv_bias_app} in {\bf Appendix D} and also {\bf Fig.~\Ninvbias{}} in {\bf Supporting Information}).
-Meanwhile, $\widehat{N_{\rm e,m}}$ is downwardly biased when $n_{\rm O}$ is relatively small to true $N_{\rm e,m}$ (e.g., see {\bf Fig.~\Nebias{}} for $c=1$ in {\bf Supporting Information}), as presented in \cite{Akita_2019}; thus, $\widehat{N_{\rm e,m}/N_{\rm m}}$ is downwardly biased.
-Contrary to the theoretical prediction for the direction of the bias (Eq.~\ref{bias}), relatively strong overdispersion results in an upwardly bias for $\widehat{N_{\rm e,m}/N_{\rm m}}$ when $N_m$ is relatively small and $c$ is relatively large (e.g., $c=20$ and $100$ in {\bf Fig.~\ref{violin}a}).
-This inconsistency may be caused by the breakdown of the approximation for deriving $\widehat{N_{\rm e,m}}$ \cite[Eq.~S14 in][]{Akita_2019}.
-Thus, as described in Eq.~\ref{V_k2}, extremely large $c$ results in a large variance of offspring number, generating a situation in which the behavior of random variable $H_{\rm MS}$ far deviates from the binomial distribution.
-
-Next, we evaluated the precision of estimators based on their coefficient of variation.
-As demonstrated in {\bf Fig.~\NeNcv{}} in {\bf Supporting Information}, the value of the coefficient of variation of $\widehat{N_{\rm e,m}/N_{\rm m}}$ is also represented on a heatmap as a function of $n_{\rm M}$ and $n_{\rm O}$; meanwhile, the violin plot ({\bf Fig.~\ref{violin}}) visually provides the degree of precision.
-For the investigated parameter sets, the degree of the coefficient of variation strongly depends on the sample sizes.
-As shown in {\bf Figs.~\Necv{} and \Ninvcv{}} in {\bf Supporting Information}, the dependency results from the combined effects of variation of both $\widehat{1/N_{\rm m}}$ and $\widehat{N_{\rm e,m}}$.
-As $c$ increases, it is noteworthy that the parameter space of sample sizes demonstrating large variation of $\widehat{1/N_{\rm m}}$ (e.g., $CV>30\%$) expands; however, when $c$ is small (e.g., $c=1$), relatively small $n_{\rm O}$ results in large variation of $\widehat{N_{\rm e,m}}$ because of a relatively large $N_{\rm e,m}$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{DISCUSSION}
-
-We theoretically developed a nearly unbiased estimator of the ratio of contemporary effective mother size to the census size ($N_{\rm e,m}/N_{\rm m}$) in a population (Eq.~\ref{NeN_hat2}).
-The proposed estimator is based on known MO relationship and MS relationships observed within the same cohort, in which sampled individuals in the cohort probably share MO relationships with sampled mothers ({\bf Fig~\ref{example}}).
-The performance of the estimator (accuracy and precision) was quantitatively evaluated by running an individual-based model ({\bf Fig.~\ref{violin}}; see also {\bf Figs.~\NeNbias{}--~\Ninvcv{}}).
-Meanwhile, the bias is analytically provided (Eq.~\ref{bias}).
-Our modeling framework utilizes two types of reproductive variations \cite[]{Akita_2019}: variance of the average offspring number per mother (parental variation, denoted by $f(\lambda)$), and variance of the offspring number across mothers with the same reproductive potential (nonparental variation, denoted by $\phi$).
-Additionally, these two effects result in a skewed distribution of offspring number and are summarized into one parameter ($c$) in the framework.
-Thus, our estimator can be calculated from sample sizes of mother and offspring ($n_{\rm M}$ and $n_{\rm O}$, respectively) and the observed numbers of MS and MO pairs ($H_{\rm MS}^{\rm obs}$ and $H_{\rm MO}^{\rm obs}$, respectively), and it does not require other parameters.
-The rationale for this is the following: i) the frequency of MS and MO pairs contains information about $N_{\rm e,m}$ and $N_{\rm m}$, respectively; ii) the estimators of $N_{\rm e,m}$ and $1/N_{\rm m}$ are independently determined based on a pedigree structure in the population and sample sizes, generating the estimator of $N_{\rm e,m}/N_{\rm m}$ by multiplying both estimators ($\widehat{N_{\rm e,m}}$ and $\widehat{1/N_{\rm m}}$).
-In this study, although $\widehat{N_{\rm e,m}/N_{\rm m}}$ is considered as a proxy of $\widehat{N_{\rm e}/N}$, our theoretical results can easily be extended to the estimator of the ratio of contemporary effective father size to the census size if fathers are also sampled.
-The comparison of both ratios could clarify the underlying processes that differentiate between the sexes in the context of reproductive ecology.
-
-The novelty of this study is that $\widehat{N_{\rm e,m}/N_{\rm m}}$ can be obtained only from the genetic data, and there are numerous advantages in using the proposed estimator instead of separately estimating $N_{\rm e}$ (via genetical method) and $N$ (via non-genetical method).
-First, sampling and analyzing designs have become substantially simplified.
-Requirements for the proposed estimator are sampling of mothers and (potentially) their offspring in an appropriate time, and the extraction of their DNA that satisfies an adequate number of markers for kinship detection.
-In addition, both MO and MS pairs can be detected by a applying unified framework of genetic analyzes (there are many algorithms to detect kinship pairs from single nucleotide polymorphisms (SNPs) or short tandem repeats (STRs)), although an MS pair involves many more DNA markers (e.g., several thousands of SNPs are required for detection) than an MO pair (e.g., several hundreds of SNPs are required for detection).
-Second, our theoretical results guide sample sizes ($n_{\rm M}$ and $n_{\rm O}$) to ensure the required accuracy and precision, especially if the order of the number of effective mothers is approximately known.
-This is due to the simple formulation of the estimator determined only by the observed values (Eq.~\ref{NeN_hat2}).
-Third, the proposed estimator directly reflects the amounts of $N_{\rm e,m}$ and $N_{\rm m}$ at the same timing (i.e., immediately after the end of the reproductive season), leading to a clear interpretation of the results, especially for genetic monitoring.
-For example, when the strong cohort is added to the spawning population in the beginning of the year, the estimator of $N_{\rm e}$ without reflecting this addition may results in an inappropriate estimation of $N_{\rm e}/N$ \cite[details of the temporal scale relevant to estimated $N_{\rm e}$ for each method were discussed in][]{Wang:2016aa}.
-
-Our modeling framework is presented by combining the context of the sibship assignment method (for estimating $N_{\rm e,m}$) and the CKMR method (for estimating $1/N_{\rm m}$), which defines a kinship-oriented estimation of effective/census population size.
-Improvements to these methods directly contribute to the estimation of $N_{\rm e,m}/N_{\rm m}$.
-Furthermore, the original theory of the sibship assignment method requires HS and FS pairs but does not require a distinction between the MS and PS pairs \cite[]{wang2009new}.
-This is a significant advantage due to the difficulty of the distinction from genetic data.
-However, the limitation of using MS or PS pair enables us to employ a nearly unbiased estimator of $N_{\rm e}$ for particular sex \cite[]{Akita_2019}, which greatly improves the accuracy of the estimation of the $N_{\rm e,m}$ in this study and thus that of $N_{\rm e,m}/N_{\rm m}$ (see {\bf Fig.~E\ref{violin_wang}} in {\bf Appendix E}).
-It is noteworthy that the estimator of $1/N$ is given by
-\begin{equation}
-\widehat{\left(\frac{1}{N}\right)} = \frac{H_{\rm PO}^{\rm obs} } {2n_{\rm P}n_{\rm O}},
-\label{N_inv_hat2}
-\end{equation}
-where $n_{\rm P}$ and $H_{\rm PO}^{\rm obs}$ denotes the sample size of the parent and the observed number of parent--offspring (PO) pairs in a sample, respectively \cite[]{bravington2016close}.
-The development of the unbiased estimator of $N_{\rm e}$ without a distinction between MS and PS pairs that could provide an unbiased estimator of $N_{\rm e}/N$ coupled with Eq.~\ref{N_inv_hat2}, is a study for the future.
-Furthermore, using cross-cohort HS pairs, the CKMR method also provides the estimator of $N$ \cite[]{bravington2016close} that does not require the sampling of the parent, which probably provides the estimator of $N_{\rm e}/N$ only from unmatured samples.
-This perspective of the study will also be conducted in the future.
-
-Finally, we note the advantage of partitioning variance in reproductive success into two components.
-As denoted in Eq.~\ref{c} in {\bf Appendix C}, the combined effect of parental and nonparental variations is given by
-\begin{equation}
-c = ({\rm effect\ of\ nonparental\ variation}) \times ({\rm effect\ of\ parental\ variation}).
-\label{partition}
-\end{equation}
-Meanwhile, as denoted in Eq.~\ref{NeN}, the estimator of $N_{\rm e,m}/N_{\rm m}$ provides the information for the lefthand-side of Eq.~\ref{partition}.
-Thus, when we obtain parental variation information from the life-history table or from other species, the estimator of $N_{\rm e,m}/N_{\rm m}$ can also estimate the degree of nonparental variation.
-This procedure provides an insight into sweepstake reproduction or family-correlated sampling of offspring (i.e., nonrandom sampling), although the theoretical formulation and its evaluation remain a task for future research.
-Alternatively, Waples et al.
-(2018) developed a genetical method for estimating $N_{\rm e}/N$ and $N_{\rm b}/N$ via estimating the degree of nonparental variation from fecundity data in southern bluefin tuna.
-
-\end{comment}
 
@@
 Migration rate $m$ is specified by $N_1/M$.
-For the demonstration purposes, the distribution is truncated, although the mean values are calculated including the truncated values.
+For the demonstration purposes, the upper side of the distribution is truncated, although the mean values are calculated including the truncated values.
 }
-
-\newcommand{\figcapsg}{Violin plots showing the distribution of relative bias of $N_{\rm e}/N$ (denoted in Eq.~\ref{NeN_wang}) for various sample sizes.
-Filled circles represent the mean values.
-The sample numbers of parents and offspring are identical (i.e., $n=n_{\rm P} = n_{\rm O}$) and indicated in the legend.
-For demonstration purposes, the distribution is truncated, although the mean values are calculated including the truncated values.
-(a) $N=2{,}000$, (b) $N=20{,}000$.}
 

### 2021-12-22 latex/ms.tex
add 4th para in Results section, #13

@@
 
-\RED{kokomade!!!!!!!!!!!!!!!!!!!!}
-
 \section{Results}\label{sec3}
 
-We numerically evaluated the performance of ${\hat M}$ or ${\hat m}$ for the case in which variable reproductive potential among parents.
+We numerically evaluated the performance of ${\hat M}$s or ${\hat m}$s for the case in which variable reproductive potential among parents.
 Scaled statistical properties of ${\hat m_1}$,  ${\hat m_2}$,  ${\hat m_3}$ and ${\hat m_4}$ are completely the same to ${\hat M_1}$, ${\hat M_2}$, ${\hat M_3}$ and ${\hat M_4}$, hereafter, we only demonstrate the results of ${\hat M_1}$-${\hat M_5}$.
@@
 As sample size or migrants increase, the precision increases and the shape of the distribution asymptotically becomes symmetric ({\bf Figure~\ref{violins}}).
-This is because increasing of a sample size or migrants increases of the probability that randomly selected two individuals share kinship between the two populations and thus decreases the CV.
+This is because an increasing of sample size or migrants is likely to increase the observed number of kinship pairs found between two populations ($\widetilde{H}_{\rm HS,bet}$ or $\widetilde{H}_{\rm PO,bet}$) and decreases the variance of those kinship pair numbers.
+In addition, the number of PO pair within a population ($\widetilde{H}_{\rm PO,1}$ or $\widetilde{H}_{\rm PO,2}$) also contributes the precision for estimating $N_1$ or $N_1$, respectively, providing ${\hat M_4}$ and ${\hat M_5}$ with a higher precision.
+
+Our simulator can handle the situation with or without invasive sampling.
+Invasive sampling potentially affect the $m$ since sampled parents in the population 1 have no chance to move to the population 2 and thus those parents cannot be sampled.
+In this case, $m$ should be defined by $M/(N_1-n_{P,1})$ not by $M/N_1$, although it does not affect the estimator ${\hat M}$s, as demonstrated in {\bf Table S1} ({\bf Supporting Information}).
+
+\RED{kokomade!!!!!!!!!!!!!!!!!!!!}
+\subsection{Invasive sampling}
 
 \subsection{Case of $N_1 \neq N_2$}
-
-\subsection{Invasive sampling}
 

### 2021-12-23 latex/ms.tex
finish Results section, #13

@@
 Our simulator can handle the situation with or without invasive sampling.
-Invasive sampling potentially affect the $m$ since sampled parents in the population 1 have no chance to move to the population 2 and thus those parents cannot be sampled.
+Invasive sampling potentially affects the degree of $m$ since sampled parents in the population 1 have no chance to move to the population 2 and thus those parents cannot be sampled.
 In this case, $m$ should be defined by $M/(N_1-n_{P,1})$ not by $M/N_1$, although it does not affect the estimator ${\hat M}$s, as demonstrated in {\bf Table S1} ({\bf Supporting Information}).
 
+Finally, we investigated the situation in which the parental number in the population 1 is much more than in the population 2 (i.e., $N_1 \gg N_2$) and thus migrants are large proportion of $N_2$.
+In such a setting, e.g., $(N_1,N_2,M)=(10^4,10^3,500)$, we confirmed the same property of ${\hat M}$s to the situation $N_1 = N_2$, as demonstrated in {\bf Table S1} ({\bf Supporting Information}), suggesting the robustness of ${\hat M}$s in heterogeneous population sizes.
+
 \RED{kokomade!!!!!!!!!!!!!!!!!!!!}
-\subsection{Invasive sampling}
-
-\subsection{Case of $N_1 \neq N_2$}
 

### 2021-12-24 latex/ms.tex
add 2para in Discussion section, #14

@@
 
+\section{Discussion}\label{sec4}
+
+We theoretically developed unbiased estimators of the contemporary migration number (${\hat M_1}$--${\hat M_5}$) and migration rate (${\hat m_1}$--${\hat m_4}$) between two populations in iteroparous species.
+The proposed estimators are based on known PO relationship and HS relationships observed between and within two populations without any error of kinship assignment.
+Users can choose the estimator developed for the situation as to whether the parental number of population 1 ($N_1$) and/or that of population 2 ($N_2$) is known ({\bf Table~\ref{parameter}}).
+The performance of the estimator (accuracy and precision) was quantitatively evaluated by running an individual-based model ({\bf Figure~\ref{violins}}; see also {\bf Table S1} in {\bf Supporting Information}).
+Our modeling framework utilizes several types of reproductive variations (survived offspring number per parent), including variance of reproductive potential between and within populations, taking account of several situations, including a body-size structure or environmental heterogeneity for reproductive success.
+
+To estimate the contemporary migration number or migration rate, our simulation-based results provide guidance for a sample size to ensure the required accuracy and precision, especially if the order of the number of migrant parents and parental sizes are approximately known ({\bf Table S1} in {\bf Supporting Information}).
+Even if there is no information about these numbers, $1/\sqrt{H_{\rm HS, bet}}$ (or $1/\sqrt{H_{\rm PO, bet}}$) provides an approximate lower bound on the CV, which can be used as an indicator of the precision of ${\hat M}$ or ${\hat m}$.
+Furthermore, the condition that $n>\sqrt{N_2}$ is also used as rule of thumb especially when planning a research project (see also Equations~\ref{RS-1} and \ref{RS-2}).
+
+%Novelty: reproductive potential does not affect for estimating migration number
+
+%Scope of applications
+%Case of small migration rate
+%Contemporary / historical migration rate
+
 \RED{kokomade!!!!!!!!!!!!!!!!!!!!}
-
-\section{Discussion}\label{sec4}
 

### 2022-01-11 latex/ms.tex
add novelty, #14

@@
 
+There are several novelties of this study.
+First, we formulated probabilities of kinship pairs randomly chosen between two populations, which provide estimators of the migration number or rate.
+While similar derivations are found in the context of a mark-recapture method (REF), these are limited to the situation such that sampling can be non-invasive and adult individuals are sampled.
+Our proposed method can avoid such limitations, where such advantages are generally characterized in CKMR method.
+Second, we reveal that the probabilities and then the estimators are approximately independent of reproductive potential if migration event and the potential are independent.
+It is useful property of the estimators because heterogeneity of reproductive potential within/between populations are well-known in iteroprous species.
+Third, we demonstrate applicability that the estimation can be obtained only from the genetic data.
+
 To estimate the contemporary migration number or migration rate, our simulation-based results provide guidance for a sample size to ensure the required accuracy and precision, especially if the order of the number of migrant parents and parental sizes are approximately known ({\bf Table S1} in {\bf Supporting Information}).
@@
 
-%Novelty: reproductive potential does not affect for estimating migration number
+%Novelty: reproductive potential does not affect for estimating migration number, asymmetric migration,
 
 %Scope of applications
+%Caveat: selectivity, family correlated migration
 %Case of small migration rate

### 2022-01-11 latex/ms.tex
modify novelty, #14

--- 2021-12-24 latex/ms.tex
@@
 
+We presented mainly three novel points in this paper.
+First, we formulated probabilities of kinship pairs randomly chosen between two populations ($\pi_{\rm HS,bet}$ and $\pi_{\rm PO,bet}$), which provide estimators of the migration number or rate.
+While similar derivations are found in the context of a mark-recapture method (REF), these are limited to the situation such that sampling can be non-invasive and adult individuals are sampled.
+Our proposed method can avoid these limitations, where such advantages are generally characterized in CKMR method.
+Second, we revealed that the probabilities of kinship pairs are approximately independent of reproductive potential and thus information about it is not needed for the estimation, if migration event and the potential are independent.
+This is a useful property of the estimators because heterogeneity of reproductive potential within/between populations are generally observed in iteroprous species.
+Third, we demonstrate applicability that the estimation can be obtained only from the genetic data, and there are numerous advantages in using the proposed estimator instead of separately estimating $\pi_{\rm HS,bet}$ (and/or $\pi_{\rm PO,bet}$) (via genetic method) and $N_1$ (and/or $N_2$) (via nongenetical method).
+
+\RED{kokomade!!!!!!!!!!!!!!!!!!!!}
+
 To estimate the contemporary migration number or migration rate, our simulation-based results provide guidance for a sample size to ensure the required accuracy and precision, especially if the order of the number of migrant parents and parental sizes are approximately known ({\bf Table S1} in {\bf Supporting Information}).
@@
 
-%Novelty: reproductive potential does not affect for estimating migration number
+%Novelty: reproductive potential does not affect for estimating migration number, asymmetric migration,
 
 %Scope of applications
+%Caveat: selectivity, family correlated migration
 %Case of small migration rate
 %Contemporary / historical migration rate
-
-\RED{kokomade!!!!!!!!!!!!!!!!!!!!}
 

### 2022-01-12 latex/ms.tex
add scope, #14

@@
 
-\title{Estimating migration rates for iteroparous species using kinship pairs found between populations}
+\title{Estimating contemporary migration rates for iteroparous species using kinship pairs found between populations}
 \author{
@@
 
-We theoretically developed unbiased estimators of the contemporary migration number (${\hat M_1}$--${\hat M_5}$) and migration rate (${\hat m_1}$--${\hat m_4}$) between two populations in iteroparous species.
+We theoretically developed unbiased estimators of the contemporary migration number (${\hat M_1}$--${\hat M_5}$) and migration rate (${\hat m_1}$--${\hat m_4}$) of parents between two populations in iteroparous species, where the migration direction is specified.
 The proposed estimators are based on known PO relationship and HS relationships observed between and within two populations without any error of kinship assignment.
@@
 While similar derivations are found in the context of a mark-recapture method (REF), these are limited to the situation such that sampling can be non-invasive and adult individuals are sampled.
-Our proposed method can avoid these limitations, where such advantages are generally characterized in CKMR method.
+Our proposed method can avoid these limitations, where such an advantages is characterized by CKMR method.
 Second, we revealed that the probabilities of kinship pairs are approximately independent of reproductive potential and thus information about it is not needed for the estimation, if migration event and the potential are independent.
 This is a useful property of the estimators because heterogeneity of reproductive potential within/between populations are generally observed in iteroprous species.
-Third, we demonstrate applicability that the estimation can be obtained only from the genetic data, and there are numerous advantages in using the proposed estimator instead of separately estimating $\pi_{\rm HS,bet}$ (and/or $\pi_{\rm PO,bet}$) (via genetic method) and $N_1$ (and/or $N_2$) (via nongenetical method).
-
-\RED{kokomade!!!!!!!!!!!!!!!!!!!!}
+Third, we demonstrated applicability that the estimation can be obtained only from the genetic data (i.e., ${\hat M_5}$ and ${\hat m_4}$).
+There are several advantages in using the proposed estimator instead of separately estimating $\pi_{\rm HS,bet}$ (and/or $\pi_{\rm PO,bet}$) (via genetic method) and $N_1$ (and/or $N_2$) (via nongenetical method), including simplified sampling and analyzing designs and availability of unified framework of genetic analyzes for detecting PO and HS pairs (similar discussion is found for estimating effective breeding size per census size, $N_{\rm b}/N$, in \cite{Akita_2020}).
 
@@
 
-%Novelty: reproductive potential does not affect for estimating migration number, asymmetric migration,
+There may be several cases where it is desirable to apply the proposed estimator.
+The first case is where there is a certain number of migrants between populations, e.g., $M>100$, which is too large to be detected by population genetics method if $M$ is interpreted as effective migration number.
+Information on movement between populations is essential for assessing population dynamics in the context of conservation and management, even if migrant number is so large that it cannot be genetically assigned to two populations.
+The second is the case of the application to genetic monitoring conducted annually.
+This is because proposed estimators have information about contemporary migration, thus the time series data for migration reflect environmental changes, which provides insights into the underlying ecological processes.
+In addition, HS pairs found within the genetic population provides $N_{\rm b}$ \cite[]{wang2009new}, which is also used for assessing a genetic health.
+The third case is where sampling adults is difficult due to conservation purpose or other reasons instead sampling offspring is relatively easy.
+In this case, although $N_2$ (and $N_1$) need to be given externally for the usage of $\hat m_1$ (and $\hat M_1$), there is presently no other method for estimating adult movement especially when two populations cannot be genetically distinct, indicating that proposed method has the potential to greatly widen the scope of population monitoring.
 
-%Scope of applications
-%Caveat: selectivity, family correlated migration
-%Case of small migration rate
-%Contemporary / historical migration rate
+%必要条件としては、個体数管理のため、細かすぎる時空かんスケールはだめ。大雑把なpopulationを仮定したい時に限る（空間的に細かいグリッドは困難？）、集団構造がspecifyされた後に実施される。繁殖タイミングの間隔の移動を統合したもの、子供の移動については何も言ってない。
+
+\RED{kokomade!!!!!!!!!!!!!!!!!!!!}
+
+%Caveat: 近親判別エラー、selectivity, family correlated migration、
 

### 2022-01-14 latex/ms.tex
add caveats, #14

@@
 Information on movement between populations is essential for assessing population dynamics in the context of conservation and management, even if migrant number is so large that it cannot be genetically assigned to two populations.
-The second is the case of the application to genetic monitoring conducted annually.
+The second is the case of the application to genetic monitoring conducted every reproductive timing (e.g., annually).
 This is because proposed estimators have information about contemporary migration, thus the time series data for migration reflect environmental changes, which provides insights into the underlying ecological processes.
@@
 
+Finally, we note several caveats in applying proposed method.
+Our theory for developing estimators assumes that kinships are detected without any error.
+There are many algorithms to detect kinship pairs from single nucleotide polymorphisms (SNPs) or short tandem repeats (STRs) (REF), although a HS pair requires many more DNA markers than a PO pair.
+In addition, iteroprous species potentially has several kinship types such as halfsib-uncle/nephew or halfsib-cousin, which are expected to appear frequently and should be correctly distinguished from HS pairs.
+It is desirable to estimate in advance how many markers are needed for kinship detections in target populations associated with simulation of a pedigree reconstruction including distant kinships (e.g., \cite{Anderson_2020}).
+
 %必要条件としては、個体数管理のため、細かすぎる時空かんスケールはだめ。大雑把なpopulationを仮定したい時に限る（空間的に細かいグリッドは困難？）、集団構造がspecifyされた後に実施される。繁殖タイミングの間隔の移動を統合したもの、子供の移動については何も言ってない。
@@
 
-%Caveat: 近親判別エラー、selectivity, family correlated migration、
+%Caveat: selectivity, family correlated migration、skip spawning,
 

### 2022-01-18 latex/ms.tex
add note in Discussion, #14

@@
 First, we formulated probabilities of kinship pairs randomly chosen between two populations ($\pi_{\rm HS,bet}$ and $\pi_{\rm PO,bet}$), which provide estimators of the migration number or rate.
-While similar derivations are found in the context of a mark-recapture method (REF), these are limited to the situation such that sampling can be non-invasive and adult individuals are sampled.
+While similar derivations are found in the context of a mark-recapture method (\RED{REF}), these are limited to the situation such that sampling can be non-invasive and adult individuals are sampled.
 Our proposed method can avoid these limitations, where such an advantages is characterized by CKMR method.
@@
 
-Finally, we note several caveats in applying proposed method.
+Finally, we note some caveats in applying proposed method.
 Our theory for developing estimators assumes that kinships are detected without any error.
-There are many algorithms to detect kinship pairs from single nucleotide polymorphisms (SNPs) or short tandem repeats (STRs) (REF), although a HS pair requires many more DNA markers than a PO pair.
+There are many algorithms to detect kinship pairs from single nucleotide polymorphisms (SNPs) or short tandem repeats (STRs) (\RED{REF}), although a HS pair requires many more DNA markers than a PO pair.
 In addition, iteroprous species potentially has several kinship types such as halfsib-uncle/nephew or halfsib-cousin, which are expected to appear frequently and should be correctly distinguished from HS pairs.
 It is desirable to estimate in advance how many markers are needed for kinship detections in target populations associated with simulation of a pedigree reconstruction including distant kinships (e.g., \cite{Anderson_2020}).
+Our proposed estimators only detect the parental movements on a period between breeding seasons in given populations.
 
-%必要条件としては、個体数管理のため、細かすぎる時空かんスケールはだめ。大雑把なpopulationを仮定したい時に限る（空間的に細かいグリッドは困難？）、集団構造がspecifyされた後に実施される。繁殖タイミングの間隔の移動を統合したもの、子供の移動については何も言ってない。
+%必要条件としては、個体数管理のため、細かすぎる時空かんスケールはだめ。大雑把なpopulationを仮定したい時に限る（空間的に細かいグリッドは困難？）、集団構造がspecifyされた後に実施される。繁殖タイミングの間隔の移動を統合したもの、子供の移動については何も言ってない。繁殖タイミングの間の移動しか捕捉できない。
 

### 2022-01-19 latex/ms.tex
filled letters in Discussion, #14

@@
 To estimate the contemporary migration number or migration rate, our simulation-based results provide guidance for a sample size to ensure the required accuracy and precision, especially if the order of the number of migrant parents and parental sizes are approximately known ({\bf Table S1} in {\bf Supporting Information}).
-Even if there is no information about these numbers, $1/\sqrt{H_{\rm HS, bet}}$ (or $1/\sqrt{H_{\rm PO, bet}}$) provides an approximate lower bound on the CV, which can be used as an indicator of the precision of ${\hat M}$ or ${\hat m}$.
+\RED{For example, ...} Even if there is no information about these numbers, $1/\sqrt{H_{\rm HS, bet}}$ (or $1/\sqrt{H_{\rm PO, bet}}$) provides an approximate lower bound on the CV, which can be used as an indicator of the precision of ${\hat M}$ or ${\hat m}$.
 Furthermore, the condition that $n>\sqrt{N_2}$ is also used as rule of thumb especially when planning a research project (see also Equations~\ref{RS-1} and \ref{RS-2}).
@@
 It is desirable to estimate in advance how many markers are needed for kinship detections in target populations associated with simulation of a pedigree reconstruction including distant kinships (e.g., \cite{Anderson_2020}).
-Our proposed estimators only detect the parental movements on a period between breeding seasons in given populations.
+Our proposed estimators are limited to detect one-time parental movements on a period between breeding seasons in given populations.
+Thus, the estimation of fine-scale spatial-temporal movements, which is available to integrate multiple type of data \cite[]{Thorson_2021}, goes beyond the scope of this paper, although population dynamics models with a coarser spatial resolution than the spatial scale for environmental layers are often used in the assessment models, which is the target of application of the proposed method.
+In addition, our proposed estimators require the pre-specification of a population structure.
+Kinship relationships with information of a sample location potentially provide the chance to explore a plausible population structure via estimating migration number or rate between hypothetical populations, which contributes the determination of a management unit \cite[]{Hastings_1993, Waples_2006_MolEcol, PALSBOLL200711}.
+This perspective of the study will be conducted in the future.
 
-%必要条件としては、個体数管理のため、細かすぎる時空かんスケールはだめ。大雑把なpopulationを仮定したい時に限る（空間的に細かいグリッドは困難？）、集団構造がspecifyされた後に実施される。繁殖タイミングの間隔の移動を統合したもの、子供の移動については何も言ってない。繁殖タイミングの間の移動しか捕捉できない。
+%必要条件としては、個体数管理のため、細かすぎる時空かんスケールはだめ。大雑把なpopulationを仮定したい時に限る（空間的に細かいグリッドは困難？）、集団構造がspecifyされた後に実施される。繁殖タイミングの間隔の移動を統合したもの、子供の移動については何も言ってない。繁殖タイミングの間の移動しか捕捉できない。事前に集団について割り当てておく必要がある。サンプルデザインを考えて、サンプル場所と見つかる近親関係を対応させて、管理単位の決定に寄与するような集団構造の探索は可能だろう。ヘイステングの方法などあるが、近親情報に基づいて、集団の単位を発見する理論的枠組みは、今後の課題である
 
-\RED{kokomade!!!!!!!!!!!!!!!!!!!!}
+%conn & bravington も引用しないと
 

### 2022-01-19 latex/ms.tex
add refs

@@
 First, we formulated probabilities of kinship pairs randomly chosen between two populations ($\pi_{\rm HS,bet}$ and $\pi_{\rm PO,bet}$), which provide estimators of the migration number or rate.
-While similar derivations are found in the context of a mark-recapture method (\RED{REF}), these are limited to the situation such that sampling can be non-invasive and adult individuals are sampled.
+While similar derivations are found in (nongenetical) mark-recapture method (\RED{REF}), these are limited to the situation such that sampling can be non-invasive and adult individuals are sampled.
 Our proposed method can avoid these limitations, where such an advantages is characterized by CKMR method.
@@
 To estimate the contemporary migration number or migration rate, our simulation-based results provide guidance for a sample size to ensure the required accuracy and precision, especially if the order of the number of migrant parents and parental sizes are approximately known ({\bf Table S1} in {\bf Supporting Information}).
-\RED{For example, ...} Even if there is no information about these numbers, $1/\sqrt{H_{\rm HS, bet}}$ (or $1/\sqrt{H_{\rm PO, bet}}$) provides an approximate lower bound on the CV, which can be used as an indicator of the precision of ${\hat M}$ or ${\hat m}$.
+For example, when $m=0.1$ and $N_1=N_2=10^3$, sampling 10\% and 20\% parents and an equal number of offspring in two populations leads 70\% and 39\% CV of ${\hat M_5}$, respectively (case of invasive sampling).
+Even if there is no information about these numbers, $1/\sqrt{H_{\rm HS, bet}}$ (or $1/\sqrt{H_{\rm PO, bet}}$) provides an approximate lower bound on the CV, which can be used as an indicator of the precision of ${\hat M}$ or ${\hat m}$.
 Furthermore, the condition that $n>\sqrt{N_2}$ is also used as rule of thumb especially when planning a research project (see also Equations~\ref{RS-1} and \ref{RS-2}).
@@
 Our theory for developing estimators assumes that kinships are detected without any error.
-There are many algorithms to detect kinship pairs from single nucleotide polymorphisms (SNPs) or short tandem repeats (STRs) (\RED{REF}), although a HS pair requires many more DNA markers than a PO pair.
+There are many algorithms to detect kinship pairs from single nucleotide polymorphisms (SNPs) or short tandem repeats (STRs) \cite[e.g., ][]{Wang_2009Genetics, Huisman_2017}, although a HS pair requires many more DNA markers than a PO pair.
 In addition, iteroprous species potentially has several kinship types such as halfsib-uncle/nephew or halfsib-cousin, which are expected to appear frequently and should be correctly distinguished from HS pairs.
@@
 Thus, the estimation of fine-scale spatial-temporal movements, which is available to integrate multiple type of data \cite[]{Thorson_2021}, goes beyond the scope of this paper, although population dynamics models with a coarser spatial resolution than the spatial scale for environmental layers are often used in the assessment models, which is the target of application of the proposed method.
-In addition, our proposed estimators require the pre-specification of a population structure.
+In addition, the current theory behind the estimators does not assume desynchronized reproduction within a population (e.g., skip spawning) and correlation between mobility and fertility.
+Our proposed estimators require the pre-specification of a population structure.
 Kinship relationships with information of a sample location potentially provide the chance to explore a plausible population structure via estimating migration number or rate between hypothetical populations, which contributes the determination of a management unit \cite[]{Hastings_1993, Waples_2006_MolEcol, PALSBOLL200711}.
@@
 
-%必要条件としては、個体数管理のため、細かすぎる時空かんスケールはだめ。大雑把なpopulationを仮定したい時に限る（空間的に細かいグリッドは困難？）、集団構造がspecifyされた後に実施される。繁殖タイミングの間隔の移動を統合したもの、子供の移動については何も言ってない。繁殖タイミングの間の移動しか捕捉できない。事前に集団について割り当てておく必要がある。サンプルデザインを考えて、サンプル場所と見つかる近親関係を対応させて、管理単位の決定に寄与するような集団構造の探索は可能だろう。ヘイステングの方法などあるが、近親情報に基づいて、集団の単位を発見する理論的枠組みは、今後の課題である
-
 %conn & bravington も引用しないと
+% MigEst by Wangとの比較も...
 

### 2022-01-24 latex/ms.tex
add somethings
change title
add memo in Intro

@@
 
-\title{Estimating contemporary migration rates for iteroparous species using kinship pairs found between populations}
+\title{Estimating contemporary migration rates of adults for iteroparous species using kinship pairs found between populations}
 \author{
@@
 
-Estimating the number of migrants among the populations is essential for understanding population structure and dynamics, which is a fundamental process for implementing conservation and wildlife management.
+%conn & bravington も引用しないと
+% MigEst by Wangとの比較も...もう一度よくWang 2014を読む！どうやって推定しているのか...
+%% 今回提案した方法は、ゴーストポップがあっても大丈夫
+%% MigEstは、親は動かず、子が移動することを想定している
+%% N = Neを想定
+
+%移動には２種類ある。子の移動と親の移動である。前者は花粉やラーバなど。connectivityは前者が大事かもで、どこまで遠く行くのかも重要。移動する生物の場合、後者も重要。
+
+Estimating the number of migrants among the populations is essential for understanding population structure and dynamics.
+
+, which is a fundamental process for implementing conservation and wildlife management.
 Especially in fisheries management, migration rate is a critical component for delineating a synchrony among the population, providing appropriate management units.
+
+% 近年の移動率の推定には大きく２種類に分類される。１つ目は遺伝マーカーに基づく集団遺伝学的な解析。２つ目は標識採捕の枠組みの解析。
+
 There are essentially two approaches for estimating the migrant number.
@@
 
-%conn & bravington も引用しないと
-% MigEst by Wangとの比較も...
-
+%PRE-DEFINED population !
 %Caveat: selectivity, family correlated migration、skip spawning,

### 2022-01-28 latex/ms.tex
rewrite 1st para in Intro, #15

@@
 
-%conn & bravington も引用しないと
+%conn & bravington , Trenkel & bravingtonも引用しないと
 % MigEst by Wangとの比較も...もう一度よくWang 2014を読む！どうやって推定しているのか...
@@
 %% N = Neを想定
-
 %移動には２種類ある。子の移動と親の移動である。前者は花粉やラーバなど。connectivityは前者が大事かもで、どこまで遠く行くのかも重要。移動する生物の場合、後者も重要。
 
-Estimating the number of migrants among the populations is essential for understanding population structure and dynamics.
+% 1: Estimating migration is important for both ecologically and evolutionally reasons
+
+In conservation and wildlife management, estimating the current ecological information is essential for monitoring population levels and for proposing management strategies.
+Contemporary migration rate, the recent rate of movement of individuals or gametes between populations, is a critical component to determine the current degree of synchrony among the population, which characterize the population structure and then provides information to identify appropriate management units \cite[]{Waples_2006_MolEcol, PALSBOLL200711}.
+In addition, \RED{KOKOMADE}
+
+, estimating a speed of habitat expansion,  the effective reserve network design, population restoration, and invasive species control.
+
+of organism number of migrants between populations is essential for understanding population structure in conservation and wildlife management. , and its history, which provides .
 
@@
 
-% 近年の移動率の推定には大きく２種類に分類される。１つ目は遺伝マーカーに基づく集団遺伝学的な解析。２つ目は標識採捕の枠組みの解析。
+% 2: Mark recapture method can handle ecological scale but may miss the small migration rate
+% 3: Population genetics method can handle evolutionally scale but may miss the large migration rate
+% 4: CKMR can cover the range that Mark recapture can handle with more realistic situations
+% 5: Wang 2014 can handle ecological scale with realistic situations but limited to offspring movement
+% 6: In this paper, ~
 

### 2022-01-31 latex/ms.tex
done 1st para in Intro, #15

--- 2022-01-24 latex/ms.tex
@@
 %% N = Neを想定
-
 %移動には２種類ある。子の移動と親の移動である。前者は花粉やラーバなど。connectivityは前者が大事かもで、どこまで遠く行くのかも重要。移動する生物の場合、後者も重要。
 
-Estimating the number of migrants among the populations is essential for understanding population structure and dynamics.
+%contemporary migration rateはほとんどBaysAssを使っている人の用語
 
-, which is a fundamental process for implementing conservation and wildlife management.
-Especially in fisheries management, migration rate is a critical component for delineating a synchrony among the population, providing appropriate management units.
+% 1: Estimating contemporary migration is important for both ecologically and evolutionally reasons
 
-% 近年の移動率の推定には大きく２種類に分類される。１つ目は遺伝マーカーに基づく集団遺伝学的な解析。２つ目は標識採捕の枠組みの解析。
+In conservation and wildlife management, estimating the current ecological information is essential for monitoring population levels and proposing management strategies.
+Contemporary migration rate, the recent rate of movement of individuals or gametes between pre-defined populations, is a critical component to determine the current degree of gene flow \cite[]{Crow:1970fk} and synchrony among the population \cite[]{Hastings_1993}.
+Therefore, estimation of contemporary migration rate provides information about the degree of genetic differentiation and demographic dependency, which can delineate evolutionarily significant units \cite[ESUs,][]{moritz1994defining} and identify appropriate management units \cite[]{Waples_2006_MolEcol, PALSBOLL200711}.
+In addition, the availability of migration rate can link to underlying population dynamics, allowing for a more precise and flexible evaluation of a management for many relevant topics including species range expansion/construction (REF), effective reserve network design (REF), and the invasive species control (REF).
+
+ \RED{KOKOMADE}
+
+% 2: Mark recapture method can handle ecological scale but may miss the small migration rate
+
+There are essentially two approaches for estimating the contemporary migration rate. The first is to use the mark-recapture (MR) method that directly estimates parameters of the population.
+
+% 3: Population genetics method can handle evolutionally scale but may miss the large migration rate
+% 4: CKMR can cover the range that Mark recapture can handle with more realistic situations
+% 5: Wang 2014 can handle ecological scale with realistic situations but limited to offspring movement
+% 6: In this paper, ~
 

### 2022-02-01 latex/ms.tex
2nd para in Intro, #15

@@
 
-\title{Estimating contemporary migration rates of adults for iteroparous species using kinship pairs found between populations}
+\title{Estimating contemporary migration numbers of adults for iteroparous species using kinship pairs found between populations}
 \author{
@@
 In conservation and wildlife management, estimating the current ecological information is essential for monitoring population levels and proposing management strategies.
-Contemporary migration rate, the recent rate of movement of individuals or gametes between pre-defined populations, is a critical component to determine the current degree of gene flow \cite[]{Crow:1970fk} and synchrony among the population \cite[]{Hastings_1993}.
-Therefore, estimation of contemporary migration rate provides information about the degree of genetic differentiation and demographic dependency, which can delineate evolutionarily significant units \cite[ESUs,][]{moritz1994defining} and identify appropriate management units \cite[]{Waples_2006_MolEcol, PALSBOLL200711}.
-In addition, the availability of migration rate can link to underlying population dynamics, allowing for a more precise and flexible evaluation of a management for many relevant topics including species range expansion/construction (REF), effective reserve network design (REF), and the invasive species control (REF).
-
- \RED{KOKOMADE}
+Contemporary migration rate, the recent rate of movement of individuals or gametes between pre-defined populations, is a critical component to determine the current degree of gene flow and synchrony among the population \cite[]{Waples_2006_MolEcol}.
+Therefore, estimation of contemporary migration rate provides information about the degree of genetic differentiation and demographic dependency, which can delineate evolutionarily significant units \cite[ESUs,][]{moritz1994defining} and identify appropriate management units \cite[]{PALSBOLL200711}.
+In addition, the availability of migration rate can link to underlying population dynamics, allowing for a more precise and flexible evaluation of a management for many relevant topics including stock assessment in fisheries \cite[]{methot2013stock}, species range expansion/construction (REF), effective reserve network design (REF), and the invasive species control (REF).
 
@@
 
-There are essentially two approaches for estimating the contemporary migration rate. The first is to use the mark-recapture (MR) method that directly estimates parameters of the population.
+There are essentially two approaches for estimating the contemporary migration rate.
+The first is to use the mark-recapture (MR) method that directly estimates migration rate along with other population parameters \cite[]{kery2011bayesian, Thorson_2021}.
+The rational is that, for example, conventional tags provide release and recovery location at known release and recovery dates, generating a movement fraction matrix among strata per given time interval.
+While this direct method is relatively easy to interpret, it is generally suffering from several sources of uncertainties, e.g., reporting rate and tagging-involved mortality (REF).
+In addition,
+
+% 様々な不確実性だけでなく、応用の範囲が限られている
+
+Direct estimates of migration parameters can be obtained using purely ecological approaches such as mark-release–recapture methods (MRR), but they have the inconvenience of being time consuming and impractical for the study of large and/or spatially extended metapop- ulations.
+
+ \RED{KOKOMADE}
 

### 2022-02-02 latex/ms.tex
done 2nd para in Intro, #15

@@
 Contemporary migration rate, the recent rate of movement of individuals or gametes between pre-defined populations, is a critical component to determine the current degree of gene flow and synchrony among the population \cite[]{Waples_2006_MolEcol}.
-Therefore, estimation of contemporary migration rate provides information about the degree of genetic differentiation and demographic dependency, which can delineate evolutionarily significant units \cite[ESUs,][]{moritz1994defining} and identify appropriate management units \cite[]{PALSBOLL200711}.
+Therefore, estimation of contemporary migration rate provides information about the degree of genetic differentiation and demographic dependency, which can delineate evolutionarily significant units and identify appropriate management units \cite[]{moritz1994defining, PALSBOLL200711}.
 In addition, the availability of migration rate can link to underlying population dynamics, allowing for a more precise and flexible evaluation of a management for many relevant topics including stock assessment in fisheries \cite[]{methot2013stock}, species range expansion/construction (REF), effective reserve network design (REF), and the invasive species control (REF).
@@
 The rational is that, for example, conventional tags provide release and recovery location at known release and recovery dates, generating a movement fraction matrix among strata per given time interval.
-While this direct method is relatively easy to interpret, it is generally suffering from several sources of uncertainties, e.g., reporting rate and tagging-involved mortality (REF).
-In addition,
-
-% 様々な不確実性だけでなく、応用の範囲が限られている
-
-Direct estimates of migration parameters can be obtained using purely ecological approaches such as mark-release–recapture methods (MRR), but they have the inconvenience of being time consuming and impractical for the study of large and/or spatially extended metapop- ulations.
+While this direct method is relatively easy to interpret, it is generally hampered by several sources of uncertainties, e.g., tag loss, tagging-related mortality, and reporting rate (REF).
+In addition, the MR method for estimating migration rate is generally limited in practice to situations where collection of a sufficient number of adult sample at multiple sites in a short period is available.
 
@@
 % 3: Population genetics method can handle evolutionally scale but may miss the large migration rate
+
 % 4: CKMR can cover the range that Mark recapture can handle with more realistic situations

### 2022-02-02 latex/ms.tex
write 3rd para in Intro, #15

@@
 There are essentially two approaches for estimating the contemporary migration rate.
-The first is to use the mark-recapture (MR) method that directly estimates migration rate along with other population parameters \cite[]{kery2011bayesian, Thorson_2021}.
+The first is to use the mark-recapture (MR) method that estimates migration rate along with other population parameters \cite[]{kery2011bayesian, Thorson_2021}.
 The rational is that, for example, conventional tags provide release and recovery location at known release and recovery dates, generating a movement fraction matrix among strata per given time interval.
@@
 
+% 3: Population genetics method can handle evolutionally scale but may miss the large migration rate
+
+The second is to use numerous genetic markers to assign individuals to source populations, allowing the inference of recent migration \cite[since][]{Pritchard_2000}.
+The model of \cite{Wilson_2003}, which is an one of such population assignment (PA) methods, can output point estimates of a current migration matrix.
+However,
+
  \RED{KOKOMADE}
 
-% 3: Population genetics method can handle evolutionally scale but may miss the large migration rate
+%pop assiginment method だと、mが結構大きい場合は検出されない。Hastingsが言っているような0.1よりも大きい時
 
@@
 
-There are essentially two approaches for estimating the migrant number.
-The first is to use the mark-recapture method estimate it directly from the population dynamics modeling with survey data.
-The second is to ...
+The inference model implemented by bayesass assumes linkage equilibrium but allows for deviations from Hardy– Weinberg equilibrium by estimating population-specific inbreeding coefficients.
+Migration rates among populations can be asymmetric but are constant over short periods of time (two generations).
+Additionally, it is assumed that migration rates are small (see Appendix A in Wilson  Rannala 2003).
+These two latter assumptions impose a constraint on the range of migration rates that can be considered by the method.
+More precisely, the total proportion of migrant individuals into a population per generation cannot exceed 1,3.
+Thus, nonmigrant proportions must be in the interval 2,3 to 1.
+The method also assumes that genetic drift and migration during the last few generations do not change subpopulation allele frequencies.
 

### 2022-02-03 latex/ms.tex
write 3rd more para in Intro, #15

--- 2022-02-02 latex/ms.tex
@@
 
- \RED{KOKOMADE}
-
 % 3: Population genetics method can handle evolutionally scale but may miss the large migration rate
 
+The second is to use numerous genetic markers to assign individuals to source populations, allowing the inference of recent migration \cite[since][]{Pritchard_2000}.
+The model of \cite{Wilson_2003}, which is one of such population assignment (PA) methods and implemented in a software BayesAss, can output the point estimate as an element of a current migration matrix.
+However, as evaluated by several authors \cite[]{https://doi.org/10.1111/j.1365-294X.2007.03218.x, https://doi.org/10.1111/mec.12806}, the accuracy of estimated migration rates by the model is valid only when populations are highly differentiated ($F_{\rm ST}\ge0.05$), suggesting that it may be difficult to infer the degree of demographic dependency among populations since demographic independency is realized even if there are many migrants.
+
 % 4: CKMR can cover the range that Mark recapture can handle with more realistic situations
+
+Close-kin mark-recapture (CKMR) is a recently developed method for estimating adult population size along with life-history parameters that utilizes the information about kinship in a sample, owing to the recent advances in genetic methods for kinship determination \cite[]{https://doi.org/10.1111/faf.12615}.
+
+This was possible owing to the recent advances in genetic methods for kinship determination \cite[]{Bravington_2016,bravington2016close,skaug2017parent,Hillary_2018} although similar methods have been proposed in the beginning of the 21st century \cite[]{nielsen2001statistical, pearse2001genetic, julius2001allele}.
+Besides, the rationale is that the presence of a kinship pair in the sample is analogous to the recapture of a marked individual in MR method.
+Kinship pairs in the sample are less likely to be observed in larger populations; thus, the number of kinship pairs may reflect $N$.
+While the original CKMR is designed to estimate adult abundance (i.e., $N$), the monitoring data for CKMR also produce the estimator of $N_{\rm e}$ by detecting half-sibling (HS) pairs within the same cohort \cite[]{Akita_2019}.
+This kinship-oriented estimation of $N_{\rm e}$ was presented in the context of the sibship assignment method \cite[]{wang2009new} and is expected to provide a much more accurate estimator as kinship determination becomes more accurate.
+
 % 5: Wang 2014 can handle ecological scale with realistic situations but limited to offspring movement
 % 6: In this paper, ~
-
-There are essentially two approaches for estimating the migrant number.
-The first is to use the mark-recapture method estimate it directly from the population dynamics modeling with survey data.
-The second is to ...
 
@@
 
+%  (e.g., \cite{Hastings_1993} numerically demonstrates that two populations become demographically independent when migration rate $< 0.1$)
+% withinのデータはどう使う？？
 %PRE-DEFINED population !

### 2022-02-07 latex/ms.tex
write 4th  para in Intro, #15

@@
 
-Close-kin mark-recapture (CKMR) is a recently developed method for estimating adult population size along with life-history parameters that utilizes the information about kinship in a sample, owing to the recent advances in genetic methods for kinship determination \cite[]{https://doi.org/10.1111/faf.12615}.
+Close-kin mark-recapture (CKMR) is a recently developed method for estimating adult population size along with life-history parameters that utilizes the information about kinship in a sample, owing to the recent advances in genetic methods for kinship determination \cite[recently reviewed in][]{https://doi.org/10.1111/faf.12615}.
+The rationale is that the presence of a kinship pair in the sample is analogous to the recapture of a marked individual in MR method.
+Kinship pairs in the sample are less likely to be observed in larger populations; thus, the number of kinship pairs may reflect an adult number in the population \cite[]{bravington2016close}.
+While recent studies of CKMR argued that availability of kinship information for applying estimation of migration rate \cite[]{https://doi.org/10.1002/ece3.6296, 10.1093/icesjms/fsac002}
 
-This was possible owing to the recent advances in genetic methods for kinship determination \cite[]{Bravington_2016,bravington2016close,skaug2017parent,Hillary_2018} although similar methods have been proposed in the beginning of the 21st century \cite[]{nielsen2001statistical, pearse2001genetic, julius2001allele}.
+% 最近のConnの研究では、明示的に集団構造をCKMRの枠組みでキャプチャーしようとする枠組みについて議論されているが、その明示的な取り扱いやシミュレーションについては研究されていない。
+
+%This was possible owing to the recent advances in genetic methods for kinship determination \cite[]{Bravington_2016,bravington2016close,skaug2017parent,Hillary_2018} although similar methods have been proposed in the beginning of the 21st century \cite[]{nielsen2001statistical, pearse2001genetic, julius2001allele}.
 Besides, the rationale is that the presence of a kinship pair in the sample is analogous to the recapture of a marked individual in MR method.
@@
 %  (e.g., \cite{Hastings_1993} numerically demonstrates that two populations become demographically independent when migration rate $< 0.1$)
-% withinのデータはどう使う？？
+% withinのデータはどう使う？？withinとbetweenを比較して、betweenが優位に少ないかどうかなどが構造発見につながるかもconn et al 2020 EcolEvolもチェック
 %PRE-DEFINED population !

### 2022-02-08 latex/ms.tex
write 5th  para in Intro, #15

@@
 
-%conn & bravington , Trenkel & bravingtonも引用しないと
-% MigEst by Wangとの比較も...もう一度よくWang 2014を読む！どうやって推定しているのか...
-%% 今回提案した方法は、ゴーストポップがあっても大丈夫
-%% MigEstは、親は動かず、子が移動することを想定している
-%% N = Neを想定
-%移動には２種類ある。子の移動と親の移動である。前者は花粉やラーバなど。connectivityは前者が大事かもで、どこまで遠く行くのかも重要。移動する生物の場合、後者も重要。
-
-%contemporary migration rateはほとんどBaysAssを使っている人の用語
-
 % 1: Estimating contemporary migration is important for both ecologically and evolutionally reasons
@@
 In conservation and wildlife management, estimating the current ecological information is essential for monitoring population levels and proposing management strategies.
-Contemporary migration rate, the recent rate of movement of individuals or gametes between pre-defined populations, is a critical component to determine the current degree of gene flow and synchrony among the population \cite[]{Waples_2006_MolEcol}.
+Contemporary migration rate, the recent rate of movement of individuals or gametes between pre-defined populations, is a critical component to determine the current degree of gene flow and synchrony among the population \cite[]{Waples_2006_MolEcol, https://doi.org/10.1111/j.1365-294X.2010.04688.x}.
 Therefore, estimation of contemporary migration rate provides information about the degree of genetic differentiation and demographic dependency, which can delineate evolutionarily significant units and identify appropriate management units \cite[]{moritz1994defining, PALSBOLL200711}.
-In addition, the availability of migration rate can link to underlying population dynamics, allowing for a more precise and flexible evaluation of a management for many relevant topics including stock assessment in fisheries \cite[]{methot2013stock}, species range expansion/construction (REF), effective reserve network design (REF), and the invasive species control (REF).
+In addition, the availability of migration rate can link to underlying population dynamics, allowing for a more precise and flexible evaluation of a management for many relevant topics including stock assessment in fisheries \cite[]{methot2013stock} and the invasive species control \cite[]{doi:10.1146/annurev.ecolsys.32.081501.114037}.
 
@@
 The rational is that, for example, conventional tags provide release and recovery location at known release and recovery dates, generating a movement fraction matrix among strata per given time interval.
-While this direct method is relatively easy to interpret, it is generally hampered by several sources of uncertainties, e.g., tag loss, tagging-related mortality, and reporting rate (REF).
+While this direct method is relatively easy to interpret, it is generally hampered by several sources of uncertainties, e.g., tag loss, tagging-related mortality, and reporting rate \cite[]{hilborn2013quantitative}.
 In addition, the MR method for estimating migration rate is generally limited in practice to situations where collection of a sufficient number of adult sample at multiple sites in a short period is available.
@@
 
-The second is to use numerous genetic markers to assign individuals to source populations, allowing the inference of recent migration \cite[since][]{Pritchard_2000}.
-The model of \cite{Wilson_2003}, which is one of such population assignment (PA) methods and implemented in a software BayesAss, can output the point estimate as an element of a current migration matrix.
+The second is to use numerous genetic markers to assign individuals to source populations, allowing the inference of recent migration \cite[since][]{https://doi.org/10.1111/j.1365-294X.1995.tb00227.x}.
+The model of \cite{Wilson_2003}, which is one of such population assignment methods and implemented in a software `BayesAss', can output the point estimate as an element of a current migration matrix.
 However, as evaluated by several authors \cite[]{https://doi.org/10.1111/j.1365-294X.2007.03218.x, https://doi.org/10.1111/mec.12806}, the accuracy of estimated migration rates by the model is valid only when populations are highly differentiated ($F_{\rm ST}\ge0.05$), suggesting that it may be difficult to infer the degree of demographic dependency among populations since demographic independency is realized even if there are many migrants.
 
-% 4: CKMR can cover the range that Mark recapture can handle with more realistic situations
+% 4: Wang 2014 can handle ecological scale with realistic situations but limited to offspring movement
 
-Close-kin mark-recapture (CKMR) is a recently developed method for estimating adult population size along with life-history parameters that utilizes the information about kinship in a sample, owing to the recent advances in genetic methods for kinship determination \cite[recently reviewed in][]{https://doi.org/10.1111/faf.12615}.
+Parental assignments, which is based on genetic markers and often used as a complement to the population assignment method in ecological studies, also provide information about the current level of migration.
+In contrast to the population assignment method, the parental assignment method does not require the population differentiation \cite[]{https://doi.org/10.1111/mec.12806}.
+However, the current methodology focuses on estimating dispersal kernels and strongly depends on the assumption adults are not migrant, e.g., pollen/seeds dispersal in plants \cite[]{doi:10.1080/07352689.2010.481167} or larval drift in marine animals \cite[]{https://doi.org/10.1111/eva.12288}; thus, it does not apply the movement of iteroparous species that may change the spawning ground for each breeding season.
+
+% 5: CKMR can cover the range that Mark recapture can handle with more realistic situations
+
+Close-kin mark-recapture (CKMR) is a recently developed method for estimating adult population size along with life-history parameters that utilizes the known kinship information in a sample \cite[reviewed in][]{https://doi.org/10.1111/faf.12615}.
 The rationale is that the presence of a kinship pair in the sample is analogous to the recapture of a marked individual in MR method.
 Kinship pairs in the sample are less likely to be observed in larger populations; thus, the number of kinship pairs may reflect an adult number in the population \cite[]{bravington2016close}.
-While recent studies of CKMR argued that availability of kinship information for applying estimation of migration rate \cite[]{https://doi.org/10.1002/ece3.6296, 10.1093/icesjms/fsac002}
+While recent studies of CKMR argued that availability of kinship information in estimating the migration rate \cite[]{https://doi.org/10.1002/ece3.6296, 10.1093/icesjms/fsac002}, the CKMR-based migration estimation has not been well developed and rigorously examined in a simulation study.
 
-% 最近のConnの研究では、明示的に集団構造をCKMRの枠組みでキャプチャーしようとする枠組みについて議論されているが、その明示的な取り扱いやシミュレーションについては研究されていない。
-
-%This was possible owing to the recent advances in genetic methods for kinship determination \cite[]{Bravington_2016,bravington2016close,skaug2017parent,Hillary_2018} although similar methods have been proposed in the beginning of the 21st century \cite[]{nielsen2001statistical, pearse2001genetic, julius2001allele}.
-Besides, the rationale is that the presence of a kinship pair in the sample is analogous to the recapture of a marked individual in MR method.
-Kinship pairs in the sample are less likely to be observed in larger populations; thus, the number of kinship pairs may reflect $N$.
-While the original CKMR is designed to estimate adult abundance (i.e., $N$), the monitoring data for CKMR also produce the estimator of $N_{\rm e}$ by detecting half-sibling (HS) pairs within the same cohort \cite[]{Akita_2019}.
-This kinship-oriented estimation of $N_{\rm e}$ was presented in the context of the sibship assignment method \cite[]{wang2009new} and is expected to provide a much more accurate estimator as kinship determination becomes more accurate.
-
-% 5: Wang 2014 can handle ecological scale with realistic situations but limited to offspring movement
 % 6: In this paper, ~
 
-移動率の推定は，対象生物の理解に重要なだけでなく，外来種管理・希少種保全・資源の持続的利用にとっても重要である。　特に、水産資源管理にとっては、管理単位を決めるための指標として、移動率はクリティカルな指標の一つである。既存の方法論としては，大きく２種類に大別される。１つ目は標識再捕法であり，２つ目は集団遺伝学的な方法である。前者については，サンプル対象を再捕獲が見込める親個体に限定せざるを得ない，非侵襲的な方法でのラベリングが困難であること，推定精度に見合うサンプルサイズが現実的でないこと，報告率が大きくばらつく等が問題となっている。後者については，近年(すなわち$N_{\rm e}$よりも短い世代数)の集団構造については解像度がないこと，移動個体数が大きいと遺伝的には同一の集団とみなされること等が問題となっている。
+In this study, we propose a new method for estimating the ratio of contemporary effective mother size to the census size (Ne,mNm) in a population, as a proxy of NeN.
+Assuming that kinships are ge- netically detected without any error, this method is based on the numbers of maternal-sibling (MS) and mother–offspring (MO) pairs in a sample.
+Sampling is completed at a single breeding time; sam- pling offspring within the same cohort and mothers probably shares MO relationship with sampled offspring.
+Our model provides a nearly unbiased estimator of Ne,mNm that explicitly incorporates two types of overdispersed reproduction (i.e., parental and nonpa- rental variations; Akita, 2020), making it possible to target a species that shows iteroparity (i.e., multiple reproductive cycles during the lifetime) and/or sweepstakes reproductive success.
+This estimator applying an iteroparous species corresponds to the estimator of the ratio of contemporary effective breeding mother size to the census size, Nb,mNm.
+First, we explain the modeling assumption and sam- pling scheme.
+Then, we analytically determine (nearly) the unbiased estimators of Ne,m, 1Nm, and Ne,mNm, which are based on the num- bers of MS and/or MO pairs.
+Finally, by running an individual-based model, we investigate the performance of the estimator and pro- vide a guide for a sample size.
+It is noteworthy that our modeling framework can be applied to diverse animal species.
+However, the description of the model focuses on fish species, which are presently the best candidate target of our proposed method.
+
+We theoretically developed unbiased estimators of the contemporary migration number (${\hat M_1}$--${\hat M_5}$) and migration rate (${\hat m_1}$--${\hat m_4}$) of parents between two populations in iteroparous species, where the migration direction is specified.
+The proposed estimators are based on known PO relationship and HS relationships observed between and within two populations without any error of kinship assignment.
+Users can choose the estimator developed for the situation as to whether the parental number of population 1 ($N_1$) and/or that of population 2 ($N_2$) is known ({\bf Table~\ref{parameter}}).
+The performance of the estimator (accuracy and precision) was quantitatively evaluated by running an individual-based model ({\bf Figure~\ref{violins}}; see also {\bf Table S1} in {\bf Supporting Information}).
+Our modeling framework utilizes several types of reproductive variations (survived offspring number per parent), including variance of reproductive potential between and within populations, taking account of several situations, including a body-size structure or environmental heterogeneity for reproductive success.
 
 本ノートでは，近親標識法(Close-kin mark-recapture, CKMR)という近年発達した方法論を用いて，移動率の推定を試みる。CKMRとは，親集団が小さいほど近親ペアが見つかりやすいことに着目した方法である。今回は，多回繁殖する生物を対象として，２つのサブ集団間で見つかる０歳の半兄弟(Half-sibling, HS)ペアを用いて，そのペアの親候補となる個体の数（もしくは移動率）を推定する。ただし，移動前の集団および移動後の集団における親魚尾数が，移動個体数の推定には必要となる。
-
-応用例として，３年間にわたって２つのサブ集団からサンプルされた当歳魚から見出される半兄弟ペアをもとに，個体数・移動率・生存率を推定する枠組みを提示する。そこでは，同じサブ集団から年を跨いで見つかる半兄弟ペアに基づく関係式と，今回新たに開発した関係式を組み合わせて用いる。
 
@@
 % withinのデータはどう使う？？withinとbetweenを比較して、betweenが優位に少ないかどうかなどが構造発見につながるかもconn et al 2020 EcolEvolもチェック
-%PRE-DEFINED population !
-%Caveat: selectivity, family correlated migration、skip spawning,
+%% 今回提案した方法は、ゴーストポップがあっても大丈夫
 

### 2022-02-09 latex/ms.tex
done Intro, #15

@@
 In contrast to the population assignment method, the parental assignment method does not require the population differentiation \cite[]{https://doi.org/10.1111/mec.12806}.
-However, the current methodology focuses on estimating dispersal kernels and strongly depends on the assumption adults are not migrant, e.g., pollen/seeds dispersal in plants \cite[]{doi:10.1080/07352689.2010.481167} or larval drift in marine animals \cite[]{https://doi.org/10.1111/eva.12288}; thus, it does not apply the movement of iteroparous species that may change the spawning ground for each breeding season.
+However, the current methodology focuses on estimating dispersal kernels and strongly depends on the assumption adults are not migrant, e.g., pollen/seeds dispersal in plants \cite[]{doi:10.1080/07352689.2010.481167} or larval drift in marine animals \cite[]{https://doi.org/10.1111/eva.12288}; thus, it does not apply the movement of iteroparous species (i.e., multiple reproductive cycles during the lifetime) that may change the spawning ground for each breeding season.
 
@@
 
-In this study, we propose a new method for estimating the ratio of contemporary effective mother size to the census size (Ne,mNm) in a population, as a proxy of NeN.
-Assuming that kinships are ge- netically detected without any error, this method is based on the numbers of maternal-sibling (MS) and mother–offspring (MO) pairs in a sample.
-Sampling is completed at a single breeding time; sam- pling offspring within the same cohort and mothers probably shares MO relationship with sampled offspring.
-Our model provides a nearly unbiased estimator of Ne,mNm that explicitly incorporates two types of overdispersed reproduction (i.e., parental and nonpa- rental variations; Akita, 2020), making it possible to target a species that shows iteroparity (i.e., multiple reproductive cycles during the lifetime) and/or sweepstakes reproductive success.
-This estimator applying an iteroparous species corresponds to the estimator of the ratio of contemporary effective breeding mother size to the census size, Nb,mNm.
-First, we explain the modeling assumption and sam- pling scheme.
-Then, we analytically determine (nearly) the unbiased estimators of Ne,m, 1Nm, and Ne,mNm, which are based on the num- bers of MS and/or MO pairs.
-Finally, by running an individual-based model, we investigate the performance of the estimator and pro- vide a guide for a sample size.
+In this study, we propose a new method for estimating the contemporary migration number or rate of adults between the two pre-defined populations in iteroparous species, where the migration direction is specified.
+Assuming that kinships are genetically detected without any error, this method is based on the numbers of half-sibling (HS) and parent-offspring (PO) pairs in a sample.
+Sampling can be invasive or non-invasive and is completed at two breeding seasons; sampling offspring (young-of-year individuals) and parents probably shares PO relationship with sampled offspring in the one population at the first breeding season and in the another population at the second breeding season.
+The rationale is that the number of PO and HS pairs found between populations have information as to how often parental movements are realized.
+Our model explicitly incorporates reproductive variation within and between populations, making it possible to target a species whose fertility is affected by environmental differences between populations.
+
+First, we explain the modeling assumption and sampling scheme.
+Then, we analytically determine the estimators of the contemporary migration number or rate of adults, which are based on the numbers of HS and/or PO pairs.
+Finally, by running an individual-based model, we investigate the performance of the estimator and provide a guide for a sample size.
 It is noteworthy that our modeling framework can be applied to diverse animal species.
 However, the description of the model focuses on fish species, which are presently the best candidate target of our proposed method.
-
-We theoretically developed unbiased estimators of the contemporary migration number (${\hat M_1}$--${\hat M_5}$) and migration rate (${\hat m_1}$--${\hat m_4}$) of parents between two populations in iteroparous species, where the migration direction is specified.
-The proposed estimators are based on known PO relationship and HS relationships observed between and within two populations without any error of kinship assignment.
-Users can choose the estimator developed for the situation as to whether the parental number of population 1 ($N_1$) and/or that of population 2 ($N_2$) is known ({\bf Table~\ref{parameter}}).
-The performance of the estimator (accuracy and precision) was quantitatively evaluated by running an individual-based model ({\bf Figure~\ref{violins}}; see also {\bf Table S1} in {\bf Supporting Information}).
-Our modeling framework utilizes several types of reproductive variations (survived offspring number per parent), including variance of reproductive potential between and within populations, taking account of several situations, including a body-size structure or environmental heterogeneity for reproductive success.
-
-本ノートでは，近親標識法(Close-kin mark-recapture, CKMR)という近年発達した方法論を用いて，移動率の推定を試みる。CKMRとは，親集団が小さいほど近親ペアが見つかりやすいことに着目した方法である。今回は，多回繁殖する生物を対象として，２つのサブ集団間で見つかる０歳の半兄弟(Half-sibling, HS)ペアを用いて，そのペアの親候補となる個体の数（もしくは移動率）を推定する。ただし，移動前の集団および移動後の集団における親魚尾数が，移動個体数の推定には必要となる。
 

### 2022-02-09 latex/ms.tex
review entire ms

@@
 \usepackage[normalem]{ulem} %%
-%\linenumbers
+\linenumbers
 \usepackage{bm}
@@
 Therefore, estimation of contemporary migration rate provides information about the degree of genetic differentiation and demographic dependency, which can delineate evolutionarily significant units and identify appropriate management units \cite[]{moritz1994defining, PALSBOLL200711}.
-In addition, the availability of migration rate can link to underlying population dynamics, allowing for a more precise and flexible evaluation of a management for many relevant topics including stock assessment in fisheries \cite[]{methot2013stock} and the invasive species control \cite[]{doi:10.1146/annurev.ecolsys.32.081501.114037}.
+In addition, the availability of migration rate can link to underlying population dynamics, allowing for a more precise and flexible evaluation of a management for many relevant topics including stock assessment in fisheries \cite[]{hampton2001spatially} and the invasive species control \cite[]{doi:10.1146/annurev.ecolsys.32.081501.114037}.
 
@@
 The rational is that, for example, conventional tags provide release and recovery location at known release and recovery dates, generating a movement fraction matrix among strata per given time interval.
-While this direct method is relatively easy to interpret, it is generally hampered by several sources of uncertainties, e.g., tag loss, tagging-related mortality, and reporting rate \cite[]{hilborn2013quantitative}.
+While this direct method is relatively easy to interpret, it is generally hampered by several sources of uncertainties, e.g., tag loss, tagging-related mortality, and time-varying reporting rate \cite[]{hilborn2013quantitative}.
 In addition, the MR method for estimating migration rate is generally limited in practice to situations where collection of a sufficient number of adult sample at multiple sites in a short period is available.
@@
 The model of \cite{Wilson_2003}, which is one of such population assignment methods and implemented in a software `BayesAss', can output the point estimate as an element of a current migration matrix.
-However, as evaluated by several authors \cite[]{https://doi.org/10.1111/j.1365-294X.2007.03218.x, https://doi.org/10.1111/mec.12806}, the accuracy of estimated migration rates by the model is valid only when populations are highly differentiated ($F_{\rm ST}\ge0.05$), suggesting that it may be difficult to infer the degree of demographic dependency among populations since demographic independency is realized even if there are many migrants.
+However, as evaluated by several authors \cite[]{https://doi.org/10.1111/j.1365-294X.2007.03218.x, https://doi.org/10.1111/mec.12806}, the accuracy of estimated migration rates by the model is valid only when populations are highly differentiated (e.g., $F_{\rm ST}\ge0.05$), suggesting that it may be difficult to infer the degree of demographic dependency among populations since demographic independency is realized even if there are many migrants.
 
@@
 In contrast to the population assignment method, the parental assignment method does not require the population differentiation \cite[]{https://doi.org/10.1111/mec.12806}.
-However, the current methodology focuses on estimating dispersal kernels and strongly depends on the assumption adults are not migrant, e.g., pollen/seeds dispersal in plants \cite[]{doi:10.1080/07352689.2010.481167} or larval drift in marine animals \cite[]{https://doi.org/10.1111/eva.12288}; thus, it does not apply the movement of iteroparous species (i.e., multiple reproductive cycles during the lifetime) that may change the spawning ground for each breeding season.
+However, the current methodology focuses on estimating dispersal kernels and, for estimating migration rate, requires the assumption that adults are not migrant, e.g., pollen/seeds dispersal in plants \cite[]{doi:10.1080/07352689.2010.481167} or larval drift in marine animals \cite[]{https://doi.org/10.1111/eva.12288}; thus, it may not apply the adult movement of iteroparous species (i.e., multiple reproductive cycles during the lifetime) that may change the spawning ground for each breeding season.
 
@@
 Close-kin mark-recapture (CKMR) is a recently developed method for estimating adult population size along with life-history parameters that utilizes the known kinship information in a sample \cite[reviewed in][]{https://doi.org/10.1111/faf.12615}.
-The rationale is that the presence of a kinship pair in the sample is analogous to the recapture of a marked individual in MR method.
+The rationale is that the presence of a kinship pair in the sample is analogous to the recapture of a marked individual in the MR method.
 Kinship pairs in the sample are less likely to be observed in larger populations; thus, the number of kinship pairs may reflect an adult number in the population \cite[]{bravington2016close}.
@@
 
-In this study, we propose a new method for estimating the contemporary migration number or rate of adults between the two pre-defined populations in iteroparous species, where the migration direction is specified.
+In this study, we propose a new method for estimating the contemporary migration number or rate of adults between two pre-defined populations in iteroparous species, where the migration direction is specified.
 Assuming that kinships are genetically detected without any error, this method is based on the numbers of half-sibling (HS) and parent-offspring (PO) pairs in a sample.
 Sampling can be invasive or non-invasive and is completed at two breeding seasons; sampling offspring (young-of-year individuals) and parents probably shares PO relationship with sampled offspring in the one population at the first breeding season and in the another population at the second breeding season.
-The rationale is that the number of PO and HS pairs found between populations have information as to how often parental movements are realized.
+The rationale is that the number of PO and HS pairs found between populations have information as to how often parental movements during the breeding interval are realized.
 Our model explicitly incorporates reproductive variation within and between populations, making it possible to target a species whose fertility is affected by environmental differences between populations.
-
 First, we explain the modeling assumption and sampling scheme.
@@
 
-We theoretically developed unbiased estimators of the contemporary migration number (${\hat M_1}$--${\hat M_5}$) and migration rate (${\hat m_1}$--${\hat m_4}$) of parents between two populations in iteroparous species, where the migration direction is specified.
+We theoretically developed estimators of the contemporary migration number (${\hat M_1}$--${\hat M_5}$) and migration rate (${\hat m_1}$--${\hat m_4}$) of parents between two pre-defined populations in iteroparous species.
 The proposed estimators are based on known PO relationship and HS relationships observed between and within two populations without any error of kinship assignment.
@@
 The performance of the estimator (accuracy and precision) was quantitatively evaluated by running an individual-based model ({\bf Figure~\ref{violins}}; see also {\bf Table S1} in {\bf Supporting Information}).
-Our modeling framework utilizes several types of reproductive variations (survived offspring number per parent), including variance of reproductive potential between and within populations, taking account of several situations, including a body-size structure or environmental heterogeneity for reproductive success.
+Our modeling framework utilizes several types of reproductive variations (survived offspring number per parent), including variance of reproductive potential within and between populations, taking account of several situations, including a body-size structure or environmental heterogeneity for reproductive success.
 
@@
 First, we formulated probabilities of kinship pairs randomly chosen between two populations ($\pi_{\rm HS,bet}$ and $\pi_{\rm PO,bet}$), which provide estimators of the migration number or rate.
-While similar derivations are found in (nongenetical) mark-recapture method (\RED{REF}), these are limited to the situation such that sampling can be non-invasive and adult individuals are sampled.
+While similar derivations may be found in (nongenetical) the MR method, these are limited to the situation such that sampling can be non-invasive and adult individuals are sampled.
 Our proposed method can avoid these limitations, where such an advantages is characterized by CKMR method.
-Second, we revealed that the probabilities of kinship pairs are approximately independent of reproductive potential and thus information about it is not needed for the estimation, if migration event and the potential are independent.
-This is a useful property of the estimators because heterogeneity of reproductive potential within/between populations are generally observed in iteroprous species.
+Second, we revealed that the probabilities of kinship pairs are approximately independent of reproductive potential and thus information about it is not needed for the estimation, provided that migration assumes to occur independently of the reproductive potential.
+This is a useful property of the estimators because it is natural that heterogeneity of reproductive potential within and between populations exits in iteroprous species but its observation is generally difficult except a body size.
 Third, we demonstrated applicability that the estimation can be obtained only from the genetic data (i.e., ${\hat M_5}$ and ${\hat m_4}$).
-There are several advantages in using the proposed estimator instead of separately estimating $\pi_{\rm HS,bet}$ (and/or $\pi_{\rm PO,bet}$) (via genetic method) and $N_1$ (and/or $N_2$) (via nongenetical method), including simplified sampling and analyzing designs and availability of unified framework of genetic analyzes for detecting PO and HS pairs (similar discussion is found for estimating effective breeding size per census size, $N_{\rm b}/N$, in \cite{Akita_2020}).
+There are several advantages in using the proposed estimator instead of separately estimating $\pi_{\rm HS,bet}$ (and/or $\pi_{\rm PO,bet}$) (via genetic method) and $N_1$ (and/or $N_2$) (via nongenetical method), including simplified sampling and analyzing designs and availability of unified framework of genetic analyzes for detecting HS and PO pairs (similar discussion is found for estimating the ratio of effective breeding size to the census size, $N_{\rm b}/N$, in \cite{Akita_2020}).
 
@@
 Even if there is no information about these numbers, $1/\sqrt{H_{\rm HS, bet}}$ (or $1/\sqrt{H_{\rm PO, bet}}$) provides an approximate lower bound on the CV, which can be used as an indicator of the precision of ${\hat M}$ or ${\hat m}$.
-Furthermore, the condition that $n>\sqrt{N_2}$ is also used as rule of thumb especially when planning a research project (see also Equations~\ref{RS-1} and \ref{RS-2}).
+Furthermore, the condition that $n>\sqrt{N_2}$ is also used as rule of thumb especially when planning a research project ($n = n_{\rm O, 1}=n_{\rm O, 2}=n_{\rm P, 2}$, see also Equations~\ref{RS-1} and \ref{RS-2}).
 

### 2022-02-14 latex/ms.tex
modify Discussion

@@
 While similar derivations may be found in (nongenetical) the MR method, these are limited to the situation such that sampling can be non-invasive and adult individuals are sampled.
-Our proposed method can avoid these limitations, where such an advantages is characterized by CKMR method.
+Our proposed method can avoid these limitations, where such an advantages is characterized by CKMR method for estimating population sizes.
 Second, we revealed that the probabilities of kinship pairs are approximately independent of reproductive potential and thus information about it is not needed for the estimation, provided that migration assumes to occur independently of the reproductive potential.
@@
 There may be several cases where it is desirable to apply the proposed estimator.
-The first case is where there is a certain number of migrants between populations, e.g., $M>100$, which is too large to be detected by population genetics method if $M$ is interpreted as effective migration number.
-Information on movement between populations is essential for assessing population dynamics in the context of conservation and management, even if migrant number is so large that it cannot be genetically assigned to two populations.
+The first case is where there is a large number of migrants between populations, e.g., $M>100$, which vanishes the population differentiation and thus hampers the detection of $M$ population genetics method if $M$ is interpreted as effective migration number.
+Information on movement between populations is essential for assessing population dynamics in the context of conservation and management, even if the migrant number is so large that it cannot be genetically assigned to two populations.
 The second is the case of the application to genetic monitoring conducted every reproductive timing (e.g., annually).
-This is because proposed estimators have information about contemporary migration, thus the time series data for migration reflect environmental changes, which provides insights into the underlying ecological processes.
-In addition, HS pairs found within the genetic population provides $N_{\rm b}$ \cite[]{wang2009new}, which is also used for assessing a genetic health.
-The third case is where sampling adults is difficult due to conservation purpose or other reasons instead sampling offspring is relatively easy.
+This is because proposed estimators have information about contemporary migration that is explicitly specified the timing (e.g., year), thus the time series data for migration may reflect environmental changes, which provides insights into the underlying ecological processes.
+In addition, HS pairs found within the genetic population provides $N_{\rm b}$ \cite[]{wang2009new,WAPLES_2011}, which is also used for assessing a genetic health.
+The third is the case is to develop integrated models that combines several sources of data into a single analysis \cite[]{MAUNDER201361}.
+One example of this direction is to provide additional information about migration to ongoing CKMR projects for stock assessment in fisheries, which utilizes kinship pairs for simultaneous estimation of population parameters \cite[e.g.,][]{Bravington_2016,Hillary_2018,https://doi.org/10.1002/ece3.6296,ecolevol2021p,10.1093/icesjms/fsac002}.
+If population structure is hypothetically defined, accumulated data in these projects are readily connected to our theory via likelihood methods.
+The forth case is where sampling adults is difficult due to conservation purpose or other reasons instead sampling offspring is relatively easy.
 In this case, although $N_2$ (and $N_1$) need to be given externally for the usage of $\hat m_1$ (and $\hat M_1$), there is presently no other method for estimating adult movement especially when two populations cannot be genetically distinct, indicating that proposed method has the potential to greatly widen the scope of population monitoring.
@@
 It is desirable to estimate in advance how many markers are needed for kinship detections in target populations associated with simulation of a pedigree reconstruction including distant kinships (e.g., \cite{Anderson_2020}).
-Our proposed estimators are limited to detect one-time parental movements on a period between breeding seasons in given populations.
+Our proposed estimators are limited to detect parental movements on a period between breeding seasons in given populations.
 Thus, the estimation of fine-scale spatial-temporal movements, which is available to integrate multiple type of data \cite[]{Thorson_2021}, goes beyond the scope of this paper, although population dynamics models with a coarser spatial resolution than the spatial scale for environmental layers are often used in the assessment models, which is the target of application of the proposed method.
-In addition, the current theory behind the estimators does not assume desynchronized reproduction within a population (e.g., skip spawning) and correlation between mobility and fertility.
+In addition, the current theory behind the estimators does not assume desynchronized reproduction within a population (e.g., skip spawning, see also \cite{https://doi.org/10.1111/faf.12615}) and correlation between mobility and fertility.
 Our proposed estimators require the pre-specification of a population structure.
-Kinship relationships with information of a sample location potentially provide the chance to explore a plausible population structure via estimating migration number or rate between hypothetical populations, which contributes the determination of a management unit \cite[]{Hastings_1993, Waples_2006_MolEcol, PALSBOLL200711}.
+Kinship relationships with information of a sample location potentially provide the chance to explore a plausible population structure via estimating migration number or rate between hypothetical populations, which contributes the determination of a management unit.
 This perspective of the study will be conducted in the future.

### 2022-02-14 latex/ms.tex
done Discussion

@@
 \begin{align}
-\widehat{N_2} &= \frac{ 2 n_{\rm O, 2} n_{\rm P, 2} + 1 }{\widetilde{H}_{\rm PO, 2} + 1} ,
+\widehat{N_2} &= \frac{ 2 n_{\rm O, 2} n_{\rm P, 2}  }{\widetilde{H}_{\rm PO, 2} + 1} ,
 \label{AP-3}
@@
 \begin{align}
-\widehat{M_4} &=  \frac{ N_{1} \left(\widetilde{H}_{\rm HS,bet} + \widetilde{H}_{\rm PO,bet}\right) \left(2 n_{\rm O, 2} n_{\rm P, 2} + 1\right)} {2n_{\rm O, 1} \left(2 n_{\rm O, 2} + n_{\rm P, 2}\right) \left(\widetilde{H}_{\rm PO, 2} + 1\right)},
+\widehat{M_4} &=  \frac{ n_{\rm O, 2} n_{\rm P, 2} N_{1} \left(\widetilde{H}_{\rm HS,bet} + \widetilde{H}_{\rm PO,bet}\right) } {n_{\rm O, 1} \left(2 n_{\rm O, 2} + n_{\rm P, 2}\right) \left(\widetilde{H}_{\rm PO, 2} + 1\right)},
 \label{AP-4}
@@
 \begin{align}
-\widehat{m_4} &=  \frac{ \left(\widetilde{H}_{\rm HS,bet} + \widetilde{H}_{\rm PO,bet}\right) \left(2 n_{\rm O, 2} n_{\rm P, 2} + 1\right)} {2n_{\rm O, 1} \left(2 n_{\rm O, 2} + n_{\rm P, 2}\right) \left(\widetilde{H}_{\rm PO, 2} + 1\right)}.
+\widehat{m_4} &=  \frac{ n_{\rm O, 2} n_{\rm P, 2}\left(\widetilde{H}_{\rm HS,bet} + \widetilde{H}_{\rm PO,bet}\right)} {n_{\rm O, 1} \left(2 n_{\rm O, 2} + n_{\rm P, 2}\right) \left(\widetilde{H}_{\rm PO, 2} + 1\right)}.
 \label{AP-5}
@@
 \begin{align}
-\widehat{N_1} &= \frac{ 2 n_{\rm O, 1} n_{\rm P, 1} + 1 }{\widetilde{H}_{\rm PO, 1} + 1},
+\widehat{N_1} &= \frac{ 2 n_{\rm O, 1} n_{\rm P, 1} }{\widetilde{H}_{\rm PO, 1} +1},
 \label{AP-6}
@@
 \begin{align}
-\widehat{M_5} &=  \frac{ \left(\widetilde{H}_{\rm HS,bet} + \widetilde{H}_{\rm PO,bet}\right) \left(2 n_{\rm O, 1} n_{\rm P, 1} + 1\right) \left(2 n_{\rm O, 2} n_{\rm P, 2} + 1\right)} {2n_{\rm O, 1} \left(2 n_{\rm O, 2} + n_{\rm P, 2}\right) \left(\widetilde{H}_{\rm PO, 1} + 1\right) \left(\widetilde{H}_{\rm PO, 2} + 1\right)}.
+\widehat{M_5} &=  \frac{ 2 n_{\rm O, 1} n_{\rm P, 1} n_{\rm O, 2} n_{\rm P, 2} \left(\widetilde{H}_{\rm HS,bet} + \widetilde{H}_{\rm PO,bet}\right)} {n_{\rm O, 1} \left(2 n_{\rm O, 2} + n_{\rm P, 2}\right) \left(\widetilde{H}_{\rm PO, 1} + 1\right) \left(\widetilde{H}_{\rm PO, 2} + 1\right)}.
 \label{AP-7}
@@
 Furthermore, the condition that $n>\sqrt{N_2}$ is also used as rule of thumb especially when planning a research project ($n = n_{\rm O, 1}=n_{\rm O, 2}=n_{\rm P, 2}$, see also Equations~\ref{RS-1} and \ref{RS-2}).
+It should be noted that the guidance is to estimate the information about one-way migration between two populations; thus, estimating two-way migrations among two and three populations requires twice and three times the number of samples, respectively, compared to our guidance for a sample size.
 
@@
 Thus, the estimation of fine-scale spatial-temporal movements, which is available to integrate multiple type of data \cite[]{Thorson_2021}, goes beyond the scope of this paper, although population dynamics models with a coarser spatial resolution than the spatial scale for environmental layers are often used in the assessment models, which is the target of application of the proposed method.
-In addition, the current theory behind the estimators does not assume desynchronized reproduction within a population (e.g., skip spawning, see also \cite{https://doi.org/10.1111/faf.12615}) and correlation between mobility and fertility.
 Our proposed estimators require the pre-specification of a population structure.
 Kinship relationships with information of a sample location potentially provide the chance to explore a plausible population structure via estimating migration number or rate between hypothetical populations, which contributes the determination of a management unit.
-This perspective of the study will be conducted in the future.
-
-%  (e.g., \cite{Hastings_1993} numerically demonstrates that two populations become demographically independent when migration rate $< 0.1$)
-% withinのデータはどう使う？？withinとbetweenを比較して、betweenが優位に少ないかどうかなどが構造発見につながるかもconn et al 2020 EcolEvolもチェック
-%% 今回提案した方法は、ゴーストポップがあっても大丈夫
+In addition, the current theory behind the estimators does not assume desynchronized reproduction within a population (e.g., skip spawning, see also \cite{https://doi.org/10.1111/faf.12615}), correlation between individual mobility and fertility and non-random sampling of parents (e.g., mothers with a large number of offspring are likely to be sampled).
+These perspectives of the study will be conducted in the future.
 
@@
 \section*{ACKNOWLEDGMENTS}
-The author thanks Y. Tsukahara and N. Suzuki for fruitful discussions. This work was supported by JSPS KAKENHI Grant Number 19K06862 and 20H03012.
+The author thanks N. Shinohara, N. Suzuki and Y. Tsukahara for fruitful discussions. This work was supported by JSPS KAKENHI Grant Number 19K06862 and 20H03012.
 
@@
 \begin{table}[tb]
-\begin{center}
+\begin{flushleft}
    \caption[]{Table 2: Summary of proposed estimators for required parameters and kinship types}
@@
     \end{tabular}
+    \\HSP and POP indicates half-sibling pair and parent-offspring pair, respectively. 
     \label{parameter} 
-\end{center} 
+\end{flushleft} 
 \end{table}

### 2022-02-15 latex/ms.tex
add abstract

@@
 \def\BLUE#1{\textcolor{blue}{#1}} %%
+
+% https://onlinelibrary.wiley.com/page/journal/17550998/homepage/forauthors.html
+
 \begin{document}
 
-\title{Estimating contemporary migration numbers of adults for iteroparous species using kinship pairs found between populations}
+\title{Estimating contemporary migration numbers of adults for iteroparous species based on kinship relationships found between populations}
 \author{
@@
    }
-\date{Manuscript Intended for \emph{Methods in Ecology and Evolution}, \today}
+\date{Manuscript Intended for \emph{Molecular Ecology and Resources}, \today}
 \maketitle
@@
 \begin{abstract}
-本ノートでは，多回繁殖(iteroparity)する種を対象として，半兄弟ペア数から親魚による２つのサブ集団間の移動率を推定する理論($\hat{M}=N_1N_2H_{\rm obs}/(4n_1n_2)$)を紹介する。この推定式は、親をサンプルする通常の標識放流と同じである。もし、繁殖ポテンシャルの分布が集団間で異なっていても上記の式で問題ないことを示した。一方，サンプル数としては$\sqrt {N}$以上のオーダーが求められる。
+This study develops estimators of the contemporary migration number and rate of adults for iteroparous species between two populations.
+The proposed estimators are based on both known half-sibling (HS) and/or parent-offspring (PO) relationships observed between the populations across the breeding seasons.
+The rationale is that such HS and PO pairs have information as to how often parental movements during the breeding interval are realized.
+Our method allows for variance of the average number of offspring per parent within and between populations.
+In addition, coupled with PO pairs found within population, the estimators can be obtained only from genetic data.
+Roughly speaking, a sample size of square root of population size is required for obtaining meaningful information on migration.
+We also evaluate the detailed performance of the estimators by running an individual-based model, providing a guidance for sample sizes to ensure the required accuracy and precision.
+Furthermore, in the face of the current situation where there is little effective method for estimating adult movement especially when populations cannot be genetically distinct, we discuss the usefulness of this proposed sibship assignment method in terms of conservation biology and wildlife management.
 \\
 \end{abstract}
-\textbf{Key words:} effective population size; sibship assignment; overdispersed reproduction; close-kin mark-recapture\\
-\textbf{Running head:} Estimating migration rates using kinship pairs\\
+
+\textbf{Key words:} dispersion; sibship assignment; reproductive potential; close-kin mark-recapture\\
+\textbf{Running head:} Estimating migration numbers using kinship pairs\\
+\textbf{Subject Area:} Molecular and Statistical Advances\\
 
@@
 
-Close-kin mark-recapture (CKMR) is a recently developed method for estimating adult population size along with life-history parameters that utilizes the known kinship information in a sample \cite[reviewed in][]{https://doi.org/10.1111/faf.12615}.
+Close-kin mark-recapture (CKMR) is a recently developed method for estimating adult population size along with life-history parameters that utilizes the known kinship information in a sample \cite[][and references therein]{https://doi.org/10.1111/faf.12615}.
 The rationale is that the presence of a kinship pair in the sample is analogous to the recapture of a marked individual in the MR method.
@@
 Sampling can be invasive or non-invasive and is completed at two breeding seasons; sampling offspring (young-of-year individuals) and parents probably shares PO relationship with sampled offspring in the one population at the first breeding season and in the another population at the second breeding season.
-The rationale is that the number of PO and HS pairs found between populations have information as to how often parental movements during the breeding interval are realized.
+The rationale is that the number of HS and PO pairs found between populations have information as to how often parental movements during the breeding interval are realized.
 Our model explicitly incorporates reproductive variation within and between populations, making it possible to target a species whose fertility is affected by environmental differences between populations.
@@
 \section{Theory}\label{sec2}
-In this section, we present the theoretical foundation for estimating a migrant number and a migration rate of iteroparous species using HS or PO pairs, which are found between two populations with a different sample timing.
+In this section, we present the theoretical foundation for estimating a migrant number and migration rate of iteroparous species using HS or PO pairs, which are found between two populations with a different sample timing.
 While the estimators can hold under flexible assumptions for reproduction (see {\bf Appendix 2}), here we assume a relatively simple situation for explanation purposes.
@@
 Suppose that we have a set of two populations labelled 1 and 2 where random mating occurs within each population and that parents can move to the other population after the end of the reproductive season.
-Hereafter, without loss of generality, we consider the movement of parents in the direction from population 1 to population 2 and focus on the migration number or rate, and that is what we attempt to estimate.
+Hereafter, without loss of generality, we consider the movement of parents in the direction from the population 1 to the population 2 and focus on the migration number or rate, and that is what we attempt to estimate.
 In this framework, we show that considering two reproductive seasons (hereafter, we call them "the first year" and "the second year") is enough to estimate it.
@@
 $\pi_{\rm PO, bet}$ can be partitioned into the three probabilities: (i) the probability that sampled offspring in the population 1 born to a migrant; (ii) the probability that a migrant is sampled; and (iii) the probability that the migrant of a sampled offspring in the population 1 and the migrant sampled in the population 2 are identical.
-The first and second probabilities are the same as the one introduced in the previous subsection, that is, $2M/N_{1}$ and $1/M$.
+The first and third probabilities are the same as the one introduced in the previous subsection, that is, $2M/N_{1}$ and $1/M$.
 The second probability is $M/N_{2}$ by definition.
@@
 It should be noted that very tiny $m$, which dramatically increases the required sample size, produces significant genetic differences between two populations.
-In such a case, there are several methods to estimate migration rate by population genetics technique; alternatively, we focus the situation of moderate/large migration rate, which leads little genetic differences between two populations (see details in {\bf Discussion} section).
+In such a case, there are several methods to estimate migration rate by population genetics technique; alternatively, we focus the situation of moderate/large migration rate, which leads little genetic differences between two populations.
 
@@
 {\bf Figure~\ref{violins}} illustrates the distribution of the relative bias of ${\hat M}$ for limiting cases where parent and offspring sample numbers are identical (i.e., $n=n_{\rm P,1}=n_{\rm P,2}=n_{\rm O,1}= n_{\rm O,2}$) and parent numbers in the two populations are also identical (i.e., $N=N_1=N_2$).
-Relative bias is calculated by applying outputs of the individual-based model, which is defined as follows: ``averaged estimator - true value/true value.'' Full list of parameter sets to evaluate the performance (relative bias and CV of ${\hat M}$s) is summarized in {\bf Table S1} in {\bf Supporting Information}.
+Relative bias is calculated by applying outputs of the individual-based model, which is defined as follows: ``(averaged estimator - true value)/true value.'' Full list of parameter sets to evaluate the performance (relative bias and CV of ${\hat M}$s) is summarized in {\bf Table S1} in {\bf Supporting Information}.
 
@@
 Our simulator can handle the situation with or without invasive sampling.
-Invasive sampling potentially affects the degree of $m$ since sampled parents in the population 1 have no chance to move to the population 2 and thus those parents cannot be sampled.
+Invasive sampling potentially affects the level of $m$ since sampled parents in the population 1 have no chance to move to the population 2 and thus those parents cannot be sampled.
 In this case, $m$ should be defined by $M/(N_1-n_{P,1})$ not by $M/N_1$, although it does not affect the estimator ${\hat M}$s, as demonstrated in {\bf Table S1} ({\bf Supporting Information}).
@@
 Finally, we investigated the situation in which the parental number in the population 1 is much more than in the population 2 (i.e., $N_1 \gg N_2$) and thus migrants are large proportion of $N_2$.
-In such a setting, e.g., $(N_1,N_2,M)=(10^4,10^3,500)$, we confirmed the same property of ${\hat M}$s to the situation $N_1 = N_2$, as demonstrated in {\bf Table S1} ({\bf Supporting Information}), suggesting the robustness of ${\hat M}$s in heterogeneous population sizes.
+In such a setting, e.g., $(N_1,N_2,M)=(10^4,10^3,500)$, we confirmed the similar property of ${\hat M}$s to the situation $N_1 = N_2$, as demonstrated in {\bf Table S1} ({\bf Supporting Information}), suggesting the robustness of ${\hat M}$s in heterogeneous population sizes.
 
@@
 \renewcommand{\theequation}{A\arabic{equation}}
-Here, we introduce the concept of the reproductive potential of parent $i$ and $j$ in the population 1 and 2, respectively, which are defined as the expected number of surviving offspring at sampling time, denoted by $\lambda_{i,1}$ and $\lambda_{j,2}$ ($i=(1, \ldots, N_1)$ and $j=(1, \ldots, N_2)$).
+Here, we introduce the concept of the reproductive potential of parent $i$ and $j$ in the population 1 and 2, respectively, which are defined as the expected number of surviving offspring at sampling time, denoted by $\lambda_{i,1}$ and $\lambda_{j,2}$ ($i=1, \ldots, N_1$ and $j=1, \ldots, N_2$).
 The reproductive potential is determined by several factors, including the parent's age, weight, residence time on the spawning ground.
@@
 \pi_{\rm HS,bet} &\approx \frac{4}{M}  \frac{ \mathbb{E}\left[ \sum_{l=1}^M \lambda_{M,l,1} \sum_{l=1}^M \lambda_{M,l,2} \right]} {\mathbb{E}\left[ \left(\sum_{l=1}^{M} \lambda_{M,l,1} + \sum_{i=M+1}^{N_1} \lambda_{i,1}\right) \left(\sum_{l=1}^{M} \lambda_{M,l,2} + \sum_{j=M+1}^{N_2} \lambda_{j,2}\right) \right] }\nonumber\\
-&= \frac{4}{M} \frac{ M^2 {\bar \lambda_{M,1}} {\bar \lambda_{M,2}} } { M {\bar \lambda_{M,1}} + (N_1 - M) {\bar \lambda_1} + M {\bar \lambda_{M,2}} + (N_2 - M) {\bar \lambda_2} }.
+&= \frac{4}{M} \frac{ M^2 {\bar \lambda_{M,1}} {\bar \lambda_{M,2}} } { \left( M {\bar \lambda_{M,1}} + (N_1 - M) {\bar \lambda_1} \right) + \left( M {\bar \lambda_{M,2}} + (N_2 - M) {\bar \lambda_2} \right)}.
 \label{App3}

### 2022-02-15 draw_violin.R

@@ -5,7 +5,7 @@ library(tidyverse)
 theme_set(theme_classic(base_size = 12, base_family = "Helvetica"))
 setwd("~/git/CKMRmig/")
 
-#1.  only one parameter set is shown
+#1. Only one parameter set is shown
 
 p = 5 # set ID for parameter set
 result_grid[p,]
@@ -31,126 +31,11 @@ gp <- ggplot(df_tmp, aes(x = M, y = relative_bias)) +
         legend.text = element_text(size=10))
 plot(gp)
 
-
-#2. several n are shown
-out_grid = result_grid %>% 
-  tibble::rownames_to_column(var = "rowname")
-use_grid = out_grid %>%
-  dplyr::filter( (N_0==10^3)&(N_1==10^3) ) %>%
-  dplyr::filter(m==0.1) %>%
-  dplyr::filter(flag_constant==0)
-use_id = use_grid %>%
-  dplyr::select(rowname) %>%
-  dplyr::pull() %>% as.numeric()  
-n_index = use_grid %>%
-  dplyr::select(nP_0) %>%
-  dplyr::pull() %>% as.numeric() 
-migration_number = use_grid$N_0[1]/2 * use_grid$m[1]
-
-for ( i in 1:5){
-  tmp_use_M_est = get(paste0("M_est",i))[use_id,]
-  rownames(tmp_use_M_est) = paste0("n = ",n_index)
-  df = tmp_use_M_est %>% t() %>% as_tibble() 
-  tb_tmp = tidyr::gather(df) %>% 
-    dplyr::mutate(M = paste0("M",i)) %>%
-    dplyr::mutate(relative_bias = (value - 2*migration_number) / (2*migration_number))
-  assign(paste0("tb", i), tb_tmp)
-}
-tb = dplyr::full_join(tb1,tb2) %>%
-  dplyr::full_join(tb3) %>%
-  dplyr::full_join(tb4) %>%
-  dplyr::full_join(tb5)
-
-gp <- ggplot(tb, aes(x = as_factor(M), y = relative_bias, fill = as_factor(key))) +
-  scale_fill_grey(start = 0.6, end = 0.9) + theme_classic() +
-  geom_violin(adjust=1,trim=T) +
-  geom_hline(yintercept=0,size=0.5,alpha=.5,linetype=1) +
-  stat_summary(fun = "mean", size=2, geom="point",colour ="black",
-               position=position_dodge(width = 0.9))+
-  xlab("Estimator of migration number") +
[…]

### 2022-02-21 latex/ms.tex
enhance README.md

@@
 \usepackage[normalem]{ulem} %%
-\linenumbers
+%\linenumbers
 \usepackage{bm}
@@
    }
-\date{Manuscript Intended for \emph{Molecular Ecology and Resources}, \today}
+\date{Manuscript Intended for \emph{Molecular Ecology Resources}, \today}% Manuscript Intended for \emph{Molecular Ecology and Resources}
 \maketitle
@@
 We also evaluate the detailed performance of the estimators by running an individual-based model, providing a guidance for sample sizes to ensure the required accuracy and precision.
-Furthermore, in the face of the current situation where there is little effective method for estimating adult movement especially when populations cannot be genetically distinct, we discuss the usefulness of this proposed sibship assignment method in terms of conservation biology and wildlife management.
+Furthermore, in the face of the current situation where there is little effective method for estimating adult movement especially when populations cannot be genetically distinct, we discuss the usefulness of this proposed kinship assignment method in terms of conservation biology and wildlife management.
 \\
 \end{abstract}
-
-\textbf{Key words:} dispersion; sibship assignment; reproductive potential; close-kin mark-recapture\\
+\textbf{Key words:} dispersion; kinship assignment; reproductive potential; close-kin mark-recapture\\
 \textbf{Running head:} Estimating migration numbers using kinship pairs\\
@@
 \section*{ACKNOWLEDGMENTS}
-The author thanks N. Shinohara, N. Suzuki and Y. Tsukahara for fruitful discussions. This work was supported by JSPS KAKENHI Grant Number 19K06862 and 20H03012.
+The author thanks N.
+Shinohara, N.
+Suzuki and Y.
+Tsukahara for fruitful discussions.
+The author also thanks W.M.
+Iwasaki for helping me in coding C{++}.
+This work was supported by JSPS KAKENHI Grant Number 19K06862 and 20H03012.
 
@@
 \pi_{\rm HS,bet} &\approx \frac{4}{M}  \frac{ \mathbb{E}\left[ \sum_{l=1}^M \lambda_{M,l,1} \sum_{l=1}^M \lambda_{M,l,2} \right]} {\mathbb{E}\left[ \left(\sum_{l=1}^{M} \lambda_{M,l,1} + \sum_{i=M+1}^{N_1} \lambda_{i,1}\right) \left(\sum_{l=1}^{M} \lambda_{M,l,2} + \sum_{j=M+1}^{N_2} \lambda_{j,2}\right) \right] }\nonumber\\
-&= \frac{4}{M} \frac{ M^2 {\bar \lambda_{M,1}} {\bar \lambda_{M,2}} } { \left( M {\bar \lambda_{M,1}} + (N_1 - M) {\bar \lambda_1} \right) + \left( M {\bar \lambda_{M,2}} + (N_2 - M) {\bar \lambda_2} \right)}.
+&= \frac{4}{M} \frac{ M^2 {\bar \lambda_{M,1}} {\bar \lambda_{M,2}} } { \left( M {\bar \lambda_{M,1}} + (N_1 - M) {\bar \lambda_1} \right) \left( M {\bar \lambda_{M,2}} + (N_2 - M) {\bar \lambda_2} \right)}.
 \label{App3}

### 2022-02-21 handle_main_2.R

@@ -1,10 +1,10 @@
 # ---
 # one test-run and drawing result
-# 1: simulation 6 estimators with fixed parameters
+# 1: simulation 5 estimators with fixed parameters
 # 2: draw
 # ---
 
-# 1: simulation 6 estimators with fixed parameters
+# 1: simulation 5 estimators with fixed parameters
 
 setwd("~/git/CKMRmig/")
 rm(list=ls())
@@ -87,8 +87,8 @@ for (rep in 1:REP) {
   
   pi_est_HS[rep] = (HS_01[rep]) / (sampled_child_number_0 * sampled_child_number_1) 
   pi_est_PO[rep] = (PO_01[rep]) / (sampled_child_number_0 * (sampled_father_number_1+sampled_mother_number_1))  
-  N_0_est[rep] = (2*sampled_child_number_0 * (sampled_father_number_0+sampled_mother_number_0) + 1) / (PO_0[rep] + 1)
-  N_1_est[rep] = (2*sampled_child_number_1 * (sampled_father_number_1+sampled_mother_number_1) + 1) / (PO_1[rep] + 1)
+  N_0_est[rep] = (2*sampled_child_number_0 * (sampled_father_number_0+sampled_mother_number_0) ) / (PO_0[rep] + 1)
+  N_1_est[rep] = (2*sampled_child_number_1 * (sampled_father_number_1+sampled_mother_number_1) ) / (PO_1[rep] + 1)
   M_est0_HS[rep] = pi_est_HS[rep] * (2*init_parent_pair_number_0) * (2*init_parent_pair_number_1) / 4
   M_est0_PO[rep] = pi_est_PO[rep] * (2*init_parent_pair_number_0) * (2*init_parent_pair_number_1) / 2
   M_est0_both[rep] = ( (2*init_parent_pair_number_0) * (2*init_parent_pair_number_1) / 2 / sampled_child_number_0 ) * ( (HS_01[rep]+PO_01[rep]) / (2*sampled_child_number_1 + (sampled_father_number_1+sampled_mother_number_1)) )

### 2022-02-24 latex/ms.tex
reflect revision in abst and intro

@@
 \begin{abstract}
-This study develops estimators of the contemporary migration number and rate of adults for iteroparous species between two populations.
-The proposed estimators are based on both known half-sibling (HS) and/or parent-offspring (PO) relationships observed between the populations across the breeding seasons.
-The rationale is that such HS and PO pairs have information as to how often parental movements during the breeding interval are realized.
-Our method allows for variance of the average number of offspring per parent within and between populations.
-In addition, coupled with PO pairs found within population, the estimators can be obtained only from genetic data.
-Roughly speaking, a sample size of square root of population size is required for obtaining meaningful information on migration.
-We also evaluate the detailed performance of the estimators by running an individual-based model, providing a guidance for sample sizes to ensure the required accuracy and precision.
-Furthermore, in the face of the current situation where there is little effective method for estimating adult movement especially when populations cannot be genetically distinct, we discuss the usefulness of this proposed kinship assignment method in terms of conservation biology and wildlife management.
+In this paper, we describe the development of estimators for the contemporary migration number and rate of adults of iteroparous species between two populations.
+The proposed estimators are based on known half-sibling (HS) and/or parent--offspring (PO) relationships observed between the populations across breeding seasons.
+The rationale is that the HS and PO pairs exhibit information about the occurrence frequency of parental movements during the breeding interval.
+The proposed method allows for variance in the average number of offspring per parent both within and between populations.
+In addition, coupled with the PO pairs found within the population, the estimators can be obtained from only genetic data.
+Generally, a sample size representing the square root of the population size is required to obtain meaningful information regarding migration.
+We describe a detailed evaluation of the performance of the estimators by running an individual-based model, and the results provide guidance regarding sample sizes to ensure the required accuracy and precision.
+Furthermore, given that there are few effective methods to estimate adult movement (especially when populations cannot be genetically distinct), we discuss the usefulness of this proposed kinship assignment method in terms of conservation biology and wildlife management.
 \\
@@
 
-In conservation and wildlife management, estimating the current ecological information is essential for monitoring population levels and proposing management strategies.
-Contemporary migration rate, the recent rate of movement of individuals or gametes between pre-defined populations, is a critical component to determine the current degree of gene flow and synchrony among the population \cite[]{Waples_2006_MolEcol, https://doi.org/10.1111/j.1365-294X.2010.04688.x}.
-Therefore, estimation of contemporary migration rate provides information about the degree of genetic differentiation and demographic dependency, which can delineate evolutionarily significant units and identify appropriate management units \cite[]{moritz1994defining, PALSBOLL200711}.
-In addition, the availability of migration rate can link to underlying population dynamics, allowing for a more precise and flexible evaluation of a management for many relevant topics including stock assessment in fisheries \cite[]{hampton2001spatially} and the invasive species control \cite[]{doi:10.1146/annurev.ecolsys.32.081501.114037}.
+In conservation and wildlife management, estimating current ecological information is essential for monitoring population levels and proposing effective management strategies.
+The contemporary migration rate, i.e., the recent rate of movement of individuals or gametes between predefined populations, is a critical component when determining the current degree of gene flow and synchrony among the population \cite[]{Waples_2006_MolEcol, https://doi.org/10.1111/j.1365-294X.2010.04688.x}.
+Therefore, estimating the contemporary migration rate provides information about the degree of genetic differentiation and demographic dependency, which can delineate evolutionarily significant units and identify appropriate management units \cite[]{moritz1994defining, PALSBOLL200711}.
+In addition, the availability of migration rate can link to underlying population dynamics, allowing for more precise and flexible evaluations of management practices, e.g., stock assessment in fisheries \cite[]{hampton2001spatially} and invasive species control \cite[]{doi:10.1146/annurev.ecolsys.32.081501.114037}.
 
 % 2: Mark recapture method can handle ecological scale but may miss the small migration rate
+%KOKOMADE enago%%%
 

### 2022-03-02 latex/ms.tex
reflect revision

@@
 % 2: Mark recapture method can handle ecological scale but may miss the small migration rate
-%KOKOMADE enago%%%
 
-There are essentially two approaches for estimating the contemporary migration rate.
-The first is to use the mark-recapture (MR) method that estimates migration rate along with other population parameters \cite[]{kery2011bayesian, Thorson_2021}.
-The rational is that, for example, conventional tags provide release and recovery location at known release and recovery dates, generating a movement fraction matrix among strata per given time interval.
-While this direct method is relatively easy to interpret, it is generally hampered by several sources of uncertainties, e.g., tag loss, tagging-related mortality, and time-varying reporting rate \cite[]{hilborn2013quantitative}.
-In addition, the MR method for estimating migration rate is generally limited in practice to situations where collection of a sufficient number of adult sample at multiple sites in a short period is available.
+Essentially, there are two approaches to estimate the contemporary migration rate.
+The first approach involves using the mark-recapture (MR) method, which estimates the migration rate along with other population parameters \cite[]{kery2011bayesian, Thorson_2021}.
+Here, the rational is that, for example, conventional tags provide release and recovery location information for known release and recovery dates, which generates a movement fraction matrix among strata per given time interval.
+This direct method is relatively easy to interpret; however, it is generally hampered by several uncertainties, e.g., tag loss, tagging-related mortality, and time-varying reporting rates \cite[]{hilborn2013quantitative}.
+In addition, the MR method is generally limited in practice to situations where collection of a sufficient number of adult samples at multiple sites is possible over a short period.
 
@@
 
-The second is to use numerous genetic markers to assign individuals to source populations, allowing the inference of recent migration \cite[since][]{https://doi.org/10.1111/j.1365-294X.1995.tb00227.x}.
-The model of \cite{Wilson_2003}, which is one of such population assignment methods and implemented in a software `BayesAss', can output the point estimate as an element of a current migration matrix.
-However, as evaluated by several authors \cite[]{https://doi.org/10.1111/j.1365-294X.2007.03218.x, https://doi.org/10.1111/mec.12806}, the accuracy of estimated migration rates by the model is valid only when populations are highly differentiated (e.g., $F_{\rm ST}\ge0.05$), suggesting that it may be difficult to infer the degree of demographic dependency among populations since demographic independency is realized even if there are many migrants.
+The second approach involves using numerous genetic markers to assign individuals to source populations, thereby allowing the inference of recent migration \cite[since][]{https://doi.org/10.1111/j.1365-294X.1995.tb00227.x}.
+The previously developed model of \cite{Wilson_2003}, which is one of the population assignment methods and implemented in a software `BayesAss', can output the point estimate as an element of the current migration matrix.
+However, according to several papers \cite[]{https://doi.org/10.1111/j.1365-294X.2007.03218.x, https://doi.org/10.1111/mec.12806}, the accuracy of the migration rates estimated by this model is valid only when populations are highly differentiated (e.g., $F_{\rm ST}\ge0.05$), which suggests that it may be difficult to infer the degree of demographic dependency among populations because demographic independency is realized even if there are many migrants.
 
@@
 
-Parental assignments, which is based on genetic markers and often used as a complement to the population assignment method in ecological studies, also provide information about the current level of migration.
-In contrast to the population assignment method, the parental assignment method does not require the population differentiation \cite[]{https://doi.org/10.1111/mec.12806}.
-However, the current methodology focuses on estimating dispersal kernels and, for estimating migration rate, requires the assumption that adults are not migrant, e.g., pollen/seeds dispersal in plants \cite[]{doi:10.1080/07352689.2010.481167} or larval drift in marine animals \cite[]{https://doi.org/10.1111/eva.12288}; thus, it may not apply the adult movement of iteroparous species (i.e., multiple reproductive cycles during the lifetime) that may change the spawning ground for each breeding season.
+Parental assignments, which are based on genetic markers and are frequently used to complement the population assignment method in ecological studies, also provide information about the current level of migration.
+In contrast to the population assignment method, the parental assignment method does not require population differentiation \cite[]{https://doi.org/10.1111/mec.12806}; however, the current methodology focuses on estimating dispersal kernels and, to estimate the migration rate, requires the assumption that adults are not migrant, e.g., pollen/seed dispersal in plants \cite[]{doi:10.1080/07352689.2010.481167} or larval drift in marine animals \cite[]{https://doi.org/10.1111/eva.12288}.
+Thus, this method may not consider the adult movement of iteroparous species, i.e., multiple reproductive cycles during the lifetime, which may change the spawning ground for each breeding season.
 
 % 5: CKMR can cover the range that Mark recapture can handle with more realistic situations
+%KOKOMADE enago%%%
 

### 2022-03-03 latex/ms.tex
reflect revision

@@
 % 5: CKMR can cover the range that Mark recapture can handle with more realistic situations
-%KOKOMADE enago%%%
 
-Close-kin mark-recapture (CKMR) is a recently developed method for estimating adult population size along with life-history parameters that utilizes the known kinship information in a sample \cite[][and references therein]{https://doi.org/10.1111/faf.12615}.
-The rationale is that the presence of a kinship pair in the sample is analogous to the recapture of a marked individual in the MR method.
-Kinship pairs in the sample are less likely to be observed in larger populations; thus, the number of kinship pairs may reflect an adult number in the population \cite[]{bravington2016close}.
-While recent studies of CKMR argued that availability of kinship information in estimating the migration rate \cite[]{https://doi.org/10.1002/ece3.6296, 10.1093/icesjms/fsac002}, the CKMR-based migration estimation has not been well developed and rigorously examined in a simulation study.
+Close-kin mark-recapture (CKMR) is a recently developed method to estimate adult population size along with life-history parameters that utilizes the known kinship information in a sample \cite[][and references therein]{https://doi.org/10.1111/faf.12615}.
+In the CKMR method, the presence of a kinship pair in the sample is analogous to the recapture of a marked individual in the MR method.
+Note that kinship pairs in the sample are less likely to be observed in larger populations; thus, the number of kinship pairs may reflect the number of adults in the population \cite[]{bravington2016close}.
+While recent studies of CKMR argued that availability of kinship information to identify metapopulation structure \cite[]{https://doi.org/10.1002/ece3.6296, 10.1093/icesjms/fsac002}, CKMR-based migration estimation has not been well developed or examined extensively in a simulation study.
 
@@
 
-In this study, we propose a new method for estimating the contemporary migration number or rate of adults between two pre-defined populations in iteroparous species, where the migration direction is specified.
-Assuming that kinships are genetically detected without any error, this method is based on the numbers of half-sibling (HS) and parent-offspring (PO) pairs in a sample.
-Sampling can be invasive or non-invasive and is completed at two breeding seasons; sampling offspring (young-of-year individuals) and parents probably shares PO relationship with sampled offspring in the one population at the first breeding season and in the another population at the second breeding season.
-The rationale is that the number of HS and PO pairs found between populations have information as to how often parental movements during the breeding interval are realized.
-Our model explicitly incorporates reproductive variation within and between populations, making it possible to target a species whose fertility is affected by environmental differences between populations.
+Thus, in this paper, we propose a method to estimate the contemporary migration number or rate of adults between two predefined populations in iteroparous species, where the migration direction is specified.
+Under the assumption that kinships are genetically detected without error, the proposed method is based on the numbers of half-sibling (HS) and parent--offspring (PO) pairs in a sample.
+Here, sampling can be either invasive or noninvasive and is completed at two breeding seasons; sampling offspring (young-of-year individuals) and parents likely share a PO relationship with the offspring sampled in one population at the first breeding season and in the other population at the second breeding season.
+The rationale for estimating the migration number or rate is that the number of HS and PO pairs found between populations contains information about the frequency of parental movements during the breeding interval.
+Our model explicitly incorporates reproductive variation within and between populations, thereby making it possible to target a species whose fertility is affected by environmental differences between populations.
 First, we explain the modeling assumption and sampling scheme.
@@
 Finally, by running an individual-based model, we investigate the performance of the estimator and provide a guide for a sample size.
-It is noteworthy that our modeling framework can be applied to diverse animal species.
-However, the description of the model focuses on fish species, which are presently the best candidate target of our proposed method.
+Note that the proposed modeling framework can be applied to diverse animal species; however, the description of the model focuses on fish species, which are presently the best target candidate for the proposed method.
 
 \section{Theory}\label{sec2}
-In this section, we present the theoretical foundation for estimating a migrant number and migration rate of iteroparous species using HS or PO pairs, which are found between two populations with a different sample timing.
-While the estimators can hold under flexible assumptions for reproduction (see {\bf Appendix 2}), here we assume a relatively simple situation for explanation purposes.
-The main symbols used in the current paper are summarized in {\bf Table \ref{symbols}}.
+Here, we present the theoretical foundation of estimating a migrant number and migration rate of iteroparous species using HS or PO pairs found between two populations with different sample timing.
+Note that the estimators can hold under flexible assumptions for reproduction ({\bf Appendix 2}); however, here, we assume a relatively simple case.
+The main symbols used in this paper are summarized in {\bf Table \ref{symbols}}.
 
@@
 
-Suppose that we have a set of two populations labelled 1 and 2 where random mating occurs within each population and that parents can move to the other population after the end of the reproductive season.
-Hereafter, without loss of generality, we consider the movement of parents in the direction from the population 1 to the population 2 and focus on the migration number or rate, and that is what we attempt to estimate.
-In this framework, we show that considering two reproductive seasons (hereafter, we call them "the first year" and "the second year") is enough to estimate it.
-{\bf Figure \ref{cartoon}a} presents a schematic representation of the kinship relationships and movements of parents.
+Assume that we have a set of populations 1 and 2, where random mating occurs within each population and parents can move to the other population after the reproductive season ends.
+Without loss of generality, we consider the movement of parents from population 1 to population 2, and we focus on estimating the migration number or rate.
+In this framework, we demonstrate that considering two reproductive seasons (hereafter referred to as "the first year" and "the second year") is sufficient to estimate the migration number or rate.
+{\bf Figure \ref{cartoon}a} shows a schematic representation of the kinship relationships and parent movements.
 
-Suppose there are $N_1$ parents in the population 1 at the beginning of the first year.
-Each parent produces offspring in which the number is governed by the parent's reproductive potential, denoted by $\lambda_{i,1}$ ($i=1,2,\ldots,N_1$).
-After the reproductive season, part of the parents would start to moving towards the population 2; $M$ survived migrants arrive in the population 2 so that there are $N_2$ parents in the population 2 at the beginning of the second year ($M \le N_1$ and $M \le N_2$).
-Similar to the population 1, $N_2$ parents produce offspring in which the number is governed by $\lambda_{j,2}$ ($j=1,2,\ldots,N_2$).
-The reproductive potential is determined by several factors and its details are summarized in {\bf Appendix 1}; theoretically speaking, the number of offspring for each parent is set as a random variable with mean $\lambda_{i,1}$ or $\lambda_{j,2}$.
+Assume that there are $N_1$ parents in population 1 at the beginning of the first year.
+Each parent produces a number of offspring that is governed by the parent's reproductive potential, which is denoted by $\lambda_{i,1}$ ($i=1,2,\ldots,N_1$).
+After the reproductive season, some parents begin to move toward population 2.
+Here $M$ survived migrants arrive in population 2; thus, there are $N_2$ parents in population 2 at the beginning of the second year ($M \le N_1$ and $M \le N_2$).
+Similar to population 1, $N_2$ parents produce a number of offspring governed by $\lambda_{j,2}$ ($j=1,2,\ldots,N_2$).
+Note that reproductive potential is determined by several factors.
+Additional details about reproductive potential can be found in {\bf Appendix 1}.
+Theoretically, the number of offspring for each parent is set as a random variable with mean $\lambda_{i,1}$ or $\lambda_{j,2}$.
 
@@
 To estimate the migration number or rate, we utilize the number of HS and/or PO pairs observed in a sample.
-In the both populations, $n_{\rm O, 1}$ and $n_{\rm O, 2}$ offspring are randomly sampled in the first and second year, respectively, which are identified as young-of-year individuals without errors.
-Additionally, $n_{\rm P, 1}$ and $n_{\rm P, 2}$ parents are randomly sampled immediately after the end of the reproductive season in the first and second year, respectively.
-For mathematical tractability, parents have to survive during the reproductive season; therefore, both mother and father of a certain offspring have a potential to be sampled even in the same year.
-It should be noted that all the four kinds of a sample (i.e., $n_{\rm P, 1}$, $n_{\rm P, 2}$, $n_{\rm O, 1}$, and $n_{\rm O, 2}$) are not always required for estimating migration number or rate; what kinds of a sample are needed depends on the situation, as explained later.
-Up to the subsection 2.6, we only focus HS pairs and PO pairs found between the two populations.
-For the applicability of fishery management, we assume invasive sampling procedure, preventing the finding of a parent-offspring pair such that a parent and offspring is sampled in the population 1 and 2, respectively.
-{\bf Figure~\ref{cartoon}b} illustrates a timeline of sampling scheme for hypothetical populations.
+In both populations, $n_{\rm O, 1}$ and $n_{\rm O, 2}$ offspring are sampled randomly in the first and second year, respectively, which are identified as young-of-year individuals without error.
+In addtion, $n_{\rm P, 1}$ and $n_{\rm P, 2}$ parents are sampled randomly immediately after the end of the reproductive season in the first and second years, respectively.
+For mathematical tractability, the parents must survive the reproductive season; therefore, both the mother and father of a give offspring have the potential to be sampled in the same year.
+Note that all the four sample types, i.e., $n_{\rm P, 1}$, $n_{\rm P, 2}$, $n_{\rm O, 1}$, and $n_{\rm O, 2}$, are not always required to estimate the migration number or rate.
+The types of required samples depends on the given situation, which is explained later.
+Up to subsection 2.6, we focus on only the HS and PO pairs found between populations 1 and 2.
+To apply the proposed method to the fishery assessment, we assume an invasive sampling procedure, which prevents us from finding a PO pair such that a parent and offspring is sampled in population 1 and 2, respectively.
+{\bf Figure~\ref{cartoon}b} shows the timeline of the sampling scheme for these hypothetical populations.
 
-In the example depicted in {\bf Fig~\ref{cartoon}a}, five offspring and four parents are sampled in the population 1 and four offspring and six parents are sampled in the population 2, and two HS and one PO pairs found between the two populations are observed.
-In addition, there are several PO pairs observed within the same population, which are available to estimate parent numbers, as explained in the following section.
-In our modeling framework, if full-sibling (FS) relationship is found, we count it as two HS pairs.
-The numbers of HS and PO pairs found between the two populations are determined by pairwise comparison of all the sample individuals ($n_{\rm O,1}\times n_{\rm O,2}$ and $n_{\rm O,1}\times n_{\rm P,2}$ comparisons, respectively).
+In the example shown in {\bf Fig.~\ref{cartoon}a}, five offspring and four parents are sampled in population 1, four offspring and six parents are sampled in population 2, and two HS pairs and a single PO pair are observed between the two populations 1 and 2.
+In addition, there are several PO pairs observed within the same population, which are available to estimate parent numbers, which is explained in subsection 2.7.
+In our modeling framework, if a full-sibling relationship is found, we count it as two HS pairs.
+The numbers of HS and PO pairs found between the two populations are determined via pairwise comparison of all the sample individuals, i.e., comparisons of $n_{\rm O,1}\times n_{\rm O,2}$ and $n_{\rm O,1}\times n_{\rm P,2}$, respectively.
 
@@
 
-Here, we consider the probability that two offspring sampled in the population 1 and 2 share an HS relationship with an arbitrary mother or father, denoted by $\pi_{\rm HS, bet}$.
-For the explanation purpose, we assume equal reproductive potential among parents up to the subsection 2.7, although this assumption can be relaxed for most of the case (see details in {\bf Appendix 2}).
-$\pi_{\rm HS, bet}$ can be partitioned into the three probabilities: (i) the probability that sampled offspring in the population 1 born to a parent that safely arrives in the population 2 (hereafter, called "migrant"); (ii) the probability that sampled offspring in the population 2 born to a migrant; and (iii) the probability that the migrant of a sampled offspring in the population 1 and the migrant of a sampled offspring in the population 2 are identical.
+Here, we consider the probability that two offspring sampled in populations 1 and 2 will share an HS relationship with an arbitrary mother or father, denoted by $\pi_{\rm HS, bet}$.
+Note that we assume equal reproductive potential among parents (up to subsection 2.7) although this assumption can be relaxed for most of the case (see {\bf Appendix 2} for additional information).
+Here, $\pi_{\rm HS, bet}$ can be partitioned into three probabilities, i.e., (i) the probability that sampled offspring in population 1 born to a parent that safely arrives in population 2 (hereafter, referred to as a "migrant"); (ii) the probability that sampled offspring in population 2 are born to a migrant; and (iii) the probability that the migrant of a sampled offspring in population 1 and the migrant of a sampled offspring in population 2 are identical.
 
-To assess these probabilities, recall there must be two parents of arbitral offspring; the first probability is the sum of father-offspring and mother-offspring relationship, which can be written by $r_{\rm M}M/(r_{\rm S,1}N_{1}) + (1 - r_{\rm M})M/((1-r_{\rm S,1})N_{1})$, where $r_{\rm M}$ and $r_{\rm S,1}$ indicates sex ratio of parents in the migrants and in the whole of the population 1, respectively.
-Assuming $r_{\rm M} = r_{\rm S,1}$, the probability is simplified as $2M/N_{1}$.
-Similarly, the second probability is simplified as $2M/N_{2}$, implying the assumption of equal sex ratio in the migrants and the others.
-The third probability corresponds to the probability that randomly selected two migrants are identical, that is $1/M$.
-Taken together, we obtain
+To assess these probabilities, recall that there must be two parents of arbitral offspring.
+The first probability is the sum of the father--offspring and mother--offspring relationship, which can be expressed as $r_{\rm M}M/(r_{\rm S,1}N_{1}) + (1 - r_{\rm M})M/((1-r_{\rm S,1})N_{1})$, where $r_{\rm M}$ and $r_{\rm S,1}$ indicate the sex ratio of the parents in the migrants and in all of the population 1, respectively.
+Under the assumption that $r_{\rm M} = r_{\rm S,1}$, the probability is simplified to $2M/N_{1}$.
+Similarly, the second probability is simplified to $2M/N_{2}$, which implies the assumption regarding an equal sex ratio in migrants and others.
+The third probability corresponds to the probability that two randomly selected migrants are identical, i.e., $1/M$.
+Taken together, we obtain the following:
 \begin{align}
@@
 \end{align}
-This form holds under a flexible setting for the reproductive potential, such as a situation with random variable of $\lambda_{i,1}$ and $\lambda_{j,2}$, as noted in {\bf Appendix 2}.
-If all $N_1$ parents safely move to the population 2 (i.e., $M = N_1$), $\pi_{\rm HS,bet}$ equals $4/N_2$; meanwhile, if the population 2 consists only of migrants (i.e., $M = N_2$), $\pi_{\rm HS,bet}$ equals $4/N_1$.
-These probabilities in the extreme cases are similar forms to HS probability that is randomly sampled from two different cohorts within a population \cite[]{bravington2016close}.
+This form holds under a flexible setting for the reproductive potential, e.g., a situation with random variable of $\lambda_{i,1}$ and $\lambda_{j,2}$ ({\bf Appendix 2}).
+If all $N_1$ parents safely move to population 2 (i.e., $M = N_1$), $\pi_{\rm HS,bet}$ equals $4/N_2$.
+In addition, if population 2 comprises only migrants (i.e., $M = N_2$), $\pi_{\rm HS,bet}$ equals $4/N_1$.
+In extreme cases, these probabilities take similar forms as the HS probability, which is sampled randomly from two different cohorts within a population \cite[]{bravington2016close}.
 
-Let $H_{\rm HS,bet}$ be the number of HS pairs found in offspring samples of size $n_{\rm O, 1}$ and $n_{\rm O, 2}$.
-Assuming that the total number of HS pairs in the population is much higher than $H_{\rm HS,bet}$, the distribution is approximated by a binomial form (i.e., $H_{\rm HS,bet} \sim {\rm Binom}[\pi_{\rm HS,bet}, n_{\rm O, 1} n_{\rm O, 2}]$); thus, the theoretical expectation of $H_{\rm HS,bet}$ is
-
+Let $H_{\rm HS,bet}$ be the number of HS pairs found in the offspring samples of size $n_{\rm O, 1}$ and $n_{\rm O, 2}$.
+Assuming the total number of HS pairs in the population is much greater than $H_{\rm HS,bet}$, the distribution is approximated by a binomial form (i.e., $H_{\rm HS,bet} \sim {\rm Binom}[\pi_{\rm HS,bet}, n_{\rm O, 1} n_{\rm O, 2}]$).
+Thus, the theoretical expectation of $H_{\rm HS,bet}$ is given as follows:
 \begin{align}
@@
 \end{align}
-where $m$ indicates the migration rate satisfying $M = mN_{1}$.
-The observed number of HS pairs in a sample found between the two populations is defined by $\widetilde{H}_{\rm HS, bet}$, and $\mathbb{E}[H_{\rm HS, bet}]$ in Equation \ref{HS-2-1} is replaced by $\widetilde{H}_{\rm HS, bet}$, generating the linear estimator of $M$:
+where $m$ is the migration rate satisfying $M = mN_{1}$.
+The observed number of HS pairs in a sample found between the populations 1 and 2 is defined by $\widetilde{H}_{\rm HS, bet}$, and $\mathbb{E}[H_{\rm HS, bet}]$ in Equation \ref{HS-2-1} is replaced by $\widetilde{H}_{\rm HS, bet}$, thereby generating the linear estimator of $M$:
 
@@
 \end{align}
-In this paper, a ``tilde'' and ``hat'' indicates the observation and estimator of a variable, respectively.
-Similarly, $\mathbb{E}[H_{\rm HS, bet}]$ in Equation \ref{HS-2-2} is replaced by $\widetilde{H}_{\rm HS, bet}$, generating the linear estimator of $m$:
+In this paper, a ``tilde'' and ``hat'' symbols indicates the observation and estimator of a variable, respectively.
+Similarly, $\mathbb{E}[H_{\rm HS, bet}]$ in Equation \ref{HS-2-2} is replaced by $\widetilde{H}_{\rm HS, bet}$, which generates the linear estimator of $m$:
 
@@
 \end{align}
-Subscription of these estimators indicates the numbering of proposed estimators appeared in this paper, which is summarized in Table \ref{parameter}.
+The subscripts associated with these estimators indicate the numbering of the proposed estimators, which is summarized in Table \ref{parameter}.
 
@@
 
+%KOKOMADE enago%%%
 \subsection{PO pair-based model}

### 2022-03-04 latex/ms.tex
reflect revision

@@
 
-%KOKOMADE enago%%%
 \subsection{PO pair-based model}
 
-Next, we consider the probability that offspring sampled in the population 1 and a parent sampled in the population 2 share an PO relationship, denoted by $\pi_{\rm PO, bet}$.
-$\pi_{\rm PO, bet}$ can be partitioned into the three probabilities: (i) the probability that sampled offspring in the population 1 born to a migrant; (ii) the probability that a migrant is sampled; and (iii) the probability that the migrant of a sampled offspring in the population 1 and the migrant sampled in the population 2 are identical.
-The first and third probabilities are the same as the one introduced in the previous subsection, that is, $2M/N_{1}$ and $1/M$.
-The second probability is $M/N_{2}$ by definition.
-Taken together, we obtain
+In the folowing, we consider the probability that offspring sampled in population 1 and a parent sampled in population 2 share a PO relationship, denoted by $\pi_{\rm PO, bet}$.
+$\pi_{\rm PO, bet}$ can be partitioned into the above mentioned probabilities.
+Note that probabilities (i) and (iii) are the same as that introduced in the previous subsection, i.e., $2M/N_{1}$ and $1/M$.
+In addition, probability (ii) is $M/N_{2}$ by definition.
+Taken together, we obtain the following:
 \begin{align}
@@
 \end{align}
-This form also holds under a flexible setting for the reproductive potential, as noted in {\bf Appendix}.
-If all $N_1$ parents safely move to the population 2 (i.e., $M = N_1$), $\pi_{\rm PO,bet}$ equals $2/N_2$; meanwhile, if the population 2 consists only of migrants (i.e., $M = N_2$), $\pi_{\rm PO,bet}$ equals $2/N_1$.
-These probabilities in the extreme cases are similar forms to PO probability that is randomly sampled within a population \cite[]{bravington2016close}.
+This form also holds under a flexible setting for the reproductive potential, as noted in the {\bf Appendix 2}.
+Here, if all $N_1$ parents safely move to population 2 (i.e., $M = N_1$), $\pi_{\rm PO,bet}$ equals $2/N_2$.
+In addition, if population 2 comprises only migrants (i.e., $M = N_2$), $\pi_{\rm PO,bet}$ equals $2/N_1$.
+In extreme cases, these probabilities take similar forms to the PO probability that is sampled randomly within a population \cite[]{bravington2016close}.
 
 Let $H_{\rm PO,bet}$ be the number of PO pairs found in offspring samples of size $n_{\rm O, 1}$ and parent samples of size $n_{\rm P, 2}$.
-Assuming that the total number of PO pairs in the two populations is much higher than $H_{\rm PO,bet}$, the distribution is approximated by a binomial form (i.e., $H_{\rm PO,bet} \sim {\rm Binom}[\pi_{\rm PO,bet}, n_{\rm O, 1} n_{\rm P, 2}]$); thus, the theoretical expectation of $H_{\rm PO,bet}$ is
+Under the assumption that the total number of PO pairs in the two populations is much greater than $H_{\rm PO,bet}$, the distribution is approximated by a binomial form (i.e., $H_{\rm PO,bet} \sim {\rm Binom}[\pi_{\rm PO,bet}, n_{\rm O, 1} n_{\rm P, 2}]$).
+Thus, the theoretical expectation of $H_{\rm PO,bet}$ is expressed as follows:
 \begin{align}
@@
 \end{align}
-The observed number of PO pairs in a sample is defined by $\widetilde{H}_{\rm PO, bet}$, and $\mathbb{E}[H_{\rm PO, bet}]$ in Equations \ref{PO-2-1} and \ref{PO-2-2} are replaced by $\widetilde{H}_{\rm PO, bet}$, generating the linear estimator of $M$ and $m$:
+The observed number of PO pairs in a sample is defined by $\widetilde{H}_{\rm PO, bet}$, and $\mathbb{E}[H_{\rm PO, bet}]$ in Equations \ref{PO-2-1} and \ref{PO-2-2} are replaced by $\widetilde{H}_{\rm PO, bet}$, which generates the linear estimators of $M$ and $m$ as follows:
 \begin{align}
@@
 
-Proposed estimators are based on the observed number of kinship pairs.
-Their expected number is linearly determined by the number of pairwise comparison (Eqs.~\ref{HS-2-1}-\ref{HS-2-2} and \ref{PO-2-1}-\ref{PO-2-2}), providing guidance for a sample size to ensure the condition that at least one or more kinship pairs can be found.
-The conditions are given by
+The proposed estimators are based on the observed number of kinship pairs.
+Their expected number is linearly determined by the number of pairwise comparison (Eqs.~\ref{HS-2-1}-\ref{HS-2-2} and \ref{PO-2-1}-\ref{PO-2-2}), which provides sample size guidance to ensure the condition that at least one or more kinship pairs can be found.
+The conditions are given as follows:
 \begin{align}
@@
 \end{align}
-Roughly speaking, required sample size to ensure above conditions is that $n>\sqrt{N_2}$, where $n = n_{\rm O, 1}=n_{\rm O, 2}=n_{\rm P, 2}$.
-It should be noted that very tiny $m$, which dramatically increases the required sample size, produces significant genetic differences between two populations.
-In such a case, there are several methods to estimate migration rate by population genetics technique; alternatively, we focus the situation of moderate/large migration rate, which leads little genetic differences between two populations.
+Generally, the required sample size to ensure the above conditions is $n>\sqrt{N_2}$, where $n = n_{\rm O, 1}=n_{\rm O, 2}=n_{\rm P, 2}$.
+Noted that a very small $m$ value, which dramatically increases the required sample size, produces significant genetic differences between the two populations.
+In such cases, there are several methods to estimate migration rate using population genetics technique.
+Alternatively, we focus on moderate/large migration rate, which yields little genetic differences between the two populations.
 
-Other guidance for the required sample size is obtained by an approximate lower bound on the CV (coefficient of variation) of $M_1$ or $m_1$, defined by $1/\sqrt{H_{\rm HS, bet}}$, which is applied in the context of a classic mark-recapture \cite[]{seber1982estimation} or close-kin mark-recapture \cite[]{bravington2016close}.
-For example, to achieve a 30\% CV, the target of $H_{\rm HS, bet}$ is more than 10, providing the required sample size when population parameters are given (e.g., $N_1$, $N_2$ and $M$).
-Similarly, the CV of $M_2$ or $m_2$, defined by $1/\sqrt{H_{\rm PO, bet}}$, provides the required sample size for estimating $M_2$ or $m_2$.
+Other guidance for the required sample size is obtained by an approximate lower bound on the coefficient of variation (CV) of $M_1$ or $m_1$, which is defined as $1/\sqrt{H_{\rm HS, bet}}$.
+This is applied in the context of classic MR \cite[]{seber1982estimation} or CKMR \cite[]{bravington2016close}.
+For example, to achieve a 30\% CV, the target of $H_{\rm HS, bet}$ is greater than 10, thereby providing the required sample size when the population parameters are given (e.g., $N_1$, $N_2$, and $M$).
+Similarly, the CV of $M_2$ or $m_2$, defined by $1/\sqrt{H_{\rm PO, bet}}$, provides the sample size required to estimate $M_2$ or $m_2$.
 
@@
 
-When the both HS pairs and PO pairs, which are found between populations, are simultaneously available, we can obtain efficient estimators by combined $\widehat{M_1}$ and $\widehat{M_2}$ for migration number:
+When both HS and PO pairs, which are found between populations, are available simultaneously, we can obtain efficient estimators by combined $\widehat{M_1}$ and $\widehat{M_2}$ for migration number: 
 \begin{align}
@@
 \end{align}
-and by combining $\widehat{m_1}$ and $\widehat{m_2}$ for migration rate: 
+and by combining $\widehat{m_1}$ and $\widehat{m_2}$ for the migration rate: 
 \begin{align}
@@
 \end{align}
-For those estimators, $\widetilde{H}_{\rm HS,bet}$ and $\widetilde{H}_{\rm PO,bet}$ is weighted by a sample size $n_{\rm O, 2}$ and $n_{\rm P, 2}$, respectively.
+For those estimators, $\widetilde{H}_{\rm HS,bet}$ and $\widetilde{H}_{\rm PO,bet}$ are weighted by sample size $n_{\rm O, 2}$ and $n_{\rm P, 2}$, respectively.
 
-\subsection{Estimation of parent number by PO pairs found within a population}
+\subsection{Estimation of parent number by PO pairs in a population}
 
-So far, we provide the formulation of the estimators, presented in Equations \ref{HS-3}-\ref{HS-4} and \ref{PO-3}-\ref{PO-4}, is a function with parent numbers for each population ($N_1$ and/or $N_2$); in other words, such estimators are available only when those parent number(s) are known.
-In this subsection, we provide the treatment for estimating the unknown parent numbers by additional usage of PO pairs, producing estimators for migrant number and migration rate that can be obtained only from the genetic data.
+To this point, we have stated that the formulation of the estimators, presented in Equations \ref{HS-3}-\ref{HS-4} and \ref{PO-3}-\ref{PO-4}, is a function with parent numbers for each population ($N_1$ and/or $N_2$).
+In other words, such estimators are available only when the parent number or numbers are known.
+Here, we describe how we estimate unknown parent numbers by additionally using PO pairs to produce estimators for both migration number and rate that can be obtained from only the genetic data.
 
-When PO pairs found in offspring samples and parent samples both from the population 2 in the second year are available, standard estimator of parental number can be obtained \cite[]{bravington2016close}, given by
-
+When PO pairs found in offspring samples and parent samples from population 2 in the second year are available, the standard parental number estimator can be obtained \cite[]{bravington2016close} as follows:
 \begin{align}
@@
 \end{align}
-where $\widetilde{H}_{\rm PO, 2}$ is the observed number of PO pairs found in offspring samples of size $n_{\rm O, 2}$ and parent samples of size $n_{\rm P, 2}$.
-The term ``$+1$'' reduces the bias especially when $\widetilde{H}_{\rm PO, 2}$ is small \cite[e.g.,][]{ecolevol2021p}, where a similar derivation of this bias correction is provided in \cite{Akita_2019}.
-By replacing $N_2$ by $\widehat{N_2}$ in Eqs.~\ref{AP-1} and \ref{AP-2}, we can obtain the following estimators:
-
+where $\widetilde{H}_{\rm PO, 2}$ is the observed number of PO pairs found in the offspring samples of size $n_{\rm O, 2}$ and parent samples of size $n_{\rm P, 2}$.
+This term ``$+1$'' reduces bias, especially when $\widetilde{H}_{\rm PO, 2}$ is small \cite[e.g.,][]{ecolevol2021p}, where a similar derivation of this bias correction is provided in the literature \cite{Akita_2019}.
+By replacing $N_2$ by $\widehat{N_2}$ in Eqs.~\ref{AP-1} and \ref{AP-2}, we obtain the following estimators:
 \begin{align}
@@
 \end{align}
-While estimator of the migrate number (Equation~\ref{AP-4}) requires the (unknown) parent number in the population 1 ($N_{1}$), estimator of the migration rate (Equation~\ref{AP-5}) can be obtained only the observed kinship pairs.
+While the estimator of the migration number (Equation~\ref{AP-4}) requires the (unknown) parent number in population 1 ($N_{1}$), the estimator of the migration rate (Equation~\ref{AP-5}) can be obtained using only the observed number of HS and PO pairs.
 
-Similar to estimating $N_2$, when PO pairs found in offspring samples and parent samples both from the population 1 in the first year are also available, we can obtain the estimator of $N_1$, written by
+Similar to estimating $N_2$, when PO pairs found in offspring samples and parent samples from population 1 in the first year are available, we can obtain the estimator of $N_1$ as follows:
 \begin{align}
@@
 \end{align}
-where $\widetilde{H}_{\rm PO, 1}$ is the observed number of PO pairs found in offspring samples of size $n_{\rm O, 1}$ and parent samples of size $n_{\rm P, 1}$.
-By replacing $N_1$ by $\widehat{N_1}$ in Eq.~\ref{AP-4}, we can obtain the estimator of migration number that can be calculated only from genetic data, given by
+where $\widetilde{H}_{\rm PO, 1}$ is the observed number of PO pairs in the offspring samples of size $n_{\rm O, 1}$ and parent samples of size $n_{\rm P, 1}$.
+By replacing $N_1$ with $\widehat{N_1}$ in Eq.~\ref{AP-4}, we obtain a migration number estimator that can be calculated from only genetic data, which is expressed as follows:
 \begin{align}
@@
 
-Table \ref{parameter} summarizes the conditions for estimators appeared in this paper as to whether $N_1$ and/or $N_2$ are known and which type of samples are needed for estimation, and provides required kinship type for calculating the estimator.
+Table \ref{parameter} summarizes the conditions for estimators in terms of whether $N_1$ and/or $N_2$ are known and which type of samples are required for estimation.
+In addition, Table \ref{parameter} identifies the kinship type required to calculate the estimator.
 
@@
 
-The proposed estimators are derived under the assumption that reproductive potential is the same among individuals.
-As noted in {\bf Appendix 2}, this assumption can be relaxed and the estimators still hold, which is exemplified in iteroparous species that may show significant variation in reproductive potential among individuals.
-Furthermore, the estimators even hold for most of the case where mean reproductive potential are different between population 1 and 2, which is exemplified in the situation that the environmental condition for reproductive success varies between populations.
-The necessary condition is that the migration event does not depends on the degree of reproductive potential (see details in  {\bf Appendix 3}).
+The proposed estimators are derived under the assumption that reproductive potential is equal among individuals.
+As described in {\bf Appendix 2}, this assumption can be relaxed, and the estimators still hold, which is exemplified in iteroparous species that may show significant variation in reproductive potential among individuals.
+In addition, the estimators hold for most cases where the mean reproductive potential differes between populations 1 and 2, e.g., when the environmental condition for reproductive success varies between populations.
+Here, the required condition is that the migration event does not depend on the degree of reproductive potential (refer to {\bf Appendix 3} for additional details).
 
@@
 
-We developed an individual-based model that tracks kinship relationships to evaluate the estimator's performance.
-The population structure was assumed to be identical to that in the development of the estimators.
-The population 1 and 2 comprised $N_1$ and $N_2$ parents with an equal sex ratio, and their offspring number was assumed to follow the geometric distribution with mean ${\bar \lambda_1}$ and ${\bar \lambda_2}$ (i.e., Poisson reproduction with mean $\lambda_{i,1}$ and $\lambda_{j,2}$ which follows the exponential distribution with mean ${\bar \lambda_1}$ and ${\bar \lambda_2}$), respectively.
-Migrant parents were randomly chosen from the population 1 at the end of the first year.
-Each offspring retained the parent's ID, making it possible to trace an HS and PO relationship.
+We developed an individual-based model that tracks kinship relationships to evaluate the performance of the estimators.
+Here, the population structure was assumed to be identical to that in the development of the estimators.
+Population 1 and 2 comprised $N_1$ and $N_2$ parents with an equal sex ratio, and their offspring number was assumed to follow the geometric distribution with mean ${\bar \lambda_1}$ and ${\bar \lambda_2}$ (i.e., Poisson reproduction with mean $\lambda_{i,1}$ and $\lambda_{j,2}$, which follows the exponential distribution with mean ${\bar \lambda_1}$ and ${\bar \lambda_2}$), respectively.
+Migrant parents were selected randomly from population 1 at the end of the first year, and each offspring retained IDs of the parents, thereby making it possible to trace an HS and PO relationship.
 
-Let a parameter set ($N_1$, $N_2$, $M$, ${\bar \lambda_1}$, ${\bar \lambda_2}$, $n_{\rm O,1}$, $n_{\rm O,2}$, $n_{\rm P,1}$, $n_{\rm P,2}$) be given.
-We simulated a population history and a sampling process, which generates proposed estimators; this process was repeated 1000 times, making it possible to construct the distribution of the estimators for each parameter set.
-All scripts and documentation for these analyses are available at \\https://github.com/teTUNAakita/CKMRmig.
+Here, the parameter set ($N_1$, $N_2$, $M$, ${\bar \lambda_1}$, ${\bar \lambda_2}$, $n_{\rm O,1}$, $n_{\rm O,2}$, $n_{\rm P,1}$, $n_{\rm P,2}$) is given.
+We simulated a population history and a sampling process, which generates proposed estimators.
+Note that this process was repeated 1000 times, which allows us to construct the distribution of the estimators for each parameter set.
+All scripts (written by C{++} and R languages) and documentation for these analyses are available at https://github.com/teTUNAakita/CKMRmig.
 
@@
 
-We numerically evaluated the performance of ${\hat M}$s or ${\hat m}$s for the case in which variable reproductive potential among parents.
-Scaled statistical properties of ${\hat m_1}$,  ${\hat m_2}$,  ${\hat m_3}$ and ${\hat m_4}$ are completely the same to ${\hat M_1}$, ${\hat M_2}$, ${\hat M_3}$ and ${\hat M_4}$, hereafter, we only demonstrate the results of ${\hat M_1}$-${\hat M_5}$.
-{\bf Figure~\ref{violins}} illustrates the distribution of the relative bias of ${\hat M}$ for limiting cases where parent and offspring sample numbers are identical (i.e., $n=n_{\rm P,1}=n_{\rm P,2}=n_{\rm O,1}= n_{\rm O,2}$) and parent numbers in the two populations are also identical (i.e., $N=N_1=N_2$).
-Relative bias is calculated by applying outputs of the individual-based model, which is defined as follows: ``(averaged estimator - true value)/true value.'' Full list of parameter sets to evaluate the performance (relative bias and CV of ${\hat M}$s) is summarized in {\bf Table S1} in {\bf Supporting Information}.
+We evaluated the performance of ${\hat M}$s or ${\hat m}$s numerically for a case with variable reproductive potential among parents.
+Here, the scaled statistical properties of ${\hat m_1}$,  ${\hat m_2}$,  ${\hat m_3}$ and ${\hat m_4}$ were completely the same as ${\hat M_1}$, ${\hat M_2}$, ${\hat M_3}$, and ${\hat M_4}$; thus, hereafter, we only demonstrate the results for ${\hat M_1}$-${\hat M_5}$.
+{\bf Figure~\ref{violins}} shows the distribution of the relative bias of ${\hat M}$ for limiting cases where parent and offspring sample numbers are identical (i.e., $n=n_{\rm P,1}=n_{\rm P,2}=n_{\rm O,1}= n_{\rm O,2}$) and parent numbers in the two populations are also identical (i.e., $N=N_1=N_2$).
+The relative bias is calculated by applying the outputs of the individual-based model, which is defined as ``(averaged estimator $-$ true value)/true value.'' Refer to {\bf Table S1} in {\bf Supporting Information} for a full list of the parameter sets used to evaluate performance (relative bias and CV of ${\hat M}$s).
 
@@
 
-First, we evaluated the accuracy of ${\hat M}$s based on their relative bias.
-As expected, for most of the investigated parameter sets, we observed that their relative bias is less than 5\%, as demonstrated in {\bf Table S1} in {\bf Supporting Information}.
-Thus, when the assumption that kinships are detected without any error is satisfied, it is reasonable to call ${\hat M}$s (nearly) unbiased estimators.
+First, we evaluated the accuracy of ${\hat M}$s based on the relative bias.
+As expected, for most of the investigated parameter sets, we observed that their relative bias was less than 5\%, as shown in {\bf Table S1} in {\bf Supporting Information}.
+Thus, when the assumption that kinships are detected without any error is satisfied, it is reasonable to consider ${\hat M}$s nearly unbiased estimators.
 
-Next, we evaluated the precision of ${\hat M}$s based on their CV.
-{\bf Table S1} in {\bf Supporting Information} demonstrated the value of the CV; meanwhile, the violin plot ({\bf Figure~\ref{violins}}) visually provides the degree of precision.
-For each estimator ${\hat M}$, the precision increases with increasing of sample size.
-It should be noted that total sample size depends on the estimator.
-For example, $n=50$ in Fig.~\ref{violins}, the total sample size of ${\hat M_1}$, ${\hat M_2}$, ${\hat M_3}$, ${\hat M_4}$ and ${\hat M_5}$ is 100 ($=n_{\rm O,1}+n_{\rm O,2}$), 100 ($=n_{\rm O,1}+n_{\rm P,2}$), 150 ($=n_{\rm O,1}+n_{\rm O,2}+n_{\rm P,2}$), 150 ($=n_{\rm O,1}+n_{\rm O,2}+n_{\rm P,2}$) and 200 ($=n_{\rm O,1}+n_{\rm O,2}+n_{\rm P,1}+n_{\rm P,2}$), respectively.
+Next, we evaluated the precision of ${\hat M}$s based on the CV value.
+{\bf Table S1} in {\bf Supporting Information} shows the CV value, and the violin plot in {\bf Figure~\ref{violins}} visualizes the degree of precision.
+For each estimator ${\hat M}$, we found that precision increases with increasing sample size.
+Note that the total sample size depends on the estimator.
+For example, $n=50$ in Fig.~\ref{violins}, the total sample sizes of ${\hat M_1}$, ${\hat M_2}$, ${\hat M_3}$, ${\hat M_4}$, and ${\hat M_5}$ were 100 ($=n_{\rm O,1}+n_{\rm O,2}$), 100 ($=n_{\rm O,1}+n_{\rm P,2}$), 150 ($=n_{\rm O,1}+n_{\rm O,2}+n_{\rm P,2}$), 150 ($=n_{\rm O,1}+n_{\rm O,2}+n_{\rm P,2}$), and 200 ($=n_{\rm O,1}+n_{\rm O,2}+n_{\rm P,1}+n_{\rm P,2}$), respectively.
 
-As sample size or migrants increase, the precision increases and the shape of the distribution asymptotically becomes symmetric ({\bf Figure~\ref{violins}}).
-This is because an increasing of sample size or migrants is likely to increase the observed number of kinship pairs found between two populations ($\widetilde{H}_{\rm HS,bet}$ or $\widetilde{H}_{\rm PO,bet}$) and decreases the variance of those kinship pair numbers.
-In addition, the number of PO pair within a population ($\widetilde{H}_{\rm PO,1}$ or $\widetilde{H}_{\rm PO,2}$) also contributes the precision for estimating $N_1$ or $N_1$, respectively, providing ${\hat M_4}$ and ${\hat M_5}$ with a higher precision.
+As the sample size or number of migrants increase, precision increases, and the shape of the distribution asymptotically becomes symmetric ({\bf Fig.~\ref{violins}}) because an increasing sample size or increasing number of migrants is likely to increase the observed number of kinship pairs found between the two populations ($\widetilde{H}_{\rm HS,bet}$ or $\widetilde{H}_{\rm PO,bet}$) and decreases the variance of those kinship pair numbers.
+In addition, the number of PO pairs in a given population ($\widetilde{H}_{\rm PO,1}$ or $\widetilde{H}_{\rm PO,2}$) contributes to the precision of estimating $N_1$ or $N_1$, respectively, thereby providing ${\hat M_4}$ and ${\hat M_5}$ with higher precision.
 
-Our simulator can handle the situation with or without invasive sampling.
-Invasive sampling potentially affects the level of $m$ since sampled parents in the population 1 have no chance to move to the population 2 and thus those parents cannot be sampled.
-In this case, $m$ should be defined by $M/(N_1-n_{P,1})$ not by $M/N_1$, although it does not affect the estimator ${\hat M}$s, as demonstrated in {\bf Table S1} ({\bf Supporting Information}).
+Note that our simulation can handle case with and without invasive sampling.
+Invasive sampling potentially affects the level of $m$ because the sampled parents from population 1 have no chance to move to population 2; thus, such parents cannot be sampled.
+In this case, $m$ should be defined by $M/(N_1-n_{P,1})$ rather than $M/N_1$, although this does not affect the estimator ${\hat M}$s, as demonstrated in {\bf Table S1} ({\bf Supporting Information}).
 
-Finally, we investigated the situation in which the parental number in the population 1 is much more than in the population 2 (i.e., $N_1 \gg N_2$) and thus migrants are large proportion of $N_2$.
-In such a setting, e.g., $(N_1,N_2,M)=(10^4,10^3,500)$, we confirmed the similar property of ${\hat M}$s to the situation $N_1 = N_2$, as demonstrated in {\bf Table S1} ({\bf Supporting Information}), suggesting the robustness of ${\hat M}$s in heterogeneous population sizes.
+Finally, we investigated the case where the parental number in population 1 is much greater in population 2 (i.e., $N_1 \gg N_2$); thus, migrants represent a  large proportion of $N_2$.
+For such cases, e.g., $(N_1,N_2,M)=(10^4,10^3,500)$, we confirmed the similar property of ${\hat M}$s to the $N_1 = N_2$ situation, as shown in {\bf Table S1} ({\bf Supporting Information}), which suggests the robustness of ${\hat M}$s in the presence of heterogeneous population sizes.
 
@@
 
-We theoretically developed estimators of the contemporary migration number (${\hat M_1}$--${\hat M_5}$) and migration rate (${\hat m_1}$--${\hat m_4}$) of parents between two pre-defined populations in iteroparous species.
-The proposed estimators are based on known PO relationship and HS relationships observed between and within two populations without any error of kinship assignment.
-Users can choose the estimator developed for the situation as to whether the parental number of population 1 ($N_1$) and/or that of population 2 ($N_2$) is known ({\bf Table~\ref{parameter}}).
-The performance of the estimator (accuracy and precision) was quantitatively evaluated by running an individual-based model ({\bf Figure~\ref{violins}}; see also {\bf Table S1} in {\bf Supporting Information}).
-Our modeling framework utilizes several types of reproductive variations (survived offspring number per parent), including variance of reproductive potential within and between populations, taking account of several situations, including a body-size structure or environmental heterogeneity for reproductive success.
+In this study, we theoretically developed estimators for the contemporary migration number (${\hat M_1}$--${\hat M_5}$) and migration rate (${\hat m_1}$--${\hat m_4}$) of parents between two predefined populations in iteroparous species.
+The proposed estimators are based on the known PO relationship and HS relationships observed between and within the two populations without any error in terms of kinship assignment.
+Users can select the appropriate estimator for cases where the parental number of population 1 ($N_1$) and/or that of population 2 ($N_2$) is known ({\bf Table~\ref{parameter}}).
+The performance of the estimator (accuracy and precision) was evaluated quantitatively by performing an individual-based simulation ({\bf Fig.~\ref{violins}} and {\bf Table S1} in {\bf Supporting Information}).
+The proposed modeling framework utilizes several types of reproductive variations (i.e., the number of survived offspring per parent), including the variance of reproductive potential within and between populations, in consideration of several situations, including a body-size structure or environmental heterogeneity for reproductive success.
 
-We presented mainly three novel points in this paper.
-First, we formulated probabilities of kinship pairs randomly chosen between two populations ($\pi_{\rm HS,bet}$ and $\pi_{\rm PO,bet}$), which provide estimators of the migration number or rate.
-While similar derivations may be found in (nongenetical) the MR method, these are limited to the situation such that sampling can be non-invasive and adult individuals are sampled.
-Our proposed method can avoid these limitations, where such an advantages is characterized by CKMR method for estimating population sizes.
-Second, we revealed that the probabilities of kinship pairs are approximately independent of reproductive potential and thus information about it is not needed for the estimation, provided that migration assumes to occur independently of the reproductive potential.
-This is a useful property of the estimators because it is natural that heterogeneity of reproductive potential within and between populations exits in iteroprous species but its observation is generally difficult except a body size.
-Third, we demonstrated applicability that the estimation can be obtained only from the genetic data (i.e., ${\hat M_5}$ and ${\hat m_4}$).
-There are several advantages in using the proposed estimator instead of separately estimating $\pi_{\rm HS,bet}$ (and/or $\pi_{\rm PO,bet}$) (via genetic method) and $N_1$ (and/or $N_2$) (via nongenetical method), including simplified sampling and analyzing designs and availability of unified framework of genetic analyzes for detecting HS and PO pairs (similar discussion is found for estimating the ratio of effective breeding size to the census size, $N_{\rm b}/N$, in \cite{Akita_2020}).
+Our primary contributions are summarized as follows.
+First, we formulated the probabilities of kinship pairs randomly selected between two populations ($\pi_{\rm HS,bet}$ and $\pi_{\rm PO,bet}$), which provides migration number or rate estimators.
+While similar derivations may be found in the (nongenetic) MR method, these are limited to cases where sampling is non-invasive and adult individuals are sampled.
+The proposed method can avoid these limitations, where such an advantages is characterized by the CKMR method for estimating population sizes.
+Second, we have demonstrated that the probabilities of kinship pairs are approximately independent of the reproductive potential; thus, information about it is not required to realize the estimation provided that migration is assumed to occur independently of the reproductive potential.
+This is a useful property of the estimators because it is natural that heterogeneity of reproductive potential within and between populations exits in iteroparous species but its observation is generally difficult.
+Third, we have demonstrated that estimators can be obtained using only genetic data (i.e., ${\hat M_5}$ and ${\hat m_4}$).
+There are several advantages in using the proposed estimator rather than estimating $\pi_{\rm HS,bet}$ (and/or $\pi_{\rm PO,bet}$) separately (via a genetic method) and $N_1$ (and/or $N_2$) (via a nongenetic method), including simplified sampling processes and analyzing designs and the availability of a unified framework of genetic analyses for detecting HS and PO pairs (similar discussion is found for estimating the ratio of effective breeding size to the census size, $N_{\rm b}/N$, in \cite{Akita_2020}).
 
-To estimate the contemporary migration number or migration rate, our simulation-based results provide guidance for a sample size to ensure the required accuracy and precision, especially if the order of the number of migrant parents and parental sizes are approximately known ({\bf Table S1} in {\bf Supporting Information}).
-For example, when $m=0.1$ and $N_1=N_2=10^3$, sampling 10\% and 20\% parents and an equal number of offspring in two populations leads 70\% and 39\% CV of ${\hat M_5}$, respectively (case of invasive sampling).
-Even if there is no information about these numbers, $1/\sqrt{H_{\rm HS, bet}}$ (or $1/\sqrt{H_{\rm PO, bet}}$) provides an approximate lower bound on the CV, which can be used as an indicator of the precision of ${\hat M}$ or ${\hat m}$.
-Furthermore, the condition that $n>\sqrt{N_2}$ is also used as rule of thumb especially when planning a research project ($n = n_{\rm O, 1}=n_{\rm O, 2}=n_{\rm P, 2}$, see also Equations~\ref{RS-1} and \ref{RS-2}).
-It should be noted that the guidance is to estimate the information about one-way migration between two populations; thus, estimating two-way migrations among two and three populations requires twice and three times the number of samples, respectively, compared to our guidance for a sample size.
+To estimate the contemporary migration number or migration rate, our simulation-based results provide sample size guidance to ensure the required accuracy and precision, especially if the order of the number of migrant parents and parental sizes are approximately known ({\bf Table S1} in {\bf Supporting Information}).
+For example, when $m=0.1$ and $N_1=N_2=10^3$, sampling 10\% and 20\% of the parents and an equal number of offspring in both populations leads to 70\% and 39\% CV of ${\hat M_5}$, respectively (in the invasive sampling case).
+Even no information is available about these numbers, $1/\sqrt{H_{\rm HS, bet}}$ (or $1/\sqrt{H_{\rm PO, bet}}$) provides an approximate lower bound on the CV, which can be used as an indicator of the precision of ${\hat M}$ or ${\hat m}$.
+In addition, the condition that $n>\sqrt{N_2}$ is also used as rule of thumb especially when planning a research project ($n = n_{\rm O, 1}=n_{\rm O, 2}=n_{\rm P, 2}$; refer to Equations~\ref{RS-1} and \ref{RS-2}).
+Noted that the guidance is to estimate the information about one-way migration between two populations; thus, estimating two-way migrations among two or three populations would require twice and three times the number of samples, respectively, compared to our sample size guidance.
 
-There may be several cases where it is desirable to apply the proposed estimator.
-The first case is where there is a large number of migrants between populations, e.g., $M>100$, which vanishes the population differentiation and thus hampers the detection of $M$ population genetics method if $M$ is interpreted as effective migration number.
-Information on movement between populations is essential for assessing population dynamics in the context of conservation and management, even if the migrant number is so large that it cannot be genetically assigned to two populations.
-The second is the case of the application to genetic monitoring conducted every reproductive timing (e.g., annually).
-This is because proposed estimators have information about contemporary migration that is explicitly specified the timing (e.g., year), thus the time series data for migration may reflect environmental changes, which provides insights into the underlying ecological processes.
-In addition, HS pairs found within the genetic population provides $N_{\rm b}$ \cite[]{wang2009new,WAPLES_2011}, which is also used for assessing a genetic health.
-The third is the case is to develop integrated models that combines several sources of data into a single analysis \cite[]{MAUNDER201361}.
-One example of this direction is to provide additional information about migration to ongoing CKMR projects for stock assessment in fisheries, which utilizes kinship pairs for simultaneous estimation of population parameters \cite[e.g.,][]{Bravington_2016,Hillary_2018,https://doi.org/10.1002/ece3.6296,ecolevol2021p,10.1093/icesjms/fsac002}.
-If population structure is hypothetically defined, accumulated data in these projects are readily connected to our theory via likelihood methods.
-The forth case is where sampling adults is difficult due to conservation purpose or other reasons instead sampling offspring is relatively easy.
-In this case, although $N_2$ (and $N_1$) need to be given externally for the usage of $\hat m_1$ (and $\hat M_1$), there is presently no other method for estimating adult movement especially when two populations cannot be genetically distinct, indicating that proposed method has the potential to greatly widen the scope of population monitoring.
+We believe there are several scenarios where the proposed estimator may be beneficial.
+The first case is where there is a large number of migrants between populations, e.g., $M>100$, which eliminates population differentiation and thus hampers the detection of the $M$ via population genetics method if $M$ is interpreted as an effective migration number.
+Information about movement between populations is essential to assess population dynamics in the conservation and management contexts, even if the migrant number is so large that it cannot be genetically assigned to two populations.
+The second case involves genetic monitoring conducted for each reproductive period (e.g., annually) because the proposed estimators consider information about contemporary migration that is explicitly specified the timing (e.g., year); thus, the time-series data for migration may reflect environmental changes, and this would provide insights into the underlying ecological processes.
+In addition, HS pairs found within the genetic population provide $N_{\rm b}$ \cite[]{wang2009new,WAPLES_2011}, which is also used to assess genetic health.
+The third is the case involves the development of integrated models that combine several data sources into a single analysis \cite[]{MAUNDER201361}.
+An example of this direction is to provide additional information about migration to ongoing CKMR projects for stock assessment in fisheries \cite[e.g.,][]{Bravington_2016,Hillary_2018,https://doi.org/10.1002/ece3.6296,ecolevol2021p,10.1093/icesjms/fsac002}, which would utilize kinship pairs for simultaneous estimation of population parameters.
+If the population structure is defined hypothetically, the data accumulated in such projects could be readily connected to our theory via likelihood methods.
+The fourth case is where sampling adults is difficult due to conservation practices or other reasons but instead sampling offspring is relatively easy.
+In such cases, although $N_2$ (and $N_1$) must be given externally to employ $\hat m_1$ (and $\hat M_1$), there is presently no existing method to estimate adult movement, especially when two populations cannot be genetically distinct, which indicates that the proposed method has the potential to expand the scope of current population monitoring techniques.
 
-Finally, we note some caveats in applying proposed method.
-Our theory for developing estimators assumes that kinships are detected without any error.
-There are many algorithms to detect kinship pairs from single nucleotide polymorphisms (SNPs) or short tandem repeats (STRs) \cite[e.g., ][]{Wang_2009Genetics, Huisman_2017}, although a HS pair requires many more DNA markers than a PO pair.
-In addition, iteroprous species potentially has several kinship types such as halfsib-uncle/nephew or halfsib-cousin, which are expected to appear frequently and should be correctly distinguished from HS pairs.
-It is desirable to estimate in advance how many markers are needed for kinship detections in target populations associated with simulation of a pedigree reconstruction including distant kinships (e.g., \cite{Anderson_2020}).
-Our proposed estimators are limited to detect parental movements on a period between breeding seasons in given populations.
-Thus, the estimation of fine-scale spatial-temporal movements, which is available to integrate multiple type of data \cite[]{Thorson_2021}, goes beyond the scope of this paper, although population dynamics models with a coarser spatial resolution than the spatial scale for environmental layers are often used in the assessment models, which is the target of application of the proposed method.
-Our proposed estimators require the pre-specification of a population structure.
-Kinship relationships with information of a sample location potentially provide the chance to explore a plausible population structure via estimating migration number or rate between hypothetical populations, which contributes the determination of a management unit.
-In addition, the current theory behind the estimators does not assume desynchronized reproduction within a population (e.g., skip spawning, see also \cite{https://doi.org/10.1111/faf.12615}), correlation between individual mobility and fertility and non-random sampling of parents (e.g., mothers with a large number of offspring are likely to be sampled).
-These perspectives of the study will be conducted in the future.
+Finally, we discuss some caveats in terms of applying the proposed method.
+Our theory for developing the estimators assumes that kinships are detected without error.
+Many algorithms can be used to detect kinship pairs from single nucleotide polymorphisms or short tandem repeats \cite[e.g., ][]{Wang_2009Genetics, Huisman_2017}, although a HS pair requires many more DNA markers than a PO pair.
+In addition, iteroparous species may has several kinship types e.g., half-uncle--nephew or half-cousins, which are expected to appear frequently and should be accurately differentiated from HS pairs.
+It is desirable to estimate in advance how many markers are required for kinship detection in the target populations associated with simulation of pedigree reconstruction (e.g., \cite{Anderson_2020}).
+Note that the proposed estimators are limited to detecting parental movements on a period between breeding seasons in the given populations.
+Thus, the estimation of fine-scale spatiotemporal movements, which is available to integrate data sources \cite[]{Thorson_2021}, is beyond the scope of this paper.
+Although population dynamics models with coarser spatial resolution than the spatial scale of environmental layers are frequently used in assessment models, i.e., the target application of the proposed method, the proposed estimators require pre-specification of the population structure.
+Kinship relationships with sample location information potentially realize the ability to explore a plausible population structure by estimating the migration number or rate between hypothetical populations, which is expected to contribute the determination of a management unit.
+In addition, the current theory behind the estimators does not assume desynchronized reproduction within a population (e.g., skip spawning), correlation between individual mobility and fertility, and nonrandom sampling of parents (e.g., mothers with a large number of offspring are likely to be sampled).
+These issues will be the focus of future work.
 
@@
 Suzuki and Y.
-Tsukahara for fruitful discussions.
+Tsukahara for their fruitful discussions.
 The author also thanks W.M.
-Iwasaki for helping me in coding C{++}.
-This work was supported by JSPS KAKENHI Grant Number 19K06862 and 20H03012.
+Iwasaki for helping with the C{++} coding.
+This work was supported by JSPS KAKENHI Grant Numbers 19K06862 and 20H03012.
 
@@
        & & \\
-	$n_{\rm P,1}, n_{\rm P, 2}$			& Sampled number of parents from the population 1 and 2\\ 
+	$n_{\rm P,1}, n_{\rm P, 2}$			& Sampled number of parents from population 1 and 2\\ 
 		                						& \\
-	$n_{\rm O, 1}, n_{\rm O, 2}$			& Sampled number of offspring from the population 1 and 2\\ 
+	$n_{\rm O, 1}, n_{\rm O, 2}$			& Sampled number of offspring from population 1 and 2\\ 
 		                						& \\
-	$N_{1}, N_{2}$						& Number of parents in the population 1 and 2 when sampled offspring are born\\
+	$N_{1}, N_{2}$						& Number of parents in population 1 and 2 when sampled offspring are born\\
 		                						& \\
-	$M$								& Number of survived migrants of parents from the population 1 to population 2\\
+	$M$								& Number of survived migrants of parents from population 1 to population 2\\
 		                						& \\
-	$m$								& Migration rate of parents from the population 1 to population 2, defined by $M/N_1$.\\
+	$m$								& Migration rate of parents from population 1 to population 2, defined by $M/N_1$.\\
 		                						& \\
@@
 	$\pi_{\rm PO,1}, \pi_{\rm PO,2}$		& Probability that a randomly selected pair (parent and offspring) \\
-	                							& shares a parent-offspring relationship within the population 1 and 2\\
+	                							& shares a parent-offspring relationship within population 1 and 2\\
 									& \\
 	$\pi_{\rm PO, bet}$					& Probability that a randomly selected pair (parent and offspring) \\
-	                							& shares a parent-offspring relationship between the population 1 and 2\\
+	                							& shares a parent-offspring relationship between population 1 and 2\\
 									& \\
 	$\pi_{\rm HS, bet}$					& Probability that a randomly selected pair (two offspring) \\
-	                							& shares a half-sibling relationship between the population 1 and 2\\
+	                							& shares a half-sibling relationship between population 1 and 2\\
 					                			& \\
-	$\lambda_{i,1}, \lambda_{j,2}$			& Expected number of surviving offspring of parent $i$ and $j$ at sampling in the population 1 and 2\\
+	$\lambda_{i,1}, \lambda_{j,2}$			& Expected number of surviving offspring of parent $i$ and $j$ at sampling in population 1 and 2\\
 		                						& \\
-	$\lambda_{M,l,1}, \lambda_{M,l,2}$		& Expected number of surviving offspring of migrant $l$ at sampling in the population 1 and 2\\
+	$\lambda_{M,l,1}, \lambda_{M,l,2}$		& Expected number of surviving offspring of migrant $l$ at sampling in population 1 and 2\\
 		                						& \\
-	$k_{i,1}, k_{j,2}$					& Number of surviving offspring born to parent $i$ and $j$ in the population 1 and 2\\ 
+	$k_{i,1}, k_{j,2}$					& Number of surviving offspring born to parent $i$ and $j$ in population 1 and 2\\ 
 	                							& \\
-	$H_{\rm PO, 1}, H_{\rm PO, 2}$		& Number of parent-offspring pairs observed in samples within the population 1 and 2\\ 
+	$H_{\rm PO, 1}, H_{\rm PO, 2}$		& Number of parent-offspring pairs observed in samples within population 1 and 2\\ 
 	                							& \\
-	$H_{\rm PO, bet}$					& Number of parent-offspring pairs observed in samples between the population 1 and 2\\ 
+	$H_{\rm PO, bet}$					& Number of parent-offspring pairs observed in samples between population 1 and 2\\ 
 	                							& \\
-	$H_{\rm HS, bet}$					& Number of half-sibling pairs observed in samples between the population 1 and 2\\ 
+	$H_{\rm HS, bet}$					& Number of half-sibling pairs observed in samples between population 1 and 2\\ 
 	                							& \\              		
@@
     \label{symbols} 
-\\Subscription ``1'' and ``2'' indicates the quantity in the population 1 during the first year and in the population 2 during the second year, respectively. 
+\\Subscripts ``1'' and ``2'' indicate the quantity in population 1 during the first year and in population 2 during the second year, respectively. 
 \end{table}
@@
     \end{tabular}
-    \\HSP and POP indicates half-sibling pair and parent-offspring pair, respectively. 
+    \\HSP: half-sibling pair; POP: parent--offspring pair. 
     \label{parameter} 
@@
 \clearpage
+
+%KOKOMADE enago%%%
 

### 2022-03-07 latex/ms.tex
done revision

@@
 Generally, the required sample size to ensure the above conditions is $n>\sqrt{N_2}$, where $n = n_{\rm O, 1}=n_{\rm O, 2}=n_{\rm P, 2}$.
-Noted that a very small $m$ value, which dramatically increases the required sample size, produces significant genetic differences between the two populations.
+Note that a very small $m$ value, which dramatically increases the required sample size, produces significant genetic differences between the two populations.
 In such cases, there are several methods to estimate migration rate using population genetics technique.
@@
 In addition, the condition that $n>\sqrt{N_2}$ is also used as rule of thumb especially when planning a research project ($n = n_{\rm O, 1}=n_{\rm O, 2}=n_{\rm P, 2}$; refer to Equations~\ref{RS-1} and \ref{RS-2}).
-Noted that the guidance is to estimate the information about one-way migration between two populations; thus, estimating two-way migrations among two or three populations would require twice and three times the number of samples, respectively, compared to our sample size guidance.
+Note that the guidance is to estimate the information about one-way migration between two populations; thus, estimating two-way migrations among two or three populations would require twice and three times the number of samples, respectively, compared to our sample size guidance.
 
@@
 \newcommand{\figcapa}{(a) Hypothetical populations with $N_{1}=16$, $N_{2}=14$, and $M=6$.
-Upper and lower square indicates individuals belonging to the population 1 before migration (at sample timing in the first year) and individuals belonging to the population 2 after reproduction (at sample timing in the second year), respectively.
-The open circles on the left side, right side, and the center represent mothers, fathers, and their offspring, respectively.
-The thin line denotes parent-offspring relationship.
-The bold arrow denotes the migration and the symbol x denotes a failure to survive at sampling in the second year.
+Upper and lower areas indicate individuals in population 1 before migration (at the sample timing in the first year) and individuals in population 2 after reproduction (at the sample timing in the second year), respectively.
+Open circles on the left, right, and center represent mothers, fathers, and their offspring, respectively.
+The thin line denotes PO relationship.
+Bold arrows denote migration, and x denotes failure to survive at the sampling in the second year.
 Sampled individuals are labeled with an index number.
-The number of sampled individuals in this example: $n_{\rm P, 1}=4$, $n_{\rm O, 1}=5$, $n_{\rm P, 2}=6$, $n_{\rm O, 2}=4$; the numbers of kinship pairs: $H_{\rm PO, bet}=1$ (i.e., ``7-10'' pair), $H_{\rm HS, bet}=2$ (i.e., ``8-16'' and ``9-16'' pairs), $H_{\rm PO, 1}=3$ (i.e., ``1-6'', ``3-5'' and ``4-7'' pairs), and $H_{\rm PO, 2}=2$ (i.e., ``11-17'' and ``15-16'' pairs).
-(b) The phases of the events relevant to this study along the time line.}
+Number of sampled individuals in this example: $n_{\rm P, 1}=4$, $n_{\rm O, 1}=5$, $n_{\rm P, 2}=6$, $n_{\rm O, 2}=4$; numbers of kinship pairs: $H_{\rm PO, bet}=1$ (i.e., ``7-10'' pair), $H_{\rm HS, bet}=2$ (i.e., ``8-16'' and ``9-16'' pairs), $H_{\rm PO, 1}=3$ (i.e., ``1-6'', ``3-5'' and ``4-7'' pairs), and $H_{\rm PO, 2}=2$ (i.e., ``11-17'' and ``15-16'' pairs).
+(b) Phases of events relevant to this study in the given timeline.}
 
-\newcommand{\figcapb}{Violin plots showing the distribution of relative bias in our estimator of $M$ for various values sample sizes, parent numbers and migration rate.
-Filled circles represent the mean values.
-Sample sizes for parents and offspring are identical (i.e., $n=n_{\rm P,1}=n_{\rm P,2}=n_{\rm O,1}= n_{\rm O,2}$) and parent sizes in the two populations are also identical (i.e., $N=N_1=N_2$), which are indicated in the legend.
+\newcommand{\figcapb}{Violin plots showing the distribution of relative bias in the estimator of $M$ for various sample sizes, parent numbers, and migration rates.
+Filled circles represent mean values.
+The sample sizes for parents and offspring are identical (i.e., $n=n_{\rm P,1}=n_{\rm P,2}=n_{\rm O,1}= n_{\rm O,2}$), and the parent sizes in the two populations are identical (i.e., $N=N_1=N_2$), as indicated in the legend.
 Migration rate $m$ is specified by $N_1/M$.
-For the demonstration purposes, the upper side of the distribution is truncated, although the mean values are calculated including the truncated values.
+For demonstration purposes, the upper side of the distribution is truncated, although the mean values are calculated (including the truncated values).
 }
@@
 \renewcommand{\theequation}{A\arabic{equation}}
-Here, we introduce the concept of the reproductive potential of parent $i$ and $j$ in the population 1 and 2, respectively, which are defined as the expected number of surviving offspring at sampling time, denoted by $\lambda_{i,1}$ and $\lambda_{j,2}$ ($i=1, \ldots, N_1$ and $j=1, \ldots, N_2$).
-The reproductive potential is determined by several factors, including the parent's age, weight, residence time on the spawning ground.
-It should be noted that the magnitude of this parameter includes information about the survival rate of the offspring, the number of days after egg hatching, and the egg number; this implies that the parameter reflects the sample timing.
-It should also be noted that the modeling framework does not depend on whether the reproductive potential is heritable or not.
+Here, we introduce the concept of the reproductive potentials of parents $i$ and $j$ in the population 1 and 2, respectively, which are defined as the expected number of surviving offspring at the given sampling time, denoted by $\lambda_{i,1}$ and $\lambda_{j,2}$ ($i=1, \ldots, N_1$ and $j=1, \ldots, N_2$).
+Reproductive potential is determined by several factors, including the parent age, weight, and residence time in the spawning ground.
+Note that the magnitude of this parameter includes information about offspring survival rate, the number of days after egg hatching, and the number of eggs.
+This implies that the parameter reflects the sample timing.
+Also note that the modeling framework does not depend on whether the reproductive potential is heritable or not.
 
@@
 In the main text, we ignore the variation of reproductive potential among parents (i.e., both $\lambda_{i,1}$ and $\lambda_{j,2}$ are constant) to derive $\pi_{\rm HS,bet}$ and $\pi_{\rm PO,bet}$.
-Let $k_{i,1}$ and $k_{j,2}$ be the number of surviving offspring of parent $i$ and $j$ at sampling in the population 1 and 2, respectively, and $k_{i,1}$ and $k_{j,2}$ is assumed to follow a kind of discrete distribution (e.g., negative binomial distribution) with mean $\lambda_{i,1}$ and $\lambda_{j,2}$.
-Without loss of generality, we set the index such that parents with $i=1$ to $M$ in the population 1 and $j=1$ to $M$ in the population 2 are identical migrants; for example, the parent with $i=1$ reproduce $k_{1,1}$ offspring (in the population 1) and then reproduce $k_{1,2}$ offspring (in the population 2) after migration.
-Giving $k_{i,1}$ and $k_{j,2}$, the conditional probability that two offspring sampled in the population 1 and 2 share an HS relationship is
+Here, let $k_{i,1}$ and $k_{j,2}$ be the number of surviving offspring of parents $i$ and $j$ at sampling time in populations 1 and 2, and assumed to follow a kind of discrete distribution (e.g., Poisson or negative binomial distribution) with mean $\lambda_{i,1}$ and $\lambda_{j,2}$, respectively.
+Without loss of generality, we set the index such that parents with $i=1$ to $M$ in population 1 and $j=1$ to $M$ in population 2 are identical migrants.
+For example, the parent with $i=1$ reproduces $k_{1,1}$ offspring (in population 1) and then reproduce $k_{1,2}$ offspring (in population 2) after migration.
+Given $k_{i,1}$ and $k_{j,2}$, the conditional probability that two offspring sampled in populations 1 and 2 share an HS relationship is expressed as follows:
 \begin{align}
@@
 where $\boldsymbol{k_1}=(k_{1,1}, \ldots, k_{M,1}, \ldots, k_{N_1,1})$ and $\boldsymbol{k_2}=(k_{1,2}, \ldots, k_{M,2}, \ldots, k_{N_2,2})$.
-It should be noted that $k_{i,1}$ and $k_{j,1}$ is a random variable with mean $\lambda_{i,1}$ and $\lambda_{j,2}$, respectively.
-By taking the expectation over the distribution of offspring number, the conditional probability is approximately given by
+Note that $k_{i,1}$ and $k_{j,1}$ are a random variables with mean $\lambda_{i,1}$ and $\lambda_{j,2}$, respectively.
+By taking the expectation over the distribution of the offspring number, the conditional probability is given approximately as follows:
 \begin{align}
@@
 where $\boldsymbol{\lambda_1}=(\lambda_{1,1}, \ldots, \lambda_{M,1}, \ldots, \lambda_{N_1,1})$ and $\boldsymbol{\lambda_2}=(\lambda_{1,2}, \ldots, \lambda_{M,2}, \ldots, \lambda_{N_2,2})$.
-From the second to the third line, we use the approximation that $\mathbb{E}[g1(k)/g2(k)] \approx \mathbb{E}[g_1(k)] / \mathbb{E}[g_2(k)]$.
-From the third to the forth line, we use the relationship that $\mathbb{E}[k_{i,1}k_{j,2} | _{\lambda_{i,1}, \lambda_{j,2}}] = \mathbb{E}[k_{i,1}|_{\lambda_{i,1}}]\mathbb{E}[k_{j,2}|_{\lambda_{j,2}}]$, implying statistical independence of offspring number before and after parental movement.
-In other words, the conditional probability does not affected by $\mathbb{V}[k|_\lambda]$.
-We assume that $\lambda_{i,1}$ and $\lambda_{j,2}$ is also a random variable followed by an arbitral function with mean ${\bar \lambda_{1}}$ and ${\bar \lambda_{2}}$, respectively.
-By taking the expectation over $\lambda$ and applying a similar approximation, the unconditional probability is given by
+From the second to third lines, we use the approximation that $\mathbb{E}[g1(k)/g2(k)] \approx \mathbb{E}[g_1(k)] / \mathbb{E}[g_2(k)]$.
+From the third to forth lines, we use the relationship that $\mathbb{E}[k_{i,1}k_{j,2} | _{\lambda_{i,1}, \lambda_{j,2}}] = \mathbb{E}[k_{i,1}|_{\lambda_{i,1}}]\mathbb{E}[k_{j,2}|_{\lambda_{j,2}}]$, which implies the statistical independence of the offspring number before and after parental movement.
+In other words, the conditional probability is not affected by $\mathbb{V}[k|_\lambda]$.
+Here, we assume that $\lambda_{i,1}$ and $\lambda_{j,2}$ are also random variables that are followed by an arbitrary function with mean ${\bar \lambda_{1}}$ and ${\bar \lambda_{2}}$, respectively.
+By taking the expectation over $\lambda$ and applying a similar approximation, the unconditional probability is given as follows:
 \begin{align}
@@
 which provides the same formulation described in Eq.\ref{HS-1}.
-It should be noted that, from the third to the forth line, we assume that $\lambda_{l,1}$ and $\lambda_{l,2}$ ($l = 1, \ldots, M$) are independent variables (i.e., $\mathbb{E}[\lambda_{l,1}\lambda_{l,2}] = {\bar \lambda_{1}}{\bar \lambda_{2}}$), implying variable reproductive potential of an identical parent before and after migration.
+Note that, from the third to forth lines, we assume that $\lambda_{l,1}$ and $\lambda_{l,2}$ ($l = 1, \ldots, M$) are independent variables (i.e., $\mathbb{E}[\lambda_{l,1}\lambda_{l,2}] = {\bar \lambda_{1}}{\bar \lambda_{2}}$), which implies variable reproductive potential of an identical parent before and after migration.
 
-Next, we derive the probability that offspring sampled in the population 1 and a parent sampled in the population 2 share an PO relationship ($\pi_{\rm PO,bet}$) under the flexible settings of $\lambda$, which is similar to the derivation of $\pi_{\rm HS,bet}$.
-The conditional probability is given by
+Next, we derive the probability that offspring sampled in population 1 and a parent sampled in population 2 share a PO relationship ($\pi_{\rm PO,bet}$) under the flexible settings of $\lambda$, which is similar to the derivation of $\pi_{\rm HS,bet}$.
+The conditional probability is expressed as follows:
 \begin{align}
@@
 \end{align}
-By taking the expectation over $k$ and $\lambda$, in the same manner as noted above, the unconditional probability is approximately given by
+Here, by taking the expectation over $k$ and $\lambda$, in the same manner as noted above, the unconditional probability is approximately given as follows:
 \begin{align}
@@
 
-\section*{Difference in reproductive potential between migrants and non-migrants}
+\section*{Difference in reproductive potential between migrants and nonmigrants}
 
-In the process of the derivation of $\pi_{\rm HS,bet}$ and $\pi_{\rm PO,bet}$ in {\bf APPENDIX 2}, we ignore covariation between migration and reproductive potential.
-Here, we consider the situation in which migrants have a distinguishable distribution of reproductive potential from non-migrant parents.
-Let $\lambda_{i,1}$, $\lambda_{j,2}$, $\lambda_{M,l,1}$ and $\lambda_{M,l,2}$ be a reproductive potential of non-migrant in the population 1 and 2 and migrants in the population 1 and 2 with mean ${\bar \lambda_{1}}$, ${\bar \lambda_{2}}$, ${\bar \lambda_{M,1}}$ and ${\bar \lambda_{M,2}}$, respectively.
-Under this setting, $\pi_{\rm HS,bet}$ can be written by
+In the derivation of $\pi_{\rm HS,bet}$ and $\pi_{\rm PO,bet}$ in {\bf Appendix 2}, we ignored covariation between migration and reproductive potential.
+Here, we consider the case where migrants have a distinguishable distribution of reproductive potential from nonmigrant parents.
+Let $\lambda_{i,1}$, $\lambda_{j,2}$, $\lambda_{M,l,1}$ and $\lambda_{M,l,2}$ be the reproductive potential of nonmigrant parents in population 1 and 2 and migrants in the populations 1 and 2 with mean ${\bar \lambda_{1}}$, ${\bar \lambda_{2}}$, ${\bar \lambda_{M,1}}$, and ${\bar \lambda_{M,2}}$, respectively.
+Under this setting, $\pi_{\rm HS,bet}$ can be expressed as follows:
 \begin{align}
@@
 \end{align}
-If ${\bar \lambda_{M,1}} = {\bar \lambda_{1}}$ and ${\bar \lambda_{M,2}} = {\bar \lambda_{2}}$, Eq.~\ref{App3} reduces to Eq.\ref{App2}.
-This formulation include reproductive potential terms, so that distinct reproductive potential between migrants and non-migrants vanishes the usefulness from proposed HS-based estimators (this is also applied to PO-based estimators proposed in this paper).
+If ${\bar \lambda_{M,1}} = {\bar \lambda_{1}}$ and ${\bar \lambda_{M,2}} = {\bar \lambda_{2}}$, Eq.~\ref{App3} can be reduced Eq.\ref{App2}.
+This formulation includes reproductive potential terms such that the distinct reproductive potential between migrants and nonmigrants eliminates the usefulness of the proposed HS-based estimators (this is also applied to the proposed PO-based estimators).
 

### 2022-03-08 latex/ms.tex
modify ~2.5

@@
 
-In the example shown in {\bf Fig.~\ref{cartoon}a}, five offspring and four parents are sampled in population 1, four offspring and six parents are sampled in population 2, and two HS pairs and a single PO pair are observed between the two populations 1 and 2.
+In the example shown in {\bf Figure~\ref{cartoon}a}, five offspring and four parents are sampled in population 1, four offspring and six parents are sampled in population 2, and two HS pairs and a single PO pair are observed between the two populations 1 and 2.
 In addition, there are several PO pairs observed within the same population, which are available to estimate parent numbers, which is explained in subsection 2.7.
@@
 
-Here, we consider the probability that two offspring sampled in populations 1 and 2 will share an HS relationship with an arbitrary mother or father, denoted by $\pi_{\rm HS, bet}$.
+Here, we consider the probability that two offspring sampled in populations 1 and 2 will share a HS relationship with an arbitrary mother or father, denoted by $\pi_{\rm HS, bet}$.
 Note that we assume equal reproductive potential among parents (up to subsection 2.7) although this assumption can be relaxed for most of the case (see {\bf Appendix 2} for additional information).
@@
 
-To assess these probabilities, recall that there must be two parents of arbitral offspring.
+To assess these probabilities, recall that there must be two parents of arbitrary offspring.
 The first probability is the sum of the father--offspring and mother--offspring relationship, which can be expressed as $r_{\rm M}M/(r_{\rm S,1}N_{1}) + (1 - r_{\rm M})M/((1-r_{\rm S,1})N_{1})$, where $r_{\rm M}$ and $r_{\rm S,1}$ indicate the sex ratio of the parents in the migrants and in all of the population 1, respectively.
@@
 Let $H_{\rm HS,bet}$ be the number of HS pairs found in the offspring samples of size $n_{\rm O, 1}$ and $n_{\rm O, 2}$.
-Assuming the total number of HS pairs in the population is much greater than $H_{\rm HS,bet}$, the distribution is approximated by a binomial form (i.e., $H_{\rm HS,bet} \sim {\rm Binom}[\pi_{\rm HS,bet}, n_{\rm O, 1} n_{\rm O, 2}]$).
+Assuming the total number of HS pairs between the two populations much greater than $H_{\rm HS,bet}$, the distribution is approximated by a binomial form (i.e., $H_{\rm HS,bet} \sim {\rm Binom}[\pi_{\rm HS,bet}, n_{\rm O, 1} n_{\rm O, 2}]$).
 Thus, the theoretical expectation of $H_{\rm HS,bet}$ is given as follows:
@@
 \end{align}
-In this paper, a ``tilde'' and ``hat'' symbols indicates the observation and estimator of a variable, respectively.
+In this paper, a ``tilde'' and ``hat'' symbols indicate the observation and estimator of a variable, respectively.
 Similarly, $\mathbb{E}[H_{\rm HS, bet}]$ in Equation \ref{HS-2-2} is replaced by $\widetilde{H}_{\rm HS, bet}$, which generates the linear estimator of $m$:
@@
 Let $H_{\rm PO,bet}$ be the number of PO pairs found in offspring samples of size $n_{\rm O, 1}$ and parent samples of size $n_{\rm P, 2}$.
-Under the assumption that the total number of PO pairs in the two populations is much greater than $H_{\rm PO,bet}$, the distribution is approximated by a binomial form (i.e., $H_{\rm PO,bet} \sim {\rm Binom}[\pi_{\rm PO,bet}, n_{\rm O, 1} n_{\rm P, 2}]$).
+Under the assumption that the total number of PO pairs between the two populations is much greater than $H_{\rm PO,bet}$, the distribution is approximated by a binomial form (i.e., $H_{\rm PO,bet} \sim {\rm Binom}[\pi_{\rm PO,bet}, n_{\rm O, 1} n_{\rm P, 2}]$).
 Thus, the theoretical expectation of $H_{\rm PO,bet}$ is expressed as follows:
@@
 The proposed estimators are based on the observed number of kinship pairs.
-Their expected number is linearly determined by the number of pairwise comparison (Eqs.~\ref{HS-2-1}-\ref{HS-2-2} and \ref{PO-2-1}-\ref{PO-2-2}), which provides sample size guidance to ensure the condition that at least one or more kinship pairs can be found.
+Their expected number is linearly determined by the number of pairwise comparison (Equations~\ref{HS-2-1}-\ref{HS-2-2} and \ref{PO-2-1}-\ref{PO-2-2}), which provides sample size guidance to ensure the condition that at least one or more kinship pairs can be found.
 The conditions are given as follows:

### 2022-03-09 latex/ms.tex
finish...

@@
 \end{align}
-For those estimators, $\widetilde{H}_{\rm HS,bet}$ and $\widetilde{H}_{\rm PO,bet}$ are weighted by sample size $n_{\rm O, 2}$ and $n_{\rm P, 2}$, respectively.
+For those estimators, $\widetilde{H}_{\rm HS,bet}$ and $\widetilde{H}_{\rm PO,bet}$ are weighted by $2n_{\rm O, 2}$ and $n_{\rm P, 2}$, respectively.
 
@@
 Population 1 and 2 comprised $N_1$ and $N_2$ parents with an equal sex ratio, and their offspring number was assumed to follow the geometric distribution with mean ${\bar \lambda_1}$ and ${\bar \lambda_2}$ (i.e., Poisson reproduction with mean $\lambda_{i,1}$ and $\lambda_{j,2}$, which follows the exponential distribution with mean ${\bar \lambda_1}$ and ${\bar \lambda_2}$), respectively.
-Migrant parents were selected randomly from population 1 at the end of the first year, and each offspring retained IDs of the parents, thereby making it possible to trace an HS and PO relationship.
+Migrant parents were selected randomly from population 1 at the end of the first year, and each offspring retained IDs of the parents, thereby making it possible to trace a HS and PO relationship.
 
@@
 As expected, for most of the investigated parameter sets, we observed that their relative bias was less than 5\%, as shown in {\bf Table S1} in {\bf Supporting Information}.
-Thus, when the assumption that kinships are detected without any error is satisfied, it is reasonable to consider ${\hat M}$s nearly unbiased estimators.
+Thus, when the assumptions that (i) offspring and parents are randomly sampled, (ii) kinships are detected without any error, and (iii) the migration event does not depend on the degree of reproductive potential, are satisfied, it is reasonable to consider ${\hat M}$s nearly unbiased estimators.
 
@@
 As the sample size or number of migrants increase, precision increases, and the shape of the distribution asymptotically becomes symmetric ({\bf Fig.~\ref{violins}}) because an increasing sample size or increasing number of migrants is likely to increase the observed number of kinship pairs found between the two populations ($\widetilde{H}_{\rm HS,bet}$ or $\widetilde{H}_{\rm PO,bet}$) and decreases the variance of those kinship pair numbers.
-In addition, the number of PO pairs in a given population ($\widetilde{H}_{\rm PO,1}$ or $\widetilde{H}_{\rm PO,2}$) contributes to the precision of estimating $N_1$ or $N_1$, respectively, thereby providing ${\hat M_4}$ and ${\hat M_5}$ with higher precision.
+In addition, the number of PO pairs in a given population ($\widetilde{H}_{\rm PO,1}$ or $\widetilde{H}_{\rm PO,2}$) contributes to the precision of estimating $N_1$ or $N_2$, respectively, thereby providing ${\hat M_4}$ and ${\hat M_5}$ with a relatively high precision.
 
@@
 Invasive sampling potentially affects the level of $m$ because the sampled parents from population 1 have no chance to move to population 2; thus, such parents cannot be sampled.
-In this case, $m$ should be defined by $M/(N_1-n_{P,1})$ rather than $M/N_1$, although this does not affect the estimator ${\hat M}$s, as demonstrated in {\bf Table S1} ({\bf Supporting Information}).
+In this case, $m$ might be defined by $M/(N_1-n_{P,1})$ rather than $M/N_1$, although this does not affect the estimator ${\hat M}$s, as demonstrated in {\bf Table S1} ({\bf Supporting Information}).
 
@@
 First, we formulated the probabilities of kinship pairs randomly selected between two populations ($\pi_{\rm HS,bet}$ and $\pi_{\rm PO,bet}$), which provides migration number or rate estimators.
-While similar derivations may be found in the (nongenetic) MR method, these are limited to cases where sampling is non-invasive and adult individuals are sampled.
+While similar derivations may be found in the (nongenetic) MR method, these are limited to cases where sampling is non-invasive and adult individuals must be sampled.
 The proposed method can avoid these limitations, where such an advantages is characterized by the CKMR method for estimating population sizes.
@@
 The second case involves genetic monitoring conducted for each reproductive period (e.g., annually) because the proposed estimators consider information about contemporary migration that is explicitly specified the timing (e.g., year); thus, the time-series data for migration may reflect environmental changes, and this would provide insights into the underlying ecological processes.
-In addition, HS pairs found within the genetic population provide $N_{\rm b}$ \cite[]{wang2009new,WAPLES_2011}, which is also used to assess genetic health.
+In addition, HS pairs found within the same cohort in the genetic population provide $N_{\rm b}$ \cite[]{wang2009new,WAPLES_2011}, which is also used to assess genetic health.
 The third is the case involves the development of integrated models that combine several data sources into a single analysis \cite[]{MAUNDER201361}.
@@
 Many algorithms can be used to detect kinship pairs from single nucleotide polymorphisms or short tandem repeats \cite[e.g., ][]{Wang_2009Genetics, Huisman_2017}, although a HS pair requires many more DNA markers than a PO pair.
-In addition, iteroparous species may has several kinship types e.g., half-uncle--nephew or half-cousins, which are expected to appear frequently and should be accurately differentiated from HS pairs.
+In addition, iteroparous species may has several kinship types, e.g., half-uncle--nephew or half-cousins, which are expected to appear frequently and should be accurately differentiated from HS pairs.
 It is desirable to estimate in advance how many markers are required for kinship detection in the target populations associated with simulation of pedigree reconstruction (e.g., \cite{Anderson_2020}).
-Note that the proposed estimators are limited to detecting parental movements on a period between breeding seasons in the given populations.
+The proposed estimators are limited to detecting parental movements on a period between breeding seasons in the given populations.
 Thus, the estimation of fine-scale spatiotemporal movements, which is available to integrate data sources \cite[]{Thorson_2021}, is beyond the scope of this paper.
@@
 For example, the parent with $i=1$ reproduces $k_{1,1}$ offspring (in population 1) and then reproduce $k_{1,2}$ offspring (in population 2) after migration.
-Given $k_{i,1}$ and $k_{j,2}$, the conditional probability that two offspring sampled in populations 1 and 2 share an HS relationship is expressed as follows:
+Given $k_{i,1}$ and $k_{j,2}$, the conditional probability that two offspring sampled in populations 1 and 2 share a HS relationship is expressed as follows:
 \begin{align}
@@
 \end{align}
-which provides the same formulation described in Eq.\ref{HS-1}.
+which provides the same formulation described in Equation~\ref{HS-1}.
 Note that, from the third to forth lines, we assume that $\lambda_{l,1}$ and $\lambda_{l,2}$ ($l = 1, \ldots, M$) are independent variables (i.e., $\mathbb{E}[\lambda_{l,1}\lambda_{l,2}] = {\bar \lambda_{1}}{\bar \lambda_{2}}$), which implies variable reproductive potential of an identical parent before and after migration.
@@
 \end{align}
-If ${\bar \lambda_{M,1}} = {\bar \lambda_{1}}$ and ${\bar \lambda_{M,2}} = {\bar \lambda_{2}}$, Eq.~\ref{App3} can be reduced Eq.\ref{App2}.
+If ${\bar \lambda_{M,1}} = {\bar \lambda_{1}}$ and ${\bar \lambda_{M,2}} = {\bar \lambda_{2}}$, Equation~\ref{App3} can be reduced Equation~\ref{App2}.
 This formulation includes reproductive potential terms such that the distinct reproductive potential between migrants and nonmigrants eliminates the usefulness of the proposed HS-based estimators (this is also applied to the proposed PO-based estimators).
